### 2022-11-10 hierarchy.tex
add simulation

\documentclass[11pt,a4paper]{article}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{booktabs}

\setstretch{1.5}

\title{On the hierarchical structure: factor, accuracy and construction}
\author{Bohan Zhang}

\begin{document}

\maketitle

\section{Simulation}

To better control the factors such as trend, seasonality, dependence, we assume the bottom-level series are generated by the following innovative state space model:
\[
    \begin{aligned}
        y_t &= l_{t-1} + b_{t-1} + s_{t-m} + \varepsilon_t \\    
        l_t &= l_{t-1} + b_{t-1} + \alpha\varepsilon_t \\
        b_t &= b_{t-1} + \beta \varepsilon_t \\
        s_t &= s_{t-m} + \gamma\varepsilon_t,
    \end{aligned}
\]
where $l_t, b_t, s_t$ are level, trend and seasonal states. $\varepsilon_t$, called innovation, is the error term. 
$\alpha, \beta, \gamma$ are smoothing parameters which controls the pattern of the simulated time series. 
$m$ is the seasonal period.
This model is also known as ExponenTial Smoothing model with additive trend, additive seasonality and additive error, i.e., ETS(A, A, A)(\Citealp{ForecastingExponentialSmoothing}).

\subsection{Scenario 1: Groups of time series sharing similar pattern}
We start from a simple hierarchy with one total node and four children nodes.
These four time series are expected to belong to two groups having different patterns, but two time series within the same group shares similar patterns. 
We control the ``similar'' pattern through the smoothing parameters, innovation term and seasonal spikes.

In this scenario, $m$ is set to $12$. The initial states $l_0, b_0, s_0, \dots, s_{1-m}$ are simulated from $\mathcal{N}(0, 1)$, $\text{U}(10^{-5}, 2\times 10^{-5})$ and $\mathcal{N}(0, 0.5)$ independently for each time series, except one of the seasonal term, which we called spike period, is simulated from $\mathcal{N}(2, 0.01)$. 
The spike period is at the 2-rd and 8-th period respectively for the two groups.  Simulated $s_0,\dots,s_{-11}$ is then subtracted by their average to ensure the seasonal normalization (\Citealp{ForecastingExponentialSmoothing}). 
The innovation term is simulated from a multivariate gaussian distribution with zero mean and the following covaiance matrix $\Sigma$:
\[
\Sigma = \left[\begin{matrix}
    0.04 & 0.02 & 0 & 0 \\
    0.02 & 0.04 & 0 & 0 \\
    0 & 0 & 0.2 & 0.1  \\
    0 & 0 & 0.1 & 0.1 
\end{matrix}\right].
\]
Smoothing parameters $\alpha, \beta, \gamma$ are uniformly generated from the ranges shown in Table~\ref{tab:sim1_range}.
We simulate $252$ observations for each series and the first $120$ observations are discarded as warm-up.
An example of the simulated series is shown in Figure~\ref{fig:sim1_example}, where Series 1 and Series 2 belong to one group; Series 3 and Series 4 belong to another.

\begin{table}[h]
\centering
\caption{\label{tab:sim1_range}Range of smoothing parameters.}
\begin{tabular}{lcc}
    \toprule
    & Group 1 & Group 2 \\
    \midrule
$\alpha$ & $[0.9, 0.95]$ & $[0.8, 0.85]$ \\
$\beta$ & [$10^{-6}$, $10^{-5}$] & 0 \\
$\gamma$ & [0.005, 0.01] & [0, 0.005] \\\bottomrule
\end{tabular}
\end{table}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/sim1_example.pdf}
\caption{\label{fig:sim1_example} An example of simulated time series in Scenario 1.}
\end{figure}

\newpage

\bibliographystyle{agsm}
\bibliography{references.bib}

\end{document}

### 2022-11-10 simulation/small/simulation.R

@@ -1,0 +1,73 @@
+N <- 100
+TIME_WINDOW <- 132
+WARM_UP <- 120
+TRAIN_WINDOW <- 120
+FREQ <- 12
+GROUPS <- c(2, 2)
+ALPHA <- list(upper = c(0.95, 0.95, 0.85, 0.85), lower = c(0.9, 0.9, 0.8, 0.8))
+BETA <- list(upper = c(1e-4, 1e-4, 0, 0), lower = c(1e-5, 1e-5, 0, 0))
+GAMMA <- list(upper = c(0.01, 0.01, 0.005, 0.005), lower = c(0.005, 0.005, 0, 0))
+SPIKE <- c(2, 2, 8, 8)
+SIGMA <- diag(c(4, 4, 20, 20))
+SIGMA[2, 1] <- 2
+SIGMA[1, 2] <- 2
+SIGMA[3, 4] <- 10
+SIGMA[4, 3] <- 10
+SIGMA <- SIGMA / 100
+
+sim_param <- function(x){
+  sapply(1:length(x$upper), function(y){runif(1, x$lower[y], x$upper[y])})
+}
+
+sim <- function(){
+  Fmat <- rbind(c(1, 1, rep(0, FREQ)), 
+                c(0, 1, rep(0, FREQ)), 
+                c(rep(0, FREQ+1), 1),
+                cbind(0, 0, diag(FREQ - 1), 0))
+  wvec <- c(1, 1, rep(0, FREQ - 1), 1)
+  alpha <- sim_param(ALPHA)
+  beta <- sim_param(BETA)
+  gamma <- sim_param(GAMMA)
+  
+  epsilon <- MASS::mvrnorm(TIME_WINDOW+TIME_WINDOW, mu=rep(0, sum(GROUPS)), Sigma = SIGMA)
+  
+  state <- lapply(1:sum(GROUPS), function(x){
+    l0 <- rnorm(1)
+    b0 <- runif(1, 0.00001, 0.00002)
+    s0 <- append(rnorm(FREQ - 1, sd=0.5), rnorm(1, 2, 0.01), SPIKE[x] - 1)
+    s0 <- s0 - mean(s0)
+    s0 <- s0[FREQ : 1]
+    state <- matrix(c(l0, b0, s0), nrow = 1)
+    gvec <- c(alpha[x], beta[x], gamma[x], rep(0, FREQ - 1))
+    for (t in 1:(TIME_WINDOW + WARM_UP)){
[…]

### 2023-08-22 mortality/analysis.Rmd
update

---
title: "mortality_analysis"
author: "Bohan Zhang"
date: "2023-08-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
# ts and error representator
source("../R/construct_hierarchy.R", chdir = TRUE)

store_all <- NULL
for (batch in 0:11) {
  store_all <- readRDS(paste0("store_", batch, ".rds"))$output %>%
    output_pre() %>% mutate(batch = batch) %>%
    rowwise() %>%
    mutate(bottom_mean = mean(bottom)) %>%
    ungroup() %>%
    rbind(store_all)
}
```

## Evaluation proceduce

1. calculate the ratio between mae/rmse of reconciled forecasts and mae/rmse of base forecasts
2. mae/rmse of the total, mean, max and min mae/rmse of bottom series
3. summarised over specific domains

## mint and wlsv vs ols and wlss

```{r, include=FALSE}
store_base <- store_all %>% filter(rf_method == "base", accuracy_method == "mae") %>%
  rename(total_base = total, bottom_base = bottom) %>%
  select(batch, total_base, bottom_base)

mae_ratio <- store_all %>% filter(accuracy_method == "mae") %>%
  left_join(store_base, by = "batch") %>% 
  rowwise() %>%
  mutate(total = total/total_base, bottom = list(c(bottom/bottom_base))) %>%
  mutate(bottom_mean = mean(bottom), bottom_max = max(bottom),  bottom_min = min(bottom)) %>%
  ungroup()

store_base_rmse <- store_all %>% filter(rf_method == "base", accuracy_method == "rmse") %>%
  rename(total_base = total, bottom_base = bottom) %>%
  select(batch, total_base, bottom_base)

rmse_ratio <- store_all %>% filter(accuracy_method == "rmse") %>%
  left_join(store_base_rmse, by = "batch") %>% 
  rowwise() %>%
  mutate(total = total/total_base, bottom = list(c(bottom/bottom_base))) %>%
  mutate(bottom_mean = mean(bottom), bottom_max = max(bottom),  bottom_min = min(bottom)) %>%
  ungroup()
```

### OLS and structural scaling are more likely to produce more extreme results.

```{r}
mae_ratio %>% group_by(rf_method) %>% summarise(total= mean(total, na.rm=TRUE), bottom_max=mean(bottom_max, na.rm=TRUE), 
                                                bottom_min=mean(bottom_min, na.rm=TRUE), bottom_mean=mean(bottom_mean, na.rm=TRUE))
```
```{r}
rmse_ratio %>% group_by(rf_method) %>% summarise(total= mean(total, na.rm=TRUE), bottom_max=mean(bottom_max, na.rm=TRUE), 
                                                bottom_min=mean(bottom_min, na.rm=TRUE), bottom_mean=mean(bottom_mean, na.rm=TRUE))
```
### On average, mint and wlss don't improve the bottom level, but improve the total level.

### In general, the improvement of some series comes with the cost of some other series. It's very unlikely that reconciliation improves all the series.

```{r}
mae_ratio %>% filter(bottom_max <= 1.01, rf_method != "base") %>% select(representator, rf_method, distance, cluster, total, bottom_mean, bottom_max, bottom_min, batch) %>%
  arrange(total)
```
```{r}
rmse_ratio %>% filter(bottom_max <= 1.05, rf_method != "base") %>% select(representator, rf_method, distance, cluster, total, bottom_mean, bottom_max, bottom_min, batch) %>%
  arrange(total)
```

```{r}
rmse_ratio %>% filter(bottom_max <= 1.5, rf_method %in% c("ols", "wlss")) %>% select(representator, rf_method, distance, cluster, total, bottom_mean, bottom_max, bottom_min, batch) %>%
  arrange(total)
```

### robustness: wlsv > mint > wlss > ols

## K-medoids (only mint)

```{r}
rmse_ratio <- rmse_ratio %>% filter(rf_method == "mint") %>% select(-rf_method, -accuracy_method)
mae_ratio <- mae_ratio %>% filter(rf_method == "mint") %>% select(-rf_method, -accuracy_method)
```

```{r}
tmp <- rmse_ratio %>% filter(startsWith(cluster, "kmedoids")) %>%
  rowwise() %>% 
  mutate(n_middle = NROW(other$S)) %>%
  select(representator, distance, cluster, total, bottom_mean, bottom_max, bottom_min, n_middle, batch) %>%
  ungroup()
```

### distance:

```{r}
tmp %>% group_by(distance) %>% summarise_at(c("total", "bottom_max", "bottom_mean", "bottom_min"), c(mean=function(x){mean(x, na.rm=TRUE)}))
```

### representator: error > ts

```{r}
rmse_ratio %>% group_by(representator) %>% summarise_at(c("total", "bottom_max", "bottom_mean", "bottom_min"), c(mean=function(x){mean(x, na.rm=TRUE)}, min=function(x){min(x, na.rm=TRUE)}, max = function(x){max(x, na.rm=TRUE)}))
```

```{r}
tmp %>% group_by(n_middle) %>% summarise(total=mean(total, na.rm=TRUE), bottom_mean = mean(bottom_mean, na.rm=TRUE), bottom_max = mean(bottom_max, na.rm=TRUE), bottom_min = mean(bottom_mean, na.rm=TRUE))
```

```{r}

rmse_ratio %>% filter(cluster == "natural", batch == 0) %>% group_by(cluster)  %>% summarise(total=mean(total, na.rm=TRUE), bottom_mean = mean(bottom_mean, na.rm=TRUE), bottom_max = mean(bottom_max, na.rm=TRUE), bottom_min = mean(bottom_min, na.rm=TRUE))

```

```{r}
rmse_ratio %>% filter(cluster == "random-single-natural") %>% arrange(total, bottom_mean) %>% filter(batch == 0)
```

### 2023-08-22 R/baseforecast.R

@@ -13,7 +13,6 @@ f.arima <- function(x){
 #' @param method base forecast method
 f.store.read <- function(x, method) {
   x_str <- do.call(paste0, as.list(x))
-  method_str <- as.character(substitute(method))
   if (!(x_str %in% names(BASEFORECAST_STORE[[method]]))) {
     return(NULL)
   }
@@ -22,7 +21,6 @@ f.store.read <- function(x, method) {
 
 f.store.write <- function(x, method, fcasts) {
   x_str <- do.call(paste0, as.list(x))
-  method_str <- as.character(substitute(method))
-  BASEFORECAST_STORE[[method]][[x_str]] <- fcasts
+  BASEFORECAST_STORE[[method]][[x_str]] <<- fcasts
 }
 

### 2023-08-22 R/clustering.R

@@ -16,6 +16,37 @@ cluster.random <- function(distance_mat, n_clusters) {
   S
 }
 
+cluster.nestedkmedoids <- function(distance_mat, n_clusters) {
+  
+  output <- list()
+  output[[1]] <- list(1:NROW(distance_mat))
+  
+  for (i in 1+seq_along(n_clusters)) {
+    output[[i]] <- list()
+    k <- 1
+    for (j in seq_along(output[[i-1]])) {
+      if (length(output[[i-1]][[j]]) <= n_clusters[i-1]) {
+        next
+      }
+      res <- pam(distance_mat[output[[i-1]][[j]], output[[i-1]][[j]]], k = n_clusters[i-1], diss=TRUE,
+          nstart = 10,
+          cluster.only = TRUE)
+      for (ij in 1:n_clusters[i-1]) {
+        output[[i]][[k]] <- output[[i-1]][[j]][which(res == ij)]
+        k <- k+1
+      }
+    }
+  }
+  
+  list(do.call(rbind, lapply(output[2:length(output)], function(x) {
+    do.call(rbind, lapply(x, function(g) {
+      S_row <- vector("numeric", NROW(distance_mat))
+      S_row[g] <- 1
+      S_row
+    }))
+  })))
+}
+
 
 #' kmedoids
 #' 
@@ -36,7 +67,7 @@ cluster.kmedoids <- function(distance_mat, n_clusters) {
     })
   }
   
-  grplst2Slst(output)
+  list(do.call(rbind, grplst2Slst(output)))
 }
 
 #' hierarchical clustering

### 2023-08-22 R/construct_hierarchy.R

@@ -1,6 +1,7 @@
 library(forecast)
 library(cluster)
 library(foreach)
+library(dplyr)
 source("representator.R")
 source("distance.R")
 source("clustering.R")
@@ -33,33 +34,36 @@ hts <- function(S, bts, tts) {
 
 #' function to iterator over S, find the forecast store and return the forecast
 #' 
-fhts_helper <- function(S, all_ts, f) {
+fhts_helper <- function(S, all_ts, f_str) {
+  f <- get(paste0("f.", f_str))
   stored_forecasts <- lapply(iterators::iter(S, by = "row"), function(row){
-    f.store.read(row, method)
+    f.store.read(row, f_str)
   })
-  idx_to_forecast <- which(lapply(stored_forecasts, is.null))
+  idx_to_forecast <- which(sapply(stored_forecasts, is.null))
   
   if (exists("num.cores")) {
-    bf <- foreach::foreach(x = iterators::iter(all_ts[idx_to_forecast], by = "column"), .packages = c("forecast")) %dopar% {
+    bf <- foreach::foreach(x = iterators::iter(all_ts[,idx_to_forecast], by = "column"), .packages = c("forecast")) %dopar% {
       f(x)
     }
   } else {
-    bf <- apply(all_ts[idx_to_forecast], 2, f)
+    bf <- apply(all_ts[,idx_to_forecast, drop=FALSE], 2, f)
   }
-  for (i in 1:length(idx_to_forecast)) {
+  for (i in seq_along(idx_to_forecast)) {
     S_idx <- idx_to_forecast[i]
-    f.store.write(S[S_idx,], f, bf[[i]])
+    f.store.write(S[S_idx,], f_str, bf[[i]])
     stored_forecasts[[S_idx]] <- bf[[i]]
   }
   stored_forecasts
 }
 
 #' function to forecast hts
-forecast.hts <- function(x, f){
+#' @param x hts
+#' @param f_str baseforecast method string
+forecast.hts <- function(x, f_str){
   if (is.null(x$basef)) {
     all_ts <- x$bts %*% t(x$S)
     
-    bf <- fhts_helper(x$S, all_ts, f)
+    bf <- fhts_helper(x$S, all_ts, f_str)
     
     x$basef <- unname(do.call(cbind, lapply(bf, function(x){x$basef})))
     x$resid <- unname(do.call(cbind, lapply(bf, function(x){x$resid})))
[…]

### 2023-08-22 R/expr_utils.R

@@ -6,15 +6,11 @@ create_new_output <- function() {
   output
 }
 
-
-metrics <- c("mae", "rmse")
-store_path <- sprintf("%s/store_%s.rds", path, batch)
-bfmethod_func <- get(paste0("f.", bfmethod))
-
 saveResult <- function() {
   saveRDS(list(bfstore = BASEFORECAST_STORE,
                data = data,
-               output = output),
+               output = output,
+               features = FEATURES),
           store_path)
 }
 
@@ -42,3 +38,11 @@ output_pre <- function(output) {
     tidyr::unnest_longer(accuracy, values_to = "accuracy", indices_to = "rf_method") %>% 
     tidyr::unnest_wider(accuracy)
 }
+
+metrics <- c("mae", "rmse")
+if (exists("path")) {
+  store_path <- sprintf("%s/store_%s.rds", path, batch)
+}
+
+
+

### 2023-08-22 R/representator.R

@@ -13,3 +13,37 @@ representator.error <- function(x){
     x / sd(x)
   })
 }
+
+feature_lst <- c("acf_features", "arch_stat", "autocorr_features", "crossing_points", "dist_features",
+                 "entropy", "heterogeneity", "hurst", "lumpiness", "stability", "pacf_features", "stl_features",
+                 "unitroot_kpss", "unitroot_pp", "nonlinearity", "max_level_shift", "max_var_shift", "max_kl_shift",
+                 "holt_parameters", "hw_parameters", "flat_spots")
+
+features.compute <- function(data) {
+  library(tsfeatures)
+  FEATURES <<- list()
+  ts_features <- tsfeatures(ts(data$bts, frequency = 12), features = feature_lst)
+  FEATURES$ts <<- t(unname(as.matrix(ts_features[,!(colnames(ts_features) %in% c("nperiods", "seasonal_period"))])))
+  
+  error_features <- tsfeatures(ts(data$resid[,2:NCOL(data$resid)], frequency = 12), features = feature_lst)
+  FEATURES$error <<- t(unname(as.matrix(error_features[,!(colnames(error_features) %in% c("nperiods", "seasonal_period"))])))
+}
+
+
+representator.ts.features <- function(x) {
+  if (is.null(FEATURES)) {
+    features.compute(x)
+  }
+  apply(FEATURES$ts, 1, function(g) {
+    g / sd(g)
+  })
+}
+
+representator.error.features <- function(x) {
+  if (is.null(FEATURES)) {
+    features.compute(x)
+  }
+  apply(FEATURES$error, 1, function(g) {
+    g / sd(g)
+  })
+}

### 2023-08-22 data/dataprocessing.R

@@ -92,75 +92,6 @@ colnames(S) <- ICDcodes$ICDcodes[ICDcodes$bottom_idx>0]
 combine_cols <- dt %>% group_by(desc) %>% summarise(n_suppressed = sum(deaths == "Suppressed")) %>%
   filter(n_suppressed > 0) %>% left_join(ICDcodes %>% rename(desc = ICDcodes))
 
-# All causes have missing values are leaf causes, except Other acute lower respiratory infections (J20-J22,U04)
-
-# find_parent <- function(name){
-#   preces <- names(which(S[, name] == 1))
-#   level <- ICDcodes$level[ICDcodes$ICDcodes == name]
-#   for (prece in preces) {
-#     if (ICDcodes$level[ICDcodes$ICDcodes == prece] == level -1) {
-#       return(prece)
-#     }
-#   }
-# }
-# 
-# combine_cols <- combine_cols %>% rowwise() %>% 
-#   mutate(parent = ifelse(level == 1, "total", find_parent(desc)))
-
-
-# combine_causes <- function(x){
-#   
-#   # combine  
-#   Other <- combine_cols$desc[combine_cols$level == 1]
-#   
-#   find_all_children <- function(Other) {
-#     for (i in Other) {
-#       idx <- which(ICDcodes$ICDcodes == i)
-#       if (!ICDcodes$leaf[idx]) {
-#         children <- find_leaves(idx)
-#         Other <- c(Other, children)
-#       }
-#     }
-#     return(Other)
-#   }
-#   
-#   Other <- find_all_children(Other)
-#   
-#   # remove all the children
-#   x <- x %>% filter(!(desc %in% Other))
-#   
-#   for (i in unique(combine_cols$parent)) {
-#     if (i == "total") next
-#     name <- paste0("Combine ", i)
-#     nameToRemove <- find_all_children(combine_cols %>% filter(parent == i) %>% pull(desc))
-#     x <- x %>% filter(!(desc %in% nameToRemove))
-#     parentValue <- dt %>% filter(desc == i) %>% pull(deaths)
-#     otherChild <- setdiff(colnames(S)[which(S[i,] == 1)], nameToRemove)
-#     
-#     
-#   }
-#   
-#   for (i in unique(combine_cols$parent)) {
-#     idx <- which(ICDcodes$ICDcodes == i)
-#     allChildren <- colnames(S)[find_leaves(idx)]
[…]

### 2023-08-22 mortality/mortality.R

@@ -1,7 +1,12 @@
 # configuration
-batch <- 0
+args <- commandArgs(trailingOnly = TRUE)
+batch <- as.integer(args[[1]])
 path <- "mortality"
 bfmethod <- "arima"
+num.cores <- 8
+cl <- parallel::makeCluster(num.cores)
+doParallel::registerDoParallel(cl)
+
 source("R/construct_hierarchy.R", chdir = T)
 
 
@@ -23,8 +28,7 @@ output <- create_new_output()
 
 
 ## bottom and total forecast
-data <- forecast(data, bfmethod_func)
-
+data <- forecast(data, bfmethod)
 accs <- evaluate.hts(data, metrics, type = "base")
 output <- add_result(output, "", "", "", accs)
 data <- reconcile.all(data)
@@ -32,9 +36,5 @@ accs <- evaluate.hts(data, metrics, type = "rf")
 output <- add_result(output, "", "", "", accs)
 
 saveResult()
-
-
-
-
 
 

### 2023-08-22 mortality/mortality_analysis.R

@@ -1,20 +1,59 @@
 library(dplyr)
 # ts and error representator
-output <- readRDS("mortality/ts_error.rds")
-d1 <- output_pre(output) %>% rowwise() %>%
-  mutate(bottom = mean(bottom), num_aggregate_series = as.character(NROW(other$S))) %>%
-  select(-other) %>% 
-  arrange(total, bottom)
+source("R/construct_hierarchy.R", chdir = TRUE)
 
-output <- readRDS("mortality/output_base.rds")
-d2 <- output_pre(output) %>% 
+store_all <- NULL
+for (batch in 0:11) {
+  store_all <- readRDS(paste0("mortality/store_", batch, ".rds"))$output %>%
+    output_pre() %>% mutate(batch = batch) %>%
+    rowwise() %>%
+    mutate(bottom_mean = mean(bottom)) %>%
+    ungroup() %>%
+    rbind(store_all)
+}
+
+
+store_mint_mae <- store_all %>% filter(rf_method == "mint", accuracy_method == "mae") %>%
+  select(-rf_method, -accuracy_method, -bottom, -other)
+
+
+store_mint_rmse <- store_all %>% filter(rf_method == "mint", accuracy_method == "rmse") %>%
+  select(-rf_method, -accuracy_method, -bottom, -other)
+
+
+
+store_base <- store_all %>% filter(rf_method == "base", accuracy_method == "mae") %>%
+  rename(total_base = total, bottom_base = bottom) %>%
+  select(batch, total_base, bottom_base)
+
+mae_ratio <- store_all %>% filter(accuracy_method == "mae") %>%
+  left_join(store_base, by = "batch") %>% 
   rowwise() %>%
-  mutate(bottom = mean(bottom), 
-         num_aggregate_series = ifelse(is.null(other), "0", paste0(other$n_clusters, " * 20 "))) %>%
-  select(-other)
+  mutate(total = total/total_base, bottom = list(c(bottom/bottom_base))) %>%
+  mutate(bottom_mean = mean(bottom), bottom_max = max(bottom),  bottom_min = min(bottom)) %>%
+  ungroup()
+
+store_base_rmse <- store_all %>% filter(rf_method == "base", accuracy_method == "rmse") %>%
+  rename(total_base = total, bottom_base = bottom) %>%
+  select(batch, total_base, bottom_base)
 
 
-d <- d1 %>% add_row(d2) %>%
-  ungroup() %>%
[…]

### 2023-08-22 mortality/mortality_base.R

@@ -1,61 +1,0 @@
-batch <- 0
-path <- "mortality"
-bfmethod <- "arima"
-
-source("R/construct_hierarchy.R", chdir = T)
-
-num.cores <- 6
-cl <- parallel::makeCluster(num.cores)
-doParallel::registerDoParallel(cl)
-
-if (!file.exists(store_path)) {
-  stop("run configuration and base forecast first!")
-}
-
-BASEFORECAST_STORE <- readRDS(store_path)$bfstore
-output <- readRDS(store_path)$output
-data <- readRDS(store_path)$data
-
-# natural hierarchy
-S <- read.csv("data/S.csv", row.names = 1)
-colnames(S) <- stringi::stri_replace_all_fixed(colnames(S), ".", "-")
-natural_data <- data
-natural_data$nl <- list(list(S = unname(as.matrix(S[,colnames(mortality)][which(!(rownames(S) %in% colnames(S))), ])),
-                             basef = NULL,
-                             rf = NULL))
-
-natural_data <- forecast(natural_data, f.arima)
-natural_data <- reconcile.all(natural_data)
-accs <- evaluate.hts(natural_data, metrics, type = "nl")
-output <- add_result(output, "", "", "natural", accs, other = list(
-  S = as(natural_data$nl[[1]]$S, "sparseMatrix")
-))
-
-
-
-# random hierarchy
-for (n_cluster in 3:10) {
-  data <- build_level(data, representator.ts, 
-              distance.euclidean, cluster.random, 
-              n_clusters = rep(n_cluster, 20))
-  data <- forecast(data, f.arima)
-  data <- reconcile.all(data)
-  accs <- evaluate.hts(data, metrics, type = "average")
-  accs_single <- evaluate.hts(data, metrics, type = "nl")
-  for (acc in seq_along(accs_single)) {
-    output <- add_result(output, "", "", "random-single", accs_single[[acc]],
-                         other = list(n_clusters = n_cluster, S = as(accs$nl[[acc]]$S, "sparseMatrix")))
-  }
-  
-  output <- add_result(output, "", "", "random", accs, other = list(n_clusters = n_cluster, average=20,
-                                                                    S = lapply(data$nl, function(x){ as(x$S, "sparseMatrix") })))
-}
-
-saveResult()
-
-
-
-
-
-
-

### 2023-08-22 mortality/naturalvsrandom.R

@@ -1,0 +1,132 @@
+rm(list = ls())
+args <- commandArgs(trailingOnly = TRUE)
+batch <- as.integer(args[[1]])
+path <- "mortality"
+bfmethod <- "arima"
+
+source("R/construct_hierarchy.R", chdir = T)
+
+num.cores <- 8
+cl <- parallel::makeCluster(num.cores)
+doParallel::registerDoParallel(cl)
+
+if (!file.exists(store_path)) {
+  stop("run configuration and base forecast first!")
+}
+
+BASEFORECAST_STORE <- readRDS(store_path)$bfstore
+output <- readRDS(store_path)$output
+data <- readRDS(store_path)$data
+
+# natural hierarchy
+S <- read.csv("data/S.csv", row.names = 1)
+colnames(S) <- stringi::stri_replace_all_fixed(colnames(S), ".", "-")
+natural_data <- data
+
+natural_data$nl <- list(list(S = unname(as.matrix(S[which(!(rownames(S) %in% colnames(S))), ])),
+                             basef = NULL,
+                             rf = NULL))
+
+natural_data <- forecast(natural_data, bfmethod)
+natural_data <- reconcile.all(natural_data)
+accs <- evaluate.hts(natural_data, metrics, type = "nl")
+output <- add_result(output, "", "", "natural", accs, other = list(
+  S = as(natural_data$nl[[1]]$S, "sparseMatrix")
+))
+
+
+
+# random hierarchy
+
+for (n_repeat in c(20, 50, 100)) {
+  for (n_cluster in 3:10) {
+    data <- build_level(data, representator.ts, 
+                        distance.euclidean, cluster.random, 
+                        n_clusters = rep(n_cluster, n_repeat))
+    data <- forecast(data, bfmethod)
+    data <- reconcile.all(data)
+    accs <- evaluate.hts(data, metrics, type = "average")
+    accs_single <- evaluate.hts(data, metrics, type = "nl")
+    
+    accs_single <- lapply(1:n_repeat, function(x) {
+      tmp <- lapply(metrics, function(metric){
+        accs_single[[metric]][[x]]
+      })
+      names(tmp) <- metrics
+      tmp
+    })
+    
+    for (acc in seq_along(accs_single)) {
+      output <- add_result(output, "", "", paste0("random-single-", n_cluster), accs_single[[acc]],
+                           other = list(n_clusters = n_cluster, S = as(data$nl[[acc]]$S, "sparseMatrix")))
[…]

### 2023-08-22 mortality/ts_error.R

@@ -1,6 +1,6 @@
 rm(list = ls())
-
-batch <- 0
+args <- commandArgs(trailingOnly = TRUE)
+batch <- as.integer(args[[1]])
 path <- "mortality"
 bfmethod <- "arima"
 source("R/construct_hierarchy.R", chdir = T)
@@ -16,9 +16,17 @@ if (!file.exists(store_path)) {
 BASEFORECAST_STORE <- readRDS(store_path)$bfstore
 output <- readRDS(store_path)$output
 data <- readRDS(store_path)$data
+FEATURES <- readRDS(store_path)$features
+
 
 
 # K-medoids
+
+dt2 <- build_level(hts = data, representator = get(paste0("representator.", representator)), 
+                   distance = get(paste0("distance.", distance)), 
+                   cluster = cluster.kmedoids,
+                   n_clusters = 6)
+
 for (representator in c("ts", "error")) {
   for (distance in c("euclidean", "dtw", "negcor", "cor")) {
     for (n_clusters in 3:10) {
@@ -26,7 +34,7 @@ for (representator in c("ts", "error")) {
                         distance = get(paste0("distance.", distance)), 
                         cluster = cluster.kmedoids,
                         n_clusters = n_clusters)
-      dt <- forecast(dt, f.arima)
+      dt <- forecast(dt, bfmethod)
       dt <- reconcile.all(dt)
       accs <- evaluate.hts(dt, metrics, type = "nl")
       output <- add_result(output, 
@@ -47,7 +55,7 @@ for (representator in c("ts", "error")) {
                         distance = get(paste0("distance.", distance)), 
                         cluster = cluster.hcluster,
                         method = method)
-      dt <- forecast(dt, f.arima)
+      dt <- forecast(dt, bfmethod)
       dt <- reconcile.all(dt)
       accs <- evaluate.hts(dt, metrics, type = "nl")
       output <- add_result(output, 
@@ -60,12 +68,68 @@ for (representator in c("ts", "error")) {
   }
 }
 
+
+representator <- "ts"
+distance <- "euclidean"
+
+# K-medoids, nested
+for (representator in c("ts", "error")) {
+  for (distance in c("euclidean", "dtw", "negcor", "cor")) {
+    dt <- build_level(hts = data, representator = get(paste0("representator.", representator)), 
+                      distance = get(paste0("distance.", distance)), 
+                      cluster = cluster.nestedkmedoids,
[…]

### 2023-08-22 run.sh

@@ -1,0 +1,7 @@
+
+for i in {3..11}
+do
+    Rscript mortality/mortality.R $i
+    Rscript mortality/ts_error.R $i
+    Rscript mortality/naturalvsrandom.R $i
+done

### 2023-08-27 mortality/analysis.Rmd
update

@@
 date: "2023-08-21"
-output: html_document
+output:
+  html_document:
+    df_print: paged
+  pdf_document: default
 ---
@@
 ```{r, include=FALSE}
-store_base <- store_all %>% filter(rf_method == "base", accuracy_method == "mae") %>%
+store_base <- store_all %>% filter(rf_method == "base") %>%
   rename(total_base = total, bottom_base = bottom) %>%
-  select(batch, total_base, bottom_base)
+  select(batch, total_base, accuracy_method, bottom_base)
 
-mae_ratio <- store_all %>% filter(accuracy_method == "mae") %>%
-  left_join(store_base, by = "batch") %>% 
+ratio <- store_all %>%
+  left_join(store_base, by = c("batch", "accuracy_method")) %>% 
   rowwise() %>%
@@
   mutate(bottom_mean = mean(bottom), bottom_max = max(bottom),  bottom_min = min(bottom)) %>%
-  ungroup()
-
-store_base_rmse <- store_all %>% filter(rf_method == "base", accuracy_method == "rmse") %>%
-  rename(total_base = total, bottom_base = bottom) %>%
-  select(batch, total_base, bottom_base)
-
-rmse_ratio <- store_all %>% filter(accuracy_method == "rmse") %>%
-  left_join(store_base_rmse, by = "batch") %>% 
-  rowwise() %>%
-  mutate(total = total/total_base, bottom = list(c(bottom/bottom_base))) %>%
-  mutate(bottom_mean = mean(bottom), bottom_max = max(bottom),  bottom_min = min(bottom)) %>%
-  ungroup()
+  ungroup() %>%
+  select(-c(total_base, bottom_base, bottom)) %>%
+  filter(rf_method != "base")
 ```
@@
 ### OLS and structural scaling are more likely to produce more extreme results.
+### robustness: wlsv > mint > wlss > ols
 
 ```{r}
-mae_ratio %>% group_by(rf_method) %>% summarise(total= mean(total, na.rm=TRUE), bottom_max=mean(bottom_max, na.rm=TRUE), 
-                                                bottom_min=mean(bottom_min, na.rm=TRUE), bottom_mean=mean(bottom_mean, na.rm=TRUE))
+ratio %>% group_by(rf_method, accuracy_method) %>% 
+  summarise(total= mean(total), bottom_max=mean(bottom_max), 
+            bottom_min=mean(bottom_min), bottom_mean=mean(bottom_mean)) %>%
+  arrange(accuracy_method)
 ```
-```{r}
-rmse_ratio %>% group_by(rf_method) %>% summarise(total= mean(total, na.rm=TRUE), bottom_max=mean(bottom_max, na.rm=TRUE), 
-                                                bottom_min=mean(bottom_min, na.rm=TRUE), bottom_mean=mean(bottom_mean, na.rm=TRUE))
-```
-### On average, mint and wlss don't improve the bottom level, but improve the total level.
 
@@
 ```{r}
-mae_ratio %>% filter(bottom_max <= 1.01, rf_method != "base") %>% select(representator, rf_method, distance, cluster, total, bottom_mean, bottom_max, bottom_min, batch) %>%
-  arrange(total)
-```
-```{r}
-rmse_ratio %>% filter(bottom_max <= 1.05, rf_method != "base") %>% select(representator, rf_method, distance, cluster, total, bottom_mean, bottom_max, bottom_min, batch) %>%
-  arrange(total)
+ratio %>% filter(bottom_max <= 1.01) %>% select(representator, rf_method, distance, cluster, total, bottom_mean, bottom_max, bottom_min, batch) %>%
+  arrange(bottom_max)
 ```
 
-```{r}
-rmse_ratio %>% filter(bottom_max <= 1.5, rf_method %in% c("ols", "wlss")) %>% select(representator, rf_method, distance, cluster, total, bottom_mean, bottom_max, bottom_min, batch) %>%
-  arrange(total)
-```
-
-### robustness: wlsv > mint > wlss > ols
-
-## K-medoids (only mint)
+## K-medoids (only mint, rmse)
 
 ```{r}
-rmse_ratio <- rmse_ratio %>% filter(rf_method == "mint") %>% select(-rf_method, -accuracy_method)
-mae_ratio <- mae_ratio %>% filter(rf_method == "mint") %>% select(-rf_method, -accuracy_method)
-```
-
-```{r}
-tmp <- rmse_ratio %>% filter(startsWith(cluster, "kmedoids")) %>%
+tmp <- ratio %>% filter(startsWith(cluster, "kmedoids"), rf_method == "mint", accuracy_method == "rmse") %>%
   rowwise() %>% 
@@
 
-### distance:
+### distance
 
 ```{r}
-tmp %>% group_by(distance) %>% summarise_at(c("total", "bottom_max", "bottom_mean", "bottom_min"), c(mean=function(x){mean(x, na.rm=TRUE)}))
+tmp %>% group_by(distance) %>% summarise_at(c("total", "bottom_mean", "bottom_max", "bottom_min"), c(mean=function(x){mean(x)}))
 ```
+```{r}
+mcb <- function(x) {
+  tsutils::nemenyi(x, plottype = "vmcb")
+}
 
-### representator: error > ts
-
-```{r}
-rmse_ratio %>% group_by(representator) %>% summarise_at(c("total", "bottom_max", "bottom_mean", "bottom_min"), c(mean=function(x){mean(x, na.rm=TRUE)}, min=function(x){min(x, na.rm=TRUE)}, max = function(x){max(x, na.rm=TRUE)}))
+## total
+tmp %>% select(representator, cluster, batch, distance, total) %>% 
+  tidyr::pivot_wider(names_from = "distance", values_from = "total") %>%
+  select(-representator, -cluster, -batch) %>%
+  mcb()
 ```
@@
 ```{r}
-tmp %>% group_by(n_middle) %>% summarise(total=mean(total, na.rm=TRUE), bottom_mean = mean(bottom_mean, na.rm=TRUE), bottom_max = mean(bottom_max, na.rm=TRUE), bottom_min = mean(bottom_mean, na.rm=TRUE))
+tmp %>% select(representator, cluster, batch, distance, bottom_mean) %>% 
+  tidyr::pivot_wider(names_from = "distance", values_from = "bottom_mean") %>%
+  select(-representator, -cluster, -batch) %>%
+  mcb()
+```
+
+### representator
+
+```{r}
+tmp %>% group_by(representator) %>% summarise_at(c("total", "bottom_mean", "bottom_max", "bottom_min"), c(mean=function(x){mean(x)}))
 ```
@@
 ```{r}
-
-rmse_ratio %>% filter(cluster == "natural", batch == 0) %>% group_by(cluster)  %>% summarise(total=mean(total, na.rm=TRUE), bottom_mean = mean(bottom_mean, na.rm=TRUE), bottom_max = mean(bottom_max, na.rm=TRUE), bottom_min = mean(bottom_min, na.rm=TRUE))
-
+tmp %>% select(representator, cluster, batch, distance, total) %>% 
+  tidyr::pivot_wider(names_from = "representator", values_from = "total") %>%
+  select(-distance, -cluster, -batch) %>%
+  mcb()
 ```
@@
 ```{r}
-rmse_ratio %>% filter(cluster == "random-single-natural") %>% arrange(total, bottom_mean) %>% filter(batch == 0)
+# bottom
+tmp %>% select(representator, cluster, batch, distance, bottom_mean) %>% 
+  tidyr::pivot_wider(names_from = "representator", values_from = "bottom_mean") %>%
+  select(-distance, -cluster, -batch) %>%
+  mcb()
 ```
+### cluster
+
+```{r}
+tmp %>% select(representator, cluster, batch, distance, total) %>% 
+  tidyr::pivot_wider(names_from = "cluster", values_from = "total") %>%
+  select(-representator, -distance, -batch) %>%
+  mcb()
+```
+
+```{r}
+tmp %>% select(representator, cluster, batch, distance, bottom_mean) %>% 
+  tidyr::pivot_wider(names_from = "cluster", values_from = "bottom_mean") %>%
+  select(-representator, -distance, -batch) %>%
+  mcb()
+```
+
+## HCluster
+
+```{r}
+tmp <- ratio %>% filter(startsWith(cluster, "hcluster"), rf_method == "mint", accuracy_method == "rmse") %>%
+  rowwise() %>% 
+  mutate(n_middle = NROW(other$S)) %>%
+  select(representator, distance, cluster, total, bottom_mean, bottom_max, bottom_min, n_middle, batch) %>%
+  ungroup()
+```
+
+### representator
+
+```{r}
+tmp %>% group_by(distance) %>% summarise_at(c("total", "bottom_mean", "bottom_max", "bottom_min"), c(mean=function(x){mean(x)}))
+```
+```{r}
+## total
+tmp %>% select(representator, cluster, batch, distance, total) %>% 
+  tidyr::pivot_wider(names_from = "distance", values_from = "total") %>%
+  select(-representator, -cluster, -batch) %>%
+  mcb()
+```
+
+```{r}
+tmp %>% select(representator, cluster, batch, distance, bottom_mean) %>% 
+  tidyr::pivot_wider(names_from = "distance", values_from = "bottom_mean") %>%
+  select(-representator, -cluster, -batch) %>%
+  mcb()
+```
+
+### representator
+
+```{r}
+tmp %>% group_by(representator) %>% summarise_at(c("total", "bottom_mean", "bottom_max", "bottom_min"), c(mean=function(x){mean(x)}))
+```
+
+```{r}
+tmp %>% select(representator, cluster, batch, distance, total) %>% 
+  tidyr::pivot_wider(names_from = "representator", values_from = "total") %>%
+  select(-distance, -cluster, -batch) %>%
+  mcb()
+```
+
+```{r}
+# bottom
+tmp %>% select(representator, cluster, batch, distance, bottom_mean) %>% 
+  tidyr::pivot_wider(names_from = "representator", values_from = "bottom_mean") %>%
+  select(-distance, -cluster, -batch) %>%
+  mcb()
+```
+### cluster
+
+```{r}
+tmp %>% group_by(cluster) %>% summarise_at(c("total", "bottom_mean", "bottom_max", "bottom_min"), c(mean=function(x){mean(x)}))
+```
+
+```{r}
+tmp %>% select(representator, cluster, batch, distance, total) %>% 
+  tidyr::pivot_wider(names_from = "cluster", values_from = "total") %>%
+  select(-representator, -distance, -batch) %>%
+  mcb()
+```
+
+```{r}
+tmp %>% select(representator, cluster, batch, distance, bottom_mean) %>% 
+  tidyr::pivot_wider(names_from = "cluster", values_from = "bottom_mean") %>%
+  select(-representator, -distance, -batch) %>%
+  mcb()
+```
+
+### natural hierarchy, random
+
+```{r}
+tmp <- ratio %>% filter((cluster == "natural") | (startsWith(cluster, "random-average") | (startsWith(cluster, "random-average-natural")))) %>%
+  filter(rf_method == "mint", accuracy_method == "mae") %>%
+  select(-representator, -distance) %>%
+  select(batch, cluster,total, bottom_mean)
+```
+
+```{r}
+tmp %>% group_by(cluster) %>% summarise_at(c("total", "bottom_mean"), c(mean=function(x){mean(x)})) %>%
+  arrange(bottom_mean_mean)
+```
+
+```{r}
+tmp %>% select(-total) %>%
+  tidyr::pivot_wider(names_from = "cluster", values_from = "bottom_mean") %>%
+  select(-batch) %>%
+  mcb()
+```
+
+```{r}
+tmp %>% select(-bottom_mean) %>%
+  tidyr::pivot_wider(names_from = "cluster", values_from = "total") %>%
+  select(-batch) %>%
+  mcb()
+```
+
+```{r}
+saveRDS(ratio, "ratio.rds")
+```

### 2023-08-27 R/baseforecast.R

@@ -1,6 +1,9 @@
 library(forecast)
 
 f.arima <- function(x){
+  if(length(x) == 1) {
+    stop("length == 1")
+  }
   mdl <- auto.arima(ts(x, frequency = 12))
   list(basef=forecast(mdl, h=12)$mean, resid=residuals(mdl))
 }

### 2023-08-27 R/construct_hierarchy.R

@@ -42,7 +42,7 @@ fhts_helper <- function(S, all_ts, f_str) {
   idx_to_forecast <- which(sapply(stored_forecasts, is.null))
   
   if (exists("num.cores")) {
-    bf <- foreach::foreach(x = iterators::iter(all_ts[,idx_to_forecast], by = "column"), .packages = c("forecast")) %dopar% {
+    bf <- foreach::foreach(x = iterators::iter(all_ts[,idx_to_forecast,drop=FALSE], by = "column"), .packages = c("forecast")) %dopar% {
       f(x)
     }
   } else {
@@ -146,7 +146,7 @@ build_level <- function(
   }
   
   for (i in seq_along(nl)) {
-    nl[[i]]$S <-nl[[i]]$S[which(!(apply(nl[[i]]$S, 1, concat_str) %in% orig_rows)),]
+    nl[[i]]$S <-nl[[i]]$S[which(!(apply(nl[[i]]$S, 1, concat_str) %in% orig_rows)),,drop=FALSE]
   }
   
   nl <- Filter(function(x){NROW(x$S) > 0}, nl)

### 2023-08-27 R/distance.R

@@ -11,3 +11,4 @@ distance.dtw <- function(x, y) { dtw(x, y, distance.only = TRUE)$distance }
 #' Correlation
 distance.negcor <- function(x, y) { cov(x, y) + 1 }
 distance.cor <- function(x, y) { abs(cov(x, y) - 1) }
+distance.uncorrelation <- function(x, y) { abs(cov(x, y)) }

### 2023-08-27 R/representator.R

@@ -1,16 +1,24 @@
 representator.ts <- function(x) {
   apply(x$bts, 2, function(x){
-    x / sd(x)
+    (x - mean(x)) / sd(x)
   })
 }
 
+representator.forecast <- function(x) {
+  apply(unclass(x$basef), 2, function(x){
+    if (sd(x) < 1e-4) {
+      return (vector("numeric", length(x)))
+    }
+    (x - mean(x)) / sd(x)
+  })
+}
 
 representator.error <- function(x){
   stopifnot(!is.null(x$basef))
   n <- NROW(x$S)
   m <- NCOL(x$S)
   apply(x$resid[,(n-m+1):n], 2, function(x) {
-    x / sd(x)
+    (x - mean(x)) / sd(x)
   })
 }
 
@@ -34,16 +42,16 @@ representator.ts.features <- function(x) {
   if (is.null(FEATURES)) {
     features.compute(x)
   }
-  apply(FEATURES$ts, 1, function(g) {
-    g / sd(g)
-  })
+  t(apply(FEATURES$ts, 1, function(g) {
+    (g - mean(g)) / sd(g)
+  }))
 }
 
 representator.error.features <- function(x) {
   if (is.null(FEATURES)) {
     features.compute(x)
   }
-  apply(FEATURES$error, 1, function(g) {
-    g / sd(g)
-  })
+  t(apply(FEATURES$error, 1, function(g) {
+    (g - mean(g)) / sd(g)
+  }))
 }

### 2023-08-27 mortality/mortality.R

@@ -4,6 +4,8 @@ batch <- as.integer(args[[1]])
 path <- "mortality"
 bfmethod <- "arima"
 num.cores <- 8
+set.seed(42)
+
 cl <- parallel::makeCluster(num.cores)
 doParallel::registerDoParallel(cl)
 
@@ -34,7 +36,7 @@ output <- add_result(output, "", "", "", accs)
 data <- reconcile.all(data)
 accs <- evaluate.hts(data, metrics, type = "rf")
 output <- add_result(output, "", "", "", accs)
-
+FEATURES <- NULL
 saveResult()
 
 

### 2023-08-27 mortality/mortality_analysis.R

@@ -1,59 +1,0 @@
-library(dplyr)
-# ts and error representator
-source("R/construct_hierarchy.R", chdir = TRUE)
-
-store_all <- NULL
-for (batch in 0:11) {
-  store_all <- readRDS(paste0("mortality/store_", batch, ".rds"))$output %>%
-    output_pre() %>% mutate(batch = batch) %>%
-    rowwise() %>%
-    mutate(bottom_mean = mean(bottom)) %>%
-    ungroup() %>%
-    rbind(store_all)
-}
-
-
-store_mint_mae <- store_all %>% filter(rf_method == "mint", accuracy_method == "mae") %>%
-  select(-rf_method, -accuracy_method, -bottom, -other)
-
-
-store_mint_rmse <- store_all %>% filter(rf_method == "mint", accuracy_method == "rmse") %>%
-  select(-rf_method, -accuracy_method, -bottom, -other)
-
-
-
-store_base <- store_all %>% filter(rf_method == "base", accuracy_method == "mae") %>%
-  rename(total_base = total, bottom_base = bottom) %>%
-  select(batch, total_base, bottom_base)
-
-mae_ratio <- store_all %>% filter(accuracy_method == "mae") %>%
-  left_join(store_base, by = "batch") %>% 
-  rowwise() %>%
-  mutate(total = total/total_base, bottom = list(c(bottom/bottom_base))) %>%
-  mutate(bottom_mean = mean(bottom), bottom_max = max(bottom),  bottom_min = min(bottom)) %>%
-  ungroup()
-
-store_base_rmse <- store_all %>% filter(rf_method == "base", accuracy_method == "rmse") %>%
-  rename(total_base = total, bottom_base = bottom) %>%
-  select(batch, total_base, bottom_base)
-
-
-rmse_ratio <- store_all %>% filter(accuracy_method == "rmse") %>%
-  left_join(store_base_rmse, by = "batch") %>% 
-  rowwise() %>%
-  mutate(total = total/total_base, bottom = list(c(bottom/bottom_base))) %>%
-  mutate(bottom_mean = mean(bottom), bottom_max = max(bottom),  bottom_min = min(bottom)) %>%
-  ungroup()
-
-
-
-# Conclusion 1
-mae_ratio %>% group_by(rf_method) %>% summarise(total= mean(total, na.rm=TRUE), bottom_max=mean(bottom_max, na.rm=TRUE), 
[…]

### 2023-08-27 mortality/naturalvsrandom.R

@@ -3,6 +3,7 @@ args <- commandArgs(trailingOnly = TRUE)
 batch <- as.integer(args[[1]])
 path <- "mortality"
 bfmethod <- "arima"
+set.seed(42)
 
 source("R/construct_hierarchy.R", chdir = T)
 
@@ -17,6 +18,7 @@ if (!file.exists(store_path)) {
 BASEFORECAST_STORE <- readRDS(store_path)$bfstore
 output <- readRDS(store_path)$output
 data <- readRDS(store_path)$data
+FEATURES <- readRDS(store_path)$features
 
 # natural hierarchy
 S <- read.csv("data/S.csv", row.names = 1)

### 2023-08-27 mortality/ts_error.R

@@ -4,7 +4,8 @@ batch <- as.integer(args[[1]])
 path <- "mortality"
 bfmethod <- "arima"
 source("R/construct_hierarchy.R", chdir = T)
-
+set.seed(42)
+# rm(.Random.seed, envir=globalenv())
 num.cores <- 8
 cl <- parallel::makeCluster(num.cores)
 doParallel::registerDoParallel(cl)
@@ -18,17 +19,19 @@ output <- readRDS(store_path)$output
 data <- readRDS(store_path)$data
 FEATURES <- readRDS(store_path)$features
 
+cluster_to_remove <- c("kmedoids", "kmedoids-d-nested")
+idx_to_stay <- which(!(output$cluster %in% cluster_to_remove))
+output$representator <- output$representator[idx_to_stay]
+output$distance <- output$distance[idx_to_stay]
+output$cluster <- output$cluster[idx_to_stay]
+output$accuracy <- output$accuracy[idx_to_stay]
+output$other <- output$other[idx_to_stay]
 
 
 # K-medoids
-
-dt2 <- build_level(hts = data, representator = get(paste0("representator.", representator)), 
-                   distance = get(paste0("distance.", distance)), 
-                   cluster = cluster.kmedoids,
-                   n_clusters = 6)
-
-for (representator in c("ts", "error")) {
-  for (distance in c("euclidean", "dtw", "negcor", "cor")) {
+for (representator in c("ts", "error", "ts.features", "error.features", "forecast")) {
+  for (distance in c("euclidean", "dtw", "negcor", "cor", "uncorrelation")) {
+    print(sprintf("%s-%s", representator, distance))
     for (n_clusters in 3:10) {
       dt <- build_level(hts = data, representator = get(paste0("representator.", representator)), 
                         distance = get(paste0("distance.", distance)), 
@@ -40,41 +43,44 @@ for (representator in c("ts", "error")) {
       output <- add_result(output, 
                            representotar = representator, 
                            distance = distance, 
-                           cluster = "kmedoids", 
+                           cluster = paste0("kmedoids-", n_clusters), 
                            accs = accs,
                            other = list(S = as(dt$nl[[1]]$S, "sparseMatrix")))
     }
   }
 }
 
-
-for (representator in c("ts", "error")) {
-  for (distance in c("euclidean", "dtw", "negcor", "cor")) {
-    for (method in c("ward", "average", "single", "complete", "weighted")) {
[…]

### 2023-08-27 run.sh

@@ -1,7 +1,8 @@
 
-for i in {3..11}
+for i in {0..10}
 do
-    Rscript mortality/mortality.R $i
+    echo $i
+    #Rscript mortality/mortality.R $i
     Rscript mortality/ts_error.R $i
-    Rscript mortality/naturalvsrandom.R $i
+    #Rscript mortality/naturalvsrandom.R $i
 done

### 2023-09-26 analysis.Rmd
add tourism

---
title: "Constructing hierarchies"
author: "Bohan Zhang"
date: "2023-09-26"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Illustrative example

Consider a hierarchy with $4$ time series A,C,D,E, $A=C+D+E$. We consider
two kind of aggregation $B_1 = D+E$, $B_2 = C+D$.

```{r, include=FALSE, echo=FALSE}
S <- rbind(c(1,1,1), c(0, 1, 1), diag(3))

weights <- function(W) {
  W_inv <- solve(W)
  S %*% solve(t(S) %*% W_inv %*% S, t(S) %*% W_inv)
}

weights_plot <- function(offdiag, title = "Setting 1") {

  construct_W <- function(offdiag, x) {
    m <- matrix(0, 5, 5)
    m[lower.tri(m)] <- offdiag
    m[upper.tri(m)] <- t(m)[upper.tri(t(m))]
    diag(m) <- c(1, 1, 1, 1, 1)
    m[4, 5] <- x
    m[5, 4] <- x
    diag(sqrt(c(3, 2.1, 0.9, 1.05, 1.04))) %*% m %*% diag(sqrt(c(3, 2.1, 0.9, 1.05, 1.04)))
  }
  print(construct_W(offdiag, 0.5))

  weights_all <- vector("list", 5)

  for (i in seq(-0.99, 0.99, by = 0.01)) {
    W <- construct_W(offdiag, i)
    weight_i <- weights(W)
    for (j in 1:5){
      weights_all[[j]] <- rbind(weights_all[[j]], c(i, weight_i[,j]))
    }
  }
  library(dplyr)
  for (j in 1:5) {
    colnames(weights_all[[j]]) <- c("cor", "A", "B", "C", "D", "E")
    weights_all[[j]] <- as_tibble(weights_all[[j]]) %>%
      mutate(weights_col = c("A", "B", "C", "D", "E")[j])
  }

  weights_all <- do.call(rbind, weights_all)

  weights_all <- weights_all %>% tidyr::pivot_longer(names_to = "weights_row", cols = c("A", "B", "C", "D", "E"))

  library(ggplot2)

  ggplot(weights_all)  +
    geom_line(mapping = aes(x = cor, y = value, color = weights_row, group=weights_row)) +
    facet_wrap(~ weights_col) +
    ggtitle(title)
}
```

## Trend of weights

Consider the hierarchy $A, B_1, C, D, E$, $B_1 = D+E$ and variance $[3, 2.1, 0.9, 1.05, 1.04]'$

### Trend of weights: Scenario 1

All the correlation coefficients are $0$.

$$
\begin{bmatrix}
1 & 0 & 0 & 0 & 0 \\
0 &1 & 0 & 0 & 0 \\
0 & 0 & 1 & 0 & 0 \\
0 & 0 & 0 & 1 & x \\
0 & 0 & 0 & x & 1
\end{bmatrix}
$$

The trends of weights:

```{r, echo=FALSE, message=FALSE, results='hide'}
weights_plot(0)
```

### Trend of weights: Scenario 2

All the correlation coefficients are uniformly drawn from $[0, 0.5]$.

```{r, echo=FALSE, message=FALSE}
offdiag <- runif(10, 0, 0.5)
weights_plot(offdiag, title = "Setting 2")
```

### Trend of weights: Scenario 3

All the correlation coefficients are uniformly drawn from $[-0.5, 0]$.

```{r, echo=FALSE, message=FALSE}
offdiag <- runif(10, -0.5, 0)
weights_plot(offdiag, title = "Setting 3")
```

### Trend of weights: Scenario 4

All the correlation coefficients are uniformly drawn from $[-0.5, 0.5]$.

```{r, echo=FALSE, message=FALSE}
offdiag <- runif(10, -0.5, 0.5)
weights_plot(offdiag, title = "Setting 4")
```

### Conclusion

Overall, the weights for Series $B_1, D, E, A$ from Series $B_1$ ($G_{B_1,B_1}, G_{D,B_1}, G_{E,B_1}, G_{A, B_1}$) increase as the correlation between $D$ and $E$ increase. (See the panel B in each figure)

## forecast accuracy of two different grouping method: B1 and B2

```{r, echo=FALSE, message=FALSE}
source("R/reconciliation.R")
library(forecast)
step2 <- function(Wb) {

  errors <- MASS::mvrnorm(1000, rep(0, 3), Wb)

  AR <- diag(c(0, 0.3, 0.4))
  series <- matrix(0, 1001, 3)
  for (i in 2:1001) {
    series[i,] <- AR %*% series[i-1, ] + errors[i-1,]
  }
  series <- series[102:1001,]
  series[,1] <- seq(from=1, to=5, length = 900) + series[,1]
  series[,2] <- seq(from=1, to=5, length = 900) + series[,2]

  plot_series <- ts(series)
  colnames(series) <- c("C", "D", "E")
  plot(plot_series)

  S2 <- S
  S2[2,] <- c(1, 1, 0)

  series2 <- series %*% t(S2)
  series <- series %*% t(S)
  # Cross Validation
  init_window <- 800
  step <- 10

  mat2list <- function(x){
    r <- lapply(seq_len(ncol(x)), function(i) unname(x[,i]))
    names(r) <- colnames(x)
    r
  } 
  accs <- vector("list", 3)
  names(accs) <- c("base", "mint", "mint2")
  for (i in 1:10) {
    train <- series[1:(790+10*i),]
    test <- series[(791+10*i):(800+10*i),]

    fcasts <- lapply(iterators::iter(train, by="col"), function(s){
      mdl <- forecast(auto.arima(s, seasonal = FALSE), h=10)
      list(resid = as.numeric(residuals(mdl)), fcasts = as.numeric(mdl$mean))
    })

    resids <- do.call(cbind, lapply(fcasts, function(x){
      x$resid
    }))
    fcasts <- do.call(cbind, lapply(fcasts, function(x){
      x$fcasts
    }))

    fcasts_B2 <- forecast(auto.arima(series2[1:(790+10*i), 2], seasonal = FALSE), h=10)
    resids2 <- resids
    resids2[,2] <- as.numeric(residuals(fcasts_B2))
    fcasts2 <- fcasts
    fcasts2[,2] <- as.numeric(fcasts_B2$mean)

    reconf <- reconcile.mint(S, fcasts, resids)
    reconf2 <- reconcile.mint(S2, fcasts2, resids2)

    rmse <- function(x, y) { 
      r <- sapply(c(1, 3, 4, 5), function(i){
        sqrt(mean((x[,i]-y[,i])^2))
      })
      names(r) <- c("A", "C", "D", "E")
      r
    }
    accs$base <- rbind(accs$base, rmse(fcasts, test))
    accs$mint <- rbind(accs$mint, rmse(reconf, test))
    accs$mint2 <- rbind(accs$mint2, rmse(reconf2, test))
  }
  accs$base <- mat2list(accs$base)
  accs$mint <- mat2list(accs$mint)
  accs$mint2 <- mat2list(accs$mint2)
  as_tibble(accs) %>% mutate(names = c("A", "C", "D", "E")) %>% tidyr::unnest(cols = c("base", "mint", "mint2"))
}
```

Simulation procedure:

1. produce time series
2. test reconciliation accuracy for $B_1$ hierarchy and $B_2$ hierarchy through CV.

$$
\begin{bmatrix}
y_{C,t} \\ y_{D,t} \\ y_{E,t}
\end{bmatrix} = \begin{bmatrix}0.0055 \\ 0.0055 \\ 0\end{bmatrix}t + \begin{bmatrix}
0 & 0 & 0 \\
0 & 0.3 & 0 \\
0 & 0 & 0.4
\end{bmatrix} \begin{bmatrix}
y_{C,t-1} \\ y_{D,t-1} \\ y_{E,t-1}
\end{bmatrix} + \begin{bmatrix}
e_{C,t} \\ e_{D,t} \\ e_{E,t}
\end{bmatrix}
$$

$\boldsymbol{e}_t$ has the following covariance matrix

$$
\begin{bmatrix}
1 & 0 & 0 \\
0 & 1 & x \\
0 & x & 1 \\
\end{bmatrix}
$$

### x=0.9

```{r, message=FALSE, echo=FALSE}
W <- diag(3)
W[2,3] <- 0.9
W[3,2] <- 0.9
r1 <- step2(W)
r1 %>% group_by(names) %>% summarise_all(mean)
```

### x=-0.9

```{r, message=FALSE, echo=FALSE}
W <- diag(3)
W[2,3] <- -0.9
W[3,2] <- -0.9
r1 <- step2(W)
r1 %>% group_by(names) %>% summarise_all(mean)
```

## Mortality

```{r, echo=FALSE, message=FALSE}

library(dplyr)
library(tidyr)

# ts and error representator
source("R/construct_hierarchy.R", chdir = TRUE)

rf_method <- "mint"
accuracy_method <- "rmse"

# read all the results
store_all <- NULL
for (batch in 0:11) {
  store_all <- readRDS(paste0("mortality/store_", batch, ".rds"))$output %>%
    output_pre() %>% mutate(batch = batch) %>%
    filter(rf_method == .env$rf_method, accuracy_method == .env$accuracy_method) %>%
    dplyr::select(-rf_method, -accuracy_method) %>%
    rbind(store_all)
}

store_all <- store_all %>% rowwise() %>%
  mutate(values = list(c(total, bottom))) %>% ungroup() %>%
  dplyr::select(-total, -bottom)

## remove single random
store_all <- store_all %>% filter(!startsWith(cluster, "random-single"))

# store_all %>% group_by(representator, distance, cluster) %>% tally() %>%
#   pull(n) %>% table()

## combine the results of 12 batches for one clustering method

store_all <- store_all %>% select(-other) %>% nest(values = c(batch, values)) %>%
  mutate_at("values", purrr::map, function(x){
    x <- arrange(x, batch)
    do.call(c, x$values)
  })

## convert the tibble to a data.frame used for comparing ranks
store_mat <- do.call(cbind, store_all$values)
store_rank <- apply(store_mat, 1, rank) %>% t() %>% colMeans()
store_all$rank <- store_rank

## MCB test
mcb <- function(x) {
  tsutils::nemenyi(x, plottype = "vmcb")
}

method_desc <- function(row){
  print(sprintf("representator: %s, distance: %s, cluster: %s", 
                store_all$representator[row],
                store_all$distance[row],
                store_all$cluster[row]))
}
```

### Overall rank

```{r}
mcb(store_mat)
```

```{r}
store_all %>% arrange(rank)
```

### representator rank

```{r}
# representator rank
representator_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(representator, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans()
    x %>% select(-values) %>%
      pivot_wider(names_from = "representator", values_from = "rank")
  }) %>%
  unnest("values")

representators <- c("error", "ts", "error.features", "ts.features", "forecast")

## in most cases, error is the best
representator_summarise %>% rowwise() %>%
  mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
  pull(min) %>%
  table()

## only in one case, error is the worst
representator_summarise %>% rowwise() %>%
  mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
  pull(max) %>%
  table()
mcb(representator_summarise %>% select(representators))

# no hierarchy is not good: 391 / 428
rank(store_all$rank)[1]

# natural hierarchy is not bad: 72/428
rank(store_all$rank)[2]

# random versus random natural versus natural

tmp <- store_all %>% filter(distance == "")
tmp$rank <- do.call(cbind, tmp$values) %>% apply(1, rank) %>%
  t() %>% colMeans()

## 1. all the averaged random hierarchies beat no hierarchy
## 2. deep and wide hierarchy wins
## 3. average of more hierarchies does not obtain better results. 
##   Some really bad hierarchies destroy the results. 
##.  Deeper hierarchies have the ability to mitigate the affect of bad series

```

### cluster rank
```{r}
# cluster rank
cluster_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(cluster, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans() %>% rank()
    x %>% select(-values) %>%
      pivot_wider(names_from = "cluster", values_from = "rank")
  }) %>%
  unnest("values")

cluster_summarise %>% select(-c(representator, distance)) %>%
  mcb()

## 1. kmedoids unnested is really bad
## 2. hcluster with single linkage is bad
## 3. nested kmedoids performs really well, which forms a natural-like unbalanced hierarchy.
```

### distance rank

```{r}
distance_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(distance, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans() %>% rank()
    x %>% select(-values) %>%
      pivot_wider(names_from = "distance", values_from = "rank")
  }) %>%
  unnest("values")
distance_summarise %>% select(-c(representator, cluster)) %>%
  mcb()

distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
distance_summarise %>% rowwise() %>%
  mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
  pull(max) %>%
  table()
distance_summarise %>% rowwise() %>%
  mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
  pull(min) %>%
  table()
```

## Tourism

```{r, include=FALSE, echo=FALSE}
store_all <- NULL
for (batch in 0:8) {
  store_all <- readRDS(paste0("tourism/store_", batch, ".rds"))$output %>%
    output_pre() %>% mutate(batch = batch) %>%
    filter(rf_method == .env$rf_method, accuracy_method == .env$accuracy_method) %>%
    dplyr::select(-rf_method, -accuracy_method) %>%
    rbind(store_all)
}

store_all <- store_all %>% rowwise() %>%
  mutate(values = list(c(total, bottom))) %>% ungroup() %>%
  dplyr::select(-total, -bottom)

## remove single random
store_all <- store_all %>% filter(!startsWith(cluster, "random-single"))

# store_all %>% group_by(representator, distance, cluster) %>% tally() %>%
#   pull(n) %>% table()

## combine the results of 12 batches for one clustering method

store_all <- store_all %>% dplyr::select(-other) %>% nest(values = c(batch, values)) %>%
  mutate_at("values", purrr::map, function(x){
    x <- arrange(x, batch)
    do.call(c, x$values)
  })

## convert the tibble to a data.frame used for comparing ranks
store_mat <- do.call(cbind, store_all$values)
store_rank <- apply(store_mat, 1, rank) %>% t() %>% colMeans()
store_all$rank <- store_rank
```

```{r}
mcb(store_mat)
```
```{r}
store_all %>% arrange(rank)
```

### representator rank

```{r, message=FALSE}
# representator rank
representator_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(representator, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans()
    x %>% dplyr::select(-values) %>%
      pivot_wider(names_from = "representator", values_from = "rank")
  }) %>%
  unnest("values")

representators <- c("error", "ts", "error.features", "ts.features", "forecast")

## in most cases, error is the best
representator_summarise %>% rowwise() %>%
  mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
  pull(min) %>%
  table()

## only in one case, error is the worst
representator_summarise %>% rowwise() %>%
  mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
  pull(max) %>%
  table()
mcb(representator_summarise %>% dplyr::select(all_of(representators)))

# no hierarchy
rank(store_all$rank)[which(store_all$cluster == "")]

# natural hierarchy
rank(store_all$rank)[which(store_all$cluster == "natural")]

# random versus random natural versus natural

tmp <- store_all %>% filter(distance == "")
tmp$rank <- do.call(cbind, tmp$values) %>% apply(1, rank) %>%
  t() %>% colMeans()

## 1. all the averaged random hierarchies beat no hierarchy
## 2. deep and wide hierarchy wins
## 3. average of more hierarchies does not obtain better results. 
##   Some really bad hierarchies destroy the results. 
##.  Deeper hierarchies have the ability to mitigate the affect of bad series

```

### cluster rank
```{r}
# cluster rank
cluster_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(cluster, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans() %>% rank()
    x %>% dplyr::select(-values) %>%
      pivot_wider(names_from = "cluster", values_from = "rank")
  }) %>%
  unnest("values")

cluster_summarise %>% dplyr::select(-c(representator, distance)) %>%
  mcb()

## 1. kmedoids unnested is really bad
## 2. hcluster with single linkage is bad
## 3. nested kmedoids performs really well, which forms a natural-like unbalanced hierarchy.
```

### distance rank

```{r}
distance_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(distance, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans() %>% rank()
    x %>% select(-values) %>%
      pivot_wider(names_from = "distance", values_from = "rank")
  }) %>%
  unnest("values")
distance_summarise %>% select(-c(representator, cluster)) %>%
  mcb()

distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
distance_summarise %>% rowwise() %>%
  mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
  pull(max) %>%
  table()
distance_summarise %>% rowwise() %>%
  mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
  pull(min) %>%
  table()
```

### 2023-09-26 R/construct_hierarchy.R
minor fix

@@ -69,6 +69,12 @@ forecast.hts <- function(x, f_str){
     x$resid <- unname(do.call(cbind, lapply(bf, function(x){x$resid})))
   }
   
+  if (!is.null(x$nl)) {
+    new_S <- do.call(rbind, lapply(x$nl, function(g){ g$S }))
+    all_nts <- x$bts %*% t(new_S)
+    bf <- fhts_helper(new_S, all_nts, f_str)
+  }
+  
   for (level in seq_along(x$nl)) {
     if (is.null(x$nl[[level]]$basef)) {
       all_nts <-x$bts %*% t(x$nl[[level]]$S)

### 2023-09-26 illurstrative.R

@@ -2,15 +2,6 @@
 
 S <- rbind(c(1,1,1), c(0, 1, 1), diag(3))
 
-cov_mat <- function(x) {
-  output <- matrix(0, 5, 5)
-  diag(output) <- c(1, 1, 1, 1, 1)
-  output[4, 5] <- x
-  output[5, 4] <- x
-  
-  
-}
-
 
 weights <- function(W) {
   W_inv <- solve(W)

### 2023-09-26 tourism/naturalvsrandom.R

@@ -4,7 +4,6 @@ batch <- as.integer(args[[1]])
 path <- "tourism"
 bfmethod <- "arima"
 set.seed(43)
-
 source("R/construct_hierarchy.R", chdir = T)
 
 num.cores <- 8
@@ -25,9 +24,9 @@ S <- read.csv("tourism/S.csv", row.names = 1)
 S <- unname(as.matrix(S))
 natural_data <- data
 
-natural_data$nl <- list(list(S = S[2:251,]),
+natural_data$nl <- list(list(S = S[2:251,],
                              basef = NULL,
-                             rf = NULL)
+                             rf = NULL))
 
 natural_data <- forecast(natural_data, bfmethod)
 natural_data <- reconcile.all(natural_data)
@@ -36,11 +35,11 @@ output <- add_result(output, "", "", "natural", accs, other = list(
   S = as(natural_data$nl[[1]]$S, "sparseMatrix")
 ))
 
-
+saveResult()
 
 # random hierarchy
 
-for (n_repeat in c(20, 50, 100)) {
+for (n_repeat in c(20, 50)) {
   for (n_cluster in 5:15) {
     data <- build_level(data, representator.ts, 
                         distance.euclidean, cluster.random, 
@@ -67,6 +66,8 @@ for (n_repeat in c(20, 50, 100)) {
                                                                                                                  S = lapply(data$nl, function(x){ as(x$S, "sparseMatrix") })))
   }
 }
+
+saveResult()
 
 
 # random natural
@@ -98,33 +99,40 @@ for (acc in seq_along(accs_single)) {
 output <- add_result(output, "", "", paste0("random-average-natural-", 20), accs, other = list(average=20, S = lapply(data$nl, function(x){ as(x$S, "sparseMatrix") })))
 
 
-data$nl <- lapply(1:100, function(i) {
-  list(S = new_S[,sample(NCOL(new_S), NCOL(new_S))],
-       basef = NULL,
-       rf = NULL)
-})
-
-data <- forecast(data, "arima")
-data <- reconcile.all(data)
-accs <- evaluate.hts(data, metrics, type="average")
-accs_single <- evaluate.hts(data, metrics, type="nl")
-
-accs_single <- lapply(1:100, function(x) {
-  tmp <- lapply(metrics, function(metric){
-    accs_single[[metric]][[x]]
-  })
-  names(tmp) <- metrics
-  tmp
-})
-
[…]

### 2023-10-02 analysis.Rmd
update

@@
 ```{r, include=FALSE, echo=FALSE}
+
+set.seed(1065)
 S <- rbind(c(1,1,1), c(0, 1, 1), diag(3))
@@
 ```{r, echo=FALSE, message=FALSE}
-source("R/reconciliation.R")
-library(forecast)
-step2 <- function(Wb) {
-
-  errors <- MASS::mvrnorm(1000, rep(0, 3), Wb)
-
-  AR <- diag(c(0, 0.3, 0.4))
-  series <- matrix(0, 1001, 3)
-  for (i in 2:1001) {
-    series[i,] <- AR %*% series[i-1, ] + errors[i-1,]
-  }
-  series <- series[102:1001,]
-  series[,1] <- seq(from=1, to=5, length = 900) + series[,1]
-  series[,2] <- seq(from=1, to=5, length = 900) + series[,2]
-
-  plot_series <- ts(series)
-  colnames(series) <- c("C", "D", "E")
-  plot(plot_series)
-
-  S2 <- S
-  S2[2,] <- c(1, 1, 0)
-
-  series2 <- series %*% t(S2)
-  series <- series %*% t(S)
-  # Cross Validation
-  init_window <- 800
-  step <- 10
-
-  mat2list <- function(x){
-    r <- lapply(seq_len(ncol(x)), function(i) unname(x[,i]))
-    names(r) <- colnames(x)
-    r
-  } 
-  accs <- vector("list", 3)
-  names(accs) <- c("base", "mint", "mint2")
-  for (i in 1:10) {
-    train <- series[1:(790+10*i),]
-    test <- series[(791+10*i):(800+10*i),]
-
-    fcasts <- lapply(iterators::iter(train, by="col"), function(s){
-      mdl <- forecast(auto.arima(s, seasonal = FALSE), h=10)
-      list(resid = as.numeric(residuals(mdl)), fcasts = as.numeric(mdl$mean))
-    })
-
-    resids <- do.call(cbind, lapply(fcasts, function(x){
-      x$resid
-    }))
-    fcasts <- do.call(cbind, lapply(fcasts, function(x){
-      x$fcasts
-    }))
-
-    fcasts_B2 <- forecast(auto.arima(series2[1:(790+10*i), 2], seasonal = FALSE), h=10)
-    resids2 <- resids
-    resids2[,2] <- as.numeric(residuals(fcasts_B2))
-    fcasts2 <- fcasts
-    fcasts2[,2] <- as.numeric(fcasts_B2$mean)
-
-    reconf <- reconcile.mint(S, fcasts, resids)
-    reconf2 <- reconcile.mint(S2, fcasts2, resids2)
-
-    rmse <- function(x, y) { 
-      r <- sapply(c(1, 3, 4, 5), function(i){
-        sqrt(mean((x[,i]-y[,i])^2))
-      })
-      names(r) <- c("A", "C", "D", "E")
-      r
-    }
-    accs$base <- rbind(accs$base, rmse(fcasts, test))
-    accs$mint <- rbind(accs$mint, rmse(reconf, test))
-    accs$mint2 <- rbind(accs$mint2, rmse(reconf2, test))
-  }
-  accs$base <- mat2list(accs$base)
-  accs$mint <- mat2list(accs$mint)
-  accs$mint2 <- mat2list(accs$mint2)
-  as_tibble(accs) %>% mutate(names = c("A", "C", "D", "E")) %>% tidyr::unnest(cols = c("base", "mint", "mint2"))
-}
+source("illurstrative.R")
 ```
@@
 \begin{bmatrix}
+e_{C,t} \\ e_{D,t} \\ e_{E,t}
+\end{bmatrix} = \begin{bmatrix}
+0 & 0 & 0 \\
+0 & 0.4 & x \\
+0 & x & 0.4
+\end{bmatrix} \begin{bmatrix}
+e_{C,t-1} \\ e_{D,t-1} \\ e_{E,t-1}
+\end{bmatrix} + \begin{bmatrix}
+\varepsilon_{C,t} \\ \varepsilon_{D,t} \\ \varepsilon_{E,t}
+\end{bmatrix}
+$$
+$$
+\begin{bmatrix}
 y_{C,t} \\ y_{D,t} \\ y_{E,t}
-\end{bmatrix} = \begin{bmatrix}0.0055 \\ 0.0055 \\ 0\end{bmatrix}t + \begin{bmatrix}
-0 & 0 & 0 \\
-0 & 0.3 & 0 \\
-0 & 0 & 0.4
-\end{bmatrix} \begin{bmatrix}
-y_{C,t-1} \\ y_{D,t-1} \\ y_{E,t-1}
-\end{bmatrix} + \begin{bmatrix}
+\end{bmatrix} = \begin{bmatrix}
+0 \\
+0.05 \\
+0.045
+\end{bmatrix} t + \begin{bmatrix}
 e_{C,t} \\ e_{D,t} \\ e_{E,t}
@@
 
-$\boldsymbol{e}_t$ has the following covariance matrix
+$\boldsymbol{\varepsilon}_t$ are white noises.
 
-$$
-\begin{bmatrix}
-1 & 0 & 0 \\
-0 & 1 & x \\
-0 & x & 1 \\
-\end{bmatrix}
-$$
+```{r}
+r1 <- step2(c(0.3, 0.3))
+r1 %>% mutate(mint = mint/base, mint2 = mint2/base) %>% group_by(names) %>% summarise_at(c("mint", "mint2"), mean)
 
-### x=0.9
+r2 <- step2(c(0, 0))
+r2 %>% mutate(mint = mint/base, mint2 = mint2/base) %>% group_by(names) %>% summarise_at(c("mint", "mint2"), mean)
 
-```{r, message=FALSE, echo=FALSE}
-W <- diag(3)
-W[2,3] <- 0.9
-W[3,2] <- 0.9
-r1 <- step2(W)
-r1 %>% group_by(names) %>% summarise_all(mean)
-```
+r3 <- step2(c(-0.3, -0.4))
+#r3 %>% group_by(names) %>% summarise_at(c("base", "mint", "mint2"), mean)
+r3 %>% mutate(mint = mint/base, mint2 = mint2/base) %>% group_by(names) %>% summarise_at(c("mint", "mint2"), mean)
 
-### x=-0.9
-
-```{r, message=FALSE, echo=FALSE}
-W <- diag(3)
-W[2,3] <- -0.9
-W[3,2] <- -0.9
-r1 <- step2(W)
-r1 %>% group_by(names) %>% summarise_all(mean)
 ```
@@
 
+```{r, include=FALSE}
+
+which.best <- function(x){
+  names(x$means)[1]
+}
+
+is.bestsignificant <- function(x){
+  x$mean[1] + x$cd/2 < x$mean[2] - x$cd/2
+}
+
+which.worst <- function(x){
+  names(x$means)[length(x$means)]
+}
+
+is.worstsignificant <- function(x){
+  x$mean[1] + x$cd/2 < x$mean[x$k] - x$cd/2
+}
+
+tmp_mcb <- function(x){
+  a <- do.call(cbind, x$values)
+  colnames(a) <- x$representator
+  tsutils::nemenyi(a, plottype = "vmcb")
+}
+```
+
 ```{r}
@@
   nest(values = c(representator, values, rank)) %>%
+  mutate(orig_values = values) %>%
   mutate_at("values", purrr::map, function(x){
-    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
-      t() %>% colMeans()
-    x %>% select(-values) %>%
-      pivot_wider(names_from = "representator", values_from = "rank")
-  }) %>%
-  unnest("values")
 
-representators <- c("error", "ts", "error.features", "ts.features", "forecast")
+    a <- do.call(cbind, x$values)
+    colnames(a) <- x$representator
+    tsutils::nemenyi(a, plottype = "none")
+  })
 
-## in most cases, error is the best
-representator_summarise %>% rowwise() %>%
-  mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
-  pull(min) %>%
-  table()
+representator_summarise <- representator_summarise %>%
+  rowwise() %>% mutate(best = which.best(values),
+                       sigbest = is.bestsignificant(values),
+                       worst = which.worst(values),
+                       sigworst = is.worstsignificant(values))
 
-## only in one case, error is the worst
-representator_summarise %>% rowwise() %>%
-  mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
-  pull(max) %>%
-  table()
-mcb(representator_summarise %>% select(representators))
+representors <- c("ts", "error", "ts.features", "error.features", "forecast")
+for (method in representors) {
+  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
+                NROW(representator_summarise %>% filter(best == method)),
+                method,
+                NROW(representator_summarise %>% filter(best == method, sigbest)),
+                NROW(representator_summarise %>% filter(worst == method)),
+                NROW(representator_summarise %>% filter(worst == method, sigworst))))
+}
+```
+
+```{r}
+
+# representators <- c("error", "ts", "error.features", "ts.features", "forecast")
+#
+# ## in most cases, error is the best
+# representator_summarise %>% rowwise() %>%
+#   mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
+#   pull(min) %>%
+#   table()
+#
+# ## only in one case, error is the worst
+# representator_summarise %>% rowwise() %>%
+#   mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
+#   pull(max) %>%
+#   table()
+# mcb(representator_summarise %>% select(representators))
 
@@
   nest(values = c(cluster, values, rank)) %>%
+  mutate(orig_values = values) %>%
   mutate_at("values", purrr::map, function(x){
-    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
-      t() %>% colMeans() %>% rank()
-    x %>% select(-values) %>%
-      pivot_wider(names_from = "cluster", values_from = "rank")
-  }) %>%
-  unnest("values")
+    a <- do.call(cbind, x$values)
+    colnames(a) <- x$cluster
+    tsutils::nemenyi(a, plottype = "none")
+  }) %>% rowwise() %>% mutate(best = which.best(values),
+                       sigbest = is.bestsignificant(values),
+                       worst = which.worst(values),
+                       sigworst = is.worstsignificant(values))
 
-cluster_summarise %>% select(-c(representator, distance)) %>%
-  mcb()
+cluster_summarise
+# cluster_summarise %>% select(-c(representator, distance)) %>%
+#   mcb()
 
@@
 ```{r}
+
 distance_summarise <- store_all %>% filter(distance != "") %>%
   nest(values = c(distance, values, rank)) %>%
+  mutate(orig_values = values) %>%
   mutate_at("values", purrr::map, function(x){
-    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
-      t() %>% colMeans() %>% rank()
-    x %>% select(-values) %>%
-      pivot_wider(names_from = "distance", values_from = "rank")
-  }) %>%
-  unnest("values")
-distance_summarise %>% select(-c(representator, cluster)) %>%
-  mcb()
+    a <- do.call(cbind, x$values)
+    colnames(a) <- x$distance
+    tsutils::nemenyi(a, plottype = "none")
+  }) %>% rowwise() %>% mutate(best = which.best(values),
+                       sigbest = is.bestsignificant(values),
+                       worst = which.worst(values),
+                       sigworst = is.worstsignificant(values))
 
-distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
-distance_summarise %>% rowwise() %>%
-  mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
-  pull(max) %>%
-  table()
-distance_summarise %>% rowwise() %>%
-  mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
-  pull(min) %>%
-  table()
+distance_summarise
+
+# distance_summarise <- store_all %>% filter(distance != "") %>%
+#   nest(values = c(distance, values, rank)) %>%
+#   mutate_at("values", purrr::map, function(x){
+#     x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
+#       t() %>% colMeans() %>% rank()
+#     x %>% select(-values) %>%
+#       pivot_wider(names_from = "distance", values_from = "rank")
+#   }) %>%
+#   unnest("values")
+# distance_summarise %>% select(-c(representator, cluster)) %>%
+#   mcb()
+#
+# distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
+# distance_summarise %>% rowwise() %>%
+#   mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
+#   pull(max) %>%
+#   table()
+# distance_summarise %>% rowwise() %>%
+#   mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
+#   pull(min) %>%
+#   table()
+```
+
+```{r}
+distances <- c("cor", "dtw", "euclidean", "negcor", "uncorrelation")
+for (method in distances) {
+  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
+                NROW(distance_summarise %>% filter(best == method)),
+                method,
+                NROW(distance_summarise %>% filter(best == method, sigbest)),
+                NROW(distance_summarise %>% filter(worst == method)),
+                NROW(distance_summarise %>% filter(worst == method, sigworst))))
+}
 ```
@@
 
-```{r, message=FALSE}
+```{r}
 # representator rank
@@
   nest(values = c(representator, values, rank)) %>%
+  mutate(orig_values = values) %>%
   mutate_at("values", purrr::map, function(x){
-    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
-      t() %>% colMeans()
-    x %>% dplyr::select(-values) %>%
-      pivot_wider(names_from = "representator", values_from = "rank")
-  }) %>%
-  unnest("values")
 
-representators <- c("error", "ts", "error.features", "ts.features", "forecast")
+    a <- do.call(cbind, x$values)
+    colnames(a) <- x$representator
+    tsutils::nemenyi(a, plottype = "none")
+  })
 
-## in most cases, error is the best
-representator_summarise %>% rowwise() %>%
-  mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
-  pull(min) %>%
-  table()
+representator_summarise <- representator_summarise %>%
+  rowwise() %>% mutate(best = which.best(values),
+                       sigbest = is.bestsignificant(values),
+                       worst = which.worst(values),
+                       sigworst = is.worstsignificant(values))
 
-## only in one case, error is the worst
-representator_summarise %>% rowwise() %>%
-  mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
-  pull(max) %>%
-  table()
-mcb(representator_summarise %>% dplyr::select(all_of(representators)))
+representors <- c("ts", "error", "ts.features", "error.features", "forecast")
+for (method in representors) {
+  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
+                NROW(representator_summarise %>% filter(best == method)),
+                method,
+                NROW(representator_summarise %>% filter(best == method, sigbest)),
+                NROW(representator_summarise %>% filter(worst == method)),
+                NROW(representator_summarise %>% filter(worst == method, sigworst))))
+}
+```
 
-# no hierarchy
-rank(store_all$rank)[which(store_all$cluster == "")]
+```{r}
 
-# natural hierarchy
-rank(store_all$rank)[which(store_all$cluster == "natural")]
+# representators <- c("error", "ts", "error.features", "ts.features", "forecast")
+#
+# ## in most cases, error is the best
+# representator_summarise %>% rowwise() %>%
+#   mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
+#   pull(min) %>%
+#   table()
+#
+# ## only in one case, error is the worst
+# representator_summarise %>% rowwise() %>%
+#   mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
+#   pull(max) %>%
+#   table()
+# mcb(representator_summarise %>% select(representators))
+
+# no hierarchy is not good: 391 / 428
+print(sprintf("rank of no clustering: %s", rank(store_all$rank)[1]))
+
+# natural hierarchy is not bad: 72/428
+print(sprintf("rank of natural hierarchy: %s", rank(store_all$rank)[2]))
 
@@
   nest(values = c(cluster, values, rank)) %>%
+  mutate(orig_values = values) %>%
   mutate_at("values", purrr::map, function(x){
-    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
-      t() %>% colMeans() %>% rank()
-    x %>% dplyr::select(-values) %>%
-      pivot_wider(names_from = "cluster", values_from = "rank")
-  }) %>%
-  unnest("values")
+    a <- do.call(cbind, x$values)
+    colnames(a) <- x$cluster
+    tsutils::nemenyi(a, plottype = "none")
+  }) %>% rowwise() %>% mutate(best = which.best(values),
+                       sigbest = is.bestsignificant(values),
+                       worst = which.worst(values),
+                       sigworst = is.worstsignificant(values))
 
-cluster_summarise %>% dplyr::select(-c(representator, distance)) %>%
-  mcb()
+cluster_summarise
+# cluster_summarise %>% select(-c(representator, distance)) %>%
+#   mcb()
 
@@
 ```{r}
+
 distance_summarise <- store_all %>% filter(distance != "") %>%
   nest(values = c(distance, values, rank)) %>%
+  mutate(orig_values = values) %>%
   mutate_at("values", purrr::map, function(x){
-    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
-      t() %>% colMeans() %>% rank()
-    x %>% select(-values) %>%
-      pivot_wider(names_from = "distance", values_from = "rank")
-  }) %>%
-  unnest("values")
-distance_summarise %>% select(-c(representator, cluster)) %>%
-  mcb()
+    a <- do.call(cbind, x$values)
+    colnames(a) <- x$distance
+    tsutils::nemenyi(a, plottype = "none")
+  }) %>% rowwise() %>% mutate(best = which.best(values),
+                       sigbest = is.bestsignificant(values),
+                       worst = which.worst(values),
+                       sigworst = is.worstsignificant(values))
 
-distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
-distance_summarise %>% rowwise() %>%
-  mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
-  pull(max) %>%
-  table()
-distance_summarise %>% rowwise() %>%
-  mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
-  pull(min) %>%
-  table()
+distance_summarise
+
+# distance_summarise <- store_all %>% filter(distance != "") %>%
+#   nest(values = c(distance, values, rank)) %>%
+#   mutate_at("values", purrr::map, function(x){
+#     x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
+#       t() %>% colMeans() %>% rank()
+#     x %>% select(-values) %>%
+#       pivot_wider(names_from = "distance", values_from = "rank")
+#   }) %>%
+#   unnest("values")
+# distance_summarise %>% select(-c(representator, cluster)) %>%
+#   mcb()
+#
+# distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
+# distance_summarise %>% rowwise() %>%
+#   mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
+#   pull(max) %>%
+#   table()
+# distance_summarise %>% rowwise() %>%
+#   mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
+#   pull(min) %>%
+#   table()
 ```
+
+```{r}
+distances <- c("cor", "dtw", "euclidean", "negcor", "uncorrelation")
+for (method in distances) {
+  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
+                NROW(distance_summarise %>% filter(best == method)),
+                method,
+                NROW(distance_summarise %>% filter(best == method, sigbest)),
+                NROW(distance_summarise %>% filter(worst == method)),
+                NROW(distance_summarise %>% filter(worst == method, sigworst))))
+}
+```
+
+## Prison
+
+```{r, include=FALSE, echo=FALSE}
+store_all <- NULL
+for (batch in 0:7) {
+  store_all <- readRDS(paste0("prison/store_", batch, ".rds"))$output %>%
+    output_pre() %>% mutate(batch = batch) %>%
+    filter(rf_method == .env$rf_method, accuracy_method == .env$accuracy_method) %>%
+    dplyr::select(-rf_method, -accuracy_method) %>%
+    rbind(store_all)
+}
+
+store_all <- store_all %>% rowwise() %>%
+  mutate(values = list(c(total, bottom))) %>% ungroup() %>%
+  dplyr::select(-total, -bottom)
+
+## remove single random
+store_all <- store_all %>% filter(!startsWith(cluster, "random-single"))
+
+# store_all %>% group_by(representator, distance, cluster) %>% tally() %>%
+#   pull(n) %>% table()
+
+## combine the results of 12 batches for one clustering method
+
+store_all <- store_all %>% dplyr::select(-other) %>% nest(values = c(batch, values)) %>%
+  mutate_at("values", purrr::map, function(x){
+    x <- arrange(x, batch)
+    do.call(c, x$values)
+  })
+
+## convert the tibble to a data.frame used for comparing ranks
+store_mat <- do.call(cbind, store_all$values)
+store_rank <- apply(store_mat, 1, rank) %>% t() %>% colMeans()
+store_all$rank <- store_rank
+```
+
+```{r}
+mcb(store_mat)
+```
+For prison data, all the methods are insignificantly different.
+```{r}
+store_all %>% arrange(rank)
+```
+
+### representator rank
+
+```{r}
+# representator rank
+representator_summarise <- store_all %>% filter(distance != "") %>%
+  nest(values = c(representator, values, rank)) %>%
+  mutate(orig_values = values) %>%
+  mutate_at("values", purrr::map, function(x){
+
+    a <- do.call(cbind, x$values)
+    colnames(a) <- x$representator
+    tsutils::nemenyi(a, plottype = "none")
+  })
+
+representator_summarise <- representator_summarise %>%
+  rowwise() %>% mutate(best = which.best(values),
+                       sigbest = is.bestsignificant(values),
+                       worst = which.worst(values),
+                       sigworst = is.worstsignificant(values))
+
+representors <- c("ts", "error", "ts.features", "error.features", "forecast")
+for (method in representors) {
+  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
+                NROW(representator_summarise %>% filter(best == method)),
+                method,
+                NROW(representator_summarise %>% filter(best == method, sigbest)),
+                NROW(representator_summarise %>% filter(worst == method)),
+                NROW(representator_summarise %>% filter(worst == method, sigworst))))
+}
+```
+
+```{r}
+# no hierarchy is not good: 391 / 428
+print(sprintf("rank of no clustering: %s", rank(store_all$rank)[1]))
+
+# natural hierarchy is not bad: 72/428
+print(sprintf("rank of natural hierarchy: %s", rank(store_all$rank)[2]))
+
+# random versus random natural versus natural
+
+tmp <- store_all %>% filter(distance == "")
+tmp$rank <- do.call(cbind, tmp$values) %>% apply(1, rank) %>%
+  t() %>% colMeans()
+```
+
+### cluster rank
+```{r}
+# cluster rank
+cluster_summarise <- store_all %>% filter(distance != "") %>%
+  nest(values = c(cluster, values, rank)) %>%
+  mutate(orig_values = values) %>%
+  mutate_at("values", purrr::map, function(x){
+    a <- do.call(cbind, x$values)
+    colnames(a) <- x$cluster
+    tsutils::nemenyi(a, plottype = "none")
+  }) %>% rowwise() %>% mutate(best = which.best(values),
+                       sigbest = is.bestsignificant(values),
+                       worst = which.worst(values),
+                       sigworst = is.worstsignificant(values))
+
+cluster_summarise
+```
+
+### distance rank
+
+```{r}
+
+distance_summarise <- store_all %>% filter(distance != "") %>%
+  nest(values = c(distance, values, rank)) %>%
+  mutate(orig_values = values) %>%
+  mutate_at("values", purrr::map, function(x){
+    a <- do.call(cbind, x$values)
+    colnames(a) <- x$distance
+    tsutils::nemenyi(a, plottype = "none")
+  }) %>% rowwise() %>% mutate(best = which.best(values),
+                       sigbest = is.bestsignificant(values),
+                       worst = which.worst(values),
+                       sigworst = is.worstsignificant(values))
+
+distance_summarise
+```
+
+```{r}
+distances <- c("cor", "dtw", "euclidean", "negcor", "uncorrelation")
+for (method in distances) {
+  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
+                NROW(distance_summarise %>% filter(best == method)),
+                method,
+                NROW(distance_summarise %>% filter(best == method, sigbest)),
+                NROW(distance_summarise %>% filter(worst == method)),
+                NROW(distance_summarise %>% filter(worst == method, sigworst))))
+}
+```

### 2023-10-02 illurstrative.R

@@ -52,21 +52,21 @@ weights_plot <- function(offdiag, title = "Setting 1") {
 }
 
 
-# Setting 1
-weights_plot(0)
-
-# Setting 2
-
-offdiag <- runif(10, 0, 0.5)
-weights_plot(offdiag, title = "Setting 2")
-
-# Setting 3
-offdiag <- runif(10, -0.5, 0)
-weights_plot(offdiag, title = "Setting 3")
-
-# Setting 4
-offdiag <- runif(10, -0.3, 0.3)
-weights_plot(offdiag, title = "Setting 4")
+# # Setting 1
+# weights_plot(0)
+# 
+# # Setting 2
+# 
+# offdiag <- runif(10, 0, 0.5)
+# weights_plot(offdiag, title = "Setting 2")
+# 
+# # Setting 3
+# offdiag <- runif(10, -0.5, 0)
+# weights_plot(offdiag, title = "Setting 3")
+# 
+# # Setting 4
+# offdiag <- runif(10, -0.3, 0.3)
+# weights_plot(offdiag, title = "Setting 4")
 
 
 
@@ -77,23 +77,26 @@ weights_plot(offdiag, title = "Setting 4")
 library(forecast)
 source("R/reconciliation.R")
 step2 <- function(offdiag) {
-  
   Wb <- diag(3)
-  Wb[lower.tri(Wb)] <- offdiag
-  Wb[upper.tri(Wb)] <- t(Wb)[upper.tri(t(Wb))]
+  # Wb[lower.tri(Wb)] <- c(0, offdiag)
+  # Wb[upper.tri(Wb)] <- t(Wb)[upper.tri(t(Wb))]
   
-  Wb <- diag(sqrt(c(100, 50, 20))) %*% Wb %*% diag(sqrt(c(100, 50, 20)))
-  
+  Wb <- diag(sqrt(c(10, 4, 4))) %*% Wb %*% diag(sqrt(c(10, 4, 4)))
   errors <- MASS::mvrnorm(1000, rep(0, 3), Wb)
-  
-  AR <- diag(c(0, 0.3, 0.4))
+  print(cov(errors))
+  AR <- diag(c(0, 0.35, 0.35))
+  AR[2,3] <- offdiag[1]
+  AR[3,2] <- offdiag[2]
   series <- matrix(0, 1001, 3)
   for (i in 2:1001) {
     series[i,] <- AR %*% series[i-1, ] + errors[i-1,]
   }
-  series <- series[102:1001,]
[…]

### 2023-10-02 mortality/mortality.R

@@ -30,7 +30,7 @@ output <- create_new_output()
 
 
 ## bottom and total forecast
-data <- forecast(data, bfmethod)
+data <- forecast(data, bfmethod, h=12, frequency=12)
 accs <- evaluate.hts(data, metrics, type = "base")
 output <- add_result(output, "", "", "", accs)
 data <- reconcile.all(data)

### 2023-10-02 run.sh

@@ -1,8 +1,0 @@
-
-for i in {0..10}
-do
-    echo $i
-    #Rscript mortality/mortality.R $i
-    Rscript mortality/ts_error.R $i
-    #Rscript mortality/naturalvsrandom.R $i
-done

### 2023-10-02 tourism/clustering.R

@@ -19,7 +19,7 @@ data <- readRDS(store_path)$data
 FEATURES <- readRDS(store_path)$features
 
 if (is.null(FEATURES)) {
-  features.compute(data)
+  features.compute(data, frequency = 12)
 }
 
 # K-medoids

### 2023-10-05 R/baseforecast.R
support ets

@@ -1,10 +1,15 @@
-library(forecast)
+library(forecast, quietly = TRUE)
 
 f.arima <- function(x, h, frequency){
   if(length(x) == 1) {
     stop("length == 1")
   }
   mdl <- auto.arima(ts(x, frequency = frequency))
+  list(basef=forecast(mdl, h=h)$mean, resid=residuals(mdl))
+}
+
+f.ets <- function(x, h, frequency) {
+  mdl <- ets(ts(x, frequency = frequency))
   list(basef=forecast(mdl, h=h)$mean, resid=residuals(mdl))
 }
 

### 2023-10-05 saintycheck.R

@@ -1,0 +1,121 @@
+library(FoReco)
+library(forecast)
+library(dplyr)
+source("R/reconciliation.R")
+
+mortality <- readRDS("tourism/store_5.rds")
+bts <- mortality$data$bts
+tts <- mortality$data$tts
+S <- mortality$data$S
+
+# check the base forecasts
+
+check_bf <- function() {
+  idx <- sample(length(mortality$bfstore$ets), 1)
+  series_name <- names(mortality$bfstore$ets)[idx]
+  S <- as.numeric(strsplit(series_name, "")[[1]])
+  series <- bts %*% matrix(S, ncol=1)
+  series <- ts(series[,1], frequency = 12)
+  tts <- ts((tts %*% matrix(S, ncol=1))[,1], frequency = 12, start = c(20, 8))
+  ets_mdl <- ets(series)
+  
+  # check forecasts
+  fcasts <- forecast(ets_mdl, h=12)
+  print(sprintf("base forecasts: %s", all.equal(fcasts$mean, mortality$bfstore$ets[[series_name]]$basef)))
+  resid <- residuals(ets_mdl)
+  print(sprintf("residuals: %s", all.equal(resid, mortality$bfstore$ets[[series_name]]$resid)))
+  
+  # check plots
+  plot(series, main = series_name)
+  lines(fcasts$mean, col="red")
+  lines(fitted(ets_mdl), col="blue")
+  lines(tts, col="green")
+}
+
+check_bf()
+
+# check reconciliation
+check_rf <- function(idx = NULL) {
+  if (is.null(idx)) {
+    idx <- sample(length(mortality$output$cluster), 1)
+  }
+  m <- NCOL(mortality$data$bts)
+  S <- mortality$output$other[[idx]]$S
+  if (!is.null(S)) {
+    S <- as.matrix(S)
+  }
+  C <- rbind(rep(1, m), S)
+  S <- rbind(C, diag(m))
+  tts <- mortality$data$tts %*% t(S)
+  
+  base <- lapply(iterators::iter(S, by="row"), function(x){
+    series_name <- do.call(paste0, as.list(x))
+    mortality$bfstore$ets[[series_name]]$basef
+  }) %>% do.call(cbind, .)
+  
+  res <- lapply(iterators::iter(S, by="row"), function(x){
+    series_name <- do.call(paste0, as.list(x))
+    mortality$bfstore$ets[[series_name]]$resid
[…]

### 2023-10-05 R/clustering.R
quietly import

@@ -1,4 +1,4 @@
-library(cluster)
+library(cluster, quietly = TRUE)
 
 cluster.random <- function(distance_mat, n_clusters) {
   

### 2023-10-05 R/construct_hierarchy.R

@@ -1,7 +1,7 @@
-library(forecast)
-library(cluster)
-library(foreach)
-library(dplyr)
+library(forecast, quietly = TRUE)
+library(cluster, quietly = TRUE)
+library(foreach, quietly = TRUE)
+library(dplyr, quietly = TRUE)
 source("representator.R")
 source("distance.R")
 source("clustering.R")
@@ -129,15 +129,8 @@ build_level <- function(
   stopifnot(is.hts(hts))
   
   n <- NCOL(hts$bts)
-  cluster_input <- representator(hts)
-  distance_mat <- matrix(0, n, n)
   
-  for(i in 1:n) {
-    for (j in 1:i) {
-      distance_mat[i, j] <- distance(cluster_input[, i], cluster_input[, j])
-      distance_mat[j, i] <- distance_mat[i, j]
-    }
-  }
+  distance_mat <- DISTANCEMAT[[representator]][[distance]]
   
   group_result <- cluster(distance_mat, ...)
   

### 2023-10-05 R/distance.R

@@ -3,7 +3,7 @@
 distance.euclidean <- function(x, y) { sqrt(sum((x - y)^2)) }
 
 
-library(dtw)
+library(dtw, quietly = TRUE)
 #' Dynamic Time Warping
 distance.dtw <- function(x, y) { dtw(x, y, distance.only = TRUE)$distance }
 

### 2023-10-05 R/expr_utils.R

@@ -1,4 +1,4 @@
-library(Matrix)
+library(Matrix, quietly = TRUE)
 
 create_new_output <- function() {
   output <- vector("list", 5)
@@ -10,7 +10,8 @@ saveResult <- function() {
   saveRDS(list(bfstore = BASEFORECAST_STORE,
                data = data,
                output = output,
-               features = FEATURES),
+               features = FEATURES,
+               distance = DISTANCEMAT),
           store_path)
 }
 
@@ -40,9 +41,6 @@ output_pre <- function(output) {
 }
 
 metrics <- c("mae", "rmse")
-if (exists("path")) {
-  store_path <- sprintf("%s/store_%s.rds", path, batch)
-}
 
 
 

### 2023-10-05 R/reconciliation.R
fix mint and wlsv

@@ -46,16 +46,17 @@ reconcile.ols <- function(S, basef, resid) {
 }
 
 reconcile.mint <- function(S, basef, resid) {
-  lamb <- lambda_estimate(resid)
-  W <- cov(resid)
-  W <- solve((1-lamb) * W + lamb * diag(diag(W)))
+  # lamb <- lambda_estimate(resid)
+  # W <- cov(resid)
+  W <- solve(lambda_estimate(resid))
   rm <- S %*% solve(t(S) %*% W %*% S, t(S) %*% W)
   
   basef %*% t(rm)
 }
 
 reconcile.wlsv <- function(S, basef, resid) {
-  W <- diag(1/apply(resid, 2, var))
+  # W <- diag(1/apply(resid, 2, var))
+  W <- diag(1 /diag(crossprod(resid)))
   rm <- S %*% solve(t(S) %*% W %*% S, t(S) %*% W)
   basef %*% t(rm)
 }
@@ -76,5 +77,7 @@ lambda_estimate <- function(error){
   xs2 = xs^2
   v = 1/(timeT*(timeT-1))*(t(xs2) %*% xs2 - 1/timeT*(t(xs) %*% xs)^2)
   diag(v) = 0
-  max(min(c(sum(v)/d, 1)), 0)
+  lamb <- max(min(c(sum(v)/d, 1)), 0)
+  
+  lamb * diag(diag(covm)) + (1-lamb) * covm
 }

### 2023-10-05 mortality/mortality.R
ets

@@ -1,8 +1,5 @@
-# configuration
-args <- commandArgs(trailingOnly = TRUE)
-batch <- as.integer(args[[1]])
 path <- "mortality"
-bfmethod <- "arima"
+bfmethod <- "ets"
 num.cores <- 8
 set.seed(42)
 
@@ -16,27 +13,51 @@ mortality <- read.csv("data/mortality.csv")
 colnames(mortality) <- stringi::stri_replace_all_fixed(colnames(mortality), ".", "-")
 
 
-## load dataset
-data <- hts(rbind(rep(1, 98), diag(98)), 
-            bts = unname(as.matrix(mortality))[1:(240-batch),],
-            tts = unname(as.matrix(mortality))[(241 - batch):(252 - batch),])
-
-# Workflow
-
-## load base forecast store
-BASEFORECAST_STORE <- list()
-BASEFORECAST_STORE[[bfmethod]] <- list()
-output <- create_new_output()
-
-
-## bottom and total forecast
-data <- forecast(data, bfmethod, h=12, frequency=12)
-accs <- evaluate.hts(data, metrics, type = "base")
-output <- add_result(output, "", "", "", accs)
-data <- reconcile.all(data)
-accs <- evaluate.hts(data, metrics, type = "rf")
-output <- add_result(output, "", "", "", accs)
-FEATURES <- NULL
-saveResult()
-
+for (batch in 0:11) {
+  
+  store_path <- sprintf("mortality/store_%s.rds", batch)
+  
+  data <- hts(rbind(rep(1, 98), diag(98)), 
+              bts = unname(as.matrix(mortality))[1:(240-batch),],
+              tts = unname(as.matrix(mortality))[(241 - batch):(252 - batch),])
+  # BASEFORECAST_STORE <- list()
+  # BASEFORECAST_STORE[[bfmethod]] <- list()
+  BASEFORECAST_STORE <- readRDS(sprintf("mortality/ets_backup/store_%s.rds", batch))$bfstore
+  output <- create_new_output()
+  
+  ## bottom and total forecast
+  data <- forecast(data, bfmethod, h=12, frequency=12)
+  accs <- evaluate.hts(data, metrics, type = "base")
+  output <- add_result(output, "", "", "", accs)
+  data <- reconcile.all(data)
+  accs <- evaluate.hts(data, metrics, type = "rf")
+  output <- add_result(output, "", "", "", accs)
+  
+  
+  print("computing features .....")
+  # FEATURES <- NULL
[…]

### 2023-10-05 mortality/naturalvsrandom.R

@@ -1,9 +1,8 @@
-rm(list = ls())
 args <- commandArgs(trailingOnly = TRUE)
 batch <- as.integer(args[[1]])
 path <- "mortality"
-bfmethod <- "arima"
-set.seed(42)
+bfmethod <- "ets"
+set.seed(146)
 
 source("R/construct_hierarchy.R", chdir = T)
 
@@ -11,14 +10,13 @@ num.cores <- 8
 cl <- parallel::makeCluster(num.cores)
 doParallel::registerDoParallel(cl)
 
-if (!file.exists(store_path)) {
-  stop("run configuration and base forecast first!")
-}
+store_path <- sprintf("mortality/store_%s.rds", batch)
 
 BASEFORECAST_STORE <- readRDS(store_path)$bfstore
 output <- readRDS(store_path)$output
 data <- readRDS(store_path)$data
 FEATURES <- readRDS(store_path)$features
+DISTANCEMAT <- readRDS(store_path)$distance
 
 # natural hierarchy
 S <- read.csv("data/S.csv", row.names = 1)
@@ -29,12 +27,13 @@ natural_data$nl <- list(list(S = unname(as.matrix(S[which(!(rownames(S) %in% col
                              basef = NULL,
                              rf = NULL))
 
-natural_data <- forecast(natural_data, bfmethod)
+natural_data <- forecast(natural_data, bfmethod, frequency=12, h=12)
 natural_data <- reconcile.all(natural_data)
 accs <- evaluate.hts(natural_data, metrics, type = "nl")
 output <- add_result(output, "", "", "natural", accs, other = list(
   S = as(natural_data$nl[[1]]$S, "sparseMatrix")
 ))
+saveResult()
 
 
 
@@ -42,10 +41,10 @@ output <- add_result(output, "", "", "natural", accs, other = list(
 
 for (n_repeat in c(20, 50, 100)) {
   for (n_cluster in 3:10) {
-    data <- build_level(data, representator.ts, 
-                        distance.euclidean, cluster.random, 
+    data <- build_level(data, "ts", 
+                        "euclidean", cluster.random, 
                         n_clusters = rep(n_cluster, n_repeat))
-    data <- forecast(data, bfmethod)
+    data <- forecast(data, bfmethod, frequency=12, h=12)
     data <- reconcile.all(data)
     accs <- evaluate.hts(data, metrics, type = "average")
     accs_single <- evaluate.hts(data, metrics, type = "nl")
[…]

### 2023-10-05 mortality/ts_error.R

@@ -1,43 +1,31 @@
-rm(list = ls())
 args <- commandArgs(trailingOnly = TRUE)
 batch <- as.integer(args[[1]])
 path <- "mortality"
-bfmethod <- "arima"
+bfmethod <- "ets"
 source("R/construct_hierarchy.R", chdir = T)
 set.seed(42)
-# rm(.Random.seed, envir=globalenv())
 num.cores <- 8
 cl <- parallel::makeCluster(num.cores)
 doParallel::registerDoParallel(cl)
 
-if (!file.exists(store_path)) {
-  stop("run configuration and base forecast first!")
-}
+store_path <- sprintf("mortality/store_%s.rds", batch)
 
 BASEFORECAST_STORE <- readRDS(store_path)$bfstore
 output <- readRDS(store_path)$output
 data <- readRDS(store_path)$data
 FEATURES <- readRDS(store_path)$features
-
-cluster_to_remove <- c("kmedoids", "kmedoids-d-nested")
-idx_to_stay <- which(!(output$cluster %in% cluster_to_remove))
-output$representator <- output$representator[idx_to_stay]
-output$distance <- output$distance[idx_to_stay]
-output$cluster <- output$cluster[idx_to_stay]
-output$accuracy <- output$accuracy[idx_to_stay]
-output$other <- output$other[idx_to_stay]
-
+DISTANCEMAT <- readRDS(store_path)$distance
 
 # K-medoids
 for (representator in c("ts", "error", "ts.features", "error.features", "forecast")) {
   for (distance in c("euclidean", "dtw", "negcor", "cor", "uncorrelation")) {
     print(sprintf("%s-%s", representator, distance))
     for (n_clusters in 3:10) {
-      dt <- build_level(hts = data, representator = get(paste0("representator.", representator)), 
-                        distance = get(paste0("distance.", distance)), 
+      dt <- build_level(hts = data, representator=representator, 
+                        distance = distance, 
                         cluster = cluster.kmedoids,
                         n_clusters = n_clusters)
-      dt <- forecast(dt, bfmethod)
+      dt <- forecast(dt, bfmethod, h=12, frequency=12)
       dt <- reconcile.all(dt)
       accs <- evaluate.hts(dt, metrics, type = "nl")
       output <- add_result(output, 
@@ -53,39 +41,38 @@ for (representator in c("ts", "error", "ts.features", "error.features", "forecas
 saveResult()
 
 
[…]

### 2023-10-05 tourism/base.R

@@ -1,8 +1,7 @@
 # configuration
-args <- commandArgs(trailingOnly = TRUE)
-batch <- as.integer(args[[1]])
+
 path <- "tourism"
-bfmethod <- "arima"
+bfmethod <- "ets"
 num.cores <- 8
 set.seed(42)
 
@@ -12,29 +11,68 @@ doParallel::registerDoParallel(cl)
 source("R/construct_hierarchy.R", chdir = T)
 
 
-dt <- readRDS("tourism/data.rds")
+# dt <- readRDS("tourism/data.rds")
 
 ## load dataset
-data <- hts(rbind(rep(1, 304), diag(304)), 
-            bts = dt$data[1:(216-batch), 252:555],
-            tts = dt$data[(217-batch):(228-batch), 252:555])
+for (batch in 0:11) {
+  store_path <- sprintf("tourism/store_%s.rds", batch)
+  
+  # data <- hts(rbind(rep(1, 304), diag(304)),
+  #             bts = dt$data[1:(216-batch), 252:555],
+  #             tts = dt$data[(217-batch):(228-batch), 252:555])
+  # 
+  # ## load base forecast store
+  # BASEFORECAST_STORE <- list()
+  # BASEFORECAST_STORE[[bfmethod]] <- list()
+  orig_path <- sprintf("tourism/ets_backup/store_%s.rds", batch)
+  
+  BASEFORECAST_STORE <- readRDS(orig_path)$bfstore
+  FEATURES <- readRDS(orig_path)$features
+  DISTANCEMAT <- readRDS(orig_path)$distance
+  
+  output <- create_new_output()
+  data <- readRDS(orig_path)$data
+  data$basef <- NULL
+  data$rf <- NULL
+  data$resid <- NULL
+  
+  ## bottom and total forecast
+  data <- forecast(data, bfmethod, h=12, frequency = 12)
+  accs <- evaluate.hts(data, metrics, type = "base")
+  output <- add_result(output, "", "", "", accs)
+  data <- reconcile.all(data)
+  accs <- evaluate.hts(data, metrics, type = "rf")
+  output <- add_result(output, "", "", "", accs)
+  # FEATURES <- NULL
+  # features.compute(data, frequency = 12)
+  
+  
+  # output <- readRDS(store_path)$output
+  
+ 
+  
+  # distance matrix
+  # print("computing distance matrix ....")
+  # DISTANCEMAT <- list()
[…]

### 2023-10-05 tourism/clustering.R

@@ -1,7 +1,7 @@
 args <- commandArgs(trailingOnly = TRUE)
 batch <- as.integer(args[[1]])
 path <- "tourism"
-bfmethod <- "arima"
+bfmethod <- "ets"
 source("R/construct_hierarchy.R", chdir = T)
 set.seed(42)
 # rm(.Random.seed, envir=globalenv())
@@ -9,35 +9,30 @@ num.cores <- 8
 cl <- parallel::makeCluster(num.cores)
 doParallel::registerDoParallel(cl)
 
-if (!file.exists(store_path)) {
-  stop("run configuration and base forecast first!")
-}
+store_path <- sprintf("tourism/store_%s.rds", batch)
 
 BASEFORECAST_STORE <- readRDS(store_path)$bfstore
 output <- readRDS(store_path)$output
 data <- readRDS(store_path)$data
 FEATURES <- readRDS(store_path)$features
-
-if (is.null(FEATURES)) {
-  features.compute(data, frequency = 12)
-}
+DISTANCEMAT <- readRDS(store_path)$distance
 
 # K-medoids
 for (representator in c("ts", "error", "ts.features", "error.features", "forecast")) {
   for (distance in c("euclidean", "dtw", "negcor", "cor", "uncorrelation")) {
-    print(sprintf("%s-%s", representator, distance))
+    print(sprintf("Kmedoids: %s-%s", representator, distance))
     for (n_clusters in 5:15) {
-      dt <- build_level(hts = data, representator = get(paste0("representator.", representator)), 
-                        distance = get(paste0("distance.", distance)), 
+      dt <- build_level(hts = data, representator = representator,
+                        distance = distance,
                         cluster = cluster.kmedoids,
                         n_clusters = n_clusters)
-      dt <- forecast(dt, bfmethod)
+      dt <- forecast(dt, bfmethod, frequency = 12, h = 12)
       dt <- reconcile.all(dt)
       accs <- evaluate.hts(dt, metrics, type = "nl")
-      output <- add_result(output, 
-                           representotar = representator, 
-                           distance = distance, 
-                           cluster = paste0("kmedoids-", n_clusters), 
+      output <- add_result(output,
+                           representotar = representator,
+                           distance = distance,
+                           cluster = paste0("kmedoids-", n_clusters),
                            accs = accs,
                            other = list(S = as(dt$nl[[1]]$S, "sparseMatrix")))
     }
@@ -51,11 +46,11 @@ for (representator in c("ts", "error", "ts.features", "error.features", "forecas
[…]

### 2023-10-05 tourism/naturalvsrandom2.R

@@ -3,7 +3,7 @@ args <- commandArgs(trailingOnly = TRUE)
 batch <- as.integer(args[[1]])
 path <- "tourism"
 bfmethod <- "ets"
-set.seed(44)
+set.seed(810975)
 source("R/construct_hierarchy.R", chdir = T)
 
 num.cores <- 8
@@ -18,30 +18,14 @@ data <- readRDS(store_path)$data
 FEATURES <- readRDS(store_path)$features
 DISTANCEMAT <- readRDS(store_path)$distance
 
-# natural hierarchy
 S <- read.csv("tourism/S.csv", row.names = 1)
 S <- unname(as.matrix(S))
-natural_data <- data
-
-natural_data$nl <- list(list(S = S[2:251,],
-                             basef = NULL,
-                             rf = NULL))
-
-natural_data <- forecast(natural_data, bfmethod, frequency=12, h=12)
-natural_data <- reconcile.all(natural_data)
-accs <- evaluate.hts(natural_data, metrics, type = "nl")
-output <- add_result(output, "", "", "natural", accs, other = list(
-  S = as(natural_data$nl[[1]]$S, "sparseMatrix")
-))
-
-saveResult()
-print(paste0(Sys.time(), "finish natural hierarchy"))
 
 # random hierarchy
 
-for (n_repeat in c(20, 50)) {
+for (n_repeat in c(100)) {
   for (n_cluster in 5:15) {
-    print(sprintf("%s random hierarchy: %s cluster * %s repeats", as.character(Sys.time()), n_repeat, n_cluster))
+    print(sprintf("%s random hierarchy: %s repeats * %s cluster", as.character(Sys.time()), n_repeat, n_cluster))
     data <- build_level(data, "ts", 
                         "euclidean", cluster.random, 
                         n_clusters = rep(n_cluster, n_repeat))
@@ -72,9 +56,9 @@ saveResult()
 
 
 # random natural
-print(paste0(Sys.time(), "random natural 20 ......."))
+print(paste0(Sys.time(), "random natural 100 ......."))
 new_S <- S[2:251,]
-data$nl <- lapply(1:20, function(i) {
+data$nl <- lapply(1:100, function(i) {
   list(S = new_S[,sample(NCOL(new_S), NCOL(new_S))],
        basef = NULL,
        rf = NULL)
@@ -85,7 +69,7 @@ data <- reconcile.all(data)
 accs <- evaluate.hts(data, metrics, type="average")
[…]

### 2023-10-05 analysis.Rmd
update analysis

@@
 
-# representators <- c("error", "ts", "error.features", "ts.features", "forecast")
-#
-# ## in most cases, error is the best
-# representator_summarise %>% rowwise() %>%
-#   mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
-#   pull(min) %>%
-#   table()
-#
-# ## only in one case, error is the worst
-# representator_summarise %>% rowwise() %>%
-#   mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
-#   pull(max) %>%
-#   table()
-# mcb(representator_summarise %>% select(representators))
-
 # no hierarchy is not good: 391 / 428
@@
   t() %>% colMeans()
-
-## 1. all the averaged random hierarchies beat no hierarchy
-## 2. deep and wide hierarchy wins
-## 3. average of more hierarchies does not obtain better results.
-##   Some really bad hierarchies destroy the results.
-##.  Deeper hierarchies have the ability to mitigate the affect of bad series
-
 ```
@@
 cluster_summarise
-# cluster_summarise %>% select(-c(representator, distance)) %>%
-#   mcb()
-
-## 1. kmedoids unnested is really bad
-## 2. hcluster with single linkage is bad
-## 3. nested kmedoids performs really well, which forms a natural-like unbalanced hierarchy.
 ```
@@
 distance_summarise
-
-# distance_summarise <- store_all %>% filter(distance != "") %>%
-#   nest(values = c(distance, values, rank)) %>%
-#   mutate_at("values", purrr::map, function(x){
-#     x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
-#       t() %>% colMeans() %>% rank()
-#     x %>% select(-values) %>%
-#       pivot_wider(names_from = "distance", values_from = "rank")
-#   }) %>%
-#   unnest("values")
-# distance_summarise %>% select(-c(representator, cluster)) %>%
-#   mcb()
-#
-# distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
-# distance_summarise %>% rowwise() %>%
-#   mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
-#   pull(max) %>%
-#   table()
-# distance_summarise %>% rowwise() %>%
-#   mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
-#   pull(min) %>%
-#   table()
 ```
@@
 store_all <- NULL
-for (batch in 0:8) {
+for (batch in 0:11) {
   store_all <- readRDS(paste0("tourism/store_", batch, ".rds"))$output %>%
@@
 store_all <- store_all %>% filter(!startsWith(cluster, "random-single"))
-
-# store_all %>% group_by(representator, distance, cluster) %>% tally() %>%
-#   pull(n) %>% table()
 
@@
 
-### representator rank
+### representor rank
 
@@
 # representator rank
-representator_summarise <- store_all %>% filter(distance != "") %>%
+representor_summarise <- store_all %>% filter(distance != "") %>%
   nest(values = c(representator, values, rank)) %>%
@@
 
-representator_summarise <- representator_summarise %>%
+representor_summarise <- representor_summarise %>%
   rowwise() %>% mutate(best = which.best(values),
@@
   print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
-                NROW(representator_summarise %>% filter(best == method)),
+                NROW(representor_summarise %>% filter(best == method)),
                 method,
-                NROW(representator_summarise %>% filter(best == method, sigbest)),
-                NROW(representator_summarise %>% filter(worst == method)),
-                NROW(representator_summarise %>% filter(worst == method, sigworst))))
+                NROW(representor_summarise %>% filter(best == method, sigbest)),
+                NROW(representor_summarise %>% filter(worst == method)),
+                NROW(representor_summarise %>% filter(worst == method, sigworst))))
 }
@@
 ```{r}
-
-# representators <- c("error", "ts", "error.features", "ts.features", "forecast")
-#
-# ## in most cases, error is the best
-# representator_summarise %>% rowwise() %>%
-#   mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
-#   pull(min) %>%
-#   table()
-#
-# ## only in one case, error is the worst
-# representator_summarise %>% rowwise() %>%
-#   mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
-#   pull(max) %>%
-#   table()
-# mcb(representator_summarise %>% select(representators))
-
-# no hierarchy is not good: 391 / 428
-print(sprintf("rank of no clustering: %s", rank(store_all$rank)[1]))
-
-# natural hierarchy is not bad: 72/428
-print(sprintf("rank of natural hierarchy: %s", rank(store_all$rank)[2]))
+print(sprintf("rank of no clustering: %s/512", rank(store_all$rank)[which(store_all$cluster == "")]))
+print(sprintf("rank of natural hierarchy: %s/512", rank(store_all$rank)[which(store_all$cluster == "natural")]))
 
@@
   t() %>% colMeans()
-
-## 1. all the averaged random hierarchies beat no hierarchy
-## 2. deep and wide hierarchy wins
-## 3. average of more hierarchies does not obtain better results.
-##   Some really bad hierarchies destroy the results.
-##.  Deeper hierarchies have the ability to mitigate the affect of bad series
-
+tmp %>% arrange(rank)
 ```

### 2023-10-23 analysis1022.Rmd
update

---
title: "Constructing hierarchies - mortality"
author: "Bohan Zhang"
date: "2023-10-22"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include=FALSE, message=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
source("R/representator.R")
path <- "mortality"
bfmethod <- "ets"
dt <- readRDS(sprintf("%s/%s/eval.rds", path, bfmethod))
dt_orig <- readRDS(sprintf("%s/%s/batch_120.rds", path, bfmethod))
dt_names <- readRDS(sprintf("%s/names.rds", path))
source("R/run_nls.R")
```

# Number of cluters of Kmedoids

```{r number-of-cluster}
Kmedoids_clusterN(dt)
```

The below figure visualizes a euclidean distance matrix of time series.

```{r visualize-distance-matrix-ts-euclidean}
visualizeDistance(dt_orig, "ts", "euclidean")
```

```{r visualize-distance-matrix-error-dtw}
visualizeDistance(dt_orig, "error", "dtw")
```

```{r visualize-distance-matrix-forecast-euclidean}
visualizeDistance(dt_orig, "forecast", "euclidean")
```

```{r visualize-distance-matrix-accuracy-euclidean}
visualizeDistance(dt_orig, "accuracy", "euclidean")
```
# Group Visualize

```{r visualize-group-results-accuracy-euclidean}
visualizeGroup(dt_orig, "accuracy", "euclidean", names = dt_names)
```

```{r visualize-group-results-forecast-euclidean}
visualizeGroup(dt_orig, "forecast", "euclidean", names = dt_names)
```

# why there is no group when cluster by time series and error?

```{r include=FALSE}
library(cluster)
```

```{r pam-time-series-euclidean}
summary(silhouette(pam(dt_orig$distance$ts$euclidean, diss=TRUE, k=2)))
```
```{r gap-statistics-time-series}
clusGap(t(representator.ts(dt_orig)), pam, K.max = 20)
```

```{r pam-error-euclidean}
summary(silhouette(pam(dt_orig$distance$error$euclidean, diss=TRUE, k=2)))
```

# Overall statistics

```{r average-metric}
avg_measure_fn(dt, metric = "rmsse") %>% arrange(total)
```

# Overall rank mcb test

```{r compare-overall-rank}
rank_compare(dt)
```

### 2023-10-23 R/clustering.R

@@ -51,23 +51,39 @@ cluster.nestedkmedoids <- function(distance_mat, n_clusters) {
 #' kmedoids
 #' 
 cluster.kmedoids <- function(distance_mat, n_clusters) {
-  output <- vector("list", length(n_clusters))
-  for (i in seq_along(n_clusters)) {
-    output[[i]] <- pam(distance_mat, k = n_clusters[i], diss=TRUE,
-                       nstart = 10,
-                       cluster.only = TRUE)
+  
+  # calculate silhouette and determine optimal number of clusters
+  max.avgwidths <- 0
+  max.n_cluster <- 1
+  for (n_cluster in n_clusters) {
+    if (n_cluster == 1) next
+    pr <- pam(distance_mat, k=n_cluster, diss=TRUE)
+    clus_silwidth <- summary(silhouette(pr))
+    if (min(clus_silwidth$clus.avg.widths) < 0.1) next
+    if (clus_silwidth$avg.width > max.avgwidths) {
+      max.avgwidths <- clus_silwidth$avg.width
+      max.n_cluster <- n_cluster
+    }
   }
-  grplst2Slst <- function(grplsts) {
-    lapply(grplsts, function(grpvec) {
-      do.call(rbind, lapply(unique(grpvec), function(grp){
-        S_row <- vector("numeric", NCOL(distance_mat))
-        S_row[which(grpvec == grp)] <- 1
-        S_row
-      }))
-    })
+  if (max.n_cluster == 1) { return(NULL) }
+  
+  output <- pam(distance_mat, k = max.n_cluster, diss=TRUE,
+                nstart = 10)
+  grp2S <- function(grp) {
+    grpvec <- grp$clustering
+    do.call(rbind, lapply(unique(grpvec), function(grp){
+      S_row <- vector("numeric", NCOL(distance_mat))
+      S_row[which(grpvec == grp)] <- 1
+      S_row
+    }))
   }
   
-  list(do.call(rbind, grplst2Slst(output)))
+  list(S=grp2S(output), 
+       info = list(n_cluster = max.n_cluster, 
+                   width = summary(silhouette(output))$clus.avg.widths,
+                   avgwidth = summary(silhouette(output))$avg.width,
+                   medoids = output$id.med)
+       )
 }
 
 #' hierarchical clustering

### 2023-10-23 R/distance.R

@@ -1,7 +1,7 @@
 
 #' Euclidean distance
 distance.euclidean <- function(x, y) { sqrt(sum((x - y)^2)) }
-
+distance.manhattan <- function(x, y) { sum(abs(x-y)) }
 
 library(dtw, quietly = TRUE)
 #' Dynamic Time Warping

### 2023-10-23 R/reconciliation.R

@@ -7,7 +7,6 @@ toMatrix <- function(x) {
 }
 
 reconcile.all <- function(S, basef, resid, methods = c("ols", "wlss", "mint", "wlsv")){
-  # stopifnot(!is.null(x$basef))
   output <- list()
   idx <- c(which(rowSums(S) > 1), (NROW(S) - NCOL(S) + 1):NROW(S))
   C <- S[which(rowSums(S) > 1),,drop=FALSE]
@@ -24,8 +23,6 @@ reconcile.all <- function(S, basef, resid, methods = c("ols", "wlss", "mint", "w
 }
 
 reconcile.ols <- function(C, basef, resid) {
-  # rm <- S %*% solve(t(S) %*% S, t(S) )
-  # basef %*% t(rm)
   FoReco::htsrec(basef, "ols", C=C)$recf
 }
 
@@ -39,19 +36,4 @@ reconcile.wlsv <- function(C, basef, resid) {
 
 reconcile.wlss <- function(C, basef, resid) {
   FoReco::htsrec(basef, "struc", C=C, res = resid)$recf
-}
-
-lambda_estimate <- function(error){
-  timeT = dim(error)[1]
-  covm = t(error) %*% error/timeT
-  xs = apply(error, 1, function(x){x / sqrt(diag(covm))}) %>% t()
-  corm = t(xs) %*% xs / timeT
-  diag(corm) = 0
-  d = sum(corm^2)
-  xs2 = xs^2
-  v = 1/(timeT*(timeT-1))*(t(xs2) %*% xs2 - 1/timeT*(t(xs) %*% xs)^2)
-  diag(v) = 0
-  lamb <- max(min(c(sum(v)/d, 1)), 0)
-  
-  lamb * diag(diag(covm)) + (1-lamb) * covm
 }

### 2023-10-23 R/representator.R

@@ -7,7 +7,7 @@ representator.ts <- function(x) {
 representator.accuracy <- function(x) {
   sapply(2:NCOL(x$resid), function(idx) {
     sqrt(mean(x$resid[,idx]^2) / mean(diff(x$bts[,idx-1], 12)^2))
-  })
+  }) %>% matrix(nrow = 1)
 }
 
 representator.forecast <- function(x) {

### 2023-10-23 R/run_base.R

@@ -19,45 +19,49 @@ forecast_horizon <- 12
 frequency <- 12
 batch_length <- time_length - 96 - forecast_horizon
 
+REPRESENTORS <- c(rep(c("ts", "error", "forecast"), each = 6),
+                  "ts.features", "error.features","ts.features", "error.features", "accuracy")
+DISTANCES <- c(rep(c("euclidean", "manhattan", "dtw", "negcor", "cor", "uncorrelation"), 3),
+               "euclidean", "euclidean", "manhattan", "manhattan", "euclidean")
+
+
 # load dataset
-for (batch in 0:batch_length) {
+for (batch in c(0)) {
   store_path <- sprintf("%s/%s/fixwindow/batch_%s.rds", path, bfmethod, batch)
-  
   data <- hts(rbind(rep(1, m), diag(m)),
-               bts = dt$data[(1+batch):(96+batch), (n-m+1):n],
+               bts = dt$data[1:(96+batch), (n-m+1):n],
                tts = dt$data[(96+batch+1):(96+batch+forecast_horizon), (n-m+1):n])
   
   data <- hts.basef(data, bfmethod, h=forecast_horizon, frequency=12)
   
-  # print(paste0(Sys.time(), "computing features ..."))
-  # data <- features.compute(data, frequency = frequency)
-  # 
-  # print(paste0(Sys.time(), "computing distance matrix ..."))
-  # DISTANCEMAT <- list()  
-  # for (representor in c("ts", "error", "ts.features", "error.features", "forecast")) {
-  #   DISTANCEMAT[[representor]] <- list()
-  #   for (distance in c("euclidean", "dtw", "negcor", "cor", "uncorrelation")) {
-  #     cluster_input <- get(paste0("representator.", representor))(data)
-  #     distance_method <- get(paste0("distance.", distance))
-  #     distance_mat <- matrix(0, m, m)
-  # 
-  #     lst <- foreach(row=1:m, .packages = c("dtw")) %dopar% {
-  #       output <- c()
-  #       for (col in 1:row) {
-  #         dis <- distance_method(cluster_input[, row], cluster_input[, col])
-  #         output <- c(output, dis)
-  #       }
-  #       output
-  #     }
-  #     for (row in 1:m) {
-  #       distance_mat[row, 1:row] <- lst[[row]]
-  #       distance_mat[1:row, row] <- lst[[row]]
-  #     }
-  #     
[…]

### 2023-10-23 R/run_eval.R

@@ -20,7 +20,33 @@ source("R/metrics.R")
 hts.eval <- function(df, metrics, tts, bts) {
   tts <- cbind(rowSums(tts), tts)
   bts <- cbind(rowSums(bts), bts)
-
+  
+  # random
+  randoms <- unique(df$cluster[which(startsWith(df$cluster, "random"))])
+  df_random <- list()
+  df_random$S <- vector("list", 3*length(randoms))
+  df_random$other <- vector("list", 3*length(randoms))
+  df_random$cluster <- c()
+  df_random$rf <- list()
+  df_random$representor <- rep("", 3*length(randoms))
+  df_random$distance <- rep("", 3*length(randoms))
+  for (rd in randoms) {
+    tmpdt <- df %>% filter(cluster == rd)
+    for (random_n in c(10, 20, 50)) {
+      avg_rf <- list()
+      for (rf_method in c("ols", "wlss", "wlsv", "mint")) {
+        avg_rf_method <- 
+          do.call(abind::abind, list(lapply(tmpdt$rf, function(x) x[[rf_method]]), along=0))
+        avg_rf[[rf_method]] <- 
+          apply(avg_rf_method[1:random_n, ,], c(2, 3), mean)
+      }
+      df_random$cluster <- c(df_random$cluster, paste0(rd, "-", random_n))
+      df_random$rf <- append(df_random$rf, list(avg_rf))
+    }
+  }
+  df <- df %>% filter(!startsWith(cluster, "random")) %>%
+    rbind(as_tibble(df_random))
+  
   for (metric in metrics) {
     accuracy_method <- get(paste0("metric.", metric))
     
@@ -80,3 +106,6 @@ for (batch in 0:batch_length) {
 }
 
 saveRDS(list(base = dtb_base, dtb = dtb), sprintf("%s/%s/eval.rds", path, bfmethod))
+
+
+

### 2023-10-23 R/run_nl.R

@@ -20,8 +20,10 @@ frequency <- 12
 batch_length <- time_length - 96 - forecast_horizon
 
 
-REPRESENTORS <- c("ts", "error", "ts.features", "error.features", "forecast")
-DISTANCES <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
+REPRESENTORS <- c(rep(c("ts", "error", "forecast"), each = 6),
+                  "ts.features", "error.features","ts.features", "error.features", "accuracy")
+DISTANCES <- c(rep(c("euclidean", "manhattan", "dtw", "negcor", "cor", "uncorrelation"), 3),
+               "euclidean", "euclidean", "manhattan", "manhattan", "euclidean")
 
 
 # load dataset
@@ -29,70 +31,61 @@ for (batch in 0:batch_length) {
   store_path <- sprintf("%s/%s/batch_%s.rds", path, bfmethod, batch)
   data <- readRDS(store_path)
   
-  print(paste0(Sys.time(), " KMedoids ..."))
-  for (representor in REPRESENTORS) {
-    for (distance in DISTANCES) {
-      nl <- foreach(n_clusters = 5:15, .packages = "cluster") %dopar% {
-        build_level(hts = data, representor=representor, 
-                    distance = distance, 
-                    cluster = cluster.kmedoids,
-                    n_clusters = n_clusters)[[1]]
-      }
-      
-      for (l in seq_along(nl)) {
-        data <- add_nl(data, nl[[l]], representor, distance, paste0("Kmedoids-", l + 4))
-      }
-      
-      unnested <- do.call(rbind,  nl)
-      data <- add_nl(data, unnested, representor, distance, paste0("unnestedKmedoids"))
-    }
-  }
+  # for (i in seq_along(REPRESENTORS)) {
+  #   print(sprintf("%s KMedoids %s * %s ", Sys.time(), REPRESENTORS[i], DISTANCES[i]))
+  #   nl <- build_level(hts = data, representor = REPRESENTORS[i],
+  #                     distance = DISTANCES[i], 
+  #                     cluster = cluster.kmedoids,
+  #                     n_clusters = 1:30)
+  #   data <- add_nl(data, nl$S, REPRESENTORS[i], DISTANCES[i], "Kmedoids",
+  #                  other = nl$info)
+  # }
   
-  print(paste0(Sys.time(), " hierarchical clustering ..."))
+  # print(paste0(Sys.time(), " hierarchical clustering ..."))
   
   for (representor in REPRESENTORS) {
[…]

### 2023-10-23 R/run_nlr.R

@@ -3,7 +3,7 @@ path <- args[[1]]
 bfmethod <- args[[2]]
 
 num.cores <- 8
-set.seed(20231008)
+set.seed(20231019)
 
 cl <- parallel::makeCluster(num.cores)
 doParallel::registerDoParallel(cl)
@@ -25,18 +25,18 @@ for (batch in 0:batch_length) {
   store_path <- sprintf("%s/%s/batch_%s.rds", path, bfmethod, batch)
   data <- readRDS(store_path)
   
-  for (i in 1:100) {
+  for (i in 1:50) {
     for (ncluster in 5:15) {
       S <- cluster.random(data$distance$ts$euclidean, n_clusters = ncluster)[[1]]
-      data <- add_nl(data, S, "", "", paste0("random-single-", ncluster))
+      data <- add_nl(data, S, "", "", paste0("random-", ncluster))
     }
   }
   
   newS <- dt$S[2:(n-m), ]
   
-  for (i in 1:100) {
+  for (i in 1:50) {
     S <- newS[, sample(m, m)]
-    data <- add_nl(data, S, "", "", "random-single-natural")
+    data <- add_nl(data, S, "", "", "random-natural")
   }
   
   saveRDS(data, store_path)

### 2023-10-23 R/run_nls.R

@@ -1,112 +1,185 @@
-args <- commandArgs(trailingOnly = TRUE)
-path <- args[[1]]
-bfmethod <- args[[2]]
-
-dt <- readRDS(sprintf("%s/%s/eval.rds", path, bfmethod))
-dtb <- dt$base
-dt <- dt$dtb
-library(dplyr)
-
 # Calculate average RMSE to compare with mint paper
-avg_measure_fn <- function(dt) {
-  output <- list()
+nl2tibble <- function(x) {
+  output <- vector("list", 6)
+  names(output) <- c("representor", "cluster", "distance", "S", "rf", "other")
   
-  for (measure in c("rmse", "mae", "rmsse", "mase")) {
-    for (rf_method in c("ols", "wlss", "wlsv", "mint")) {
-      tmp <- dt %>% filter(cluster == "natural") %>% pull(measure) %>% 
-        lapply(function(x) {x[[rf_method]]} ) %>%
-        do.call(rbind, .) %>%
-        colMeans()
-      output[[rf_method]] <- c(output[[rf_method]], c(tmp[1], mean(tmp[2:length(tmp)])))
+  for (i in seq_along(x)) {
+    for (n in names(x[[i]])) {
+      if (is.character(x[[i]][[n]])) {
+        output[[n]] <- append(output[[n]], x[[i]][[n]])
+      } else {
+        output[[n]] <- append(output[[n]], list(x[[i]][[n]]))
+      }
     }
-    output[["metric"]] <- c(output[["metric"]], rep(measure, 2))
   }
-  
-  base_output <- list()
-  for (measure in c("rmse", "mae", "rmsse", "mase")) {
-    tmp <- dtb %>% pull(measure) %>% 
-      do.call(rbind, .) %>%
-      colMeans()
-    base_output[["base"]] <- c(base_output[["base"]], c(tmp[1], mean(tmp[2:length(tmp)])))
-    base_output[["metric"]] <- c(base_output[["metric"]], rep(measure, 2))
-  }
-  list(natural = as_tibble(output), base = as_tibble(base_output))
+  tibble::as_tibble(output)
 }
 
-(avg_measure <- avg_measure_fn(dt))
+avg_measure_fn <- function(dt, rf_method = "mint", metric = "rmse") {
+  n <- length(dt$base$rmse[[1]])
+  base <- dt$base %>% pull(metric) %>% 
+    do.call(rbind, .) %>%
+    colMeans()
+  dt$dtb %>% 
[…]

### 2023-10-23 visualize.R

@@ -180,15 +180,51 @@ visualizeSeriesError <- function(dataset, order = NULL, method = NULL) {
   }
 }
 
-# mortality_S <- read.csv("data/S.csv")
-# colnames(mortality_S) <- stringi::stri_replace_all_fixed(colnames(mortality_S), ".", "-")
-# mortality_S <- mortality_S[,2:NCOL(mortality_S)]
-
-
 visualizeSeriesError(mortality, 2)
+
 visualizeSeriesError(mortality_arima, method = list(representor = "ts.features",
-                                        distance = "dtw",
-                                        cluster = "kmedoids-10"))
+                                                    distance = "euclidean",
+                                                    cluster = "kmedoids-10"))
+
 
 visualizeSeriesError(tourism, 3)
 visualizeSeriesError(tourism_arima, 6)
+
+
+
+visualizeGroup2D <- function(dt, method) {
+  nl <- nl2tibble(dt$nl)
+  representor <- (nl$representor == method["representor"])
+  cluster <- (nl$cluster == method["cluster"])
+  distance <- (nl$distance == method["distance"])
+  
+  idx <- which(representor & cluster & distance)
+  distance_mat <- dt$distance[[method["representor"]]][[method["distance"]]]
+  d2scaled <- cmdscale(distance_mat, 2, eig = TRUE)
+  
+  d2scaled <- tibble(x=d2scaled$points[,1], y=d2scaled$points[,2])
+  S <- (dt$nl[[idx]]$S)
+  p <- ggplot(d2scaled, mapping = aes(x=x,y=y))
+  
+  if (!is.null(S)) {
+    grpvec <- vector("integer", NCOL(S))
+    sapply(1:NROW(S), function(x) { grpvec[which(S[x,] == 1)] <<- x })
+    grpvec[dt$nl[[idx]]$other$medoids] <- "medoids"
+    d2scaled$cluster <-  grpvec
+    p <- p + geom_point(aes(color = cluster, group = cluster), data = d2scaled)
+  } else {
+    p <- p + geom_point()
+  }
+   p + ggtitle(sprintf("%s %s", method["representor"], method["distance"]))
+}
+
+
+visualizeGroup2D(mortality, c(representor = "accuracy",
+                              distance = "euclidean",
+                              cluster = "Kmedoids"))
+
+
+
+
+
+

### 2023-10-30 analysis1027.Rmd
update

---
title: "Constructing hierarchies - tourism"
author: "Bohan Zhang"
date: "2023-10-27"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include=FALSE, message=FALSE}
library(dplyr)
library(tidyr)
library(cluster)
library(ggplot2)
source("R/representator.R")
path <- "tourism"
bfmethod <- "ets"
dt <- readRDS(sprintf("%s/%s/eval.rds", path, bfmethod))
dt_orig <- readRDS(sprintf("%s/%s/batch_0.rds", path, bfmethod))
dt_names <- readRDS(sprintf("%s/names.rds", path))
source("R/run_nls.R")
```

# Number of cluters of Kmedoids

```{r number-of-cluster}
Kmedoids_clusterN(dt)
```

```{r number-of-cluster-dimension-reduction}
Kmedoids_clusterN(dt, cluster = "Kmedoids-dr")
```

```{r number-of-clusters-dimension-reduction-gap}
Kmedoids_gap(dt)
```

```{r number-of-clusters-dimension-reduction-gap-summary}
gap <- Kmedoids_gap(dt)
gap %>% group_by(representor, n_gap) %>% count()
gap %>% group_by(representor, n_gap, n_cluster) %>% count()
```

```{r visualize-distance-matrix-ts-euclidean}
visualizeDistance(dt_orig, "ts-dr", "euclidean", "Kmedoids-dr")
```

```{r inspect-silhouette}
inspect_silhouette(dt_orig, "ts-dr")
```

```{r visualize-distance-matrix-error}
visualizeDistance(dt_orig, "error-dr", "euclidean", "Kmedoids-dr")
```

```{r inspect-silhouette-error}
inspect_silhouette(dt_orig, "error-dr")
```

```{r visualize-distance-matrix-accuracy-euclidean}
visualizeDistance(dt_orig, "accuracy", "euclidean")
```

# Group Visualize

```{r visualize-group-results-error-dimension-reduction}
visualizeGroup(dt_orig, "error-dr", "euclidean", cluster= "Kmedoids-dr",names = dt_names)
```

```{r visualize-group-results-ts-dimension-reduction}
visualizeGroup(dt_orig, "ts-dr", "euclidean", cluster= "Kmedoids-dr",names = dt_names)
```
```{r visualize-group-results-tsfeatures-dimension-reduction}
visualizeGroup(dt_orig, "ts.features-dr", "euclidean", cluster= "Kmedoids-dr",names = dt_names)
```

```{r visualize-group-results-errorfeatures-dimension-reduction}
visualizeGroup(dt_orig, "error.features-dr", "euclidean", cluster= "Kmedoids-dr",names = dt_names)
```

# Overall statistics

```{r average-metric}
avg_measure_fn(dt, metric = "rmsse") %>% arrange(bottom)
```

# Overall rank mcb test

```{r compare-overall-rank}
rank_compare(dt, filter_random = TRUE)
```

### 2023-10-30 R/construct_hierarchy.R

@@ -57,7 +57,7 @@ hts.basef <- function(x, f_str, h, frequency) {
 hts.nlf <- function(htst, f_str, h, frequency) {
   f <- get(paste0("f.", f_str))
   
-  idx2forecast <- Filter(function(x) { length(x$rf) == 0 }, htst$nl)
+  idx2forecast <- which(sapply(htst$nl, function(x) {length(x$rf) == 0}))
   
   smat2sstr <- function(S) {
     S_str <- c()
@@ -85,7 +85,6 @@ hts.nlf <- function(htst, f_str, h, frequency) {
   
   allts <- htst$bts %*% t(S_toforecast)
   
-  
   bf <- foreach::foreach(x = iterators::iter(allts, by = "column"), .packages = c("forecast")) %dopar% {
     f(x, h=h, frequency=frequency)
   }
@@ -111,8 +110,9 @@ hts.nlf <- function(htst, f_str, h, frequency) {
     reconcile.all(S, basef, resid)
   }
   
-  for (l in idx2forecast) {
-    htst$nl[[l]]$rf <- rfs[[l]]
+  for (l in seq_along(idx2forecast)) {
+    idxinnl <- idx2forecast[l]
+    htst$nl[[idxinnl]]$rf <- rfs[[l]]
   }
   htst
 }

### 2023-10-30 R/run_base.R

@@ -2,7 +2,7 @@ args <- commandArgs(trailingOnly = TRUE)
 path <- args[[1]]
 bfmethod <- args[[2]]
 
-num.cores <- 8
+num.cores <- 6
 
 cl <- parallel::makeCluster(num.cores)
 doParallel::registerDoParallel(cl)
@@ -29,29 +29,29 @@ DISTANCES <- rep("euclidean", 4)
 # load dataset
 for (batch in 0:batch_length) {
   store_path <- sprintf("%s/%s/batch_%s.rds", path, bfmethod, batch)
-  # data <- hts(rbind(rep(1, m), diag(m)),
-  #              bts = dt$data[1:(96+batch), (n-m+1):n],
-  #              tts = dt$data[(96+batch+1):(96+batch+forecast_horizon), (n-m+1):n])
-  # 
-  # data <- hts.basef(data, bfmethod, h=forecast_horizon, frequency=12)
-  # 
-  data <- readRDS(store_path)
-  # print(paste0(Sys.time(), "computing features ..."))
-  # data <- features.compute(data, frequency = frequency)
+  data <- hts(rbind(rep(1, m), diag(m)),
+               bts = dt$data[1:(96+batch), (n-m+1):n],
+               tts = dt$data[(96+batch+1):(96+batch+forecast_horizon), (n-m+1):n])
+
+  data <- hts.basef(data, bfmethod, h=forecast_horizon, frequency=12)
+
+  # data <- readRDS(store_path)
+  print(paste0(Sys.time(), "computing features ..."))
+  data <- features.compute(data, frequency = frequency)
 
   print(paste0(Sys.time(), "computing distance matrix ..."))
   DISTANCEMAT <- list()
+  # DISTANCEMAT <- data$distance
   for (i in seq_along(REPRESENTORS)) {
     representor <- REPRESENTORS[i]
     distance <- DISTANCES[i]
-    cluster_input <- get(paste0("representator.", representor))(data, dr = endsWith(representor, "-dr"))
+    cluster_input <- get(paste0("representator.", strsplit(representor, "-")[[1]][1]))(data, dr = endsWith(representor, "-dr"))
     distance_method <- get(paste0("distance.", distance))
     distance_mat <- matrix(0, m, m)
     
     lst <- foreach(row=1:m, .packages = c("dtw")) %dopar% {
       output <- c()
       for (col in 1:row) {
-        
[…]

### 2023-10-30 R/run_eval.R

@@ -23,6 +23,7 @@ hts.eval <- function(df, metrics, tts, bts) {
   
   # random
   randoms <- unique(df$cluster[which(startsWith(df$cluster, "random"))])
+  randoms <- c(randoms, "hcluster-random")
   df_random <- list()
   df_random$S <- vector("list", 3*length(randoms))
   df_random$other <- vector("list", 3*length(randoms))
@@ -45,6 +46,7 @@ hts.eval <- function(df, metrics, tts, bts) {
     }
   }
   df <- df %>% filter(!startsWith(cluster, "random")) %>%
+    filter(cluster != "hcluster-random") %>%
     rbind(as_tibble(df_random))
   
   for (metric in metrics) {
@@ -99,7 +101,7 @@ for (batch in 0:batch_length) {
   data_tibble <- nl2tibble(data$nl)
   data_tibble <- hts.eval(data_tibble, metrics, data$tts, data$bts)
 
-  data_tibble <- data_tibble %>% select(-other, -rf) %>% mutate(batch = batch)
+  data_tibble <- data_tibble %>% select(-rf) %>% mutate(batch = batch)
   dtb <- rbind(dtb, data_tibble)
   dtb_base <- rbind(dtb_base, as_tibble(hts.evalbase(data, metrics)) %>%
                       mutate(batch = batch))

### 2023-10-30 R/run_nl.R

@@ -41,18 +41,15 @@ for (batch in 0:batch_length) {
   
   # print(paste0(Sys.time(), " hierarchical clustering ..."))
   
-  for (representor in REPRESENTORS) {
-    for (distance in DISTANCES) {
-        nl <- build_level(hts = data, representor=representor,
-                          distance = distance,
-                          cluster = cluster.hcluster,
-                          method = "ward")[[1]]
-        data <- add_nl(data, nl, representor, distance, paste0("hcluster-dr"))
-        
-        for (i in 1:20) {
-          data <- add_nl(data, nl[,sample(NCOL(nl))], representor, distance, paste0("hcluster-dr-random"))
-        }
-    }
+  for (i in seq_along(REPRESENTORS)) {
+    nl <- build_level(hts = data, representor=REPRESENTORS[i],
+                      distance = DISTANCES[i],
+                      cluster = cluster.hcluster,
+                      method = "ward")[[1]]
+    data <- add_nl(data, nl, REPRESENTORS[i], DISTANCES[i], "hcluster-dr")
+  }
+  for (i in 1:50) {
+    data <- add_nl(data, nl[,sample(NCOL(nl))], "", "", "hcluster-random")
   }
   # 
   # print(paste0(Sys.time(), " nested Kmedoids 2 ..."))

### 2023-10-30 R/run_nls.R

@@ -34,11 +34,23 @@ avg_measure_fn <- function(dt, rf_method = "mint", metric = "rmse") {
     arrange(total)
 }
 
-rank_compare <- function(dt, methods_df = NULL, measure="rmse", rf_method = "mint") {
+rank_compare <- function(dt, methods_df = NULL, measure="rmse", rf_method = "mint", filter_random = FALSE) {
   if (is.null(methods_df)) {
+    if (filter_random) {
+      methods_random <- dt$dtb %>% select(representor, distance, cluster) %>% 
+        filter(cluster %in% c("random-15-50", "hcluster-random-50", "random-natural")) %>% 
+        unique()
+    } else {
+      methods_random <- dt$dtb %>% select(representor, distance, cluster) %>% 
+        filter(grepl(cluster, "random", fixed = TRUE)) %>% 
+        unique()
+    }
+    methods_dr <- dt$dtb %>% select(representor, distance, cluster) %>% filter(endsWith(cluster, "-dr")) %>% unique()
+    methods_natural <- dt$dtb %>% select(representor, distance, cluster) %>%
+      filter(cluster %in% c("base", "", "natural")) %>% unique()
     methods_df <- Kmedoids_clusterN(dt) %>% filter(`0` != length(dt$base$rmse) | is.na(`0`)) %>% 
       select(representor, distance) %>% mutate(cluster = "Kmedoids") %>%
-      rbind(dt$dtb %>% select(representor, distance, cluster) %>% filter(distance == "") %>% unique())
+      rbind(methods_dr, methods_random, methods_natural)
   }
   dtb <- dt$dtb %>% right_join(methods_df, by = c("representor", "distance", "cluster")) %>%
     select(representor, distance, cluster, all_of(measure), batch) %>%
@@ -47,6 +59,10 @@ rank_compare <- function(dt, methods_df = NULL, measure="rmse", rf_method = "min
       g <- arrange(g, "batch") %>% pull(measure)
       do.call(c, lapply(g, function(x) x[[rf_method]]))
     })
+  avg_n <- dt$dtb %>% right_join(methods_df, by = c("representor", "distance", "cluster")) %>%
+    rowwise() %>%
+    mutate(n = ifelse(is.null(S), 0, NROW(S))) %>%
[…]

### 2023-10-30 gap.R

@@ -1,0 +1,71 @@
+args <- commandArgs(trailingOnly = TRUE)
+path <- args[[1]]
+bfmethod <- args[[2]]
+
+cl <- parallel::makeCluster(4)
+doParallel::registerDoParallel(cl)
+
+library(cluster)
+library(foreach)
+source("R/representator.R")
+
+nl2tibble <- function(x) {
+  output <- vector("list", 6)
+  names(output) <- c("representor", "cluster", "distance", "S", "rf", "other")
+  
+  for (i in seq_along(x)) {
+    for (n in names(x[[i]])) {
+      if (is.character(x[[i]][[n]])) {
+        output[[n]] <- append(output[[n]], x[[i]][[n]])
+      } else {
+        output[[n]] <- append(output[[n]], list(x[[i]][[n]]))
+      }
+    }
+  }
+  tibble::as_tibble(output)
+}
+
+cal_gap <- function(dt, representor) {
+  a <- clusGap(t(representor(dt, dr = dr)), pam, K.max = 50, B=50)
+  maxSE(a$Tab[,3], a$Tab[,4], method = "Tibs2001SEmax")
+}
+
+
+
+dt <- readRDS(sprintf("%s/data.rds", path))
+n <- NROW(dt$S)
+m <- NCOL(dt$S)
+print(sprintf("%s dataset has %s series and %s bottom series", path, n, m))
+time_length <- NROW(dt$data)
+forecast_horizon <- 12
+frequency <- 12
+batch_length <- time_length - 96 - forecast_horizon
+
+REPRESENTORS <- paste0(c("ts", "error", "ts.features", "error.features"), "-dr")
+
+for (batch in 0:batch_length) {
+  store_path <- sprintf("%s/%s/batch_%s.rds", path, bfmethod, batch)
+  data <- readRDS(store_path)
+  nl <- nl2tibble(data$nl)
+  print(sprintf("%s %s", Sys.time(), batch))
+  
+  drts <- list()
+  for (representor in REPRESENTORS) {
+    rsplit <- strsplit(representor, "-")[[1]]
+    dr <- rsplit[2] == "dr"
+    drts[[representor]] <- t(get(paste0("representator.", rsplit[1]))(data, dr=dr))
+  }
+
+  drtgaps <- foreach(drt = iterators::iter(drts), .packages = "cluster") %dopar% {
+    a <- clusGap(drt, pam, K.max = 50, B=50)
[…]

### 2023-11-20 manuscript/manuscript.tex
add manuscript draft

\documentclass[a4paper,review,12pt,authoryear]{elsarticle}

% \usepackage{natbib}
\usepackage{amsfonts,amsmath,bbm,bm,xcolor,booktabs,hyperref,amsthm}
\usepackage{geometry}
\usepackage{subfig}
\geometry{a4paper,scale=0.8}
\usepackage{setspace}
\setstretch{1.5}
\let\code=\texttt
\let\proglang=\textsf
\setcounter{MaxMatrixCols}{20}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue}

% ADDING LINENUMBERS FOR REVIEWING:
% \usepackage{lineno}

\begin{document}

\begin{frontmatter}

  \title{Constructing hierarchies}

  \begin{abstract}

  \end{abstract}

  \begin{keyword}
  Forecasting \sep
  Hierarchical time series \sep

  \end{keyword}

\end{frontmatter}

%\clearpage
\newpage
% \linenumbers

\section{Introduction}

\section{Methodology}
\label{sec:method}

\subsection{Constructing hierarchies by clustering}

\subsubsection{Time series representations}

\subsubsection{Distance measures}

\subsubsection{Clustering algorithms}
\label{sec:clustering}

\subsection{Constructing hierarchies randomly}

\section{Simulation}
\label{sec:simulation}

In this section, we demonstrate that hierarchies constructed by clustering may not outperform hierarchies constructed randomly even if there are true clusters in the bottom level.

\subsection{Simulation design}

\subsubsection*{Time series generation}

We assume the bottom-level time series follow an additive time series pattern with a data generating process described as follows:
\begin{equation}
    \label{simu:DGP}
    \begin{aligned}
    y_t &= l_t + s_t + e_t \\
    s_t &= s_{t\mod m} \\
    l_t &= a t + \varepsilon_t,
    \end{aligned}
\end{equation}
where $l_t$ represents the trend term which increases or decreases over time at a slope of $a$. The seasonal component, denoted by $s_t$, remains constant. Both $e_t$ and $\varepsilon_t$ are white noises.

We create $6$ clusters at the bottom level by adjusting the directions of the trend and patterns of the seasonal components.
The pattern settings for all clusters can be found in Table~\ref{table:simu_params}. For an increasing trend we set the slope $a$ to $0.001$, and for a decreasing trend, we set it to $-0.002$. The variances of the corresponding white noise $\varepsilon_t$ are set to $2.5\times 10^{-5}$ and $4.9\times 10^{-5}$. The terms ``Even'' and ``Odd'' indicate the position of the seasonal peak. For ``Even'' seasonality, the peaks are located at positions $2, 4, \dots, m$, and vice versa. The values for these seasonal peaks and troughs are uniformly drawn from $[2, 3]$ and $[0,1]$, respectively. The variance of $e_t$ is set to $0.25$. We generate monthly time series data with $20$ time series per cluster. Figure~\ref{fig:simu_emps} displays example time series from each cluster while Figure~\ref{fig:simu_pca} visualises these generated time series based on the first two principal components extracted from principal component analysis of the series.

\begin{table}
\caption{\label{table:simu_params}Parameter setting for all clusters in the simulation experiments.}
\centering
\begin{tabular}{lcccccc}\toprule
& Cluster 1 & Cluster 2 & Cluster 3 & Cluster 4 & Cluster 5 & Cluster 6 \\
Trend & Increase & Increase & None & None & Decrease & Decrease \\
Seasonality & Odd & Even & Odd & Even & Odd & Even  \\
    \bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/simu_example.pdf}
\caption{\label{fig:simu_emps}Example time series for each cluster in the simulation experiments.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{figures/simu_pca.pdf}
    \caption{\label{fig:simu_pca}Visualisation of the generated time series in the simulation experiments.}
\end{figure}

\subsubsection*{Hierarchies construction}

There are a total of $120$ bottom series and $1$ total series in the hierarchy, referred to as ``C0''. Additionally, we consider $4$ clustering approaches and $2$ forecast combination approaches. ``C1'' creates $6$ middle-level series according to the designed correct clusters. We merge clusters with the same trend pattern, resulting in $3$ clusters in the middle level, denoted by ``C2''. Similarly, we construct ``C3'' and ``C4'' based on the presence of the trend term and seasonal peak positions, resulting in $2$ and $3$ middle-level series, respectively. ``A1'' combines reconciled forecasts obtained from all four clustering approaches (``C1'' to ``C4'') using equal weights. By shuffling the bottom-level series within the hierarchy ``C1'', we can randomly generate different hierarchies with identical structure. ``A2'' combines reconciled forecasts from $10$ randomly constructed hierarchies using equal weights.

\subsubsection*{Forecasting}

We construct two scenarios by considering different base forecasting models. In the first scenario, exponential smoothing (ETS) is used to generate base forecasts for all time series in hierarchies. This simulates a situation where the time series themselves are inputs to the clustering algorithms.
In the second scenario, we use historic mean to generate base forecasts for bottom-level series and ETS for other time series in hierarchies, which simulates the case where in-sample errors are inputs to the clustering algorithms. We refer to these scenarios as ``clustering by time series'' and ``clustering by error'', respectively. To reconcile the base forecasts, we employ the minimum trace method with the shrinkage estimator (\citealp{wickramasuriyaOptimalForecastReconciliation2019}). The shrinkage estimator is effective at capturing the dependence structure within the forecast errors and has demonstrated superior perofrmance in various applications. For each series, we generate $144$ observations, and the last $12$ observations are reserved for evaluation purpose.

\subsection{Evaluation}
\label{sec:simu_eval}

The purpose of constructing middle-level series is to improve the forecast performance of the total-level and bottom-level series by leveraging the strength of these new series.
Therefore, we only evaluate the reconciled forecasts at total level and bottom level. 
To assess the accuracy of single time series, we use root mean squared error (RMSE) as our metric. 
The simulation is repeated $500$ times, resulting in a total of $500\times 121$ RMSEs for each approach. 
Multiple comparisons with the best (MCB) test is then applied to compute the average ranks of the $7$ approaches along with base forecasts and to determine whether the performance differences are statistically different (\citealp{koningM3CompetitionStatistical2005}).

\subsection{Results}
\label{sec:simu_res}

Figure~\ref{fig:simu_mcb} displays the MCB test results for the two scenarios. 
In both scenarios, most approaches perform better than the base forecasts and the original two-level hierarchy ``C0''. This suggests that constructing middle-level series generally improves forecast reconciliation performance.
In the ``clustering by time series'' scenario, the correct cluster ``C1'' ranks $4$th, indicates that optimal clusters do not guarantee optimal forecast reconciliation performance. 
On the other hand, ``C1'' ranks $1$st in the ``clustering by error'' scenarios. This highlights the importance of carefully selecting time series representations when constructing new middle levels using clustering algorithms.
The simple average of $10$ random hierarchies ranks $1$st in the first scenario and the simple average of $4$ clustering hierarchies ranks $3$rd in both scenarios, indicating the importance of forecast combination.

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/simu_mcb1.pdf}
    \includegraphics[width=0.45\textwidth]{figures/simu_mcb2.pdf}
    \caption{\label{fig:simu_mcb}Average ranks and 95\% confidence intervals based on the MCB Test for the $8$ approaches in the two scenarios of the simulation experiments. Left panel displays test results for the ``clustering by time series'' scenario and right panel displays test results for the ``clustering by error'' scenario.}
\end{figure}

\section{Empirical studies}

\subsection{Datasets}

We analyse two datasets in our empirical studies. The first dataset is the monthly Australian domestic tourism dataset, which provides visitor nights numbers from 1998 to 2016. The tourism demand of Australia is geographically disaggregated into $7$ states and territories, further divided into $27$ zones and $76$ regions. Additionally, each geographical series is divided by four travel purposes (\citealp{wickramasuriyaOptimalForecastReconciliation2019}). This dataset totally contains $555$ time series with $304$ at the bottom level.

The second dataset focuses on causes of death in the U.S., using the ICD 10 coding system. We obtain monthly cause-specific death counts from the Center for Disease Control and Prevention (CDC) for the period between 1999 and 2019. The coding system forms an unbalanced hierarchy with $137$ time series, out of which $113$ time series are in the bottom level. To consolidate data with suppressed values, we combine causes that share a parent cause and calculate their death counts by subtracting death counts of sibling causes from death counts of their parent cause. The final dataset includes $120$ time series with $98$ in the bottom level.

\subsection{Experiment design}

We focus on the performance of total-level series and bottom-level series, disregarding the multiple middle levels in the original hierarchies known as "natural hierarchies". The natural hierarchy is considered one way to construct middle-level series, similar to hierarchies created through clustering. However, we demonstrate that for the purpose of forecast performance, the natural hierarchy may not be the most effective hierarchical structure.

To construct middle levels using clustering, we combine four time series representations with two distance measures and two clustering algorithms. This results in twelve different construction approaches listed in Table~\ref{tab:emp_method}. In our experiments, dimension reduction of time series representations is crucial due to a small number of time series compared to variable dimensions (i.e., length of time series and number of time series features). Without dimension reduction, undesired clustering outcomes can occur due to the curse of dimensionality when using Euclidean distance. We employ principal component analysis on the time series representations and extract the first $k$ principal components that explain at least 80\% variance in the data. These transformed representations are then used as inputs for the clustering algorithms.

\begin{table}
\caption{\label{tab:emp_method} Hierarchy construction approaches used in empirical studies.}
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{ccccc}
    \toprule
    Approaches & Representation & Dimension reduction & Distance measure & Clustering algorithms  \\
    TS-MED & Time series & Yes & Euclidean & k-Medoids \\
    ER-MED & In-sample error & Yes & Euclidean & k-Medoids \\
    TSF-ME & Time series features & Yes & Euclidean & k-Medoids \\
    ERF-ME & In-sample error features & Yes & Euclidean & k-Medoids \\
    TS-HC & Time series & Yes & Euclidean & hierarchical clustering  \\ 
    ER-HC & In-sample error & Yes & Euclidean & hierarchical clustering  \\ 
    TSF-HC & Time series features & Yes & Euclidean & hierarchical clustering  \\ 
    ERF-HC & In-sample error features & Yes & Euclidean & hierarchical clustering  \\
    TS-MED-DTW & Time series & No & DTW & k-Medoids \\
    TS-HC-DTW & In-sample error & No & DTW & hierarchical clustering \\
    ER-MED-DTW & Time series & No & DTW & k-Medoids \\
    ER-HC-DTW & In-sample error & No & DTW & hierarchical clustering 
     \\\bottomrule
\end{tabular}}
\end{table}

Additionally, we consider three forecast combination approaches. In the first approach, we create one middle level with $15$ time series by randomly assigning bottom-level series as their children. We ensure that all the middle-level series have approximately an equal number of children. The choice of having $15$ middle-level series is arbitrary with the goal of creating a moderate number of groups, each containing a moderate number of series.
We repeat this process to create $50$ such hierarchies and combine their reconciled forecasts using equal weights. This approach is referred to as ``FC-R''.
In the second approach, we create $10$ new hierarchies by randomly shuffling the positions of bottom-level series in the natural hierarchy and combine their reconciled forecasts using equal weights. This approach is denoted by ``FC-N''. The third approach, labelled by ``FC-C'', involves equally-weighted combining the reconciled forecasts obtained from the $12$ hierarchies shown in Table~\ref{tab:emp_method}.

The time series features used in this experiment are calculated using the \texttt{tsfeatures} package (\citealp{tsfeatures}) for R. After filtering out the features that are constant across all series, $56$ features are reserved. The complete list of these feature can be found in Appendix. The k-Medoids and hierarchical clustering algorithms are implemented using the \texttt{cluster}(\citealp{cluster}) package for R. The base forecasts are generated using the automatic ETS models, which are then reconciled using the minimum trace method with shrinkage estimator.

We employ the rolling window strategy to evaluate the performance of different approaches for both datasets. We start with $96$ observations and fit the base forecasting models using the available data. Then we calculate time series representations and construct new hierarchies by clustering or randomness, and then forecast $12$ steps ahead. After that, the training set is increased by one observation and new forecasts are obtained. The procedure is repeated until the last $12$ observations are used for evaluation. Finally, we can obtain $121$ $12$-step-ahead forecasts for the tourism dataset and $144$ $12$-step-ahead forecasts for the mortality dataset. We compare the forecast performance of the $15$ approaches as well as the natural hierarchy, two-level hierarchy and base forecasts for both total-level and bottom-level series.

\subsection{Results}

Same as the evaluation measure described in Section~\ref{sec:simu_eval}, we combine the forecasts of total-level and bottom-level series across all evaluation windows and conduct the MCB test. The test results for the tourism dataset and mortality dataset are shown in Figure~\ref{fig:tourism_mcb} and Figure~\ref{fig:mortality_mcb}, respectively.

Most hierarchy construction approaches outperform both base forecasts and the two-level hierarchy, except for three approaches on the mortality dataset. For both datasets, the simple average of randomised natural hierarchies (``FC-N'') performs better than both natural hierarchy and all clustering-based hierarchies. Additionally, the simple average of $12$ clustering-based hierarchies (``FC-C'') significantly outperforms all other approaches. These results indicate that using a clustering-based hierarchy can improve forecast performance. However, forecast combination is even more beneficial, as evidenced by the high ranking of ``FC-N'' and ``FC-R''.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/tourism_mcb.pdf}
    \caption{\label{fig:tourism_mcb}Average ranks and 95\% confidence intervals based on the MCB Test for the $18$ approaches on the tourism dataset.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/mortality_mcb.pdf}
    \caption{\label{fig:mortality_mcb}Average ranks and 95\% confidence intervals based on the MCB Test for the $18$ approaches on the mortality dataset.}
\end{figure}

The approach based on hierarchical clustering outperforms the approach based on k-Medoids on the tourism dataset when using the same representation and distance metric, e.g., ``TSF-HC'' significantly ourperforms ``TSF-ME''. However, this is not consistently observed for every combination of representation and distance metric on the mortality dataset. We believe this discrepancy is due to different time series patterns at the bottom level of these two datasets.
In the case of the mortality dataset, we combine rare causes of death that have suppressed values and record death counts at a national level. As a result, most series at the bottom level exhibit strong seasonality and trend. On the other hand, in the tourism dataset, the tourism demand is disaggregated for both travel purposes and geographical regions. This leads to numerous bottom-level series with high volatility and many zeros, making them more challenging to forecast.
Therefore, having a hierarchy with more middle-level series can be more advantageous for reconciliation in the tourism dataset compared to the mortality dataset. Additionally, we suspect that the inferior performance of ``FC-R'' on the tourism dataset may be partly attributed to an insufficient number of middle-level series.

In most cases, the in-sample error representation outperforms the time series representation when using the same distance metric and clustering algorithms. However, this performance difference is not as significant as what was observed in Section~\ref{sec:simu_res}. Intuitively, hierarchies constructed based on clustering in-sample error should be similar to random hierarchies when all base models are correctly specified. However, due to ubiquitous model misspecification in practice, vague patterns emerge in the in-sample error, which leads to contradictory results.

\subsubsection*{Effect of number of random hierarchies}

In our previous experiments, we set the number of random hierarchies in ``FC-R'' and ``FC-N'' to $10$ for fair comparisons with ``FC-C''. However, we believe that increasing the number of random hierarchies could further enhance performance. In this subsection, we explore the effects of using 20 and 50 random hierarchies, referred to as ``FC-N-20'', ``FC-N-50'', ``FC-R-20'', and ``FC-R-50''. We compare these variations with ``FC-R'', ``FC-C'', and ``FC-N'' using the same evaluation procedure described earlier. The results from the MCB test are presented in Figure~\ref{fig:number_mcb}, where the left panel shows results on the tourism dataset and the right panel displays results on the mortality dataset.

Generally, we observe that forecast performance improves as the number of random hierarchies increases, except for ``FC-N-20'' and ``FC-N'' on the mortality dataset. Surprisingly, on the tourism dataset, ``FC-N-50'' performs slightly better than ``FC-C''. It is important to note that employing more random hierarchies comes at a cost of increased computational resources. Therefore, one must carefully consider trade-offs between efficiency and performance when making decisions.

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/tourism_number_mcb.pdf}
\includegraphics[width=0.45\textwidth]{figures/mortality_number_mcb.pdf}
\caption{\label{fig:number_mcb}Average ranks and 95\% confidence intervals based on the MCB Test of different number of random hierarchies on two datasets. Left and right panels display test results on tourism dataset and mortality dataset, respectively.}
\end{figure}

\section{Conclusion}
\label{sec:conclusion}

\section*{Acknowledgements}

\begingroup
\setstretch{1.15}
\bibliographystyle{agsm}
\bibliography{references.bib}
\endgroup

\end{document}

### 2023-11-20 R/run_base.R
manuscript

@@ -23,8 +23,8 @@ batch_length <- time_length - 96 - forecast_horizon
 #                   "ts.features", "error.features","ts.features", "error.features", "accuracy")
 # DISTANCES <- c(rep(c("euclidean", "manhattan", "dtw", "negcor", "cor", "uncorrelation"), 3),
 #                "euclidean", "euclidean", "manhattan", "manhattan", "euclidean")
-REPRESENTORS <- c("ts-dr", "error-dr", "ts.features-dr", "error.features-dr")
-DISTANCES <- rep("euclidean", 4)
+REPRESENTORS <- c("ts-dr", "error-dr", "ts.features-dr", "error.features-dr", "ts", "error")
+DISTANCES <- c(rep("euclidean", 4), "dtw", "dtw")
 
 # load dataset
 for (batch in 0:batch_length) {

### 2023-11-20 R/run_eval.R

@@ -48,9 +48,8 @@ hts.eval <- function(df, metrics, tts, bts) {
   # cluster average
   df_random$cluster <- c(df_random$cluster, "cluster-average")
   avg_rf <- list()
-  tmpdt <- df %>% filter(!startsWith(cluster, "random")) %>%
-    filter(cluster != "hcluster-random") %>%
-    filter(cluster != "natural", cluster != "", cluster != "base")
+  tmpdt <- df %>% filter(cluster %in% c("Kmedoids-dr", "hcluster-dr")) %>%
+    rbind(df %>% filter(distance == "dtw", representor %in% c("ts", "error")))
   for (rf_method in c("ols", "wlss", "wlsv", "mint")) {
     avg_rf_method <- 
       do.call(abind::abind, list(lapply(tmpdt$rf, function(x) x[[rf_method]]), along=0))

### 2023-11-20 R/run_nl.R

@@ -24,13 +24,16 @@ REPRESENTORS <- c("ts-dr", "error-dr", "ts.features-dr", "error.features-dr")
 DISTANCES <- rep("euclidean", 4)
 
 
+REPRESENTORS2 <- c("ts", "error")
+DISTANCES2 <- rep("dtw", 2)
+
 # load dataset
 for (batch in 0:batch_length) {
   store_path <- sprintf("%s/%s/batch_%s.rds", path, bfmethod, batch)
   data <- readRDS(store_path)
   
   for (i in seq_along(REPRESENTORS)) {
-    print(sprintf("%s KMedoids %s * %s ", Sys.time(), REPRESENTORS[i], DISTANCES[i]))
+    print(sprintf("%s KMedoids dr %s * %s ", Sys.time(), REPRESENTORS[i], DISTANCES[i]))
     nl <- build_level(hts = data, representor = REPRESENTORS[i],
                       distance = DISTANCES[i],
                       cluster = cluster.kmedoids,
@@ -39,8 +42,18 @@ for (batch in 0:batch_length) {
                    other = nl$info)
   }
   
-  # print(paste0(Sys.time(), " hierarchical clustering ..."))
+  for (i in seq_along(REPRESENTORS2)) {
+    print(sprintf("%s KMedoids %s * %s ", Sys.time(), REPRESENTORS2[i], DISTANCES2[i]))
+    nl <- build_level(hts = data, representor = REPRESENTORS2[i],
+                      distance = DISTANCES2[i],
+                      cluster = cluster.kmedoids,
+                      n_clusters = 1:50)
+    data <- add_nl(data, nl$S, REPRESENTORS2[i], DISTANCES2[i], "Kmedoids",
+                   other = nl$info)
+  }
   
+  
+  # hierarchical clustering dimension reduction
   for (i in seq_along(REPRESENTORS)) {
     nl <- build_level(hts = data, representor=REPRESENTORS[i],
                       distance = DISTANCES[i],
@@ -48,42 +61,21 @@ for (batch in 0:batch_length) {
                       method = "ward")[[1]]
     data <- add_nl(data, nl, REPRESENTORS[i], DISTANCES[i], "hcluster-dr")
   }
+
+  # hierarchical clustering dtw
   for (i in 1:50) {
     data <- add_nl(data, nl[,sample(NCOL(nl))], "", "", "hcluster-random")
   }
-  # 
-  # print(paste0(Sys.time(), " nested Kmedoids 2 ..."))
[…]

### 2023-11-20 R/run_nlr.R

@@ -27,7 +27,7 @@ for (batch in 0:batch_length) {
   
   for (i in 1:50) {
     for (ncluster in 5:15) {
-      S <- cluster.random(data$distance$ts$euclidean, n_clusters = ncluster)[[1]]
+      S <- cluster.random(data$distance$ts$dtw, n_clusters = ncluster)[[1]]
       data <- add_nl(data, S, "", "", paste0("random-", ncluster))
     }
   }

### 2023-11-20 R/run_nls.R

@@ -47,7 +47,7 @@ rank_compare <- function(dt, methods_df = NULL, measure="rmse", rf_method = "min
     }
     methods_dr <- dt$dtb %>% select(representor, distance, cluster) %>% filter(endsWith(cluster, "-dr")) %>% unique()
     methods_natural <- dt$dtb %>% select(representor, distance, cluster) %>%
-      filter(cluster %in% c("base", "", "natural")) %>% unique()
+      filter(cluster %in% c("base", "", "natural", "cluster-average")) %>% unique()
     methods_df <- Kmedoids_clusterN(dt) %>% filter(`0` != length(dt$base$rmse) | is.na(`0`)) %>% 
       select(representor, distance) %>% mutate(cluster = "Kmedoids") %>%
       rbind(methods_dr, methods_random, methods_natural)

### 2023-11-20 R/summary.R

@@ -1,0 +1,111 @@
+path <- "tourism"
+bfmethod <- "ets"
+dt <- readRDS(sprintf("%s/%s/eval.rds", path, bfmethod))
+dt_orig <- readRDS(sprintf("%s/%s/batch_0.rds", path, bfmethod))
+dt_names <- readRDS(sprintf("%s/names.rds", path))
+source("R/run_nls.R")
+library(dplyr)
+library(ggplot2)
+
+rank_compare_summary <- function(dt) {
+  
+  methods_random <- dt$dtb %>% select(representor, distance, cluster) %>% 
+    filter(cluster %in% c("random-15-10", "random-natural-10")) %>% 
+    unique()
+  methods_random$name <- ifelse(methods_random$cluster == "random-15-10", "FC-R", "FC-N")
+  
+  methods_dr <- dt$dtb %>% select(representor, distance, cluster) %>% 
+    filter(endsWith(cluster, "-dr")) %>% unique()
+  
+  switch_name <- function(x){
+    x <- strsplit(x, "-")[[1]][1]
+    switch(x, ts="TS", ts.features="TSF", error="ER", error.features = "ERF")
+  }
+  
+  methods_dr$name <- paste0(sapply(methods_dr$representor, switch_name), "-",
+                            ifelse(methods_dr$cluster == "hcluster-dr", "HC", "ME"))
+  methods_dtw <- dt$dtb %>% select(representor, distance, cluster) %>% 
+    filter(distance == "dtw", representor %in% c("ts", "error")) %>% unique()
+  methods_dtw$name <- paste0(ifelse(methods_dtw$representor == "ts", "TS", "ER"), "-",
+                             ifelse(methods_dtw$cluster == "hcluster", "HC", "ME"), "-DTW")
+  methods_natural <- dt$dtb %>% select(representor, distance, cluster) %>%
+    filter(cluster %in% c("base", "", "natural", "cluster-average")) %>% unique()
+  methods_natural$name <- ifelse(methods_natural$cluster == "base", "BASE",
+                                 ifelse(methods_natural$cluster == "", "two-level",
+                                        ifelse(methods_natural$cluster == "natural", "natural", "FC-C")))
+  
+  methods_df <- rbind(methods_random, methods_dr, methods_dtw, methods_natural)
+
[…]

### 2023-11-20 data/dataprocessing.R

@@ -260,12 +260,12 @@ colnames(S)[NCOL(S)] <- "Combine-GR113-097"
 rownames(S)[NROW(S)] <- "Combine-GR113-097"
 
 
-write.csv(output, "data/mortality.csv", row.names = FALSE)
-write.csv(S, "data/S.csv")
-
-
-
-
+S <- rbind(S[!(rownames(S) %in% colnames(S)),],
+           S[colnames(S),])
+S <- rbind(rep(1, 98), S)
+rownames(S)[1] <- "Total"
+output <- as.matrix(output) %*% (t(S))
+saveRDS(list(S=S, data=output), "mortality/data.rds")
 
 
 

### 2023-11-20 simulation/simu2.R

@@ -6,21 +6,21 @@ source("R/reconciliation.R")
 
 set.seed(43)
 
-cl <- parallel::makeCluster(4)
+cl <- parallel::makeCluster(3)
 doParallel::registerDoParallel(cl)
 
 simulate.season <- function(freq = 12, length = 12, nseries = 50, oppsite.season = TRUE, allow.trend = TRUE, opposite.trend = FALSE) {
   seasons <- do.call(rbind,
-          lapply(1:nseries, function(x) {
-            a <- c(runif(freq / 2, 0, 1), runif(freq / 2, 2, 3))
-            od <- rep(1:(freq/2), each = 2)
-            if (oppsite.season) {
-              od[seq(2, freq, 2)] <- od[seq(2, freq, 2)] + freq/2
-            } else {
-              od[seq(1, freq, 2)] <- od[seq(1, freq, 2)] + freq/2
-            }
-            rep(a[od], length * length / freq)
-          }))
+                     lapply(1:nseries, function(x) {
+                       a <- c(runif(freq / 2, 0, 1), runif(freq / 2, 2, 3))
+                       od <- rep(1:(freq/2), each = 2)
+                       if (oppsite.season) {
+                         od[seq(2, freq, 2)] <- od[seq(2, freq, 2)] + freq/2
+                       } else {
+                         od[seq(1, freq, 2)] <- od[seq(1, freq, 2)] + freq/2
+                       }
+                       rep(a[od], length * length / freq)
+                     }))
   
   trend <- 0
   if (allow.trend) {
@@ -38,7 +38,7 @@ simulate.season <- function(freq = 12, length = 12, nseries = 50, oppsite.season
 
 
 simulate.forecast <- function(series) {
-
+  
   bts <- t(series[,1:(NCOL(series) - 12)])
   tts <- t(series[,(NCOL(series) - 11):NCOL(series)])
   m <- NROW(series)
@@ -60,15 +60,20 @@ simulate.forecast <- function(series) {
   nl[[53]] <- grp2S(rep(c(1,2, 1, 2, 1, 2), each=20))
   nl[[54]] <- grp2S(rep(c(1,2, 1), each=40))
   
-  all_S <- rbind(rep(1,m), do.call(rbind, nl), diag(m))
+  all_S <- rbind(rep(1,m), do.call(rbind, nl))
   allts <- bts %*% t(all_S)
[…]

### 2023-11-20 simulation/summary.R

@@ -1,6 +1,10 @@
 library(dplyr)
 library(tidyr)
-dt <- readRDS("simulation/simulation.rds")
+library(ggplot2)
+
+setting <- 2
+
+dt <- readRDS(sprintf("simulation/simulation%s.rds", setting))
 
 acc <- dt$acc %>%
   nest(values = c("batch", "rmse")) %>%
@@ -9,41 +13,44 @@ acc <- dt$acc %>%
     do.call(c, x$rmse)
   })
 
+acc$methods <- c("C0", "C1", "A2", "random-20", "random-50", "C2", "C4", "C3", "A1", "Base")
+acc <- acc %>% filter(!startsWith(methods, "random"))
+
 acc_mat <- do.call(cbind, acc$values) %>%
   `colnames<-`(acc$methods)
 
 
 
-FREQUENCIES <- c(12, 4, 12, 4)
+
 visualizeSimSeries <- function(series) {
-  par(mfrow = c(2,2))
-  grpidx <- c("1", "2", "3", "4")
-  for (i in 0:3) {
-    plot(ts(series[20*i+1,], frequency = FREQUENCIES[i+1]), ylab = "series", main = paste0("group", grpidx[i+1]))
+  par(mfrow = c(3,2))
+  grpidx <- c("1", "2", "3", "4", "5", "6")
+  for (i in 0:5) {
+    plot(ts(series[20*i+1,], frequency = 12), ylab = "series", main = paste0("Cluster", grpidx[i+1]))
   }
   par(mfrow = c(1,1))
 }
 
 visualizeSimPCA <- function(series) {
   pca <- prcomp(series, scale.=TRUE)
-  grpidx <- c("1", "2", "3", "4")
+  grpidx <- c("1", "2", "3", "4", "5", "6")
   grps <- rep(grpidx, each=20)
   ggplot(mapping = aes(x = pca$x[,1], y=pca$x[,2], color = grps, group=grps)) +
     geom_point() +
     xlab("Principal Component 1") +
     ylab("Principal Component 2") +
-    labs(color = "groups")
+    labs(color = "Clusters")
 }
 
-pdf("simulation/mcb.pdf", width = 10, height = 8)
+pdf(sprintf("manuscript/figures/simu_mcb%s.pdf", setting), width = 5, height = 5)
 tsutils::nemenyi(acc_mat, plottype = "vmcb")
 dev.off()
 
-pdf("simulation/PCA.pdf", width = 8, height = 8)
[…]

### 2023-11-24 manuscript/manuscript.tex
update

@@
 
+\subsection{Framework}
+
+1. construct hierarchies based on historic observations
+2. forecast and reconciliation
+3. evaluation
+
 \subsection{Constructing hierarchies by clustering}
 
-\subsubsection{Time series representations}
+\cite{aghabozorgiTimeseriesClusteringDecade2015a} summarised the four components of time series clustering, including time series representations, distance measures, clustering algorithms and evaluation.
+In our framework, the first three components are involved in the constructing hierarchies procedure.
+The last component includes evaluation of reconciled forecasts of the original hierarchy.
 
-\subsubsection{Distance measures}
+\subsubsection*{Time series representations}
 
-\subsubsection{Clustering algorithms}
+Time-series representations represent raw time series in another space through techniques like feature extraction or dimensionality reduction.
+By utilising diverse time series representations, we are able to obtain distinct clusters which offer varied perspectives on the same dataset.
+Despite the absence of the theoretical evidence regarding how groups in hierarchical time series affect forecast reconciliation performance, we seek to explore multiple time series representations and discern potential correlations between hierarchical structure and the efficacy of forecast reconciliation.
+
+Considering the impracticality of exploring every conceivable time series representation, we focus on four key ones: raw time series, in-sample error, features of time series, and features of in-sample error.
+The inclusion of raw time series is motivated by its simplicity and broad applicability.
+A crucial element contributing to the success of the minimum trace method proposed by \cite{wickramasuriyaOptimalForecastReconciliation2019} lies in estimating the covariance matrix of base forecast errors based on in-sample fit error.
+Hence, we consider in-sample error as a representation to examine how the structure within the error series influences reconciliation performance.
+Notably, to the best of our knowledge, we are the first to utilise in-sample error as a time series representation in the context of forecast reconciliation literature.
+The time series and in-sample error representations are standardised on a per-series basis to eliminate the impact of scale variations.
+Features, widely employed in capturing time series characteristics across literature, play a pivotal role in various time series applications, including clustering (\citealp{tianoFeatTSFeaturebasedTime2021}) and forecasting (\citealp{wangUncertaintyEstimationFeaturebased2022, liFeaturebasedIntermittentDemand2023}).
+In our exploration, we incorporate features of both time series and in-sample fit error as representations.
+These representations allow us to glean insights into the diverse aspects of hierarchical time series data and enhance our understanding of how different structures contribute to the forecast reconciliation performance.
+
+Given the limited number of time series in comparison to the variable dimensions (i.e., the length of time series and the number of time series features) within the hierarchical time series in our applications, it becomes imperative to perform dimension reduction on the aforementioned representations.
+Failure to undertake dimension reduction may lead to undesirable clustering outcomes due to the challenges posed by the curse of dimensionality.
+We conduct principal component analysis and extract the first few principal components that explain at least $80$\% variance within the data.
+
+\subsubsection*{Distance measures}
+
+Distance measures assess the similarity between two series.
+
+euclidean distance
+
+dynamic time warping
+
+\subsubsection*{Clustering algorithms}
 \label{sec:clustering}
 
+k-Medoids
+
+hierarchical clustering
+
 \subsection{Constructing hierarchies randomly}
+
+pure random
+
+random based on specific structure
+
+\subsection{Forecast combination}
 
@@
 This results in twelve different construction approaches listed in Table~\ref{tab:emp_method}.
-In our experiments, dimension reduction of time series representations is crucial due to a small number of time series compared to variable dimensions (i.e., length of time series and number of time series features).
-Without dimension reduction, undesired clustering outcomes can occur due to the curse of dimensionality when using Euclidean distance.
-We employ principal component analysis on the time series representations and extract the first $k$ principal components that explain at least 80\% variance in the data.
-These transformed representations are then used as inputs for the clustering algorithms.
 

### 2023-11-26 manuscript/manuscript.tex
update

@@
 
-Given the limited number of time series in comparison to the variable dimensions (i.e., the length of time series and the number of time series features) within the hierarchical time series in our applications, it becomes imperative to perform dimension reduction on the aforementioned representations.
-Failure to undertake dimension reduction may lead to undesirable clustering outcomes due to the challenges posed by the curse of dimensionality.
-We conduct principal component analysis and extract the first few principal components that explain at least $80$\% variance within the data.
-
 \subsubsection*{Distance measures}
 
-Distance measures assess the similarity between two series.
+Distance measures serve as crucial tools for assessing the similarity between two series, forming the foundation for clustering algorithms to detect clusters within datasets.
+In the realm of time series clustering literature, we consider two widely applied distance measures: Euclidean distance and dynamic time warping (DTW) (\citealp{warrenliaoClusteringTimeSeries2005}).
 
-euclidean distance
+Given the limited number of time series in comparison to the variable dimensions (i.e., the length of time series and the number of time series features) within hierarchical time series in our applications, dimension reduction on the aforementioned representations becomes imperative when employing Euclidean distance.
+Failure to undertake dimension reduction may result in undesirable clustering outcomes due to the challenges posed by the curse of dimensionality.
+To address this, we perform principal component analysis, extracting the first few principal components that collectively explain at least 80\% of the variance within the data.
 
-dynamic time warping
+In contrast, DTW (\citealp{sakoeDynamicProgrammingAlgorithm1978}), demonstrates reduced sensitivity to the curse of dimensionality.
+Unlike the one-to-one point comparison inherent in Euclidean distance, DTW accommodates time series of varying lengths through many-to-one comparisons.
+This adaptive approach allows for the recognition of time series with similar shapes, even in the presence of signal transformations such as shifting and/or scaling.
 
@@
 
-k-Medoids
+Regarding clustering algorithms, we consider two common approaches, k-Medoids and agglomerative hierarchical clustering.
+K-Medoids algorithm is one of the classical partitioning clustering algorithms.
+The idea behind partitioning clustering is the minimisation of the total distance between all samples in a cluster from their cluster centres.
+We consider k-Medoids instead of the well known k-Means because k-Means use mean vector of samples within a cluster as cluster centre, which is not trivial when using DTW distance measure.
+In contrast, k-Medoids select one of the samples in the cluster as cluster centre.
+We use the k-Meodoids variants partitioning around medoids (PAM, \citealp{PartitioningMedoidsProgram1990}).
+The most important parameter for k-Medoids algorithm is the number of cluster.
+We follow the suggestion of \cite{PartitioningMedoidsProgram1990} to choose the optimal number of cluster by average silhouette width (ASW), which is a popular cluster validation index to estimate the number of clusters.
+Given a clustering $\mathcal{C}$, the silhouette width for the $i$th sample is calculated as
+\[
+  SW(i) = \frac{b(i)-a(i)}{\max\{a(i), b(i)\}},  
+\]
+where $a(i)$ is the average distance of $i$the sample to samples in the cluster to which it is assigned, and $b(i)$ is the average distance of $i$th sample to the samples in the nearest cluster it is not assigned.
+A large value of silhouette means that the corresponding sample is much closer to the samples to the samples in its own cluster than to the neighbouring one.
+Silhouette width is zero for the sample which is the only sample in its cluster.
+ASW is calculated as the average of silhouette widths of all samples.
+By iterating over all possible number of clusters, we choose the clustering result $\mathcal{C}$ that maximises the ASW as the optimal result.
+One drawback of this approach is that ASW does not exist when there is only one cluster, meaning that it can not determine whether there are well separated clusters or not.
+Gap statistics (\citealp{tibshiraniEstimatingNumberClusters2002}) can address this issue, but it can not be used with DTW.
 

### 2023-12-02 manuscript/figures/aggcluster_random.tex
update

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{positioning}
\usepackage{amsmath}

\begin{document}
\begin{tikzpicture}[node distance=2cm]

    \node(A1)[draw, circle, minimum size=0.2cm]{};
    \node(B1)[draw, circle, minimum size=0.2cm, below left=0.5cm of A1]{};

    \node(D1)[draw, circle, minimum size=0.2cm, below left=0.5cm of B1]{};
    \node(F1)[draw, circle, minimum size=0.2cm, below left=0.5cm of D1]{1};
    \node(G1)[draw, circle, minimum size=0.2cm, below right=0.5cm of D1]{2};
    \node(E1)[draw, circle, minimum size=0.2cm, right=0.8727922cm of G1]{3};
    \node(C1)[draw, circle, minimum size=0.2cm, right=0.8727922cm of E1]{4};

    \draw (A1) -- (B1) -- (D1) -- (F1);
    \draw (D1) -- (G1);
    \draw (B1) -- (E1);
    \draw (A1) -- (C1);

    \node(A)[draw, circle, minimum size=0.2cm, right=5cm of A1]{};
    \node(B)[draw, circle, minimum size=0.2cm, below left=0.5cm of A]{};

    \node(D)[draw, circle, minimum size=0.2cm, below left=0.5cm of B]{};
    \node(F)[draw, circle, minimum size=0.2cm, below left=0.5cm of D]{4};
    \node(G)[draw, circle, minimum size=0.2cm, below right=0.5cm of D]{3};
    \node(E)[draw, circle, minimum size=0.2cm, right=0.8727922cm of G]{1};
    \node(C)[draw, circle, minimum size=0.2cm, right=0.8727922cm of E]{2};

    \draw (A) -- (B) -- (D) -- (F);
    \draw (D) -- (G);
    \draw (B) -- (E);
    \draw (A) -- (C);

\end{tikzpicture}
\end{document}

### 2023-12-02 manuscript/figures/pamcluster.tex
update

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{positioning}
\usepackage{amsmath}

\begin{document}
\begin{tikzpicture}[node distance=2cm]

    % \node(start)[startstop]{Start};
    \node(A)[draw, circle, minimum size=0.2cm]{};
    \node(B)[draw, circle, minimum size=0.2cm, below left=0.9cm of A]{};

    \node(D)[draw, circle, minimum size=0.2cm, below right=0.9cm of A]{};
    \node(F)[draw, circle, minimum size=0.2cm, below left=0.5cm of B]{};
    \node(G)[draw, circle, minimum size=0.2cm, below right=0.5cm of B]{};
    \node(E)[draw, circle, minimum size=0.2cm, below left =0.5cm of D]{};
    \node(C)[draw, circle, minimum size=0.2cm, below right=0.5cm of D]{};

    \draw (A) -- (B) -- (G);
    \draw (A) -- (D);
    \draw (B) -- (F);

    \draw (D) -- (E);
    \draw (D) -- (C);

\end{tikzpicture}
\end{document}

### 2023-12-02 manuscript/manuscript.tex
update

@@
 
-\subsection{Constructing hierarchies by clustering}
+\subsection{Cluster hierarchies}
 
@@
 
-Regarding clustering algorithms, we consider two common approaches, k-Medoids and agglomerative hierarchical clustering.
-K-Medoids algorithm is one of the classical partitioning clustering algorithms.
-The idea behind partitioning clustering is the minimisation of the total distance between all samples in a cluster from their cluster centres.
-We consider k-Medoids instead of the well known k-Means because k-Means use mean vector of samples within a cluster as cluster centre, which is not trivial when using DTW distance measure.
-In contrast, k-Medoids select one of the samples in the cluster as cluster centre.
-We use the k-Meodoids variants partitioning around medoids (PAM, \citealp{PartitioningMedoidsProgram1990}).
-The most important parameter for k-Medoids algorithm is the number of cluster.
-We follow the suggestion of \cite{PartitioningMedoidsProgram1990} to choose the optimal number of cluster by average silhouette width (ASW), which is a popular cluster validation index to estimate the number of clusters.
+Regarding clustering algorithms, we focus on two prevalent approaches, k-Medoids and agglomerative hierarchical clustering.
+The k-Medoids algorithm, a classical partitioning clustering method, aims to minimise the total distance between all samples within a cluster and their respective cluster centres.
+Unlike k-Means, which employs the mean vector of samples as the cluster centre, k-Medoids selects one sample within the cluster as the centre. 
+Specifically, we adopt the k-Medoids variant, partitioning around medoids (PAM, \citealp{PartitioningMedoidsProgram1990}).
+Following the recommendation of \cite{PartitioningMedoidsProgram1990}, we determine the optimal number of cluster using the average silhouette width (ASW).
+ASW, a popular cluster validation index, assesses the quality of clustering results by measuring the proximity of samples within a cluster compared to neighbouring clusters.
 Given a clustering $\mathcal{C}$, the silhouette width for the $i$th sample is calculated as 
@@
 \]
-where $a(i)$ is the average distance of $i$the sample to samples in the cluster to which it is assigned, and $b(i)$ is the average distance of $i$th sample to the samples in the nearest cluster it is not assigned.
-A large value of silhouette means that the corresponding sample is much closer to the samples to the samples in its own cluster than to the neighbouring one.
-Silhouette width is zero for the sample which is the only sample in its cluster.
-ASW is calculated as the average of silhouette widths of all samples.
-By iterating over all possible number of clusters, we choose the clustering result $\mathcal{C}$ that maximises the ASW as the optimal result.
-One drawback of this approach is that ASW does not exist when there is only one cluster, meaning that it can not determine whether there are well separated clusters or not.
-Gap statistics (\citealp{tibshiraniEstimatingNumberClusters2002}) can address this issue, but it can not be used with DTW.
+where $a(i)$ represents the average distance of the $i$th sample to others in the same cluster, and $b(i)$ is the average distance to samples in the nearest cluster it is not assigned to.
+A higher silhouette width indicates greater proximity to samples within the same cluster than to those in neighbouring clusters.
+The ASW is the average of silhouette widths across all samples.
+We select the clustering result $\mathcal{C}$ that maximises the ASW by iterating over all possible numbers of clusters.
+However, an inherent limitation of ASW is its inexistence when there is only one cluster, making it challenging to discern the presence of well-separated clusters.
+Gap statistics (\citealp{tibshiraniEstimatingNumberClusters2002}) can be used to address this limitation, but it is incompatible with DTW.
 
-hierarchical clustering
+Agglomerative hierarchical clustering begins by considering each sample as a cluster, and then gradually merges clusters until all samples forms a single cluster. 
+This process results in a binary hierarchical tree with $2n-1$ nodes.
+We employ Ward's linkage (\citealp{murtaghWardHierarchicalAgglomerative2014a}) to merge clusters, minimising the increase in within-cluster variances at each step.
+Subsequently, we construct the middle-level series from the clustering tree.
 
-\subsection{Constructing hierarchies randomly}
+Figure~\ref{fig:cluster_example} illustrates two example hierarchies generated by these clustering algorithms, showcasing their distinct behaviours. 
+The primary discrepancy between the two algorithms lies in two aspects.
+Firstly, k-Medoids constructs a hierarchy with a single middle level, while hierarchical clustering generates multiple middle levels with a nested structure.
+Secondly, k-Medoids constructs a hierarchy with the same number of series as the optimal number of clusters, whereas hierarchical clustering produces multiple middle levels with $n-2$ series.
+These distinctions become particularly relevant when the number of bottom-level series is substantial.
+We aim to investigate how these structural differences influence the performance of forecast reconciliation.
 
-pure random
+\begin{figure}
+    \centering
+    \includegraphics[width=0.3\textwidth]{figures/pamcluster.pdf}
+    \hspace{1cm}
+    \includegraphics[width=0.3\textwidth]{figures/aggcluster.pdf}
+    \caption{\label{fig:cluster_example}Example clustering results of two clustering algorithms.
+Left panel displays example for k-Medoids algorithm, and right panel displays example for agglomerative hierarchical algorithm.}
+\end{figure}
 
-random based on specific structure
+\subsection{Random hierarchies}
 
-\subsection{Forecast combination}
+A fundamental question arises concerning the factor that plays the most crucial role if the constructed hierarchies resulting from clustering significantly enhance forecast performance.
+One plausible argument posits that the improved forecasting performance should attribute to the clustering procedure, which organises series with similar features into groups.
+This organisation creates middle-level series that are hypothesised to be easier to forecast, leading to improved reconciled forecasts.
+However, this logical chain is not readily traceable for two main reasons.
+Firstly, groups of similar time series do not inherently translate to superior middle-level forecasts.
+Secondly, existing literature lacks systematic theory regarding how the pattern of the variance matrix of base forecast errors influences the performance of reconciled forecasts.
+The complexities introduced by uncertainties in clustering, base forecasting model estimation, and variance matrix estimation compound the challenge of drawing definitive conclusions (\citealp{pritulargaStochasticCoherencyForecast2021}).
+
+An alternative explanation for this question posits that the enhancement is primarily a result of an increased number of middle-level series.
+The perspective of forecast reconciliation as a form of forecast combination (\citealp{hollymanUnderstandingForecastReconciliation2021}) supports this notion.
+As new hierarchies are constructed, the reconciled forecasts are combinations of a greater number of base forecasts, leading to improved reconciled forecasts.
+
+To systematically explore these two explanations, we propose two randomised approaches to hierarchy construction.
+Constructing hierarchies randomly allows us to eliminate the influence of clustering and focus specifically on investigating the second explanation.
+The first approach generates hierarchies akin to those produced by k-Medoids clustering algorithms.
+Given $m$ bottom-level series and a number $k$, we create $\lceil\frac{m}{k}\rceil$ groups.
+The first $\lfloor\frac{m}{k}\rfloor$ groups each contain $k$ series, and the last group accommodates $n - k\lfloor\frac{n}{k}\rfloor$ series.
+The bottom-level series are then randomly assigned to these groups.
+This approach offers a straightforward way to construct random hierarchies, which is proposed to investigate the effect of new middle-level series and verify the second explanation.
+
+The second approach involves generating random hierarchies based on a given hierarchy, such as one constructed from clustering algorithms.
+Given a hierarchy tree, it creates new hierarchies by randomly permuting the leaf nodes.
+In other words, it shuffles the columns of $A$ matrix of the given hierarchy.
+This method yields a new random hierarchy with an identical structure, enabling to verify both hypothesises simultaneously.
+If the randomised version of a hierarchy significantly outperforms itself, it suggests that the second explanation holds greater importance that the first, and vice versa.
+Figure~\ref{fig:aggcluster_random} shows an example of this approach.
+The left hierarchy is the hierarchy shown in Figure~\ref{fig:cluster_example} obtained from agglomerative hierarchical algorithm.
+The right hierarchy is an example of randomisation of the left hierarchy.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/aggcluster_random.pdf}
+    \caption{\label{fig:aggcluster_random}Examples of randomisation of a given hierarchy. Right hierarchy is obtained by shuffling the leaf nodes of left hierarchy.}
+\end{figure}
+
+\subsection{Combination hierarchies}
+
+Randomness technique is usually combined with forecast combination approach in the literature.
+For example, \cite{petropoulosExploringSourcesUncertainty2018a} illustrates the effectiveness of bootstrapping aggregation for time series forecasting which combines forecast obtained from bootstrapped versions of the time series.
+Therefore, we propose the ``combination hierarchies'' which utilises multiple hierarchies to obtain the reconciled forecasts.
+The hierarchies in the pool can be random hierarchies or cluster hierarchies.
+There are two straightforward approaches to combine multiple hierarchies.
+The first one is to combine their structure.
 

### 2023-12-15 manuscript/manuscript.tex
finished manuscript

--- 2023-11-24 manuscript/manuscript.tex
@@
 
-  \title{Constructing hierarchies}
+  \title{On the performance of hierarchy construction: impacts of structure and clustering}
+
+  \author[label1]{Bohan Zhang\corref{cor1}}
+  \address[label1]{School of Economics and Management, Beihang University, Beijing, China}
+  \ead{zhangbohan@buaa.edu.cn}
+  \cortext[cor1]{Corresponding author.}
+  \author[label2]{Anastasios Panagiotelis}
+  \address[label2]{The University of Sydney Business School, NSW 2006, Australia}
+  \author[label3]{Han Li}
+  \address[label3]{Centre for Actuarial Studies, Department of Economics, The University of Melbourne, Australia}
 
   \begin{abstract}
+
+    Forecast reconciliation has attracted significant research interest in recent years, with most studies relying on pre-defined hierarchies based on time series metadata.
+With the goal of forecast performance in mind, we extend the existing literature on clustering-based reconciliation approach by proposing a novel framework based on hierarchy construction approaches.
+This framework offers three variants: cluster hierarchies, random hierarchies, and combination hierarchies.
+Utilizing the proposed approaches, we investigate the individual contributions of two primary factors, namely clustering and enriched structure, to the performance of forecast reconciliation.
+Through a simulation study and experiments on two real-world datasets, we demonstrate the practical efficacy of hierarchy construction approaches.
+Our findings provide new insights into the dynamics between clustering and enriched structure, significantly enriching our understanding of forecast reconciliation.
 
@@
   Hierarchical time series \sep
-
+  Clustering \sep
+  Hierarchy construction \sep
+  Forecast combination
   \end{keyword}
@@
 
+Hierarchical time series (HTS) has various important applications ranging from supply chain management (\citealp{syntetosSupplyChainForecasting2016}) to tourism (\citealp{kourentzesCrosstemporalCoherentForecasts2019}), electrical load (\citealp{jeonProbabilisticForecastReconciliation2019}), retail demand (\citealp{makridakisM5AccuracyCompetition2022}) forecasting.
+In recent decades, there has been an increasing interest in hierarchical forecasting, primarily driven by the success of the optimal reconciliation framework (\citealp{hyndmanOptimalCombinationForecasts2011,wickramasuriyaOptimalForecastReconciliation2019, panagiotelisProbabilisticForecastReconciliation2023}).
+Unlike the traditional approaches such as bottom-up and top-down, which generate coherent forecasts using forecasts from a single level, the reconciliation framework optimally combine base forecasts of all series in HTS.
+Numerous case studies in the literature demonstrate that reconciliation approaches not only yield coherent forecasts but also enhance overall forecast performance (\citealp{AthanasopoulosForecastReconciliationReview2023}).
+
+The primary objective of hierarchical forecasting is to produce coherent forecasts for the series within a given HTS, which we refer to as \textit{original hierarchy}, ensuring that decision-makers at different levels of the hierarchy can analyze and make informed decisions based on aligned expectations for the future.
+Consequently, the majority of existing research in forecast reconciliation literature experiments on the original hierarchy, which is typically formed according to inherent attributes of the bottom-level series, such as geographical location, gender, product category, travel purpose, and others.
+This limitation is evident in the absence of any discussion regarding cluster-based approaches in the recent comprehensive review of forecast reconciliation by \cite{AthanasopoulosForecastReconciliationReview2023}.
+However, the question arises as to whether the original hierarchy is the optimal structure and whether better structure can be constructed when pursuing superior forecast performance.
+This inquiry serves as the key motivation behind the investigation presented in this paper.
+
+Two observations have been consistently demonstrated in empirical studies on forecast reconciliation.
+First, the accuracy of base forecasts, which are influenced by the individual time series characteristics within the hierarchy, critically affects the overall performance of reconciliation.
+Second, performance improvements achieved through reconciliation do not occur across all levels of the hierarchy.
+In fact, gains for some series often come at the expense of others.
+These observations have motivated researchers to explore the idea of enriching the original hierarchy by introducing new time series via clustering analysis.
+The rationale behind this approach lies in grouping time series with similar patterns together, thereby creating parent time series with stronger signals and consequently, improved forecastability.
+Ideally, the original series can ``borrow strength'' from the newly created series, leading to improved performance across all levels.
+For example, \cite{pangHierarchicalElectricityTime2022} propose a multiple alternative clustering method to group similar electricity and solar power time series.
+In a similar vein, \cite{matteraImprovingOutofSampleForecasts2023} utilize Partition Around Medoids algorithms to unveil underlying structures in stock price indexes, while \cite{liForecastReconciliationApproach2019} apply agglomerative clustering to cause-of-death time series.
+These studies construct new hierarchies through clustering algorithms and demonstrate superior forecast performance compared to reconciliation without clustering, aligning with similar ideas from other research (e.g., \citealp{huberClusterbasedHierarchicalDemand2017, pangHierarchicalElectricityTime2018}).
+However, they are limited in scope as they concentrate solely on a specific time series clustering technique.
+To comprehensively investigate the effectiveness of clustering-based hierarchies, our approach involves a systematic comparison of multiple time series clustering techniques.
+This comparison incorporates a diverse set of time series representations, distance measures and clustering algorithms to provide a more thorough understanding of their impact on forecast performance.
+
+Despite the intuitive appeal of clustering algorithms in forming parent time series with improved forecastability, uncertainties persist.
+Even if time series with superior forecastability are constructed, such improvements do not guarantee enhanced reconciliation performance, given the inherent uncertainty in estimating covariance matrices of base forecast errors (\citealp{pritulargaStochasticCoherencyForecast2021}).
+Therefore, the conclusion that clustering technique is the primary contributor to forecast performance improvement is not straightforward.
+The observed improvement could also be attributed to the enriched structure itself, where a larger set of series is optimally combined to obtain the reconciled forecasts, leading to reduced model uncertainty and data uncertainty.
+To address these concerns, we propose a random hierarchy construction approach.
+By randomly constructing ``twin'' hierarchies with the same tree structure but different permutations of bottom-level series as a contrast to a clustering-based hierarchy, we are able to isolate the influence of clustering algorithms.
+This allows us to inspect the individual contributions of the enriched structure and clustering technique to forecast reconciliation performance.
+
+Randomness technique is commonly integrated with forecast combination approaches in the forecasting literature.
+An illustrative instance is found in the work of \cite{bergmeirBaggingExponentialSmoothing2016}, who leverage a bootstrap aggregation (bagging) technique to improve the performance of exponential smoothing models.
+This involves combining forecasts derived from bootstrapped versions of the time series, demonstrating consistent superior performance on the M3 dataset.
+Additionally, \cite{petropoulosExploringSourcesUncertainty2018a} explore three sources of uncertainty, model uncertainty (data uncertainty and parameter uncertainty), and conclude that the efficacy of bagging technique stems from model uncertainty.
+To address the uncertainty introduced by random hierarchies, we propose a method that combines reconciled forecasts derived from multiple random hierarchies, assigning equal weights to each.
+Furthermore, for a fair comparison with clustering algorithms, we include an equally weighted combination of reconciled forecasts obtained from multiple cluster-based hierarchies.
+
+This paper presents four main contributions:
+
+\begin{itemize}
+  \item We introduce a novel hierarchical forecast reconciliation framework centered on hierarchy construction.
+Within this framework, we explore and compare three distinct approaches: cluster hierarchies, random hierarchies, and combination hierarchies.
+  \item In contrast to existing literature that often focuses on a single clustering technique, our study systematically investigates the effectiveness of various time series clustering implementations.
+This investigation involves the incorporation of four time series representations, two distance measures, and two clustering algorithms.
+  \item Through a simulation study featuring an artificial example, we illustrate a scenario wherein the enriched structure, rather than clustering, emerges as the primary contributor to forecast reconciliation performance.
+Another scenario highlights the importance of carefully selecting a clustering technique.
+  \item We conduct experiments using two real-life datasets - the Australian tourism dataset and the U.S.
+cause-of-death mortality dataset.
+The results demonstrate the superior performance of hierarchy construction approaches, especially the combination hierarchies.
+Our research provides valuable insights into why clustering-based approaches enhance forecast reconciliation performance and offers guidance on the selection of hierarchy construction methods.
+\end{itemize}
+
+The rest of the paper is organized as follows.
+In section~\ref{sec:method} we introduce the proposed framework, elaborating on three approaches: cluster hierarchies, random hierarchies and combination hierarchies.
+The simulation study is presented in Section~\ref{sec:simulation}, while Section~\ref{sec:emp} details empirical experiments conducted on the Australian tourism dataset and U.S.
+mortality dataset.
+Finally, Section~\ref{sec:conclusion} concludes this paper with discussions on the findings and outlines future research directions.
+
 \section{Methodology}
@@
 
-\subsection{Framework}
+In this section, we illustrate the proposed framework for hierarchy construction.
+We begin by introducing the necessary notations, followed by detailed explanation of the overall framework.
+The three subsections followed present cluster hierarchies (Section~\ref{sec:cluster}), random hierarchies (Section~\ref{sec:random}) and combination hierarchies (Section~\ref{sec:combination}), respectively.
+Section~\ref{sec:reconciliation} describes the procedure for reconciliation and evaluation.
 
-1. construct hierarchies based on historic observations
-2. forecast and reconciliation
-3. evaluation
+Given the original hierarchy, let $m$ and $n$ denote the number of time series in the bottom level and the hierarchy, respectively.
+Vectors $\boldsymbol{b}_t$ and $\boldsymbol{y}_t$ represent observations of bottom level and hierarchy at time $t$.
+They are linked through an $n\times m$ summing matrix $\boldsymbol{S}$, which can be decomposed into an identity matrix $\boldsymbol{I}_m$ and a constraint matrix $\boldsymbol{A}$, i.e.,
+\[
+  \boldsymbol{y}_t = \boldsymbol{S}\boldsymbol{b}_t = \begin{bmatrix}
+    \boldsymbol{A} \\ \boldsymbol{I}_m 
+  \end{bmatrix}  \boldsymbol{b}_t,
+\]
+where $\boldsymbol{A}$ represents the mapping from bottom-level time series to upper-level time series.
+While HTS can accommodate general linear constraints, this paper focuses specifically on the most common aggregation constraints, where the matrix $\boldsymbol{A}$ consists solely of $0$ and $1$.
+We define hierarchy construction as the process of creating ``new middle-level series'', resulting in a modified HTS $\boldsymbol{y}^c_t$, which can be represented as:
+\[
+    \boldsymbol{y}^c_t = \boldsymbol{S}^c\boldsymbol{b}_t = \begin{bmatrix}
+        \boldsymbol{A} \\
+        \boldsymbol{C}_1' \\
+        \vdots \\
+        \boldsymbol{C}_K' \\
+        \boldsymbol{I}_m
+    \end{bmatrix}\boldsymbol{b}_t,
+\] 
+where each $\boldsymbol{C}_k$ represents a newly created middle-level series, formed by aggregating a subset of bottom-level series $\boldsymbol{b}_t$.
+The vector $\boldsymbol{C}_k$ is of $m$-dimensional and its elements $c_{k, i} \in \{0, 1\}, i=1,\dots m$ indicate whether the $i$-th bottom-level series belongs to the aggregated subset.
+Notably, different hierarchy construction approaches can result in different hierarchies with varying numbers of new middle-level series $K$.
+In this paper, we introduce and compare three hierarchy construction approaches: cluster hierarchies, random hierarchies and combination hierarchies, which are detailed in the following subsections.
 
-\subsection{Constructing hierarchies by clustering}
+\subsection{Cluster hierarchies}
+\label{sec:cluster}
 
-\cite{aghabozorgiTimeseriesClusteringDecade2015a} summarised the four components of time series clustering, including time series representations, distance measures, clustering algorithms and evaluation.
-In our framework, the first three components are involved in the constructing hierarchies procedure.
-The last component includes evaluation of reconciled forecasts of the original hierarchy.
+Cluster hierarchies are constructed based on clustering analyzes of the bottom-level time series. 
+\cite{aghabozorgiTimeseriesClusteringDecade2015a} comprehensively summarize the four key components of time series clustering: time series representations, distance measures, clustering algorithms and evaluation.
+Within our framework, the first three components are directly involved in the hierarchy construction process.
+The fourth component, including forecast reconciliation and evaluation of reconciled forecasts of the original hierarchy, will be detailed in Section~\ref{sec:reconciliation}.
 
@@
 
-Time-series representations represent raw time series in another space through techniques like feature extraction or dimensionality reduction.
-By utilising diverse time series representations, we are able to obtain distinct clusters which offer varied perspectives on the same dataset.
-Despite the absence of the theoretical evidence regarding how groups in hierarchical time series affect forecast reconciliation performance, we seek to explore multiple time series representations and discern potential correlations between hierarchical structure and the efficacy of forecast reconciliation.
+Time series representations transform raw time series into another space through techniques like feature extraction or dimension reduction.
+By utilizing diverse time series representations, we are able to obtain distinct clusters which offer varied perspectives on the same dataset.
+For example, \cite{pangHierarchicalElectricityTime2022} adopt Symbolic Aggregate approXimation (SAX) representation of time series, while \cite{liForecastReconciliationApproach2019} conduct their analysis on the normalized age-time mortality matrix.
+However, the lack of theoretical evidence regarding the relationship between specific groupings within an HTS and forecast reconciliation performance makes the selection of time series representations a challenging task.
+To address this gap, we explore the use of multiple time series representations and discern potential correlations between the resulting hierarchical structure and the efficacy of forecast reconciliation.
 
-Considering the impracticality of exploring every conceivable time series representation, we focus on four key ones: raw time series, in-sample error, features of time series, and features of in-sample error.
+Considering the impracticality of exploring every conceivable time series representation, we focus on four key ones: raw time series, in-sample one-step-ahead forecast error, features of time series, and features of in-sample one-step-ahead forecast error.
 The inclusion of raw time series is motivated by its simplicity and broad applicability.
-A crucial element contributing to the success of the minimum trace method proposed by \cite{wickramasuriyaOptimalForecastReconciliation2019} lies in estimating the covariance matrix of base forecast errors based on in-sample fit error.
-Hence, we consider in-sample error as a representation to examine how the structure within the error series influences reconciliation performance.
-Notably, to the best of our knowledge, we are the first to utilise in-sample error as a time series representation in the context of forecast reconciliation literature.
-The time series and in-sample error representations are standardised on a per-series basis to eliminate the impact of scale variations.
+A crucial element contributing to the success of the minimum trace method proposed by \cite{wickramasuriyaOptimalForecastReconciliation2019} lies in estimating the covariance matrix of base forecast errors based on in-sample one-step-ahead forecast error.
+Hence, we consider in-sample one-step-ahead forecast error as a representation to examine how the structure within the error series influences reconciliation performance.
+Raw time series and in-sample error representations are standardized on a per-series basis to eliminate the impact of scale variations.
 Features, widely employed in capturing time series characteristics across literature, play a pivotal role in various time series applications, including clustering (\citealp{tianoFeatTSFeaturebasedTime2021}) and forecasting (\citealp{wangUncertaintyEstimationFeaturebased2022, liFeaturebasedIntermittentDemand2023}).
-In our exploration, we incorporate features of both time series and in-sample fit error as representations.
+In our exploration, we incorporate features of both raw time series and in-sample forecast error as representations.
+Notably, to the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation literature.
 These representations allow us to glean insights into the diverse aspects of hierarchical time series data and enhance our understanding of how different structures contribute to the forecast reconciliation performance.
-
-Given the limited number of time series in comparison to the variable dimensions (i.e., the length of time series and the number of time series features) within the hierarchical time series in our applications, it becomes imperative to perform dimension reduction on the aforementioned representations.
-Failure to undertake dimension reduction may lead to undesirable clustering outcomes due to the challenges posed by the curse of dimensionality.
-We conduct principal component analysis and extract the first few principal components that explain at least $80$\% variance within the data.
 
@@
 
-Distance measures assess the similarity between two series.
+Distance measures serve as crucial tools for assessing the similarity/dissimilarity between two series, forming the foundation for clustering algorithms to detect clusters within datasets.
+In the context of time series clustering, we consider two widely applied distance measures: Euclidean distance and dynamic time warping (DTW).
 
-euclidean distance
+Due to the limited number of time series in comparison to the high dimensionality of individual time series (i.e., the length of time series and the number of time series features) in our applications, dimension reduction on the aforementioned representations becomes imperative when employing Euclidean distance.
+Failure to undertake dimension reduction may result in undesirable clustering outcomes due to the curse of dimensionality.
+To address this, we perform Principal Component Analysis (PCA), extracting the first few principal components that collectively explain at least 80\% of the variance within the data.
 
-dynamic time warping
+In contrast, DTW (\citealp{sakoeDynamicProgrammingAlgorithm1978}), exhibits reduced sensitivity to the curse of dimensionality.
+Unlike Euclidean distance, which performs one-to-one point comparisons, DTW accommodates time series of varying lengths through many-to-one comparisons.
+This flexible approach allows for the recognition of time series with similar shapes, even in the presence of signal transformations such as shifting and/or scaling.
 
@@
 
-k-Medoids
+Regarding clustering algorithms, we focus on two prevalent approaches, k-Medoids and agglomerative hierarchical clustering.
+The k-Medoids algorithm, a classical partitioning clustering method, aims to minimize the total distance between all samples within a cluster and their respective cluster centers.
+Unlike k-Means, which employs the mean vector of samples as the cluster center, k-Medoids selects one sample within the cluster as the center. 
+Specifically, we adopt the k-Medoids variant, partitioning around medoids (PAM, \citealp{PartitioningMedoidsProgram1990}).
+Following the recommendation of \cite{PartitioningMedoidsProgram1990}, we determine the optimal number of cluster using the average silhouette width (ASW), a popular cluster validation index.
+ASW assesses the quality of clustering results by measuring the proximity of samples within a cluster compared to neighboring clusters.
+Given a clustering result, the silhouette width for the $i$th sample is calculated as 
+\[
+  SW(i) = \frac{b(i)-a(i)}{\max\{a(i), b(i)\}},  
+\]
+where $a(i)$ represents the average distance of the $i$th sample to others in the same cluster, and $b(i)$ is the average distance to samples in the nearest cluster it is not assigned to.
+A higher silhouette width indicates greater proximity to samples within the same cluster than to those in neighboring clusters.
+The ASW is the average of silhouette widths across all samples.
+We select the clustering result that maximizes the ASW by iterating over all possible numbers of clusters.
+However, ASW has the limitation of being undefined when there is only one cluster.
+Gap statistics (\citealp{tibshiraniEstimatingNumberClusters2002}) can be used to address this limitation, but it is incompatible with DTW.
 
-hierarchical clustering
+Agglomerative hierarchical clustering begins by considering each sample as a cluster, and then gradually merges clusters until all samples forms a single cluster. 
+This process results in a binary hierarchical tree with $2m-1$ nodes.
+We employ Ward's linkage (\citealp{murtaghWardHierarchicalAgglomerative2014a}) to merge clusters, minimizing the increase of within-cluster variances at each step.
 
-\subsection{Constructing hierarchies randomly}
+New middle-level series are constructed according to the clustering results.
+For each cluster, we obtain the corresponding aggregation vector $\boldsymbol{C} = [c_{1}, \dots, c_{m}]'$, where $c_{i}$ is $1$ if the $i$-th bottom-level series belongs to the cluster and $0$ otherwise.
+Illustrated in Figure~\ref{fig:cluster_example} are two example hierarchies generated by k-Medoids and agglomerative clustering algorithms for an original hierarchy with four bottom-level series and one total series.
+These examples highlight the distinct behaviors of the two algorithms.
+Firstly, k-Medoids constructs a simple hierarchy with a single middle level, while hierarchical clustering generates multiple nested middle levels. 
+Secondly, k-Medoids produces a hierarchy with the same number of series as the optimal number of clusters, whereas hierarchical clustering yields multiple middle levels with $m-2$ series.
+As the number of bottom-level series increases, the structural differences become increasingly significant, and we aim to investigate how these differences influence the performance of forecast reconciliation.
 
-pure random
+\begin{figure}
+    \centering
+    \includegraphics[width=0.3\textwidth]{figures/pamcluster.pdf}
+    \hspace{1cm}
+    \includegraphics[width=0.3\textwidth]{figures/aggcluster.pdf}
+    \caption{\label{fig:cluster_example}Example clustering results of two clustering algorithms.
+Left panel displays example for k-Medoids algorithm, and right panel displays example for agglomerative hierarchical clustering algorithm.}
+\end{figure}
 
-random based on specific structure
+\subsection{Random hierarchies}
+\label{sec:random}
 
-\subsection{Forecast combination}
+Cluster hierarchies can potentially affect forecast performance in two aspects.
+First, clustering analysis creates time series that is easy to forecast, allowing original series to borrow strength.
+The accuracy decrease during reconciliation occurs on the newly created time series instead of the original series.
+Secondly, the enriched structure reduce data and model uncertainty within the base forecasts of bottom level, leading to improved reconciled forecasts.
+
+To systematically explore these two aspects, we introduce two randomized methods for constructing hierarchies.
+These methods allow us to eliminate the influence of clustering and focus specifically on investigating the second aspect.
+The first approach generates hierarchies akin to those produced by k-Medoids clustering algorithms.
+Given $m$ bottom-level series and the number of groups $k$, it first randomly assigns $ \lfloor \frac{m}{k}\rfloor$ number of series to each group.
+The remaining $m -  k\times\lfloor\frac{m}{k}\rfloor$ series are then shuffled and assigned to the first $m -  k\times\lfloor\frac{m}{k}\rfloor$ groups one by one.
+This straightforward yet efficient approach constructs a three-level random hierarchy, ensuring the numbers of bottom-level series of these groups  are as nearly equal as possible, allowing us to focus solely on the impact of enriched structure on the forecast reconciliation performance.
+
+The second approach generates random hierarchies based on a given hierarchy, such as one constructed from clustering results.
+Given a hierarchy tree, it creates new hierarchies by randomly permuting the leaf nodes.
+In other words, it shuffles the columns of the constraint matrix $\boldsymbol{A}$ of the given hierarchy.
+This method yields a random ``twin'' hierarchy with the same tree structure but different groupings.
+If the randomized version of a cluster hierarchy significantly outperforms its original counterpart, it suggests that the second aspect holds greater importance than the first, and vice versa.
+Figure~\ref{fig:aggcluster_random} shows an example of this approach.
+The left hierarchy is the hierarchy shown in right panel of Figure~\ref{fig:cluster_example} The right hierarchy is an example of a random ``twin'' hierarchy.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/aggcluster_random.pdf}
+    \caption{\label{fig:aggcluster_random}Examples of randomization of a given hierarchy. Right hierarchy is obtained by shuffling the leaf nodes of left hierarchy.}
+\end{figure}
+
+\subsection{Combination hierarchies}
+\label{sec:combination}
+
+To mitigate the uncertainty introduced by random hierarchies, we propose to combine multiple hierarchies.
+This strategy involves two primary methods.
+The first method focuses on combining the structures of these hierarchies.
+Assume there are $l$ hierarchies in the combination pool, it does so by constructing a new HTS with a summing matrix, which is a composite of the constraint matrices $\boldsymbol{A}_1, \dots, \boldsymbol{A}_l$ of  these hierarchies, along with the original constraint matrix $\boldsymbol{A}$ and the identity matrix $\boldsymbol{I}_m$.
+The summing matrix is thus represented as:
+\[
+  \boldsymbol{S} = \begin{bmatrix}
+    \boldsymbol{A} \\ \boldsymbol{A}_1 \\ \vdots \\ \boldsymbol{A}_l \\ \boldsymbol{I}_m
+  \end{bmatrix}.  
+\] An example of this approach is seen in the work of \cite{pangHierarchicalElectricityTime2022}, where multiple clusterings obtained from k-Means algorithms with different number of clusters are combined.
+However, this method faces challenges, particularly as the number of hierarchies in the combination pool increases, which not only raises computational time but also amplifies the uncertainty in estimating the covariance matrix.
+To address this concern, \cite{pangHierarchicalElectricityTime2022} impose sparse penalty to select ideal clusters that are helpful for reconciliation.
+
+Given the complexities of the first method, our paper concentrates on the second approach, which combines reconciled forecasts from different hierarchies.
+Firstly, we produce reconciled forecasts for each hierarchy.
+The reconciled forecasts of the original series are then extracted and combined using equal weights.
+Note that the resulted forecasts are still coherent.
+While it is possible to employ more complex methods to determine ``optimal'' weights, we adhere to equally-weighted combination due to its simplicity and well-known efficacy (\citealp{wangForecastCombinations50year2022}).
+
+\subsection{Forecast reconciliation and evaluation}
+\label{sec:reconciliation}
+
+This subsection introduces the forecast reconciliation approach used in our paper.
+Assume we are making $h$-step-ahead forecasts based on $T$ historic observations for a given hierarchy $\boldsymbol{y}^c$, which could be the original hierarchy, a cluster hierarchy or a random hierarchy.
+We first produce $h$-step-ahead base forecasts $\hat{\boldsymbol{y}}^c_{T+h}$ using arbitrary forecasting models for each time series in the hierarchy.
+Subsequently, the minimum trace (MinT, \citealp{wickramasuriyaOptimalForecastReconciliation2019}) reconciliation method is applied to produce coherent forecasts:
+\[
+    \tilde{\boldsymbol{y}}_{T+h}^c = (\boldsymbol{S}'\boldsymbol{W}_h^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}_h^{-1}\hat{\boldsymbol{y}}_{T+h}^c,
+\]
+where the superscript $c$ of $\boldsymbol{S}^c$ is omitted for ease of expression.
+$\boldsymbol{W}_h$ is the covariance matrix of $h$-step-ahead forecast errors.
+We employ the shrinkage estimator of $\boldsymbol{W}_h$ proposed by \cite{wickramasuriyaOptimalForecastReconciliation2019}, which estimates the covariance matrix based on the in-sample one-step-ahead forecast errors.
+Specifically, it sets  $\boldsymbol{W}_h = \lambda \hat{\boldsymbol{W}}_{1,D} + (1-\lambda)\hat{\boldsymbol{W}}_1$, where $\hat{\boldsymbol{W}}_1$ is the unbiased sample covariance estimator of the in-sample one-step-ahead forecast errors.
+$\hat{\boldsymbol{W}}_{1,D}$ is a diagonal matrix comprising the diagonal entries of $\hat{\boldsymbol{W}}_1$.
+$\lambda$ is a shrinkage intensity parameter proposed in \cite{SchaferStrimmer2005}.
+
+Given our specific interest in the performance of the original series, we extract reconciled forecasts of the original series from $\tilde{\boldsymbol{y}}_{T+h}^c$, i.e.,
+\[
+  \tilde{\boldsymbol{y}}_{T+h} = \tilde{\boldsymbol{y}}^c_{T+h, 1:(n-m) \cup (n_c - m + 1): n_c},
+\]
+where $n_c$ is the number of time series in the hierarchy.
+For combination hierarchies, the reconciled forecasts from $l$ hierarchies in the combination pool are equally combined to obtain the final forecasts, i.e.,
+\[
+  \tilde{\boldsymbol{y}}_{T+h}^{\text{comb}} = \frac{1}{l} \sum_{j=1}^l \tilde{\boldsymbol{y}}_{T+h}^j.
+\]
+Finally, these forecasts are used for evaluating the performance of different approaches.
 
@@
 
-In this section, we demonstrate that hierarchies constructed by clustering may not outperform hierarchies constructed randomly even if there are true clusters in the bottom level.
+Recall our hypothesis positing that the performance of cluster hierarchies is influenced predominantly by two aspects.
+The first aspect is the generation of accurate base forecasts by the newly created time series, while the second aspect is attributable to the enriched structure.
+In this section, we simulate two artificial scenarios using the same dataset but varying base forecasting models.
+The first scenario is designed to demonstrate a context where the second aspect plays a dominant role.
+Conversely, the second scenario is constructed to illustrate a situation where the first aspect is the predominant factor.
 
@@
     \begin{aligned}
-    y_t &= l_t + s_t + e_t \\
-    s_t &= s_{t\mod m} \\
-    l_t &= a t + \varepsilon_t,
+    Y_t &= L_t + S_t + \xi_t \\
+    S_t &= S_{t~\text{mod}~s} \\
+    L_t &= a t + \varepsilon_t,
     \end{aligned}
 \end{equation}
-where $l_t$ represents the trend term which increases or decreases over time at a slope of $a$.
-The seasonal component, denoted by $s_t$, remains constant.
-Both $e_t$ and $\varepsilon_t$ are white noises.
+where $L_t$ represents the trend term which increases or decreases over time at a slope of $a$.
+The seasonal component, denoted by $S_t$, is repeating and deterministic with a cycle of length $s$.
+Both $\xi_t$ and $\varepsilon_t$ are white noises.
 
-We create $6$ clusters at the bottom level by adjusting the directions of the trend and patterns of the seasonal components.
-The pattern settings for all clusters can be found in Table~\ref{table:simu_params}.
-For an increasing trend we set the slope $a$ to $0.001$, and for a decreasing trend, we set it to $-0.002$.
-The variances of the corresponding white noise $\varepsilon_t$ are set to $2.5\times 10^{-5}$ and $4.9\times 10^{-5}$.
-The terms ``Even'' and ``Odd'' indicate the position of the seasonal peak.
-For ``Even'' seasonality, the peaks are located at positions $2, 4, \dots, m$, and vice versa.
-The values for these seasonal peaks and troughs are uniformly drawn from $[2, 3]$ and $[0,1]$, respectively.
-The variance of $e_t$ is set to $0.25$.
-We generate monthly time series data with $20$ time series per cluster.
-Figure~\ref{fig:simu_emps} displays example time series from each cluster while Figure~\ref{fig:simu_pca} visualises these generated time series based on the first two principal components extracted from principal component analysis of the series.
+Instead of employing cluster algorithms, we artificially craft $6$ ideal clusters by manipulating the directions of the trend components and patterns of the seasonal components.
+The configurations for each cluster can be found in Table~\ref{table:simu_params}.
+To simulate an increasing trend, we set the slope $a$ to $0.001$, and for a decreasing trend, we set $a$ to $-0.002$.
+The variances of the associate white noise $\varepsilon_t$ are set to $2.5\times 10^{-5}$ and $4.9\times 10^{-5}$ for increasing trend and decreasing trend, respectively.
+For series without trend (``None''), the trend component $L_t$ is set to zero.
+The terms ``Even'' and ``Odd'' in our setup refer to the positioning of seasonal peak.
+Specifically, ``Even'' seasonality means that peaks occur at even-numbered positions (e.g., $2, 4, \dots$) of seasonal cycle, with the reverse being true for ``Odd'' seasonality.
+The values of these seasonal peaks and troughs are randomly drawn from uniform distributions within the ranges of $[2, 3]$ and $[0,1]$, respectively.
+The variance of $\xi_t$ is set to $0.25$.
+We generate monthly time series data, ensuring that each cluster contains $20$ distinct time series.
+For each series, we generate $144$ observations, and the last $12$ observations are reserved for evaluation purpose.
+Figure~\ref{fig:simu_emps} displays example time series from each cluster, while Figure~\ref{fig:simu_pca} visualizes these generated time series based on the first two principal components extracted from principal component analysis of the series.
 
@@
     \includegraphics[width=0.6\textwidth]{figures/simu_pca.pdf}
-    \caption{\label{fig:simu_pca}Visualisation of the generated time series in the simulation experiments.}
+    \caption{\label{fig:simu_pca}Visualization of the generated time series in the simulation experiments.}
 \end{figure}
@@
 
-There are a total of $120$ bottom series and $1$ total series in the hierarchy, referred to as ``C0''.
-Additionally, we consider $4$ clustering approaches and $2$ forecast combination approaches.
-``C1'' creates $6$ middle-level series according to the designed correct clusters.
-We merge clusters with the same trend pattern, resulting in $3$ clusters in the middle level, denoted by ``C2''.
-Similarly, we construct ``C3'' and ``C4'' based on the presence of the trend term and seasonal peak positions, resulting in $2$ and $3$ middle-level series, respectively.
-``A1'' combines reconciled forecasts obtained from all four clustering approaches (``C1'' to ``C4'') using equal weights.
-By shuffling the bottom-level series within the hierarchy ``C1'', we can randomly generate different hierarchies with identical structure.
-``A2'' combines reconciled forecasts from $10$ randomly constructed hierarchies using equal weights.
+We consider an original hierarchy with a total of $120$ bottom-level series and a single aggregated series, labelled as ``C0''.
+In addition, we examine four cluster hierarchies and two combination hierarchies.
+Note that we consider multiple cluster hierarchies in order to reflect the real-world scenario where a variety of clustering techniques may be employed.
+The first cluster hierarchy, ``C1'', forms six middle-level series according to the predefined ideal clusters.
+We then merge clusters with the same trend pattern, resulting in the cluster hierarchy with three clusters, denoted by ``C2''.
+Similarly, we construct cluster hierarchies ``C3'' and ``C4'' based on the presence of the trend term and seasonal peak positioning, resulting in $2$ and $3$ middle-level series, respectively.
+Combination hierarchy ``A1'' combines reconciled forecasts obtained from all four cluster hierarchies (``C1'' to ``C4'') using equal weights.
+Moreover, by shuffling the bottom-level series within the cluster hierarchy ``C1'', we generate random ``twin'' hierarchies, as described in Section~\ref{sec:random}.
+The second combination hierarchy ``A2'' combines reconciled forecasts from ten random ``twin'' hierarchies using equal weights.
 
@@
 
-We construct two scenarios by considering different base forecasting models.
-In the first scenario, exponential smoothing (ETS) is used to generate base forecasts for all time series in hierarchies.
-This simulates a situation where the time series themselves are inputs to the clustering algorithms.
-In the second scenario, we use historic mean to generate base forecasts for bottom-level series and ETS for other time series in hierarchies, which simulates the case where in-sample errors are inputs to the clustering algorithms.
+Given the generated hierarchies, we construct two distinct scenarios, each employing different base forecasting models.
+In the first scenario, exponential smoothing (ETS, \citealp{ForecastingExponentialSmoothing}) is used to generate base forecasts for all time series in hierarchies.
+This setup simulates a context where raw time series are used as time series representations for clustering.
+In the second scenario, we apply the historic mean for generating base forecasts for the bottom-level series, while continuing to use ETS for other time series in hierarchies.
+This approach ensures that the in-sample forecast errors exhibit patterns similar to those of the raw time series, simulating the scenario where in-sample forecast errors are considered as time series representations for clustering.
+Furthermore, this scenario aims to verify the proposition that the original series can borrow strength from the newly created series.
 We refer to these scenarios as ``clustering by time series'' and ``clustering by error'', respectively.
-To reconcile the base forecasts, we employ the minimum trace method with the shrinkage estimator (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
-The shrinkage estimator is effective at capturing the dependence structure within the forecast errors and has demonstrated superior perofrmance in various applications.
-For each series, we generate $144$ observations, and the last $12$ observations are reserved for evaluation purpose.
 
@@
 
-The purpose of constructing middle-level series is to improve the forecast performance of the total-level and bottom-level series by leveraging the strength of these new series.
-Therefore, we only evaluate the reconciled forecasts at total level and bottom level. 
-To assess the accuracy of single time series, we use root mean squared error (RMSE) as our metric. 
-The simulation is repeated $500$ times, resulting in a total of $500\times 121$ RMSEs for each approach. 
-Multiple comparisons with the best (MCB) test is then applied to compute the average ranks of the $7$ approaches along with base forecasts and to determine whether the performance differences are statistically different (\citealp{koningM3CompetitionStatistical2005}).
+Recalling that our purpose is to improve forecast performance of the original series, our evaluation focuses exclusively on reconciled forecasts of the total-level and bottom-level series. 
+Firstly, we employ the Root Mean Squared Error (RMSE) as our accuracy metric for forecasts of individual time series. 
+To ensure robustness and reliability in our findings, we conduct the simulation $500$ times, resulting in a comprehensive evaluation set comprising $500\times 121$ RMSEs for each hierarchy. 
+Multiple comparisons with the best (MCB) test is then applied to compute the average ranks of the seven hierarchies as well as the base forecasts, and to determine whether the performance differences are statistically different (\citealp{tsutils}).
 
@@
 
-Figure~\ref{fig:simu_mcb} displays the MCB test results for the two scenarios. 
-In both scenarios, most approaches perform better than the base forecasts and the original two-level hierarchy ``C0''.
-This suggests that constructing middle-level series generally improves forecast reconciliation performance.
-In the ``clustering by time series'' scenario, the correct cluster ``C1'' ranks $4$th, indicates that optimal clusters do not guarantee optimal forecast reconciliation performance. 
-On the other hand, ``C1'' ranks $1$st in the ``clustering by error'' scenarios.
-This highlights the importance of carefully selecting time series representations when constructing new middle levels using clustering algorithms.
-The simple average of $10$ random hierarchies ranks $1$st in the first scenario and the simple average of $4$ clustering hierarchies ranks $3$rd in both scenarios, indicating the importance of forecast combination.
+Figure~\ref{fig:simu_mcb} presents the MCB test results for both scenarios.
+The results reveal that in both scenarios, most approaches perform better than the base forecasts and the original two-level hierarchy ``C0''.
+This outcome indicates that hierarchy construction generally improves forecast reconciliation performance, corroborating similar findings reported in existing literature, such as those by \cite{pangHierarchicalElectricityTime2022,liForecastReconciliationApproach2019} and \cite{matteraImprovingOutofSampleForecasts2023}.
+
+In the ``clustering by time series'' scenario, the ideal cluster ``C1'' achieves a $4$th rank, indicating that optimal clustering does not necessarily translate into the best forecast reconciliation performance.
+On the other hand, ``C1'' ranks $1$st in the ``clustering by error'' scenarios and demonstrates superior performance over other clustering approaches and its randomized counterpart.
+This finding implies that in this scenario, the created series based on clustering, as opposed to enriched structure, plays a crucial role in improving forecast performance.
+However, it is important to recognize that such scenarios may be uncommon in practical applications due to careful modeling of base forecasts.
+Thus, the in-sample forecast errors in practice may not exhibit clear patterns as those observed in this simulation, leading to clustering with more uncertainty.
+Additionally, the varying  performance of ``C1'' across two scenarios highlight the significance of carefully selecting time series representations when constructing new middle levels using clustering algorithms.
+
+Regard the combination hierarchies, it is noteworthy that the equally weighted combination of ten random hierarchies achieves first rank in the first scenario.
+Meanwhile, the equally weighted combination of four clustering hierarchies ranks third in both scenarios.
+These outcomes suggest that forecast combination can further improve forecast performance of both random hierarchies and cluster hierarchies.
+Interestingly, in the first scenario, the combination of random hierarchies outperforms the combination of cluster hierarchies in.
+This implies that the enriched structure has a more significant impact on forecast performance in this context.
+We argue that this outcome can be attributed to the already high quality of base forecasts, as indicated by the close relative ranks of the various approaches.
+When the base forecasts are sufficiently accurate, the added value of reconciliation through complex hierarchical structures might be limited, while combination of hierarchies further improves performance by dealing with data and model uncertainty.
+
+In summary, our simulation effectively illustrates two distinct scenarios, each highlighting a separate factor contributing to the performance improvement offered by hierarchy contribution approaches.
+However, it is crucial to acknowledge that both scenarios represent simplified, somewhat exaggerated representations of practical situations.
+The actual practice of forecasting involves careful modeling, but is also impacted by ubiquitous model misspecification, which adds complexity that isn't fully captured in these artificial scenarios.
+To further validate and explore the effectiveness of various methodologies, we will conduct experiments on two real-world applications, thereby offering a more practical and nuanced understanding of these approaches.
 
@@
 \section{Empirical studies}
-
+\label{sec:emp}
 \subsection{Datasets}
 
-We analyse two datasets in our empirical studies.
-The first dataset is the monthly Australian domestic tourism dataset, which provides visitor nights numbers from 1998 to 2016.
-The tourism demand of Australia is geographically disaggregated into $7$ states and territories, further divided into $27$ zones and $76$ regions.
+We analyze two datasets in our empirical studies.
+The first dataset is the monthly Australian domestic tourism dataset, covering the period from January 1998 to December 2016.
+The tourism demand of Australia is geographically disaggregated into seven states and territories, which are further divided into $27$ zones and $76$ regions.
 Additionally, each geographical series is divided by four travel purposes (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
-This dataset totally contains $555$ time series with $304$ at the bottom level.
+Overall, this dataset comprises a total of $555$ time series with $304$ of those at the bottom level.
 
-The second dataset focuses on causes of death in the U.S., using the ICD 10 coding system.
-We obtain monthly cause-specific death counts from the Center for Disease Control and Prevention (CDC) for the period between 1999 and 2019.
-The coding system forms an unbalanced hierarchy with $137$ time series, out of which $113$ time series are in the bottom level.
-To consolidate data with suppressed values, we combine causes that share a parent cause and calculate their death counts by subtracting death counts of sibling causes from death counts of their parent cause.
-The final dataset includes $120$ time series with $98$ in the bottom level.
+The second dataset focuses on causes of death in the United States, using the ICD 10 coding system.
+We obtain monthly cause-specific death count data from the Center for Disease Control and Prevention (CDC) for the period between 1999 and 2019.
+The coding system inherently forms an unbalanced hierarchy containing $137$ time series, with $113$ of those being bottom-level series.
+To address issues with suppressed data values, we combine causes that contain missing values and share a parent cause.
+The death counts for these combined categories are calculated by subtracting the death counts of sibling causes from the death counts of their parent cause.
+This processing results in a refined dataset that includes $120$ time series with $98$ at the bottom level.
 
@@
 
-We focus on the performance of total-level series and bottom-level series, disregarding the multiple middle levels in the original hierarchies known as "natural hierarchies".
-The natural hierarchy is considered one way to construct middle-level series, similar to hierarchies created through clustering.
-However, we demonstrate that for the purpose of forecast performance, the natural hierarchy may not be the most effective hierarchical structure.
+In our analysis of the two datasets, we focus specifically on the total-level and bottom-level series rather than evaluating all levels of the given hierarchies.
+These two-level hierarchies are referred to as ``original hierarchy'', serving as our benchmark.
+The given hierarchy, referred to as ``natural hierarchy'', is considered as one way of hierarchy construction that is based on metadata of the time series.
+We demonstrate that for the purpose of forecast performance, the natural hierarchy may not be the most effective hierarchical structure.
 
-To construct middle levels using clustering, we combine four time series representations with two distance measures and two clustering algorithms.
-This results in twelve different construction approaches listed in Table~\ref{tab:emp_method}.
+Regarding cluster hierarchies, we employ twelve time series techniques which are derived from combinations of four time series representations, two distance measures and two clustering algorithms.
+The names and details of these approaches are listed in Table~\ref{tab:emp_method}.
+The four time series representations need to perform dimension reduction when using Euclidean distance, as we have discussed in Section~\ref{sec:clustering}.
+Combing the four dimension reduced representations with two clustering algorithms results in the first eight clustering approaches.
+Features of raw time series and in-sample forecast error are not temporal data, thus incompatible with DTW.
+The last four approaches are derived from combinations of two temporal representations, two clustering algorithms and DTW.
 
@@
     Approaches & Representation & Dimension reduction & Distance measure & Clustering algorithms  \\
-    TS-MED & Time series & Yes & Euclidean & k-Medoids \\
+    TS-MED & Raw time series & Yes & Euclidean & k-Medoids \\
     ER-MED & In-sample error & Yes & Euclidean & k-Medoids \\
-    TSF-ME & Time series features & Yes & Euclidean & k-Medoids \\
+    TSF-ME & Raw time series features & Yes & Euclidean & k-Medoids \\
     ERF-ME & In-sample error features & Yes & Euclidean & k-Medoids \\
-    TS-HC & Time series & Yes & Euclidean & hierarchical clustering  \\ 
+    TS-HC & Raw time series & Yes & Euclidean & hierarchical clustering  \\ 
     ER-HC & In-sample error & Yes & Euclidean & hierarchical clustering  \\ 
-    TSF-HC & Time series features & Yes & Euclidean & hierarchical clustering  \\ 
+    TSF-HC & Raw time series features & Yes & Euclidean & hierarchical clustering  \\ 
     ERF-HC & In-sample error features & Yes & Euclidean & hierarchical clustering  \\
@@
 
-Additionally, we consider three forecast combination approaches.
-In the first approach, we create one middle level with $15$ time series by randomly assigning bottom-level series as their children.
-We ensure that all the middle-level series have approximately an equal number of children.
-The choice of having $15$ middle-level series is arbitrary with the goal of creating a moderate number of groups, each containing a moderate number of series.
-We repeat this process to create $50$ such hierarchies and combine their reconciled forecasts using equal weights. This approach is referred to as ``FC-R''.
-In the second approach, we create $10$ new hierarchies by randomly shuffling the positions of bottom-level series in the natural hierarchy and combine their reconciled forecasts using equal weights.
-This approach is denoted by ``FC-N''.
-The third approach, labelled by ``FC-C'', involves equally-weighted combining the reconciled forecasts obtained from the $12$ hierarchies shown in Table~\ref{tab:emp_method}.
+Additionally, we explore three combination hierarchies.
+The first one, referred to as ``FC-R'', implements the first random hierarchy construction approach outlined in Section~\ref{sec:random}.
+Here, we set the number of groups $k$ to $15$, an arbitrary number chosen with the goal of creating a moderate number of groups, each containing a moderate number of series.
+We repeat this process to create ten similar hierarchies and combine their reconciled forecasts using equal weights.
+This approach is employed to verify the hypothesis that hierarchy construction can improve forecast reconciliation performance.
+The second combination hierarchy, denoted by ``FC-N'', adopts the alternative random hierarchy construction approach also discussed in Section~\ref{sec:random}.
+Specifically, we randomly create ten ``twin'' hierarchies of the natural hierarchy, to evaluate our argument that the natural hierarchy might not be the optimal hierarchy in terms of forecast performance.
+The third combination hierarchy, labelled by ``FC-C'', involves an equally-weighted combination of the reconciled forecasts obtained from the $12$ cluster hierarchies shown in Table~\ref{tab:emp_method}.
+This approach aims to demonstrate that the performance of hierarchy construction approaches can be further enhanced through forecast combination.
 
-The time series features used in this experiment are calculated using the \texttt{tsfeatures} package (\citealp{tsfeatures}) for R.
+The time series features used in this experiment are calculated using the \texttt{tsfeatures} package (\citealp{tsfeatures}) for R (\citealp{R}).
 After filtering out the features that are constant across all series, $56$ features are reserved.
-The complete list of these feature can be found in Appendix.
-The k-Medoids and hierarchical clustering algorithms are implemented using the \texttt{cluster}(\citealp{cluster}) package for R.
+The k-Medoids and hierarchical clustering algorithms are implemented using the \texttt{cluster} (\citealp{cluster}) package for R.
 The base forecasts are generated using the automatic ETS models, which are then reconciled using the minimum trace method with shrinkage estimator.
 
-We employ the rolling window strategy to evaluate the performance of different approaches for both datasets.
-We start with $96$ observations and fit the base forecasting models using the available data.
-Then we calculate time series representations and construct new hierarchies by clustering or randomness, and then forecast $12$ steps ahead.
+To rigorously validate our hypothesis, we utilize the rolling window strategy to evaluate the performance of different approaches on both datasets.
+We begin by fitting base forecasting models using the first $96$ observations.
+Then we calculate time series representations and construct new hierarchies, either through clustering or random approaches, and then forecast $12$ steps ahead.
 After that, the training set is increased by one observation and new forecasts are obtained.
@@
 Finally, we can obtain $121$ $12$-step-ahead forecasts for the tourism dataset and $144$ $12$-step-ahead forecasts for the mortality dataset.
-We compare the forecast performance of the $15$ approaches as well as the natural hierarchy, two-level hierarchy and base forecasts for both total-level and bottom-level series.
+
+We compare the forecast performance of the twelve cluster hierarchies, three combination hierarchies as well as the natural hierarchy, the original two-level hierarchy and base forecasts.
+Same as the evaluation measure described in Section~\ref{sec:simu_eval}, we first calculate RMSE for each of the $12$-step-ahead forecasts, resulting in $144 \times 99$ RMSE values for the mortality dataset and $121 \times 305$ RMSE values for the tourism dataset for each approach.
+We then conduct the MCB test on these RMSE values to statistically assess the differences in forecast accuracy.
 
@@
 
-Same as the evaluation measure described in Section~\ref{sec:simu_eval}, we combine the forecasts of total-level and bottom-level series across all evaluation windows and conduct the MCB test.
-The test results for the tourism dataset and mortality dataset are shown in Figure~\ref{fig:tourism_mcb} and Figure~\ref{fig:mortality_mcb}, respectively.
+The MCB test results for the tourism dataset and mortality dataset are shown in Figure~\ref{fig:tourism_mcb} and Figure~\ref{fig:mortality_mcb}, respectively.
+For both datasets, most hierarchy construction approaches outperform both base forecasts and the two-level hierarchy.
+The first combination approach ``FC-R'' achieves third rank on the mortality dataset eighth rank on the tourism dataset.
+These results demonstrate that hierarchy construction can enhance forecast performance, further supporting the findings in our simulation and the literature.
 
-Most hierarchy construction approaches outperform both base forecasts and the two-level hierarchy, except for three approaches on the mortality dataset.
-For both datasets, the simple average of randomised natural hierarchies (``FC-N'') performs better than both natural hierarchy and all clustering-based hierarchies.
-Additionally, the simple average of $12$ clustering-based hierarchies (``FC-C'') significantly outperforms all other approaches.
-These results indicate that using a clustering-based hierarchy can improve forecast performance.
-However, forecast combination is even more beneficial, as evidenced by the high ranking of ``FC-N'' and ``FC-R''.
+In both datasets, the evidence suggests that the natural hierarchy may not be optimal for performance.
+The equally weighted combination of "twin" hierarchies derived from the natural hierarchy (``FC-N'') outperform the natural hierarchy itself, supporting this hypothesis.
+This finding reinforces our belief that better hierarchical structures can be constructed, as evidenced by the superior performance of some cluster hierarchies on the tourism dataset.
+Most cluster hierarchies outperform the original two-level hierarchy on both datasets, further demonstrating the effectiveness of clustering approaches.
+However, three exceptions on the mortality dataset highlight the importance of choosing an appropriate clustering technique.
+
+Interestingly, unlike the simulation where either clustering or enriched structure play the primary role in performance improvement, both factors contribute to better forecasts in the two real-world datasets.
+First, the randomized natural hierarchy ``FC-N'' outperform all  cluster hierarchies and the natural hierarchy on both datasets, showcasing the benefit of enriched structure.
+Second, the equally weighted combination of cluster hierarchies achieves the top rank, demonstrating the effectiveness of clustering techniques.
+Furthermore, the impressive performance of the three combination hierarchies underscores the potential of combining forecasts from multiple hierarchies for even greater accuracy.
+This suggests that the impact of combination may even more significant than the individual contributions of clustering and enriched structure.
 
@@
 
-The approach based on hierarchical clustering outperforms the approach based on k-Medoids on the tourism dataset when using the same representation and distance metric, e.g., ``TSF-HC'' significantly ourperforms ``TSF-ME''.
+The approach based on hierarchical clustering outperforms the approach based on k-Medoids on the tourism dataset when using the same representation and distance metric, e.g., ``TSF-HC'' significantly outperforms ``TSF-ME''.
 However, this is not consistently observed for every combination of representation and distance metric on the mortality dataset.
@@
 
-\section{Conclusion}
+\section{Discussion and Conclusion}
 \label{sec:conclusion}
 
+This paper extends the current body of research on clustering-based forecast reconciliation by introducing a general hierarchical forecasting framework, incorporating three distinct approaches: cluster hierarchies, random hierarchies, and combination hierarchies.
+In contrast to the focused scope of previous studies, our approach to cluster hierarchies involves a broader exploration.
+We examine four time series representations, employ two distance measures, and utilize two clustering algorithms.
+This comprehensive method differs significantly from the existing literature, which typically concentrates on specific clustering implementations.
+We also introduce two innovative random hierarchy construction methods to investigate what drives the performance enhancements in cluster hierarchies.
+These random hierarchies help isolate the effect of clustering, allowing us to focus on the benefits derived from the enriched structure alone.
+Furthermore, we propose combination hierarchies to mitigate uncertainties inherent in random hierarchies.
+
+Our simulation study is constructed around two scenarios, each based on different base forecasting models.
+The first scenario highlights the value of the enriched structure, evident in the high-ranking performance of random combination hierarchies.
+Enriched structure can further improve forecast performance when the base forecasts are of high quality.
+The second scenario demonstrates the efficacy of clustering-based approaches, particularly when the base forecasts at the bottom level are less accurate.
+
+Empirical studies on two datasets support our simulation findings.
+In the tourism dataset, the inferior base forecasts at the bottom level lead to all cluster hierarchies surpassing the original hierarchy, with four outperforming the combination of random hierarchies, which is used to demonstrate the impact of enriched structure.
+In contrast, the superior performance of two random combination hierarchies in the mortality dataset highlights the effectiveness of enriched structure.
+These results imply that the dominant factor, whether it is the enriched structure or clustering, varies depending on the dataset's characteristics, the base forecasting models, and other variables.
+Overall, our findings suggest that hierarchy construction approaches generally enhance performance, and combining these approaches leads to further improvements.
+
+Future research based on our study could proceed in several promising directions.
+Firstly, our experiments were concentrated on total-level and bottom-level series.
+In practical applications, it might be necessary to include specific middle levels or evaluate the entire hierarchy.
+This could lead to the exploration of different hierarchy approaches, such as clustering middle-level series rather than bottom-level ones.
+Although we used equally-weighted combinations in this study, there's potential for applying more sophisticated methods to improve performance.
+The extensive literature on forecast combination, including advanced methods for calculating weights, offers numerous possibilities for enhancement (refer to \citealp{wangForecastCombinations50year2022} for an in-depth review).
+
+In Section~\ref{sec:combination}, we discuss the implications of combining multiple hierarchical structures on the uncertainty in estimating the covariance matrix of base forecast errors.
+Our conclusion was to opt for forecast combination rather than combining the structures of the hierarchies.
+However, a systematic exploration of these two strategies, combining hierarchical structures and combining forecasts, presents an intriguing area for future research.
+Specifically, addressing the challenge of uncertainty due to high dimensionality in the combination of hierarchical structures is possible.
+In this context, innovative solutions like the regularized forecast reconciliation approach, as proposed by \cite{bentaiebRegularizedRegressionHierarchical2019a}, and alternative estimators of the covariance matrix, such as those suggested by \cite{pritulargaStochasticCoherencyForecast2021} could be highly beneficial.
+
+In both our simulation and empirical studies, the combination of random hierarchies displayed competitive results compared to clustering-based methods.
+However, the efficacy of this approach in scenarios with an extremely large number of bottom-level series remains uncertain.
+In such cases, a partially random approach might be more effective.
+For instance, initially generating random hierarchies, identifying those with superior performance, and then constructing partially random hierarchies based on these well-performing structures could be a viable strategy.
+Another intriguing possibility is the integration of both clustering and random approaches.
+Moreover, our study focused specifically on the aggregation of bottom-level series, which may have constrained the potential of middle-level series.
+It's plausible to enhance forecastability at the middle level by creating series through general linear combinations.
+
+Finally, our study was centered around point forecast reconciliation and cross-sectional hierarchy.
+However, the field of probabilistic forecast reconciliation has recently gained significant interest, as evidenced by research like \cite{panagiotelisProbabilisticForecastReconciliation2023} and \cite{jeonProbabilisticForecastReconciliation2019}.
+Applying hierarchy construction approaches to probabilistic forecast reconciliation presents a novel and potentially fruitful research avenue.
+This approach could provide deeper insights and more robust forecast reconciliation methods, particularly in scenarios where uncertainty and variability are significant factors.
+Another promising direction for extending our methodologies lies in exploring temporal (\citealp{athanasopoulosForecastingTemporalHierarchies2017}) and cross-temporal hierarchies (\citealp{girolimettoCrosstemporalProbabilisticForecast2023a}).
+
 \section*{Acknowledgements}
+
+Bohan Zhang is supported by the international joint doctoral education fund of Beihang University.
 

### 2024-04-05 manuscript/manuscript.tex
minor
update

--- 2023-11-26 manuscript/manuscript.tex
@@
 \usepackage{geometry}
+\usepackage{hyperref}
 \usepackage{subfig}
@@
 \setcounter{MaxMatrixCols}{20}
+\usepackage{enumitem}
+
+% Define a new counter for your research questions
+\newcounter{researchquestion}
+\setcounter{researchquestion}{0}
+
+% Define the environment for the research questions
+\newenvironment{researchquestion}{%
+    \refstepcounter{researchquestion}%
+    \par\medskip\noindent%
+    \textbf{RQ\theresearchquestion.}~%
+}{\medskip}
 
@@
 
-  \title{Constructing hierarchies}
+  %\title{On the performance of hierarchy construction: impacts of structure and clustering}
+\title{Augmenting hierarchical time series through clustering: \\Is there an optimal way for forecasting?}
+
+  \author[label1]{Bohan Zhang\corref{cor1}}
+  \address[label1]{School of Economics and Management, Beihang University, Beijing, China}
+  \ead{zhangbohan@buaa.edu.cn}
+  \cortext[cor1]{Corresponding author.}
+  \author[label2]{Anastasios Panagiotelis}
+  \address[label2]{The University of Sydney Business School, NSW 2006, Australia}
+  \author[label3]{Han Li}
+  \address[label3]{Department of Economics, The University of Melbourne, VIC 3010, Australia}
 
   \begin{abstract}
+
+    Forecast reconciliation has attracted significant research interest in recent years, with most studies relying on pre-defined hierarchies constructed with time series metadata.
+With the goal of improving forecast accuracy in mind, we extend and contribute to the emerging research on the clustering-based reconciliation method by proposing a novel framework for hierarchy construction.
+This framework offers three approaches: cluster hierarchies, random hierarchies, and combination hierarchies.
+Utilizing the proposed approaches, we investigate the individual contributions of two primary factors, namely ``grouping'' and ``structure'', to the performance of forecast reconciliation.
+Through a simulation study and experiments on two real-world datasets, we demonstrate the practical efficacy of different hierarchy construction approaches.
+Our findings provide new insights into the dynamics between ``grouping'' and ``structure'', which lead to an improved understanding of forecast reconciliation.\\
 
@@
   \begin{keyword}
-  Forecasting \sep
+  Forecast reconciliation \sep
   Hierarchical time series \sep
-
+  Clustering \sep
+  Hierarchy construction \sep
+  Forecast combination
   \end{keyword}
@@
 
-\section{Methodology}
-\label{sec:method}
+Applications where some variables are aggregates of one another, or so-called \textit{hierarchical time series (HTS)}, are found in many forecasting problems ranging from supply chain management (\citealp{syntetosSupplyChainForecasting2016}) to tourism planning (\citealp{kourentzesCrosstemporalCoherentForecasts2019}), electrical load forecasting (\citealp{jeonProbabilisticForecastReconciliation2019}), and retail demand forecasting (\citealp{makridakisM5AccuracyCompetition2022}).
+In recent decades, there has been an increasing interest in hierarchical forecasting, primarily driven by the success of the optimal reconciliation framework (\citealp{hyndmanOptimalCombinationForecasts2011,wickramasuriyaOptimalForecastReconciliation2019, panagiotelisProbabilisticForecastReconciliation2023}).
+The original motivation for forecast reconciliation was to ensure forecasts are \textit{coherent}, that is they respect the aggregation constraints implied by the hierarchical structure.
+Coherent forecasts faciliate aligned decisions by agents acting upon different variables within the hierarchy.
+For example, consider a retail setting, where a warehouse manager supplies stock to individual store managers within their region.
+Forecasts could be incoherent when the warehouse manager forecasts low total demand while store managers forecast high demand, leading to supply shortages.
+Numerous case studies in the literature demonstrate that reconciliation approaches not only yield coherent forecasts but also enhance overall forecast performance (\citealp{AthanasopoulosForecastReconciliationReview2023}).
 
-\subsection{Framework}
+%The primary objective of hierarchical forecasting is to produce coherent forecasts for the series within a given HTS, which we refer to as \textit{original hierarchy}, ensuring that decision-makers at different levels of the hierarchy can analyze and make informed decisions based on aligned expectations for the future.
+A limitation in the overwhelming majority of the forecast reconciliation studies is that the structure of the hierarchy is taken as \textit{given}.
+This structure usually includes \textit{bottom level series}, an overall aggregate or \textit{top level series}, with various aggregation schemes used to construct \textit{middle levels series}.
+Typically, middle levels are formed according to inherent attributes of the bottom-level series, such as geographical location, gender, product category, travel purpose, and others.
+We refer to this type of structure as the \textit{natural hierarchy}.
+While in some forecasting applications, decisions must be made with respect to the natural hierarchy, in other settings there might be some flexibility in determining how bottom levels are aggregated into middle levels.
+It should be noted that,  very little attention has been paid to whether middle level series can be constructed in a way that leads to further improvements in forecast accuracy relative to a given natural hierarchy.
+To the best of our knowledge, only \cite{pangHierarchicalElectricityTime2018}, \cite{liForecastReconciliationApproach2019}, \cite{pangHierarchicalElectricityTime2022}, and \cite{matteraImprovingOutofSampleForecasts2023} have attempted to \textit{construct} middle level series in a data-driven way which ultimately improved forecast accuracy.
+All three of these works use time series clustering to construct hierarchies in a manner that is somewhat ad hoc.
+Our work conducts a more thorough investigation of issues faced when  constructing hierarchical structures in forecasting reconciliation.
+In particular, we address the following four research questions:%via time series clustering.
+%We also assess and disentangle the impact of
 
-1. construct hierarchies based on historic observations
-2. forecast and reconciliation
-3. evaluation
+%This limitation is evident in the absence of any discussion regarding cluster-based approaches in the recent comprehensive review of forecast reconciliation by \cite{AthanasopoulosForecastReconciliationReview2023}.
+However, the following questions arise when pursuing superior forecast performance, motivating the investigation presented in this paper.
 
-\subsection{Constructing hierarchies by clustering}
+\begin{researchquestion}
+In terms of forecast performance, is the natural hierarchy better than a two-level hierarchy (consisting of only top and bottom time series)? 
+%In terms of forecast performance, does the natural hierarchy outperform a two-level hierarchy of only top and bottom time series?
+\end{researchquestion}
 
-\cite{aghabozorgiTimeseriesClusteringDecade2015a} summarised the four components of time series clustering, including time series representations, distance measures, clustering algorithms and evaluation.
-In our framework, the first three components are involved in the constructing hierarchies procedure.
-The last component includes evaluation of reconciled forecasts of the original hierarchy.
+%Two observations have been consistently demonstrated in empirical studies on forecast reconciliation.
+First, the accuracy of base forecasts, which are influenced by the individual time series characteristics within the hierarchy, critically affects the overall performance of reconciliation.
+For instance, \cite{panagiotelisForecastReconciliationGeometric2021} show that greater performance improvement can be achieved when bias correction for base forecasts is involved.
+%Under the reconciliation framework, improvements in accuracy for some series often come at the expense of others (see \citealp{pritulargaStochasticCoherencyForecast2021}).
+To investigate this question, we consider two widely used empirical HTS datasets; the first is Australian tourism demand, the second, cause-of-death mortality data.
+Throughout the paper, all evaluations are carried out using the series common to all hierarchies; namely the top and bottom level series.
+In both datasets, we find that the natural hierarchy outperforms the two-level hierarchy, leading to our next research question:
+\begin{researchquestion}
+    If the use of middle level series in the ``natural'' hierarchy can lead to improvement in forecast accuracy, is it possible to construct hierarchies in a data-driven way that leads to further improvements in forecast accuracy?
+\end{researchquestion}
 
-\subsubsection*{Time series representations}
+The rationale behind the data-driven approach lies in grouping time series with similar patterns together, thereby creating middle-level series with enhanced signals and consequently, improved forecastability.
+Such arguments have been put forward by  \cite{pangHierarchicalElectricityTime2018}, \cite{liForecastReconciliationApproach2019}, \cite{pangHierarchicalElectricityTime2022}, and \cite{matteraImprovingOutofSampleForecasts2023}.
+However, these studies for the most part focus on a small number of (in some cases, a single) clustering techniques.
+In this paper, we take a more systematic approach by clustering time series using different representations (the original time series, forecast errors, features of both), different distance metrics (Euclidean, dynamic time warping), and different clustering paradigms ($k$-medioids, hierarchical).
+Using both empirical datasets, as well as a simulation study, we find evidence that constructing hierarchies via clustering can lead to improved forecasting performance, although the optimal clustering method depends on the dataset as well as the base forecasting and reconciliation method.
 
-Time-series representations represent raw time series in another space through techniques like feature extraction or dimensionality reduction.
-By utilising diverse time series representations, we are able to obtain distinct clusters which offer varied perspectives on the same dataset.
-Despite the absence of the theoretical evidence regarding how groups in hierarchical time series affect forecast reconciliation performance, we seek to explore multiple time series representations and discern potential correlations between hierarchical structure and the efficacy of forecast reconciliation.
+While the idea behind time series clustering is intuitively appealing, the increased accuracy when using clustering-based methods may be attributed to two factors.
+The first, which we refer to as     ``grouping'' is the idea that some correct subsets of series are chosen to form new middle-level series.
+This is the argument commonly made to support clustering-based hierarchy construction \citep[see e.g.][]{liForecastReconciliationApproach2019, pangHierarchicalElectricityTime2022, matteraImprovingOutofSampleForecasts2023}.
+%The idea that often motivates time series clustering is these ``groupings'' be composed of similar series. 
+The second factor, which we refer to as the ``structure'' of the hierarchy, includes the number of middle level series, the depth of the hierarchy, and the distribution of group sizes in the middle layer(s).
+Evidence showing that clustering within a forecast reconciliation framework leads to improved forecast accuracy, does not disentangle contributions from these two factors.
+Indeed, clustering methods may only work in so far as they generate a larger number of base forecasts.
+This argument would be consistent with the interpretation of reconciliation as a forecast combination of ``direct'' and ``indirect'' forecasts (\citealp{hollymanUnderstandingForecastReconciliation2021}), since more middle-level series implies a greater number of indirect forecasts in the combination.
+This leads to our third research question:
 
-Considering the impracticality of exploring every conceivable time series representation, we focus on four key ones: raw time series, in-sample error, features of time series, and features of in-sample error.
+\begin{researchquestion}
+    Can the improved accuracy of cluster-based methods be attributed to grouping together similar time series, or to the structure of the hierarchy including the number of middle level series?
+\end{researchquestion}
+
+To investigate this question, we devise the following approach.
+We take a hierarchy found using a certain clustering method (or even the natural hierarchy), and then randomly permute the bottom level series (\textit{i.e.}, the leaf nodes of the hierarchical tree).
+Multiple new ``twin'' hierarchies are formed with an identical structure to the original hierarchy, but with permuted leaves.
+In this way, we keep the \textit{hierarchical structure} fixed, but alter how series are combined.
+This method can be thought of as an informal ``permutation type'' test \citep{welch1990}.
+Our main finding is that hierarchies constructed using clustering methods do not significantly outperform their random ``twins'', leading to the conclusion that the driver of forecast improvement is the enlarged number of series in the hierarchy and/or its structure, rather than similarities between the time series.
+
+%Despite the intuitive appeal of clustering analysis, it is not straightforward to conclude that clustering itself is the primary contributor to the performance improvement illustrated in the literature.
+Except the factor of potentially accurate base forecasts of new series introduced by clustering, another factor  is the ``enriched structure'', meaning that a larger set of series is optimally combined to obtain the reconciled forecasts, leading to reduced model uncertainty and data uncertainty from forecast combination perspective (\citealp{hollymanUnderstandingForecastReconciliation2021}).
+The following question also motivates our research:
+%\begin{researchquestion}
+%Which factor, enriched structure or clustering, is the primary contributor to the performance improvement illustrated in clustering-based reconciliation approaches?
+%\end{researchquestion}
+
+%To address this question, we propose a random hierarchy construction approach.
+By randomly constructing ``twin'' hierarchies with the same tree structure but different permutations of bottom-level series as a contrast to a clustering-based hierarchy, we are able to isolate the influence of clustering algorithms.
+This allows us to inspect the individual contributions of the enriched structure and clustering technique to forecast reconciliation performance.
+
+Finally, from a practical perspective, we investigate the role of forecast combination in cluster-based hierarchical forecasting.
+With multiple hierarchies available and inspired by the forecast combination literature (\citealp{wangForecastCombinations50year2022}), we consider the last research question
+
+\begin{researchquestion}
+    Does an equally-weighted combination of reconciled forecasts derived from multiple random hierarchies improve forecast reconciliation performance?
+\end{researchquestion}
+
+Note that forecast combination here differs from that of \cite{hollymanUnderstandingForecastReconciliation2021}, in that our approach averages not only different coherent forecasts, but also over hierarchies with completely different middle level series.
+This is possible since only coherent bottom and top level forecasts are averaged and evaluated.
+\clearpage
+In summary, this paper presents four main contributions:
+
+\begin{itemize}
+  \item We introduce a novel hierarchical forecast reconciliation framework centered on hierarchy construction.
+Within this framework, we introduce and compare three distinct approaches: cluster-based hierarchies, hierarchies based on random permutation, and  forecast combinations across different hierarchies.
+  \item In contrast to existing literature that often focuses on a single clustering technique, our study systematically investigates the effectiveness of various time series clustering implementations.
+This investigation involves the incorporation of four time series representations, two distance measures, and two clustering algorithms.
+  \item We conduct experiments using two empirical datasets - the Australian tourism dataset and the U.S.
+cause-of-death mortality dataset as well as a synthetic dataset.
+The results allow for a comparison of different approaches to constructing hierarchies.
+  \item By constructing random hierarchies through permutation of leaf nodes, we show that the hierarchical structure is the primary contributor to improvements in forecast reconciliation performance, rather than the grouping of similar bottom level series.
+
+\end{itemize}
+
+The rest of the paper is organized as follows.
+Section~\ref{sec:setup} describes the experimental setup including the datasets used, the reconciliation methods employed, the clustering techniques considered, and the rolling window evaluation with associated forecast performance metrics.
+Section~\ref{sec:natural} investigates RQ1, in particular the performance of the natural hierarchy compared to the two-level hierarchy.
+The permutation approach used throughout the paper is also introduced at this juncture.
+Section~\ref{sec:clustering} evaluate the performance of different clustering approaches in answering RQ2 and RQ3 via two empirical studies.
+To avoid the concern that clusters found in the empirical datasets are spurious, a simulation study is considered in Section~\ref{sec:simulation}.
+Section~\ref{sec:combination} covers the forecast combination approaches raised in RQ4.
+Section~\ref{sec:conclusion} concludes this paper with discussions on the findings and outlines future research directions.
+
+%Section~\ref{sec:related_work} reviews related work in time series clustering, forecast reconciliation and clustering-based forecast reconciliation.
+In Section~\ref{sec:method} we introduce the proposed framework, elaborating on three approaches: cluster hierarchies, random hierarchies and combination hierarchies.
+The simulation study is presented in Section~\ref{sec:simulation}, while Section~\ref{sec:emp} details empirical experiments conducted on the Australian tourism dataset and U.S.
+mortality dataset.
+Finally, Section~\ref{sec:conclusion} concludes this paper with discussions on the findings and outlines future research directions.
+
+\section{Experiment setup}\label{sec:setup}
+
+\subsection{Dataset description}
+
+We conduct our experiments on two empirical datasets throughout this paper.
+The first one is the monthly Australian domestic tourism dataset, covering the period from January 1998 to December 2016.
+The data is recorded as ``visitor nights'', representing the total number of nights spent by Australians away from home.
+In this dataset, the total visitor nights of Australia is geographically disaggregated into seven states and territories, which are further divided into $27$ zones, and then into $76$ regions.
+Additionally, each regional-level series is divided by four travel purposes.
+Overall, this dataset comprises a total of $555$ time series with $304$ of those at the bottom level.
+Section 4 of \cite{wickramasuriyaOptimalForecastReconciliation2019} provided an in-depth explanation of this dataset.
+
+The second dataset focuses on cause-of-death mortality in the U.S.
+We obtain monthly cause-specific death count data from the Center for Disease Control and Prevention (CDC) for the period between January 1999 and December 2019.
+The dataset, organized based on the 10th revision of the International Classification of Diseases (ICD) 113 Cause List\footnote{For more detailed information on the dataset, please refer to \url{https://wonder.cdc.gov/ucd-icd10-expanded.html}.}, forms a hierarchy containing $120$ time series, with $98$ of those being bottom-level series\footnote{To address the data suppression issue, we combined certain ICD codes to ensure all death counts are no less than 10.
+}.
+The top-level series represents the aggregated deaths from all causes, while the middle-level series are constructed based on major cause-of-death groups.
+As an example, \textit{Diseases of heart} (ICD code: I00--I09, I11, I13, I20--I51; 113 Cause List: GR113-054) is a middle-level series in the hierarchy, which contains bottom-level series \textit{Hypertensive heart disease} (I11; GR113-056) and \textit{Heart failure} (I50; GR113-067), among other circulatory diseases.
+% To address issues with suppressed data values, we combine causes that contain suppressed values and share a parent cause.
+The death counts for these combined categories are calculated by subtracting the death counts of sibling causes from the death counts of their parent causes.
+This processing results in a refined dataset that includes $120$ time series with $98$ at the bottom level.
+
+Figures~\ref{fig:tourism} and~\ref{fig:mortality} illustrate the top-level series and four bottom-level series for the tourism and mortality datasets, respectively. 
+In the case of tourism data, the first three letters indicate geographical regions, and the last three denote travel purposes.
+For example, ``\textit{BEEHol}'' represents the visitor nights spent for holiday in the `Spa Country' region.
+As mentioned before, the death series are coded based on the ICD 113 Cause List.
+From the figures, we can see that the mortality dataset generally exhibits strong seasonality and trend, whereas the tourism dataset displays greater volatility and less obvious seasonal and trend components.
+We can also see that the patterns observed at the bottom level can be very different from those at the top and middle levels.
+
+%Names of mortality series are ICD codes representing causes of deaths. For example, \code{GR113-085} represents deaths because of asthma.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/tourism.pdf}
+    \caption{Visualization of selected time series from the tourism dataset.
+``AEB'', ``BAB'', ``BEB'', and ``BEE'' represent the regions `New England North West`, `Peninsula', `Western Grampians` and ``Spa Country'', respectively.
+``Bus'', ``Oth'', ``Vis'' and ``Hol'' denote travel purposes ``Business'', ``Other'', ``Visit'' and ``Holiday'', respectively.}
+    \label{fig:tourism}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/mortality.pdf}
+    \caption{{Visualization of selected time series from the death count dataset.} ``GR113-051'',  ``GR113-063'', ``GR113-085'', and ``GR113-091'' denote ``Parkinson disease'', ``All other forms of chronic ischemic heart disease'', ``Asthma'', and ``Diseases of appendix'', respectively.}
+    \label{fig:mortality}
+\end{figure}
+
+\subsection{Trace minimization forecast reconciliation approach}
+
+In this subsection, we describe the process of generating coherent forecasts using the trace minimization (MinT) reconciliation approach \citep{wickramasuriyaOptimalForecastReconciliation2019}, which will be employed throughout this paper.
+Consider a given hierarchy with $n$ time series and $m$ of them being in the bottom level.
+Let vectors $\boldsymbol{b}_t$, $\boldsymbol{a}_t$, and $\boldsymbol{y}_t$ represent observations of the bottom level, the aggregated levels (\textit{i.e.} middle and top levels), and the entire hierarchy at time $t$, respectively.
+They are linked through an $n\times m$ summing matrix $\boldsymbol{S}$, which can be decomposed into an identity matrix $\boldsymbol{I}_m$ and a constraint matrix $\boldsymbol{A}$ consisting of $0$ and $1$, such that,
+\[
+  \boldsymbol{y}_t = \boldsymbol{S}\boldsymbol{b}_t = \begin{bmatrix}
+    \boldsymbol{A} \\ \boldsymbol{I}_m 
+  \end{bmatrix}  \boldsymbol{b}_t = \begin{bmatrix}
+      \boldsymbol{a}_t \\ \boldsymbol{b}_t
+  \end{bmatrix},
+\]
+where $\boldsymbol{A}$ represents the mapping from bottom-level time series to aggregated-level time series.
+
+Assume our objective is to make $h$-step-ahead forecasts based on $T$ historic observations, we would first produce $h$-step-ahead unreconciled (or ``base'') forecasts $\hat{\boldsymbol{y}}_{T+h}$.
+Note that there are many different ways to compute such forecasts.
+In this paper, we adopt the Exponential Smoothing (ETS) method, a well-known univariate forecasting model widely used in both academia and industry \citep{ForecastingExponentialSmoothing}.
+The \code{forecast} (\citealp{forecast}) package in {R} (\citealp{R}) is implemented to produce base forecasts for each time series in the hierarchy.
+Subsequently, the MinT reconciliation method is applied to produce coherent forecasts:
+\[
+    \tilde{\boldsymbol{y}}_{T+h} = (\boldsymbol{S}'\boldsymbol{W}_h^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}_h^{-1}\hat{\boldsymbol{y}}_{T+h},
+\]
+where $\boldsymbol{W}_h$ is the covariance matrix of $h$-step-ahead forecast errors, which is estimated using the MinT shrinkage estimator based on the in-sample one-step-ahead forecast errors (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
+
+%\subsection{Grouping-based forecast reconciliation}
+\subsection{Augmenting hierarchical time series through clustering}
+
+%DELETE
+
+%Instead of a We use the term ``augmentation'' to denote the process of creating middle-level series by aggregating subsets of bottom-level series.
+leading to a modified hierarchical time series $\boldsymbol{y}^c_t$, which can be represented as:
+%leading to a modified hierarchical time series $\boldsymbol{y}^c_t$, which can be represented as:
+%\[
+%   \boldsymbol{y}^c_t = \boldsymbol{S}^c\boldsymbol{b}_t = \begin{bmatrix}
+%        \boldsymbol{A}' &
+%        \boldsymbol{C}_1 &
+%        \cdots &
+%        \boldsymbol{C}_K &
+%        \boldsymbol{I}_m
+    %\end{bmatrix}'\boldsymbol{b}_t,
+%\] 
+%where each $\boldsymbol{C}_k$ represents a newly created middle-level series, formed by aggregating a subset of bottom-level series $\boldsymbol{b}_t$.
+The vector $\boldsymbol{C}_k$ is of $m$-dimensional and its elements $c_{k, i} \in \{0, 1\}, i=1,\dots m$ indicate whether the $i$-th bottom-level series belongs to the aggregated subset.
+Notably, different augmentation approaches can result in different hierarchies with varying numbers of new middle-level series $K$.
+
+%After new hierarchies are constructed, we produce $h$-step-ahead base forecasts based on $T$ observations for each time series in the new hierarchy, and apply forecast reconciliation with MinT shrinkage estimator to obtain reconciled forecasts $\tilde{\boldsymbol{y}}^c_{T+h}$.
+Given our specific interest in the performance of the two-level hierarchy, we extract reconciled forecasts of the two-level hierarchy from $\tilde{\boldsymbol{y}}_{T+h}^c$, \textit{i.e.},
+%\[
+%  \tilde{\boldsymbol{y}}_{T+h} = \tilde{\boldsymbol{y}}^c_{T+h, 1:(n-m) \cup (n + K - m + 1): (n+K)}.
+%\]
+
+%\subsection{Cluster hierarchy construction approach}
+
+To the best of our knowledge, the following studies are the exclusive examples in the literature that propose to integrate forecast reconciliation with hierarchy construction via time series clustering.
+\cite{pangHierarchicalElectricityTime2018} detect consumption patterns of electricity smart meter data based on X-means clustering algorithm, while \cite{pangHierarchicalElectricityTime2022} propose a multiple alternative clustering method to group similar electricity and solar power time series.
+\cite{liForecastReconciliationApproach2019} apply agglomerative clustering to cause-of-death time series, and
+\cite{matteraImprovingOutofSampleForecasts2023} utilize Partition Around Medoids algorithms to unveil underlying structures in stock price indexes. 
+These studies demonstrate superior forecast performance of the clustering-based hierarchies compared to the natural hierarchy or the two-level hierarchy.
+However, these studies are limited in scope as they focus on a small number of  clustering techniques. 
+%construct hierarchies through clustering algorithms and
+
+Inspired by the comprehensive overview of time series clustering by \cite{aghabozorgiTimeseriesClusteringDecade2015a}, we consider various approaches based on three key components, namely time series representations, distance measures, and clustering algorithms.
+Our framework for creating a clustering approach is as follows: we first choose a time series representation, which can be the raw time series, the in-sample forecast error, features of the time series, or features of the in-sample forecast error.
+We then select a distance measure, either Euclidean distance or dynamic time warping.
+Once the representation and the distance measure are determined, we choose a clustering algorithm, either $k$-medoids or agglomerative hierarchical clustering, to form clusters in the dataset.
+In total, we consider 12 different clustering approaches in our experiments.
+%, and evaluation measures.
+
+% Time series clustering is an essential technique that finds applications across various domains, including finance (\citealp{DIAS2015852}), energy (\citealp{pangHierarchicalElectricityTime2018}), robotics (\citealp{gopalapillaiExperimentationAnalysisTime2014}), and others.
+It is commonly used to identify similar patterns within time series datasets, aiding in applications such as anomaly detection, pattern discovery, and recommendation.
+
+\subsubsection{Time series representations}
+
+The first step of time series clustering is to find appropriate time series representations.
+Time series representations transform time series data into another space through techniques like feature extraction or dimension reduction.
+By utilizing diverse time series representations, we are able to obtain distinct clusters which offer varied perspectives on the same dataset.
+Considering the impracticality of exploring every conceivable time series representation, we focus on four key ones: raw time series without any transformation (hereafter referred to as ``time series''), in-sample one-step-ahead forecast error, features of time series, and features of in-sample one-step-ahead forecast error.
 The inclusion of raw time series is motivated by its simplicity and broad applicability.
-A crucial element contributing to the success of the minimum trace method proposed by \cite{wickramasuriyaOptimalForecastReconciliation2019} lies in estimating the covariance matrix of base forecast errors based on in-sample fit error.
-Hence, we consider in-sample error as a representation to examine how the structure within the error series influences reconciliation performance.
-Notably, to the best of our knowledge, we are the first to utilise in-sample error as a time series representation in the context of forecast reconciliation literature.
-The time series and in-sample error representations are standardised on a per-series basis to eliminate the impact of scale variations.
+A crucial element contributing to the success of the MinT method lies in estimating the covariance matrix of base forecast errors based on in-sample one-step-ahead forecast error.
+Hence, we consider in-sample one-step-ahead forecast error as a representation to examine how the structure within the error series influences reconciliation performance.
+Raw time series and in-sample error representations are standardized to eliminate the impact of scale variations.
+This is done by normalizing each series by subtracting its mean and then dividing by the standard error.
+
 Features, widely employed in capturing time series characteristics across literature, play a pivotal role in various time series applications, including clustering (\citealp{tianoFeatTSFeaturebasedTime2021}) and forecasting (\citealp{wangUncertaintyEstimationFeaturebased2022, liFeaturebasedIntermittentDemand2023}).
-In our exploration, we incorporate features of both time series and in-sample fit error as representations.
-These representations allow us to glean insights into the diverse aspects of hierarchical time series data and enhance our understanding of how different structures contribute to the forecast reconciliation performance.
+In our exploration, we incorporate features of both raw time series and in-sample forecast error as representations.
+The included time series features, calculated by the \code{tsfeatures} (\citealp{tsfeatures}) in R, have been applied in several feature-based forecasting studies, \textit{e.g.}, \cite{montero-mansoFFORMAFeaturebasedForecast2020}.
+Notably, to the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation literature.
+These representations allow us to gain insights into the diverse aspects of hierarchical time series data.
 
-\subsubsection*{Distance measures}
+\subsubsection{Distance measures}
 
-Distance measures serve as crucial tools for assessing the similarity between two series, forming the foundation for clustering algorithms to detect clusters within datasets.
-In the realm of time series clustering literature, we consider two widely applied distance measures: Euclidean distance and dynamic time warping (DTW) (\citealp{warrenliaoClusteringTimeSeries2005}).
+Distance measures serve as crucial tools for assessing the similarity/dissimilarity between two series, significantly influencing the clustering results.
+We consider two widely applied distance measures: Euclidean distance and dynamic time warping (DTW).
+Due to the limited number of time series in comparison to the high dimensionality of individual time series (\textit{i.e.}, the length of time series and the number of time series features) in our applications, dimension reduction on the aforementioned representations becomes imperative when employing Euclidean distance.
+Failure to undertake dimension reduction may result in undesirable clustering outcomes due to the curse of dimensionality.
+To address this, we perform Principal Component Analysis (PCA), extracting the first few principal components that collectively explain at least 80\% of the variance within the representations.
 
-Given the limited number of time series in comparison to the variable dimensions (i.e., the length of time series and the number of time series features) within hierarchical time series in our applications, dimension reduction on the aforementioned representations becomes imperative when employing Euclidean distance.
-Failure to undertake dimension reduction may result in undesirable clustering outcomes due to the challenges posed by the curse of dimensionality.
-To address this, we perform principal component analysis, extracting the first few principal components that collectively explain at least 80\% of the variance within the data.
+In contrast, DTW (\citealp{sakoeDynamicProgrammingAlgorithm1978}), exhibits reduced sensitivity to the curse of dimensionality.
+Unlike Euclidean distance, which performs one-to-one point comparisons, DTW accommodates time series of varying lengths through many-to-one comparisons.
+This flexible approach allows for the recognition of time series with similar shapes, even in the presence of signal transformations such as shifting and/or scaling.
 
-In contrast, DTW (\citealp{sakoeDynamicProgrammingAlgorithm1978}), demonstrates reduced sensitivity to the curse of dimensionality.
-Unlike the one-to-one point comparison inherent in Euclidean distance, DTW accommodates time series of varying lengths through many-to-one comparisons.
-This adaptive approach allows for the recognition of time series with similar shapes, even in the presence of signal transformations such as shifting and/or scaling.
-
-\subsubsection*{Clustering algorithms}
-\label{sec:clustering}
-
-Regarding clustering algorithms, we consider two common approaches, k-Medoids and agglomerative hierarchical clustering.
-K-Medoids algorithm is one of the classical partitioning clustering algorithms.
-The idea behind partitioning clustering is the minimisation of the total distance between all samples in a cluster from their cluster centres.
-We consider k-Medoids instead of the well known k-Means because k-Means use mean vector of samples within a cluster as cluster centre, which is not trivial when using DTW distance measure.
-In contrast, k-Medoids select one of the samples in the cluster as cluster centre.
-We use the k-Meodoids variants partitioning around medoids (PAM, \citealp{PartitioningMedoidsProgram1990}).
-The most important parameter for k-Medoids algorithm is the number of cluster.
-We follow the suggestion of \cite{PartitioningMedoidsProgram1990} to choose the optimal number of cluster by average silhouette width (ASW), which is a popular cluster validation index to estimate the number of clusters.
-Given a clustering $\mathcal{C}$, the silhouette width for the $i$th sample is calculated as
+\subsubsection{Clustering algorithms}
+Clustering algorithms, such as partitioning, hierarchical, grid-based, model-based clustering, among others, identify clusters by optimizing specific objective functions (\citealp{aghabozorgiTimeseriesClusteringDecade2015a}).
+These functions are calculated based on chosen time series representations and distance measures.
+In this paper, we focus on two prevalent approaches, $k$-medoids and agglomerative hierarchical clustering.
+The $k$-medoids algorithm, a classical partitioning clustering method, aims to minimize the total distance between all samples within a cluster and their respective cluster centers.
+Unlike $k$-means which employs the mean vector of samples as the cluster center, $k$-medoids selects one sample within the cluster as the center. 
+Specifically, we adopt the $k$-medoids variant, partitioning around medoids (PAM, \citealp{PartitioningMedoidsProgram1990}).
+Following the recommendation of \cite{PartitioningMedoidsProgram1990}, we determine the optimal number of cluster using the average silhouette width (ASW), a popular cluster validation index.
+ASW assesses the quality of clustering results by measuring the proximity of samples within a cluster compared to neighboring clusters.
+Given a clustering result, the silhouette width for the $i$th sample is calculated as 
 \[
@@
 \]
-where $a(i)$ is the average distance of $i$the sample to samples in the cluster to which it is assigned, and $b(i)$ is the average distance of $i$th sample to the samples in the nearest cluster it is not assigned.
-A large value of silhouette means that the corresponding sample is much closer to the samples to the samples in its own cluster than to the neighbouring one.
-Silhouette width is zero for the sample which is the only sample in its cluster.
-ASW is calculated as the average of silhouette widths of all samples.
-By iterating over all possible number of clusters, we choose the clustering result $\mathcal{C}$ that maximises the ASW as the optimal result.
-One drawback of this approach is that ASW does not exist when there is only one cluster, meaning that it can not determine whether there are well separated clusters or not.
-Gap statistics (\citealp{tibshiraniEstimatingNumberClusters2002}) can address this issue, but it can not be used with DTW.
+where $a(i)$ represents the average distance of the $i$th sample to others in the same cluster, and $b(i)$ is the average distance to samples in the nearest cluster it is not assigned to.
+A higher silhouette width indicates greater proximity to samples within the same cluster than to those in neighboring clusters.
+The ASW is the average of silhouette widths across all samples.
+We select the clustering result that maximizes the ASW by iterating over all possible numbers of clusters.
+However, ASW has the limitation of being undefined when there is only one cluster.
 
-hierarchical clustering
+On the other hand, agglomerative hierarchical clustering begins by considering each sample as a cluster, and then gradually merges clusters until all samples forms a single cluster.
+Recall that $m$ represents the number of bottom level series.
+This process results in a binary hierarchical tree with ($2m-1$) nodes.
+We employ Ward's linkage (\citealp{murtaghWardHierarchicalAgglomerative2014a}) to merge clusters, minimizing the increase of within-cluster variances at each step.
 
-\subsection{Constructing hierarchies randomly}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/pamcluster.pdf}
+    \hspace{1cm}
+    \includegraphics[width=0.45\textwidth]{figures/aggcluster.pdf}
+    \caption{\label{fig:cluster_example}Example clustering results of two clustering algorithms.
+Left panel displays example for $k$-medoids algorithm, and right panel displays example for agglomerative hierarchical clustering algorithm.}
+\end{figure}
+Illustrated in Figure~\ref{fig:cluster_example} are two example hierarchies generated by $k$-medoids and agglomerative clustering algorithms for an original hierarchy with four bottom-level series and one total series.
+These examples highlight the distinct behaviors of the two algorithms.
+Firstly, $k$-medoids constructs a simple hierarchy with a single middle level, while hierarchical clustering generates multiple nested middle levels. 
+Secondly, $k$-medoids produces a hierarchy with the same number of series as the optimal number of clusters, whereas hierarchical clustering yields multiple middle levels with ($m-2$) series.
+As the number of bottom-level series increases, the structural differences become increasingly significant, and we aim to investigate how these differences influence the performance of forecast reconciliation.
 
-pure random
+In summary, we employ 12 time series clustering approaches which are derived from combinations of four time series representations, two distance measures, and two clustering algorithms.
+The names and details of these approaches are listed in Table~\ref{tab:P3_methods}.
+The four time series representations need to perform dimension reduction when using Euclidean distance.
+Combing the four dimension reduced representations with two clustering algorithms results in the first eight clustering approaches.
+Note that features of raw time series and in-sample forecast error are not temporal data, thus incompatible with DTW.
+Therefore, the last four approaches are derived from combinations of two temporal representations (\textit{i.e.}, raw time series and in-sample error), DTW, and two clustering algorithms.
+After filtering out the features that are constant across all series, $56$ features are reserved.
+The list and descriptions of features are available in the supplementary materials.
+The $k$-medoids and hierarchical clustering algorithms are implemented using the \texttt{cluster} (\citealp{cluster}) package in R.
 
-random based on specific structure
+\begin{table}[h!]
+\caption{\label{tab:P3_methods} Details of the 12 clustering approaches considered.}
+\centering
+\resizebox{\textwidth}{!}{
+\begin{tabular}{lcrrr}
+    \toprule
+    Approaches & Dimension reduction & Representation & Distance measure & Clustering algorithms  \\ \midrule
+    TS-EUC-ME &  Yes & Time series  & Euclidean & $k$-medoids \\
+    ER-EUC-ME & Yes& In-sample error  & Euclidean & $k$-medoids \\
+    TSF-EUC-ME & Yes& Time series features  & Euclidean & $k$-medoids \\
+    ERF-EUC-ME & Yes& In-sample error features  & Euclidean & $k$-medoids \\
+    TS-EUC-HC & Yes& Time series  & Euclidean & hierarchical   \\ 
+    ER-EUC-HC & Yes& In-sample error  & Euclidean & hierarchical   \\ 
+    TSF-EUC-HC & Yes& Time series features  & Euclidean & hierarchical   \\ 
+    ERF-EUC-HC & Yes& In-sample error features  & Euclidean & hierarchical  \\
+    TS-DTW-ME & No& Time series  & DTW & $k$-medoids \\
+    TS-DTW-HC & No& In-sample error  & DTW & hierarchical  \\
+    ER-DTW-ME & No& Time series  & DTW & $k$-medoids \\
+    ER-DTW-HC & No& In-sample error  & DTW & hierarchical 
+     \\\bottomrule
+\end{tabular}}
+\end{table}
 
-\subsection{Forecast combination}
+\subsection{Evaluation of forecast accuracy}
+\label{subsec:evaluation}
 
-\section{Simulation}
+We investigate the impact of clustering on forecast reconciliation via a systematic comparison of the forecast accuracy based on different hierarchies. 
+%time series clustering techniques in Table \ref{tab:P3_methods}.
+%This comparison incorporates a diverse set of time series representations, distance measures, and clustering algorithms to provide a more thorough understanding of their impact on forecast performance.\\
+To evaluate the accuracy of reconciled forecasts based on a given hierarchical structure, we first calculate Root Mean Squared Scaled Error (RMSSE, \citealp{makridakisM5AccuracyCompetition2022}) for each series.
+RMSSE is symmetric, independent of the data scale, and thus suitable for evaluating hierarchical forecasts (\citealp{athanasopoulosEvaluationHierarchicalForecasts2023}). 
+It is defined as follows:
+\[
+RMSSE = \sqrt{\frac{\frac{1}{h}\displaystyle\sum_{t=T+1}^{T+h}(y_t-\hat y_{t})^2}{\frac{1}{T-12}\displaystyle\sum_{t=13}^T (y_t - y_{t-12})^2}},
+\]
+where $\hat y_t$ is the reconciled forecast or base forecast of series $y_t$.
+It should be note that the denominator of our RMSSE measure is not exactly same as that in \cite{makridakisM5AccuracyCompetition2022}.
+We use the in-sample mean squared error of the seasonal naive method because the time series in our applications exhibit monthly seasonality.
+Then, we take average RMSSE of all forecasts in $\tilde{\boldsymbol{y}}_{T+h}$ as measure for the hierarchy.
+
+To rigorously validate our hypothesis, we utilize the rolling window strategy to evaluate the performance of different approaches on both datasets.
+We begin by producing and evaluating $12$-steps-ahead coherent forecasts using the first $96$ observations.
+The training set is then increased by one observation and new forecasts are obtained.
+The procedure is repeated until the last $12$ observations are used for evaluation.
+Finally, we can obtain $121$ RMSSE (January 2006 - January 2016) for the tourism dataset and $145$ RMSSE (January 2007 - January 2019) for the mortality dataset.
+Two approaches are utilized to compare and present the performance of various approaches on two datasets.
+The first one is to calculate average RMSSE across all evaluation windows, while the second involves Multiple Comparison with the Best (MCB) test (\citealp{koningM3CompetitionStatistical2005}), which computes the average ranks of different approaches across all evaluation windows and assess whether they are statistically different.
+
+\section{Natural hierarchy}\label{sec:natural}
+
+\subsection{Natural hierarchy vs two-level hierarchy}
+\label{subsec:n_vs_twolevel}
+In this subsection, we compare the performance of the natural hierarchy against the two-level hierarchy to address the first research question.
+We expect that natural hierarchy would demonstrate superior performance over the two-level hierarchy, as more time series are included in the reconciliation process.
+Following the evaluation procedure introduced in Section~\ref{subsec:evaluation}, Table~\ref{tab:P1} compares forecast accuracy of the natural hierarchy and the two-level hierarchy on tourism and mortality datasets.
+Average RMSSE is calculated across all evaluation windows.
+%in terms of average RMSSE across all evaluation windows. 
+The asterisk in table indicates significant difference according to MCB test.
+Table~\ref{tab:P1} shows that natural hierarchy significantly outperforms the two-level hierarchy on both datasets.
+It confirms our hypothesis that natural hierarchy improves forecast performance over a two-level hierarchy.
+
+\begin{table}[h!]
+    \centering
+    \caption{\label{tab:P1} Performance of natural and two-level hierarchies in terms of average RMSSE ($\times 10^{-2}$) across all evaluation windows on both datasets.
+Column-wise minimum values are displayed in bold.
+Asterisk (*) indicates significant difference according to MCB test.}
+    \begin{tabular}{lll}
+    \toprule
+        Method & tourism & mortality \\ \midrule
+        Natural & $\bold{69.13}^*$ & $\bold{75.01}^*$ \\ 
+        Two-level & $69.43$ & $75.28$ \\ \bottomrule
+    \end{tabular}
+
+\end{table}
+
+\subsection{Permutation of the natural hierarchy}
+\label{subsec:permutation}
+
+There are two potential contributors to the improvement in accuracy achieved by the natural hierarchy. First, natural hierarchy could tend to group time series with similar attributes together. 
+It is possible that these series share similar trend and seasonality pattern, similar features, strong correlations, or others, resulting in middle-level series with strong signals and easy to forecast.
+Thus, total and bottom-level series can borrow strength from these middle-level series during reconciliation. 
+We refer to this aspect as ``grouping''.
+Second, there are more series and more base forecasts to be combined during reconciliation, which leads to reduced uncertainty (\citealp{petropoulosExploringSourcesUncertainty2018a}) and improved reconciled forecasts.
+How the series are grouped is however irrelevant.
+We refer to this aspect as ``structure''.
+
+To systematically explore these two aspects, we introduce a permutation hierarchy construction method.
+Given a hierarchy tree, such as the natural hierarchy, the proposed approach constructs new hierarchies by randomly permuting the leaves.
+Recall that $\boldsymbol{A}$ is matrix consisting of $0$ and $1$ and represents the mapping from bottom-level time series to aggregated-level time series.
+In other words, it shuffles the columns of the constraint matrix $\boldsymbol{A}$ of the given hierarchy.
+This method yields random ``twin'' hierarchies with the same tree structure but different groupings.
+By generating forecasts using the twin hierarchies, we are able to eliminate the influence of grouping and focus specifically on structure. 
+If the random twin hierarchies significantly outperform the original counterpart, it suggests that structure holds greater importance than grouping, and vice versa.
+Figure~\ref{fig:aggcluster_random} shows an example of this approach, where the right hierarchy is a ``twin'' of the left hierarchy.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/aggcluster_random.pdf}
+
+    \[
+    \begin{bmatrix}
+    1 & 1 & 1 & 1\\
+    1 & 1 & 1 & 0 \\
+    1 & 1 & 0 & 0 \\
+    & I_4 & & 
+    \end{bmatrix}
+    \quad
+    \rightarrow
+    \quad
+    \begin{bmatrix}
+    1 & 1 & 1 & 1\\
+    0 & 1 & 1 & 1 \\
+    0 & 1 & 0 & 1 \\
+    & I_4 & & 
+    \end{bmatrix}
+    \]
+
+\caption{\label{fig:aggcluster_random}Examples of permutation of a given hierarchy.
+Right hierarchy is obtained by shuffling the leaves of left hierarchy.
+The upper part displays the hierarchy trees, and the lower part displays the corresponding summing matrices.}
+\end{figure}
+
+\subsection{Natural hierarchy versus its twins}
+\label{subsec:n_vs_pn}
+
+This subsection compares the performance of natural hierarchy and its random twins on mortality and tourism datasets.
+For each dataset, we first randomly generate $100$ permutations of the bottom-level series, which are applied to the natural hierarchy, producing $100$ twin hierarchies.
+Performances of natural hierarchy and its twins are compared using the evaluation process described in Section~\ref{subsec:evaluation}.
+
+Figures~\ref{fig:P2_tourism} and~\ref{fig:P2_mortality} display the MCB test results for the tourism dataset and mortality, respectively. 
+In order to save space, we only display the average rank labels for the natural hierarchy and $5$ twins.
+The grey zone indicates the confidence interval of the average rank of natural hierarchy.
+Any hierarchy whose confidence interval does not overlap with the grey zone is either significantly better or worse than the natural hierarchy.
+
+It is immediately clear that across both datasets, the natural hierarchy shows no significant outperformance compared to its random twins. 
+On the tourism dataset, it ranks the $5$th, performing indistinguishably from $32$ twins but significantly better than the remaining $68$.
+On the other hand, the performance difference is much smaller for the mortality dataset, where most twins perform insignificantly from the natural hierarchy.
+There are even three twin hierarchies significantly better than natural hierarchy.
+These results suggest that the natural hierarchy of tourism dataset may be ``smarter'' compared to that of mortality dataset.
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/hierarchy_rmsse/tourism/P2_natural_vs_pn_h12.pdf}
+    \caption{\label{fig:P2_tourism}Average ranks and 95\% confidence intervals for natural hierarchy and its $100$ twins on the tourism dataset.}
+\end{figure}
+
+\begin{figure}[!ht]
+    \centering    \includegraphics[width=0.8\textwidth]{figures/hierarchy_rmsse/mortality/P2_natural_vs_pn_h12.pdf}
+    \caption{\label{fig:P2_mortality}Average ranks and 95\% confidence intervals for natural hierarchy and its $100$ twins on the mortality dataset.}
+\end{figure}
+
+\section{Clustering-based hierarchy}
+\label{sec:clustering}
+
+Given that ``structure'' of natural hierarchy is the primary contributor to the performance improvement, we are interested in if better groupings can be constructed via clustering and become more critical than structure.
+We first review existing literature on clustering-based forecast reconciliation, and then describe the clustering techniques involved in our paper, followed by empirical results on mortality and tourism dataset.
+
+\subsection{Cluster hierarchies vs benchmarks}
+\label{subsec:P3_benchmark}
+Table~\ref{tab:P3_rmsse} shows the accuracy of benchmarks and $12$ cluster hierarchies in terms of average RMSSE across all evaluation windows using the evaluation process described in Section~\ref{subsec:evaluation}.
+The MCB test results are presented in Figure~\ref{fig:P3_mcb_benchmark}.
+On the tourism dataset, all cluster hierarchies outperform the two-level hierarchy, with ten showing significant improvement.
+While on the mortality dataset, only five cluster hierarchies surpass the two-level hierarchy in average RMSSE and eight do so in terms of average ranks. 
+However, none of these differences are statistically significant. 
+The inferiority of three $k$-medoids based cluster hierarchies highlights the importance of choosing an appropriate clustering technique.
+\begin{table}[h!]
+    \centering
+    \caption{\label{tab:P3_rmsse}Performance of cluster hierarchies and benchmark hierarchies in terms of average RMåSSE($\times 10^{-2}$) across all evaluation windows on both datasets.
+Column-wise minimum values are displayed in bold.}
+    \begin{tabular}{lll}
+    \toprule
+        Method & tourism & mortality \\ \midrule
+        Base & 69.452 & 75.295 \\ 
+        Two-level & 69.437 & 75.281 \\ 
+        Natural & 69.132 & 75.008 \\ 
+        TS-HC-EUC & 69.224 & 75.396 \\ 
+        TS-HC-DTW & 69.108 & \textbf{74.959} \\ 
+        TS-ME-EUC & 69.392 & 75.279 \\ 
+        TS-ME-DTW & 69.404 & 75.278 \\ 
+        TSF-HC-EUC & \textbf{69.086} & 75.091 \\ 
+        TSF-ME-EUC & 69.385 & 75.488 \\ 
+        ER-HC-EUC & 69.196 & 75.068 \\ 
+        ER-HC-DTW & 69.121 & 75.324 \\ 
+        ER-ME-EUC & 69.380 & 75.303 \\ 
+        ER-ME-DTW & 69.420 & 75.308 \\ 
+        ERF-HC-EUC & 69.099 & 75.010 \\ 
+        ERF-ME-EUC & 69.417 & 75.325 \\ \bottomrule
+    \end{tabular}
+\end{table}
+
+\begin{table}[!ht]
+    \centering
+    \caption{\label{tab:P3_features}Four trend and seasonality features for the tourism dataset and mortality dataset.}
+    \begin{tabular}{lll}\toprule
+        Features & mortality & tourism \\ \midrule
+        $\gamma$ parameter of Holt-Winters model & 0.0202 & 0.000165 \\ 
+        The first order seasonal ACF & 0.652 & 0.181 \\ 
+        Strength of trend & 0.757 & 0.156 \\ \bottomrule
+    \end{tabular}
+\end{table}
+
+The varying performance of cluster hierarchies across two datasets can be attributed to the unique characteristics of their bottom-level series.
+The tourism dataset, as shown in Figure~\ref{fig:tourism}, predominately contains volatile and noisy bottom-level time series with weak trend and seasonality.
+Creating new middle-level time series in this context helps elucidate the underlying pattern which can not be easily captured by bottom-level base forecasting models.
+On the other hand, bottom-level series in mortality dataset exhibit stronger trend and seasonality patterns, making creating middle-level series less beneficial.
+Table~\ref{tab:P3_features} summarises several features computed using available data in the last evaluation window, confirming the stronger seasonality and trend presence in the bottom level of mortality dataset.
+Note that the values are computed by averaging features for all bottom-level time series.
+The strength of trend is defined as
+\[
+\text{Strength of trend} = 1-\frac{\text{Var}(e_t)}{\text{Var}(f_t+e_t)},
+\]
+where $e_t$ and $f_t$ are residuals component and smoothed trend component obtained by STL decomposition of the time series (\citealp{tsfeatures}).
+
+\begin{table}[h!]
+    \centering
+    \caption{\label{tab:P3_number_series}Average number of middle-level time series for $k$-medoids-based, hierarchical-clustering-based and natural hierarchy in both datasets.}
+    \begin{tabular}{lll}
+    \toprule
+        Approach & mortality & tourism \\ \midrule
+     Natural & 21 & 250 \\ 
+        $k$-medoids clustering & 6.78 & 20.99 \\ 
+        Hierarchical clustering & 96 & 302 \\ \bottomrule
+    \end{tabular}
+\end{table}
+
+The hierarchies based on hierarchical clustering outperforms the hierarchies based on $k$-medoids when using the same representation and distance metric, e.g., ``TSF-HC-EUC'' outperforms ``TSF-ME-EUC''.
+This superiority is attributed to hierarchical clustering generating a greater number of middle-level time series than $k$-medoids, significantly enhancing the benefits of enriched structure.
+Table~\ref{tab:P3_number_series} summarises average number of middle-level series across all evaluation windows for natural, $k$-medoids-based and hierarchical clustering-based hierarchy. 
+Interestingly, the natural hierarchy shows competitive accuracy compared to hierarchical clustering-based hierarchies on both datasets, despite having fewer middle-level series.
+Regarding the superiority of any specific representation or distance metric, no consistent findings emerge.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/hierarchy_rmsse/tourism/P3_mcb_benchmarks_h12.pdf}
+    \includegraphics[width=0.45\textwidth]{figures/hierarchy_rmsse/mortality/P3_mcb_benchmarks_h12.pdf}
+    \caption{\label{fig:P3_mcb_benchmark}Average ranks and 95\% confidence intervals for twelve cluster hierarchies and three benchmarks on tourism dataset (left) and mortality dataset (right) based on MCB test.}
+\end{figure}
+
+\subsection{Cluster hierarchy vs its twins}
+\label{subsec:P3_c_vs_pc}
+
+Results in Section~\ref{subsec:P3_benchmark} demonstrate that cluster hierarchy is able to improve forecast performance compared to natural hierarchy and two-level hierarchy. 
+We are also interested in how ``structure'' and ``grouping'' contribute to these improvements.
+Following the comparison in Section~\ref{subsec:n_vs_pn}, we compare the best performing cluster hierarchy with its $100$ random twins.
+Note that we choose the best performing approach according to average RMSSE shown in Table~\ref{tab:P3_rmsse}.
+
+The MCB test results for the tourism dataset and mortality dataset are shown in Figure~\ref{fig:P3_tourism_c_vs_pc} and Figure~\ref{fig:P3_mortality_c_vs_pc}, respectively.
+We observe that in both datasets, the best performing clustering approach does not yield significantly better results than its random twins. 
+Indicatively, the best cluster approach of mortality dataset ranks nearly in the middle of its random twins, indicating that structure instead of grouping dominates the performance. 
+However, the best cluster approach of tourism dataset ranks first and significantly outperforms $70$ of its random twins. This suggests a combination effect of grouping and structure.
+
+Overall, Table~\ref{tab:P3_rmsse}, Figures~\ref{fig:P3_tourism_c_vs_pc} and \ref{fig:P3_mortality_c_vs_pc} suggest that while it is possible to construct a ``smart'' hierarchical structure that improves forecast reconciliation performance, this possibility highly depends on the dataset characteristic and the time series cluster methods employed, making it a challenging objective to achieve.
+On the other hand, no matter the ``smarter'' hierarchy is construed or not, enriched structure contributes to the performance improvement.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/hierarchy_rmsse/tourism/P3_cluster_vs_pc_h12.pdf}
+    \caption{\label{fig:P3_tourism_c_vs_pc}Average ranks and 95\% confidence intervals for best performing cluster hierarchy TSF-HC-EUC and its $100$ twins on the tourism dataset.}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/hierarchy_rmsse/mortality/P3_cluster_vs_pc_h12.pdf}
+    \caption{\label{fig:P3_mortality_c_vs_pc}Average ranks and 95\% confidence intervals for best performing cluster hierarchy TS-HC-DTW and its $100$ twins on the mortality dataset.}
+\end{figure}
+
+\section{Simulation study}
 \label{sec:simulation}
 
-In this section, we demonstrate that hierarchies constructed by clustering may not outperform hierarchies constructed randomly even if there are true clusters in the bottom level.
+The experiments in Section~\ref{sec:clustering} show the difficulty of constructing a smart hierarchy through clustering.
+However, it is possible that the clustering approaches we used are unable to detect clusters underlying the dataset.
+In this section, we simulate a scenario where ideal clusters can be detected and investigate how the two factors affect performance in this secenario.
 
@@
 
-\subsubsection*{Time series generation}
+%\subsubsection{Time series generation}
 
@@
     \begin{aligned}
-    y_t &= l_t + s_t + e_t \\
-    s_t &= s_{t\mod m} \\
-    l_t &= a t + \varepsilon_t,
+    Y_t &= L_t + S_t + \xi_t \\
+    S_t &= S_{t~\text{mod}~s} \\
+    L_t &= \alpha t + \varepsilon_t,
     \end{aligned}
 \end{equation}
-where $l_t$ represents the trend term which increases or decreases over time at a slope of $a$.
-The seasonal component, denoted by $s_t$, remains constant.
-Both $e_t$ and $\varepsilon_t$ are white noises.
+where $L_t$ represents the trend term which increases or decreases over time at a slope of $\alpha$.
+The seasonal component, denoted by $S_t$, is repeating and deterministic with a cycle of length $s$.
+Both $\xi_t$ and $\varepsilon_t$ are white noises.
 
-We create $6$ clusters at the bottom level by adjusting the directions of the trend and patterns of the seasonal components.
-The pattern settings for all clusters can be found in Table~\ref{table:simu_params}.
-For an increasing trend we set the slope $a$ to $0.001$, and for a decreasing trend, we set it to $-0.002$.
-The variances of the corresponding white noise $\varepsilon_t$ are set to $2.5\times 10^{-5}$ and $4.9\times 10^{-5}$.
-The terms ``Even'' and ``Odd'' indicate the position of the seasonal peak.
-For ``Even'' seasonality, the peaks are located at positions $2, 4, \dots, m$, and vice versa.
-The values for these seasonal peaks and troughs are uniformly drawn from $[2, 3]$ and $[0,1]$, respectively.
-The variance of $e_t$ is set to $0.25$.
-We generate monthly time series data with $20$ time series per cluster.
-Figure~\ref{fig:simu_emps} displays example time series from each cluster while Figure~\ref{fig:simu_pca} visualises these generated time series based on the first two principal components extracted from principal component analysis of the series.
+Instead of employing cluster algorithms, we artificially craft $6$ ideal clusters by manipulating the directions of the trend components and patterns of the seasonal components.
+The configurations for each cluster can be found in Table~\ref{table:simu_params}.
+To simulate an increasing trend, we set the slope $\alpha$ to $0.001$, and for a decreasing trend, we set $\alpha$ to $-0.002$.
+The variances of the associate white noise $\varepsilon_t$ are set to $2.5\times 10^{-5}$ and $4.9\times 10^{-5}$ for increasing trend and decreasing trend, respectively.
+For series without trend (``None''), the trend component $L_t$ is set to zero.
+The terms ``Even'' and ``Odd'' in our setup refer to the positioning of seasonal peak.
+Specifically, ``Even'' seasonality means that peaks occur at even-numbered positions (e.g., $2, 4, \dots$) of seasonal cycle, with the reverse being true for ``Odd'' seasonality.
+The values of these seasonal peaks and troughs are randomly drawn from uniform distributions within the ranges of $[2, 3]$ and $[0,1]$, respectively.
+The variance of $\xi_t$ is set to $0.25$.
+We generate monthly time series data, ensuring that each cluster contains $20$ distinct time series.
+For each series, we generate $144$ observations, and the last $12$ observations are reserved for evaluation purpose.
+Figure~\ref{fig:simu_emps} displays example time series from each cluster, while Figure~\ref{fig:simu_pca} visualizes these generated time series based on the first two principal components extracted from principal component analysis of the series.
 
@@
     \includegraphics[width=0.6\textwidth]{figures/simu_pca.pdf}
-    \caption{\label{fig:simu_pca}Visualisation of the generated time series in the simulation experiments.}
+    \caption{\label{fig:simu_pca}Visualization of the generated time series in the simulation experiments.}
 \end{figure}
 
-\subsubsection*{Hierarchies construction}
+\subsection{Hierarchies construction}
 
-There are a total of $120$ bottom series and $1$ total series in the hierarchy, referred to as ``C0''.
-Additionally, we consider $4$ clustering approaches and $2$ forecast combination approaches.
-``C1'' creates $6$ middle-level series according to the designed correct clusters.
-We merge clusters with the same trend pattern, resulting in $3$ clusters in the middle level, denoted by ``C2''.
-Similarly, we construct ``C3'' and ``C4'' based on the presence of the trend term and seasonal peak positions, resulting in $2$ and $3$ middle-level series, respectively.
-``A1'' combines reconciled forecasts obtained from all four clustering approaches (``C1'' to ``C4'') using equal weights.
-By shuffling the bottom-level series within the hierarchy ``C1'', we can randomly generate different hierarchies with identical structure.
-``A2'' combines reconciled forecasts from $10$ randomly constructed hierarchies using equal weights.
+We consider a two-level hierarchy with a total of $120$ bottom-level series and a single aggregated series, labelled as ``Two-level''.
+In addition, we examine four cluster hierarchies.
+Note that we consider multiple cluster hierarchies in order to reflect the real-world scenario where a variety of clustering techniques may be employed.
+The first cluster hierarchy, ``Cluster'', forms six middle-level series according to the predefined ideal clusters.
+We then merge clusters with the same trend pattern, resulting in the cluster hierarchy with three clusters, denoted by ``Cluster-trend1''.
+Similarly, we construct cluster hierarchies ``Cluster-trend2'' and ``Cluster-season'' based on the presence of the trend term and seasonal peak positioning, resulting in $2$ and $3$ middle-level series, respectively.
+Table~\ref{table:simu_params} summarizes the five approaches.
 
-\subsubsection*{Forecasting}
-
-We construct two scenarios by considering different base forecasting models.
-In the first scenario, exponential smoothing (ETS) is used to generate base forecasts for all time series in hierarchies.
-This simulates a situation where the time series themselves are inputs to the clustering algorithms.
-In the second scenario, we use historic mean to generate base forecasts for bottom-level series and ETS for other time series in hierarchies, which simulates the case where in-sample errors are inputs to the clustering algorithms.
-We refer to these scenarios as ``clustering by time series'' and ``clustering by error'', respectively.
-To reconcile the base forecasts, we employ the minimum trace method with the shrinkage estimator (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
-The shrinkage estimator is effective at capturing the dependence structure within the forecast errors and has demonstrated superior perofrmance in various applications.
-For each series, we generate $144$ observations, and the last $12$ observations are reserved for evaluation purpose.
-
-\subsection{Evaluation}
-\label{sec:simu_eval}
-
-The purpose of constructing middle-level series is to improve the forecast performance of the total-level and bottom-level series by leveraging the strength of these new series.
-Therefore, we only evaluate the reconciled forecasts at total level and bottom level. 
-To assess the accuracy of single time series, we use root mean squared error (RMSE) as our metric. 
-The simulation is repeated $500$ times, resulting in a total of $500\times 121$ RMSEs for each approach. 
-Multiple comparisons with the best (MCB) test is then applied to compute the average ranks of the $7$ approaches along with base forecasts and to determine whether the performance differences are statistically different (\citealp{koningM3CompetitionStatistical2005}).
+\begin{table}[]
+    \centering
+    \begin{tabular}{ll}\toprule
+        Approaches & Description \\ \midrule
+        Two-level &  The original two-level hierarchy. \\ 
+        Cluster & Cluster hierarchy based on ideal clustering. \\
+        Cluster-trend1 & Cluster hierarchy based on trend patterns. \\
+        Cluster-trend2 & Cluster hierarchy based on existence of trend component. \\
+        Cluster-season & Cluster hierarchy based on seasonality patterns. \\\bottomrule
+    \end{tabular}
+    \caption{\label{tab:simu_methods}Five approaches used in the simulation experiments.}
+\end{table}
 
@@
 
-Figure~\ref{fig:simu_mcb} displays the MCB test results for the two scenarios. 
-In both scenarios, most approaches perform better than the base forecasts and the original two-level hierarchy ``C0''.
-This suggests that constructing middle-level series generally improves forecast reconciliation performance.
-In the ``clustering by time series'' scenario, the correct cluster ``C1'' ranks $4$th, indicates that optimal clusters do not guarantee optimal forecast reconciliation performance. 
-On the other hand, ``C1'' ranks $1$st in the ``clustering by error'' scenarios.
-This highlights the importance of carefully selecting time series representations when constructing new middle levels using clustering algorithms.
-The simple average of $10$ random hierarchies ranks $1$st in the first scenario and the simple average of $4$ clustering hierarchies ranks $3$rd in both scenarios, indicating the importance of forecast combination.
+We repeat the simulation $500$ times and evaluate the results on these $500$ hierarchies following the evaluation procedure introduced in Section~\ref{subsec:evaluation}.
+Table~\ref{tab:simu_P3} reports the average RMSSE across all hierarchies, and
+Figure~\ref{fig:simu_P3_benchmarks} presents the MCB test results.
+The results reveal that most approaches perform better than the base forecasts and the original two-level hierarchy.
+This outcome indicates that hierarchy construction generally improves forecast reconciliation performance, corroborating our findings reported in Section~\ref{sec:clustering}.
+Interestingly, the ideal cluster ``Cluter'' achieves second rank, indicating that optimal clustering does not necessarily translate into the best forecast reconciliation performance.
+
+Furthermore, we are interested in structure or grouping contributes more to the performance improvements.
+Again, following the random hierarchy construction procedure described in Section~\ref{subsec:permutation}, we compare the ideal cluster with its $100$ random twins.
+The MCB test result is shown in Figure~\ref{fig:simu_P3_c_vs_pc}.
+Even if the optimal cluster can be obtained in this simulation, the results are similar to what we found on the mortality dataset, showing that  structure plays a greater role in improving the forecast reconciliation performance.
+It enforces our belief that the reason of clustering improving performance depends on the dataset characteristics.
+
+\begin{table}[!ht]
+    \centering
+    \caption{\label{tab:simu_P3}Performance of cluster hierarchies and benchmark hierarchies in terms of average RMSSE($\times 10^{-2}$) in simulation.
+Column-wise minimum values are displayed in bold.}
+    \begin{tabular}{ll}\toprule
+        Method & RMSSE \\ \midrule
+        Base & 77.64 \\ 
+        Two-level & 59.71 \\ 
+        Cluster & 59.63 \\ 
+        Cluster-trend1 & \textbf{59.62} \\ 
+        Cluster-trend2 & 59.65 \\ 
+        Cluster-season & 59.65 \\ \bottomrule
+    \end{tabular}
+\end{table}
 
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{figures/simu_mcb1.pdf}
-    \includegraphics[width=0.45\textwidth]{figures/simu_mcb2.pdf}
-    \caption{\label{fig:simu_mcb}Average ranks and 95\% confidence intervals based on the MCB Test for the $8$ approaches in the two scenarios of the simulation experiments.
-Left panel displays test results for the ``clustering by time series'' scenario and right panel displays test results for the ``clustering by error'' scenario.}
-\end{figure}
-
-\section{Empirical studies}
-
-\subsection{Datasets}
-
-We analyse two datasets in our empirical studies.
-The first dataset is the monthly Australian domestic tourism dataset, which provides visitor nights numbers from 1998 to 2016.
-The tourism demand of Australia is geographically disaggregated into $7$ states and territories, further divided into $27$ zones and $76$ regions.
-Additionally, each geographical series is divided by four travel purposes (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
-This dataset totally contains $555$ time series with $304$ at the bottom level.
-
-The second dataset focuses on causes of death in the U.S., using the ICD 10 coding system.
-We obtain monthly cause-specific death counts from the Center for Disease Control and Prevention (CDC) for the period between 1999 and 2019.
-The coding system forms an unbalanced hierarchy with $137$ time series, out of which $113$ time series are in the bottom level.
-To consolidate data with suppressed values, we combine causes that share a parent cause and calculate their death counts by subtracting death counts of sibling causes from death counts of their parent cause.
-The final dataset includes $120$ time series with $98$ in the bottom level.
-
-\subsection{Experiment design}
-
-We focus on the performance of total-level series and bottom-level series, disregarding the multiple middle levels in the original hierarchies known as "natural hierarchies".
-The natural hierarchy is considered one way to construct middle-level series, similar to hierarchies created through clustering.
-However, we demonstrate that for the purpose of forecast performance, the natural hierarchy may not be the most effective hierarchical structure.
-
-To construct middle levels using clustering, we combine four time series representations with two distance measures and two clustering algorithms.
-This results in twelve different construction approaches listed in Table~\ref{tab:emp_method}.
-
-\begin{table}
-\caption{\label{tab:emp_method} Hierarchy construction approaches used in empirical studies.}
-\centering
-\resizebox{\textwidth}{!}{
-\begin{tabular}{ccccc}
-    \toprule
-    Approaches & Representation & Dimension reduction & Distance measure & Clustering algorithms  \\
-    TS-MED & Time series & Yes & Euclidean & k-Medoids \\
-    ER-MED & In-sample error & Yes & Euclidean & k-Medoids \\
-    TSF-ME & Time series features & Yes & Euclidean & k-Medoids \\
-    ERF-ME & In-sample error features & Yes & Euclidean & k-Medoids \\
-    TS-HC & Time series & Yes & Euclidean & hierarchical clustering  \\ 
-    ER-HC & In-sample error & Yes & Euclidean & hierarchical clustering  \\ 
-    TSF-HC & Time series features & Yes & Euclidean & hierarchical clustering  \\ 
-    ERF-HC & In-sample error features & Yes & Euclidean & hierarchical clustering  \\
-    TS-MED-DTW & Time series & No & DTW & k-Medoids \\
-    TS-HC-DTW & In-sample error & No & DTW & hierarchical clustering \\
-    ER-MED-DTW & Time series & No & DTW & k-Medoids \\
-    ER-HC-DTW & In-sample error & No & DTW & hierarchical clustering 
-     \\\bottomrule
-\end{tabular}}
-\end{table}
-
-Additionally, we consider three forecast combination approaches.
-In the first approach, we create one middle level with $15$ time series by randomly assigning bottom-level series as their children.
-We ensure that all the middle-level series have approximately an equal number of children.
-The choice of having $15$ middle-level series is arbitrary with the goal of creating a moderate number of groups, each containing a moderate number of series.
-We repeat this process to create $50$ such hierarchies and combine their reconciled forecasts using equal weights. This approach is referred to as ``FC-R''.
-In the second approach, we create $10$ new hierarchies by randomly shuffling the positions of bottom-level series in the natural hierarchy and combine their reconciled forecasts using equal weights.
-This approach is denoted by ``FC-N''.
-The third approach, labelled by ``FC-C'', involves equally-weighted combining the reconciled forecasts obtained from the $12$ hierarchies shown in Table~\ref{tab:emp_method}.
-
-The time series features used in this experiment are calculated using the \texttt{tsfeatures} package (\citealp{tsfeatures}) for R.
-After filtering out the features that are constant across all series, $56$ features are reserved.
-The complete list of these feature can be found in Appendix.
-The k-Medoids and hierarchical clustering algorithms are implemented using the \texttt{cluster}(\citealp{cluster}) package for R.
-The base forecasts are generated using the automatic ETS models, which are then reconciled using the minimum trace method with shrinkage estimator.
-
-We employ the rolling window strategy to evaluate the performance of different approaches for both datasets.
-We start with $96$ observations and fit the base forecasting models using the available data.
-Then we calculate time series representations and construct new hierarchies by clustering or randomness, and then forecast $12$ steps ahead.
-After that, the training set is increased by one observation and new forecasts are obtained.
-The procedure is repeated until the last $12$ observations are used for evaluation.
-Finally, we can obtain $121$ $12$-step-ahead forecasts for the tourism dataset and $144$ $12$-step-ahead forecasts for the mortality dataset.
-We compare the forecast performance of the $15$ approaches as well as the natural hierarchy, two-level hierarchy and base forecasts for both total-level and bottom-level series.
-
-\subsection{Results}
-
-Same as the evaluation measure described in Section~\ref{sec:simu_eval}, we combine the forecasts of total-level and bottom-level series across all evaluation windows and conduct the MCB test.
-The test results for the tourism dataset and mortality dataset are shown in Figure~\ref{fig:tourism_mcb} and Figure~\ref{fig:mortality_mcb}, respectively.
-
-Most hierarchy construction approaches outperform both base forecasts and the two-level hierarchy, except for three approaches on the mortality dataset.
-For both datasets, the simple average of randomised natural hierarchies (``FC-N'') performs better than both natural hierarchy and all clustering-based hierarchies.
-Additionally, the simple average of $12$ clustering-based hierarchies (``FC-C'') significantly outperforms all other approaches.
-These results indicate that using a clustering-based hierarchy can improve forecast performance.
-However, forecast combination is even more beneficial, as evidenced by the high ranking of ``FC-N'' and ``FC-R''.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/tourism_mcb.pdf}
-    \caption{\label{fig:tourism_mcb}Average ranks and 95\% confidence intervals based on the MCB Test for the $18$ approaches on the tourism dataset.}
+    \includegraphics[width=0.6\textwidth]{figures/hierarchy_rmsse/simulation/P3_mcb.pdf}
+    \caption{\label{fig:simu_P3_benchmarks}Average ranks and 95\% confidence intervals for four cluster hierarchies and two benchmarks in simulation based on MCB test.}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/mortality_mcb.pdf}
-    \caption{\label{fig:mortality_mcb}Average ranks and 95\% confidence intervals based on the MCB Test for the $18$ approaches on the mortality dataset.}
+    \includegraphics[width=0.8\textwidth]{figures/hierarchy_rmsse/simulation/P3_c_vs_pc.pdf}
+    \caption{Average ranks and 95\% confidence intervals for four the ideal hierarchy and its 100 random twins in simulation based on MCB test.}
+    \label{fig:simu_P3_c_vs_pc}
 \end{figure}
 
-The approach based on hierarchical clustering outperforms the approach based on k-Medoids on the tourism dataset when using the same representation and distance metric, e.g., ``TSF-HC'' significantly ourperforms ``TSF-ME''.
-However, this is not consistently observed for every combination of representation and distance metric on the mortality dataset.
-We believe this discrepancy is due to different time series patterns at the bottom level of these two datasets.
-In the case of the mortality dataset, we combine rare causes of death that have suppressed values and record death counts at a national level.
-As a result, most series at the bottom level exhibit strong seasonality and trend.
-On the other hand, in the tourism dataset, the tourism demand is disaggregated for both travel purposes and geographical regions.
-This leads to numerous bottom-level series with high volatility and many zeros, making them more challenging to forecast.
-Therefore, having a hierarchy with more middle-level series can be more advantageous for reconciliation in the tourism dataset compared to the mortality dataset.
-Additionally, we suspect that the inferior performance of ``FC-R'' on the tourism dataset may be partly attributed to an insufficient number of middle-level series.
+\section{Combination hierarchies}
+\label{sec:combination}
 
-In most cases, the in-sample error representation outperforms the time series representation when using the same distance metric and clustering algorithms.
-However, this performance difference is not as significant as what was observed in Section~\ref{sec:simu_res}.
-Intuitively, hierarchies constructed based on clustering in-sample error should be similar to random hierarchies when all base models are correctly specified.
-However, due to ubiquitous model misspecification in practice, vague patterns emerge in the in-sample error, which leads to contradictory results.
+The results in Section~\ref{sec:clustering} and Section~\ref{sec:simulation} highlights the possibility of improving forecast reconciliation performance by constructing new middle levels through time series clustering.
+However, this possibility highly depends on the dataset characteristics and time series approaches used.
+Therefore, the classical problem of selecting the optimal clustering approaches arises.
+Considering the substantial research and empirical evidences in favor of forecast combination over selection (see e.g., \citealp{elliottForecastingEconomicsFinance2016}), we suggest employing combination of forecasts from multiple cluster hierarchies to avoid the uncertainty associated with identifying a best cluster approach.
+Specifically, the reconciled forecasts from multiple hierarchies are combined using equal weights, i.e.,
+\[
+  \tilde{\boldsymbol{y}}_{T+h}^{\text{comb}} = \frac{1}{l} \sum_{j=1}^l \tilde{\boldsymbol{y}}_{T+h}^j.
+\] Note that the resulted forecasts are still coherent. 
+While it is possible to employ more complex methods to determine ``optimal'' weights, we adhere to equally-weighted combination due to its simplicity and well-known efficacy (\citealp{wangForecastCombinations50year2022}).
 
-\subsubsection*{Effect of number of random hierarchies}
+Following the evaluation procedure introduced in Section~\ref{subsec:evaluation},
+Table~\ref{tab:P4_RMSSE} presents the accuracy in terms of average RMSSE across all evaluation windows for both datasets.
+Note that we only present accuracies of three benchmarks, the best cluster hierarchies and the combination hierarchy to save space.
+The MCB test results are shown in Figure~\ref{fig:P4_bench_mcb}.
+As expected, we observe that on both datasets, forecast combination future improves forecast performance compared to the best performing cluster hierarchy. 
+The improvement on the mortality dataset is more pronounced, with forecast combination significantly outperforms all other approaches.
+\begin{table}[!ht]
+    \centering
+    \caption{\label{tab:P4_RMSSE}Performance in terms of average RMSSE($\times 10^{-2}$) on both datasets. Column-wise minimum values are displayed in bold.}
+    \begin{tabular}{lcc}\toprule
+        Method & tourism & mortality \\ \midrule
+        Base & 69.452 & 75.295 \\ 
+        Two-level & 69.437 & 75.281 \\ 
+        Natural & 69.132 & 75.008 \\ 
+        TS-HC-DTW & 69.108 & 74.959 \\ 
+        TSF-HC-EUC & 69.086 & 75.091 \\ 
+        Combination & \textbf{69.019} & \textbf{74.234} \\ \bottomrule
+    \end{tabular}
+\end{table}
 
-In our previous experiments, we set the number of random hierarchies in ``FC-R'' and ``FC-N'' to $10$ for fair comparisons with ``FC-C''.
-However, we believe that increasing the number of random hierarchies could further enhance performance.
-In this subsection, we explore the effects of using 20 and 50 random hierarchies, referred to as ``FC-N-20'', ``FC-N-50'', ``FC-R-20'', and ``FC-R-50''.
-We compare these variations with ``FC-R'', ``FC-C'', and ``FC-N'' using the same evaluation procedure described earlier.
-The results from the MCB test are presented in Figure~\ref{fig:number_mcb}, where the left panel shows results on the tourism dataset and the right panel displays results on the mortality dataset.
-
-Generally, we observe that forecast performance improves as the number of random hierarchies increases, except for ``FC-N-20'' and ``FC-N'' on the mortality dataset.
-Surprisingly, on the tourism dataset, ``FC-N-50'' performs slightly better than ``FC-C''.
-It is important to note that employing more random hierarchies comes at a cost of increased computational resources.
-Therefore, one must carefully consider trade-offs between efficiency and performance when making decisions.
-
-\begin{figure}
+\begin{figure}[!h]
     \centering
-\includegraphics[width=0.45\textwidth]{figures/tourism_number_mcb.pdf}
-\includegraphics[width=0.45\textwidth]{figures/mortality_number_mcb.pdf}
-\caption{\label{fig:number_mcb}Average ranks and 95\% confidence intervals based on the MCB Test of different number of random hierarchies on two datasets.
-Left and right panels display test results on tourism dataset and mortality dataset, respectively.}
+    \includegraphics[width=0.45\textwidth]{figures/hierarchy_rmsse/tourism/P4_benchmarks_h12.pdf}
+    \includegraphics[width=0.45\textwidth]{figures/hierarchy_rmsse/mortality/P4_benchmarks_h12.pdf}
+    \caption{Average ranks and 95\% confidence intervals for all approaches on tourism dataset(left) and mortality dataset(right) based on MCB test.}
+    \label{fig:P4_bench_mcb}
 \end{figure}
 
-\section{Conclusion}
+\subsection{Combination hierarchy vs its random twins}
+
+We are also interested in if combination of cluster hierarchies significantly differ from its random twins.
+We propose to extend the permutation hierarchy generation approach introduced in Section~\ref{subsec:permutation} to combination hierarchy.
+First, we apply the same permutations of bottom-level series used in Section~\ref{subsec:P3_c_vs_pc} to all other cluster hierarchies.
+Then for each of the $100$ permutations, the twelve reconciled forecasts obtained from corresponding random twins of cluster hierarchies are combined through equally-weighted combination, resulting $100$ random twins of combination hierarchy.
+The results of MCB test for combination hierarchy and its $100$ random twins on the mortality dataset are presented in Figure~\ref{fig:P4_a_vs_pa}.
+It is not surprising that the combination hierarchy ranks $100$th, given that even the best-performing cluster hierarchy failed to demonstrate absolute superiority.
+This comparison is conducted solely on the mortality dataset, as computing random twins for all cluster hierarchies on the tourism dataset is time-consuming.
+\begin{figure}[h!]
+\vspace{-0.1in}
+    \centering
+    \includegraphics[width=0.75\textwidth]{figures/hierarchy_rmsse/mortality/P4_average_vs_pa_h12.pdf}
+    \caption{\label{fig:P4_a_vs_pa} Average ranks and 95\% confidence intervals for combination of twelve cluster hierarchies and its $100$ random twins on mortality dataset based on MCB test.}
+\end{figure}
+
+\clearpage 
+\newpage
+
+% \subsection{Results on simulation dataset}
+
+% Table~\ref{}, Figures~\ref{} and We apply these analyses on the simulation dataset, leading to
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.8\textwidth]{figures/hierarchy_rmsse/simulation/P4.pdf}
+%     \caption{}
+%     \label{fig:}
+% \end{figure}
+
+\section{Discussion and Conclusion}
 \label{sec:conclusion}
 
-\section*{Acknowledgements}
+This paper extends the current body of research on clustering-based forecast reconciliation by introducing a general hierarchical forecasting framework, incorporating three distinct approaches: cluster hierarchies, random hierarchies, and combination hierarchies.
+In contrast to the focused scope of previous studies, our approach to cluster hierarchies involves a broader exploration.
+We examine four time series representations, employ two distance measures, and utilize two clustering algorithms.
+This comprehensive method differs significantly from the existing literature, which typically concentrates on specific clustering implementations.
+We also introduce two innovative random hierarchy construction methods to investigate what drives the performance enhancements in cluster hierarchies.
+These random hierarchies help isolate the effect of clustering, allowing us to focus on the benefits derived from the structure alone.
+Furthermore, we propose combination hierarchies to mitigate uncertainties inherent in random hierarchies.
+
+Our simulation study is constructed around two scenarios, each based on different base forecasting models.
+The first scenario highlights the value of the structure, evident in the high-ranking performance of random combination hierarchies.
+Structure can further improve forecast performance when the base forecasts are of high quality.
+The second scenario demonstrates the efficacy of clustering-based approaches, particularly when the base forecasts at the bottom level are less accurate.
+
+Empirical studies on two datasets support our simulation findings.
+In the tourism dataset, the inferior base forecasts at the bottom level lead to all cluster hierarchies surpassing the original hierarchy, with four outperforming the combination of random hierarchies, which is used to demonstrate the impact of enriched structure.
+In contrast, the superior performance of two random combination hierarchies in the mortality dataset highlights the effectiveness of enriched structure.
+These results imply that the dominant factor, whether it is the enriched structure or clustering, varies depending on the dataset's characteristics, the base forecasting models, and other variables.
+Overall, our findings suggest that hierarchy construction approaches generally enhance performance, and combining these approaches leads to further improvements.
+
+Future research based on our study could proceed in several promising directions.
+Firstly, our experiments were concentrated on total-level and bottom-level series.
+In practical applications, it might be necessary to include specific middle levels or evaluate the entire hierarchy.
+This could lead to the exploration of different hierarchy approaches, such as clustering middle-level series rather than bottom-level ones.
+Although we used equally-weighted combinations in this study, there's potential for applying more sophisticated methods to improve performance.
+The extensive literature on forecast combination, including advanced methods for calculating weights, offers numerous possibilities for enhancement (refer to \citealp{wangForecastCombinations50year2022} for an in-depth review).
+
+% In Section~\ref{sec:combination}, we discuss the implications of combining multiple hierarchical structures on the uncertainty in estimating the covariance matrix of base forecast errors.
+Our conclusion was to opt for forecast combination rather than combining the structures of the hierarchies.
+However, a systematic exploration of these two strategies, combining hierarchical structures and combining forecasts, presents an intriguing area for future research.
+Specifically, addressing the challenge of uncertainty due to high dimensionality in the combination of hierarchical structures is possible.
+In this context, innovative solutions like the regularized forecast reconciliation approach, as proposed by \cite{bentaiebRegularizedRegressionHierarchical2019a}, and alternative estimators of the covariance matrix, such as those suggested by \cite{pritulargaStochasticCoherencyForecast2021} could be highly beneficial.
+
+In both our simulation and empirical studies, the combination of random hierarchies displayed competitive results compared to clustering-based methods.
+However, the efficacy of this approach in scenarios with an extremely large number of bottom-level series remains uncertain.
+In such cases, a partially random approach might be more effective.
+For instance, initially generating random hierarchies, identifying those with superior performance, and then constructing partially random hierarchies based on these well-performing structures could be a viable strategy.
+Another intriguing possibility is the integration of both clustering and random approaches.
+Moreover, our study focused specifically on the aggregation of bottom-level series, which may have constrained the potential of middle-level series.
+It's plausible to enhance forecastability at the middle level by creating series through general linear combinations.
+
+Finally, our study was centered around point forecast reconciliation and cross-sectional hierarchy.
+However, the field of probabilistic forecast reconciliation has recently gained significant interest, as evidenced by research like \cite{panagiotelisProbabilisticForecastReconciliation2023} and \cite{jeonProbabilisticForecastReconciliation2019}.
+Applying hierarchy construction approaches to probabilistic forecast reconciliation presents a novel and potentially fruitful research avenue.
+This approach could provide deeper insights and more robust forecast reconciliation methods, particularly in scenarios where uncertainty and variability are significant factors.
+Another promising direction for extending our methodologies lies in exploring temporal (\citealp{athanasopoulosForecastingTemporalHierarchies2017}) and cross-temporal hierarchies (\citealp{girolimettoCrosstemporalProbabilisticForecast2023a}).
+
+\clearpage 
+\newpage
+
+%\section*{Acknowledgements}
+
+%Bohan Zhang is supported by the international joint doctoral education fund of Beihang University.
 

### 2024-04-05 R/expr_utils.R

@@ -173,7 +173,7 @@ nemenyi <- function (data, conf.level = 0.95, sort = c(TRUE, FALSE), plottype = 
                               sprintf("%1.2f", round(ranks.means[axis_at], 2)))
       }
       axis(2, at = (1:cols.number)[-axis_at], labels = FALSE)
-      axis(2, at = axis_at, labels = axis_labels, las = 2, col.ticks="red", cex.axis=0.8)
+      axis(2, at = axis_at, labels = axis_labels, las = 2, col.ticks="red", cex.axis=1.5)
       axis(1)
       for (i in 1:cols.number) {
         lines(ranks.means[i] + c(-1, 1) * 0.5 * r.stat, 
@@ -222,3 +222,87 @@ output_pre <- function(output) {
 
 
 
+method_name <- function(representor, distance, cluster) {
+  if (startsWith(cluster, "permute")) {
+    spl <- strsplit(cluster, "-")[[1]]
+    return (spl[length(spl)])
+  }
+  representor <- strsplit(representor, "-")[[1]][1]
+  representor <- ifelse(!is.na(representor), switch(representor,
+                                                    error = "ER-",
+                                                    error.features = "ERF-",
+                                                    ts = "TS-",
+                                                    ts.features = "TSF-"
+  ), "")
+  distance <- ifelse(distance == "", "",
+                     switch(distance,
+                            euclidean = "EUC",
+                            dtw = "DTW"
+                     )
+  )
+  cluster <- strsplit(cluster, "-")[[1]][1]
+  cluster <- ifelse(
+    !is.na(cluster),
+    switch(cluster,
+           natural = "Natural",
+           Kmedoids = "-ME",
+           hcluster = "-HC",
+           base = "Base",
+           "average" = "Combination"
+    ),
+    "Two-level"
+  )
+  paste0(representor, distance, cluster)
+}
+
+
+
+mcb_ <- function(orig, type, plot_type, target,
+                 file_path, mar = NULL, conf.level) {
+  orig_ <- orig %>%
+    select(method, rmsse, batch) %>%
+    tidyr::nest(rmsse = -c("method")) %>%
+    mutate_at("rmsse", purrr::map, function(g) {
[…]

### 2024-04-05 R/run_series_summary.R

@@ -1,0 +1,89 @@
+source("R/run_nls.R")
+library(dplyr)
+library(ggplot2)
+library(Matrix)
+library(tsutils)
+
+source("R/metrics.R")
+source("R/expr_utils.R")
+
+# natural vs two-level
+P1 <- function(dt, path, type = "series", conf.level = 0.95) {
+  
+  
+  path <- sprintf("manuscript/figures/%s_rmsse/%s/P1_natural_vs_twolevel_h%s.pdf", type, path, forecast_horizon)
+  
+  mcb_(dt %>% filter(method %in% c("Natural", "Two-level", "Base")), type = type, 
+       plot_type = "orig", file_path = path, conf.level = conf.level)
+}
+
+# natural vs its randomization
+P2 <- function(dt, path, type = "series", conf.level = 0.95) {
+  path <- sprintf("manuscript/figures/%s_rmsse/%s/P2_natural_vs_pn_h%s.pdf", type, path, forecast_horizon)
+  
+  mcb_(dt %>% 
+         filter(cluster == "natural" | startsWith(cluster, "permute-natural")),
+       type = type, plot_type = "custom", file_path = path, mar=c(4,14,3,2), 
+       target = "Natural", conf.level = conf.level)
+}
+
+
+
+P3 <- function(dt, path, type = "series", conf.level = 0.95) {
+  
+  file_path <- sprintf("manuscript/figures/%s_rmsse/%s/P3_mcb_benchmarks_h%s.pdf", type, path, forecast_horizon)
+  mcb_(dt %>% 
+         filter(!startsWith(cluster, "permute"), cluster != "average"),
+       type = type, plot_type = "orig", file_path = file_path, conf.level = conf.level)
+  
+  
+  bench_rmsse <- dt %>%
+    filter(representor != "", !startsWith(cluster, "permute")) %>%
+    rowwise() %>%
+    mutate(rmsse = mean(rmsse)) %>%
+    select(representor, distance, cluster, method, batch, rmsse) %>%
+    group_by(representor, distance, cluster, method) %>%
+    summarise(rmsse = mean(rmsse), .groups = "drop") %>%
+    arrange(rmsse)
+
+  best_ <- bench_rmsse[1, ]
+  file_path <- sprintf("manuscript/figures/%s_rmsse/%s/P3_cluster_vs_pc_h%s.pdf", type, path, forecast_horizon)
+  mcb_(dt %>% 
[…]

### 2024-04-05 R/run_summary_mcs.r

@@ -1,0 +1,221 @@
+source("R/run_nls.R")
+library(dplyr)
+library(ggplot2)
+library(Matrix)
+library(tsutils)
+library(MCS)
+
+source("R/metrics.R")
+source("R/expr_utils.R")
+
+
+cl <- parallel::makeCluster(8)
+
+method_name <- function(representor, distance, cluster) {
+  representor <- strsplit(representor, "-")[[1]][1]
+  representor <- ifelse(!is.na(representor), switch(representor,
+    error = "ER-",
+    error.features = "ERF-",
+    ts = "TS-",
+    ts.features = "TSF-"
+  ), "")
+  distance <- ifelse(distance == "", "",
+    switch(distance,
+      euclidean = "EUC",
+      dtw = "DTW"
+    )
+  )
+  cluster <- strsplit(cluster, "-")[[1]][1]
+  cluster <- ifelse(
+    !is.na(cluster),
+    switch(cluster,
+      natural = "Natural",
+      Kmedoids = "-ME",
+      hcluster = "-HC",
+      base = "Base",
+      "average" = "Combination"
+    ),
+    "Two-level"
+  )
+  paste0(representor, distance, cluster)
+}
+
+mcs_hierarchy_rmsse <- function(orig, rand, name, alpha) {
+  orig_rmsse <- orig %>%
+    rowwise() %>%
+    mutate(rmsse = mean(rmsse)) %>%
+    arrange(batch) %>%
+    pull(rmsse)
+
+  rand_rmsse <- rand %>%
+    rowwise() %>%
+    mutate(rmsse = mean(rmsse)) %>%
+    arrange(batch, cluster) %>%
+    tidyr::nest(rmsse = -"cluster") %>%
+    pull(rmsse) %>%
+    lapply(function(x) {
+      x %>%
+        arrange(batch) %>%
+        pull(rmsse)
+    }) %>%
+    do.call(cbind, .)
+
+  all_rmsse <- cbind(orig_rmsse, rand_rmsse)
+  colnames(all_rmsse) <- c(name, 1:100)
+  MCSprocedure(all_rmsse, alpha = alpha, cl=cl)
+}
+
+
+# natural vs two-level
+P1 <- function(dt, path, alpha) {
+  a <- dt$dtb %>%
+    filter(cluster %in% c("natural", "")) %>%
+    mutate(method = ifelse(cluster == "natural", "Natural", "Two-level")) %>%
[…]

### 2024-04-05 R/run_summary_permute.R

@@ -4,7 +4,6 @@ library(ggplot2)
 library(Matrix)
 library(tsutils)
 
-forecast_horizon <- 1
 source("R/metrics.R")
 source("R/expr_utils.R")
 
@@ -18,8 +17,8 @@ method_name <- function(representor, distance, cluster) {
   ), "")
   distance <- ifelse(distance == "", "",
     switch(distance,
-      euclidean = "-EUC",
-      dtw = "-DTW"
+      euclidean = "EUC",
+      dtw = "DTW"
     )
   )
   cluster <- strsplit(cluster, "-")[[1]][1]
@@ -27,14 +26,14 @@ method_name <- function(representor, distance, cluster) {
     !is.na(cluster),
     switch(cluster,
       natural = "Natural",
-      Kmedoids = "ME",
-      hcluster = "HC",
+      Kmedoids = "-ME",
+      hcluster = "-HC",
       base = "Base",
       "average" = "Combination"
     ),
     "Two-level"
   )
-  paste0(representor, cluster, distance)
+  paste0(representor, distance, cluster)
 }
 
 
@@ -152,6 +151,7 @@ P2 <- function(dt, path) {
   pdf(sprintf("manuscript/figures/series_rmsse/%s/P2_natural_vs_pn_h%s.pdf", path, forecast_horizon),
     width = 8, height = 6
   )
+  par(mar=c(4,14,3,2))
   natural_series <- mcb_series_rmsse(
     dt$dtb %>% filter(cluster == "natural"),
     dt$dtb %>% filter(startsWith(cluster, "permute-natural")),
@@ -163,6 +163,7 @@ P2 <- function(dt, path) {
   pdf(sprintf("manuscript/figures/hierarchy_rmsse/%s/P2_natural_vs_pn_h%s.pdf", path, forecast_horizon),
     width = 8, height = 6
   )
+  par(mar=c(4,14,3,2))
   natural_hierarchy <- mcb_hierarchy_rmsse(
     dt$dtb %>% filter(cluster == "natural"),
     dt$dtb %>% filter(startsWith(cluster, "permute-natural")),
@@ -213,7 +214,7 @@ P3 <- function(dt, path) {
 
   best_ <- bench_rmsse %>%
     group_by(representor, distance, cluster) %>%
[…]

### 2024-04-05 data/visualization.R

@@ -7,10 +7,17 @@ for (data in c("mortality", "tourism")) {
   dt <- readRDS(sprintf("%s/data.rds", data))
   n <- NROW(dt$S)
   m <- NCOL(dt$S)
-  dt_names <- readRDS(sprintf("%s/names.rds", data))
-  dt_select_bottom <- sort(sample(1:m, 4))
-  dt_selected <- as.data.frame(dt$data[,c(1, dt_select_bottom  + n - m)])
-  colnames(dt_selected) <- c("Total", dt_names[dt_select_bottom])
+  dt_names <- colnames(dt$data)
+  if (data == "tourism") {
+    dt_select_middle <- sample(2:251, 1)
+    dt_select_bottom <- (sample(1:76, 3) - 1) * 4 + 1:3
+  } else {
+    dt_select_middle <- sample(2:(n-m),1)
+    dt_select_bottom <- sort(sample(1:m, 3))
+  }
+  mid_names <- colnames(dt$data[,dt_select_middle,drop=FALSE])
+  bottom_names <- colnames(dt$data[,dt_select_bottom + n - m])
+  dt_selected <- as.data.frame(dt$data[,c(1, dt_select_middle, dt_select_bottom  + n - m)])
   if (data == "tourism") {
     index <- make_yearmonth(year = rep(1998:2016, each = 12), month = rep(1:12, 19))
   } else {
@@ -21,18 +28,28 @@ for (data in c("mortality", "tourism")) {
     tidyr::pivot_longer(cols = -index, names_to = "key", 
                         values_to = "y")
   
-  pdf(sprintf("manuscript/figures/%s.pdf", data), width = 6, height=6)
   p1 <- ggplot(data = dt_selected %>% filter(key == "Total") %>%
                  mutate(key = ifelse(data == "tourism", "Australian tourism", "U.S. Death"))) +
     geom_line(mapping = aes(x = index, y = y)) +
     ylab("") + xlab("") + 
     facet_wrap(~key)
-  p2 <- ggplot(data = dt_selected %>% filter(key != "Total")) +
+  
+  
+  p2 <- ggplot(data = dt_selected %>% filter(key != "Total", key %in% mid_names)) +
     geom_line(mapping = aes(x = index, y = y)) +
     facet_wrap(~ key, ncol = 2, scales = "free") +
     ylab("") + xlab("") + guides(colour = "none")
   
[…]

### 2024-04-05 simulation/simu_summary.R

@@ -60,7 +60,7 @@ test <- function(mat, name) {
 # natural hierarchy vs its counterpart
 pdf("manuscript/figures/hierarchy_rmsse/simulation/P3_c_vs_pc.pdf", width = 8, height = 6)
 natural_ <- evaluate_idx(best_hierarchy)
-natural_test <- test(cbind(natural_, evaluate_idx(permute_best)), "Cluster")
+natural_test <- test(cbind(natural_, evaluate_idx(permute_best)), "Cluster-predefined")
 dev.off()
 # 39
 #
@@ -153,22 +153,20 @@ base_ <- calculate_base()
 
 
 cluster_mat <- cbind(base_, two_level, natural_, trend_dir_, trend_exis_, season_)
-colnames(cluster_mat) <- c("Base", "Two-level", "Cluster", "Cluster-trend1", "Cluster-trend2", "Cluster-season")
+colnames(cluster_mat) <- c("Base", "Two-level", "Cluster-predefined", "Cluster-trend1", "Cluster-trend2", "Cluster-season")
 clusters_tbl <- data.frame(
-  method = c("Base", "Two-level", "Cluster", "Cluster-trend1", "Cluster-trend2", "Cluster-season"),
+  method = c("Base", "Two-level", "Cluster-predefined", "Cluster-trend1", "Cluster-trend2", "Cluster-season"),
   rmsse = colMeans(cluster_mat) * 100
 ) %>%
   arrange(rmsse) %>%
   mutate(rmsse = round(rmsse, digits = 2)) %>%
   write.csv("manuscript/figures/hierarchy_rmsse/simulation/simulation_methods.csv")
 
-pdf("manuscript/figures/hierarchy_rmsse/simulation/P3_mcb.pdf", width = 6, height = 6)
-tsutils::nemenyi(cluster_mat, plottype = "vmcb")
-dev.off()
+  
 
 output <- list()
 output$cluster <- c(
-  which(names(natural_test$means) == "Cluster"),
+  which(names(natural_test$means) == "Cluster-predefined"),
   mean(natural_)
 )
 

### 2024-04-07 manuscript/manuscript.tex
revise by tas and han

@@
 \usepackage{geometry}
+\usepackage{todonotes}
 \usepackage{hyperref}
+\usepackage{ulem}
 \usepackage{subfig}
@@
   %\title{On the performance of hierarchy construction: impacts of structure and clustering}
-\title{Augmenting hierarchical time series through clustering: \\Is there an optimal way for forecasting?}
+\title{Constructing hierarchical time series through clustering: \\Is there an optimal way for forecasting?}
 
@@
 
-    Forecast reconciliation has attracted significant research interest in recent years, with most studies relying on pre-defined hierarchies constructed with time series metadata.
-With the goal of improving forecast accuracy in mind, we extend and contribute to the emerging research on the clustering-based reconciliation method by proposing a novel framework for hierarchy construction.
-This framework offers three approaches: cluster hierarchies, random hierarchies, and combination hierarchies.
-Utilizing the proposed approaches, we investigate the individual contributions of two primary factors, namely ``grouping'' and ``structure'', to the performance of forecast reconciliation.
-Through a simulation study and experiments on two real-world datasets, we demonstrate the practical efficacy of different hierarchy construction approaches.
-Our findings provide new insights into the dynamics between ``grouping'' and ``structure'', which lead to an improved understanding of forecast reconciliation.\\
+    Forecast reconciliation has attracted significant research interest in recent years, with most studies taking the hierarchy of time series as given.
+We extend existing work that uses time series clustering to construct hierarchies, with the goal of improving forecast accuracy, in three ways.
+First, we investigate multiple approaches to clustering, including not only different clustering algorithms, but also the way time series are represented and how distance between time series is defined.
+We find that cluster-based hierarchies lead to improvements in forecast accuracy relative to two-level hierarchies.
+Second, we devise an approach based on random permutation of hierarchies, keeping the structure of the hierarchy fixed, while time series are randomly allocated to clusters.
+In doing so, we find that improvements in forecast accuracy that accrue from using clustering do not arise from grouping together similar series but from the structure of the hierarchy.
+Third, we propose an approach based on averaging forecasts across hierarchies constructed using different clustering methods, that is shown to outperform any single clustering method.
+All analysis is carried out on two benchmark datasets and a simulated dataset.
+Our findings provide new insights into the role of hierarchy construction in forecast reconciliation and offer valuable guidance on forecasting practice.
+\\
+
+    %the dynamics between ``grouping'' and ``structure'', which lead to an improved understanding of forecast reconciliation.\\
 
@@
 The original motivation for forecast reconciliation was to ensure forecasts are \textit{coherent}, that is they respect the aggregation constraints implied by the hierarchical structure.
-Coherent forecasts faciliate aligned decisions by agents acting upon different variables within the hierarchy.
+Coherent forecasts facilitate aligned decisions by agents acting upon different variables within the hierarchy.
 For example, consider a retail setting, where a warehouse manager supplies stock to individual store managers within their region.
@@
 %The primary objective of hierarchical forecasting is to produce coherent forecasts for the series within a given HTS, which we refer to as \textit{original hierarchy}, ensuring that decision-makers at different levels of the hierarchy can analyze and make informed decisions based on aligned expectations for the future.
-A limitation in the overwhelming majority of the forecast reconciliation studies is that the structure of the hierarchy is taken as \textit{given}.
-This structure usually includes \textit{bottom level series}, an overall aggregate or \textit{top level series}, with various aggregation schemes used to construct \textit{middle levels series}.
+A limitation in the overwhelming majority of forecast reconciliation studies is that the structure of the hierarchy is taken as \textit{given}.
+This structure usually includes \textit{bottom level series}, an overall aggregate or \textit{top level series}, with various aggregation schemes used to construct \textit{middle level series}.
 Typically, middle levels are formed according to inherent attributes of the bottom-level series, such as geographical location, gender, product category, travel purpose, and others.
@@
 While in some forecasting applications, decisions must be made with respect to the natural hierarchy, in other settings there might be some flexibility in determining how bottom levels are aggregated into middle levels.
-It should be noted that,  very little attention has been paid to whether middle level series can be constructed in a way that leads to further improvements in forecast accuracy relative to a given natural hierarchy.
+Moreover, a predefined natural hierarchy may not always exist in hierarchical settings, underscoring the importance of a hierarchical construction framework for forecasting purposes.
+It should be noted that very little attention has been paid to whether middle level series can be constructed in a way that leads to further improvements in forecast accuracy relative to a given natural hierarchy.
 To the best of our knowledge, only \cite{pangHierarchicalElectricityTime2018}, \cite{liForecastReconciliationApproach2019}, \cite{pangHierarchicalElectricityTime2022}, and \cite{matteraImprovingOutofSampleForecasts2023} have attempted to \textit{construct} middle level series in a data-driven way which ultimately improved forecast accuracy.
-All three of these works use time series clustering to construct hierarchies in a manner that is somewhat ad hoc.
-Our work conducts a more thorough investigation of issues faced when  constructing hierarchical structures in forecasting reconciliation.
-In particular, we address the following four research questions:%via time series clustering.
+However, all of these works use time series clustering to construct hierarchies in a manner that is somewhat ad hoc.
+Our work conducts a more thorough investigation of issues faced when  constructing hierarchical structures in forecast reconciliation.
+In particular, we address the following three research questions:%via time series clustering.
 %We also assess and disentangle the impact of
@@
 
-\begin{researchquestion}
-In terms of forecast performance, is the natural hierarchy better than a two-level hierarchy (consisting of only top and bottom time series)? 
+\begin{researchquestion} In terms of forecast performance, can the use of middle level series lead to improvement compared to a two-level hierarchy (consisting of only top and bottom time series)?
+If so, is it possible to construct hierarchies in a data-driven way that leads to further improvements in forecast accuracy?
+
+%In terms of forecast performance, is the natural hierarchy better than a two-level hierarchy (consisting of only top and bottom time series)? 
 %In terms of forecast performance, does the natural hierarchy outperform a two-level hierarchy of only top and bottom time series?
 \end{researchquestion}
+%\begin{researchquestion}
+%    If the use of middle level series in the ``natural'' hierarchy can lead to improvement in forecast accuracy, is it possible to construct hierarchies in a data-driven way that leads to further improvements in forecast accuracy?
+%\end{researchquestion}
 
@@
 %Under the reconciliation framework, improvements in accuracy for some series often come at the expense of others (see \citealp{pritulargaStochasticCoherencyForecast2021}).
-To investigate this question, we consider two widely used empirical HTS datasets; the first is Australian tourism demand, the second, cause-of-death mortality data.
+To investigate these questions, we consider two widely used empirical HTS datasets; the first is Australian tourism demand, the second, cause-of-death mortality data.
 Throughout the paper, all evaluations are carried out using the series common to all hierarchies; namely the top and bottom level series.
-In both datasets, we find that the natural hierarchy outperforms the two-level hierarchy, leading to our next research question:
-\begin{researchquestion}
-    If the use of middle level series in the ``natural'' hierarchy can lead to improvement in forecast accuracy, is it possible to construct hierarchies in a data-driven way that leads to further improvements in forecast accuracy?
-\end{researchquestion}
+In both datasets, we find that the natural hierarchy outperforms the two-level hierarchy, and data-driven hierarchy via clustering can further improve forecast performance compared to natural hierarchy.
 
@@
 Such arguments have been put forward by  \cite{pangHierarchicalElectricityTime2018}, \cite{liForecastReconciliationApproach2019}, \cite{pangHierarchicalElectricityTime2022}, and \cite{matteraImprovingOutofSampleForecasts2023}.
+They all demonstrate superior forecast performance from hierarchies constructed via clustering, relative to the natural hierarchy or the two-level hierarchy.
 However, these studies for the most part focus on a small number of (in some cases, a single) clustering techniques.
 In this paper, we take a more systematic approach by clustering time series using different representations (the original time series, forecast errors, features of both), different distance metrics (Euclidean, dynamic time warping), and different clustering paradigms ($k$-medioids, hierarchical).
-Using both empirical datasets, as well as a simulation study, we find evidence that constructing hierarchies via clustering can lead to improved forecasting performance, although the optimal clustering method depends on the dataset as well as the base forecasting and reconciliation method.
+The models used to obtain base forecasts and the reconciliation method are fixed throughout the experiments.
+Using both empirical datasets, as well as a simulation study, we find evidence that constructing hierarchies via clustering can lead to improved forecasting performance, although the optimal clustering method depends on the dataset characteristics.% \textbf{We use the same base forecasting model and reconciliation method through this paper}.
 
@@
 The first, which we refer to as     ``grouping'' is the idea that some correct subsets of series are chosen to form new middle-level series.
-This is the argument commonly made to support clustering-based hierarchy construction \citep[see e.g.][]{liForecastReconciliationApproach2019, pangHierarchicalElectricityTime2022, matteraImprovingOutofSampleForecasts2023}.
+This is the argument commonly made to support clustering-based hierarchy construction \citep[see \textit{e.g.}][]{liForecastReconciliationApproach2019, pangHierarchicalElectricityTime2022, matteraImprovingOutofSampleForecasts2023}.
 %The idea that often motivates time series clustering is these ``groupings'' be composed of similar series. 
-The second factor, which we refer to as the ``structure'' of the hierarchy, includes the number of middle level series, the depth of the hierarchy, and the distribution of group sizes in the middle layer(s).
+The second factor, which we refer to as the ``structure'' of the hierarchy, includes the number of middle-level series, the depth of the hierarchy, and the distribution of group sizes in the middle layer(s).
 Evidence showing that clustering within a forecast reconciliation framework leads to improved forecast accuracy, does not disentangle contributions from these two factors.
@@
 This argument would be consistent with the interpretation of reconciliation as a forecast combination of ``direct'' and ``indirect'' forecasts (\citealp{hollymanUnderstandingForecastReconciliation2021}), since more middle-level series implies a greater number of indirect forecasts in the combination.
-This leads to our third research question:
+This leads to our second research question:
 
 \begin{researchquestion}
-    Can the improved accuracy of cluster-based methods be attributed to grouping together similar time series, or to the structure of the hierarchy including the number of middle level series?
+    Should the improved accuracy of clustering-based methods be attributed to grouping together similar time series, or to the structure of the hierarchy? %including the number of middle level series?
 \end{researchquestion}
@@
 Multiple new ``twin'' hierarchies are formed with an identical structure to the original hierarchy, but with permuted leaves.
-In this way, we keep the \textit{hierarchical structure} fixed, but alter how series are combined.
+In this way, we keep the \text{hierarchical structure} fixed, but alter how series are combined.
 This method can be thought of as an informal ``permutation type'' test \citep{welch1990}.
@@
 \begin{researchquestion}
-    Does an equally-weighted combination of reconciled forecasts derived from multiple random hierarchies improve forecast reconciliation performance?
+    Does an equally-weighted combination of reconciled forecasts derived from multiple hierarchies improve forecast reconciliation performance?
 \end{researchquestion}
 
-Note that forecast combination here differs from that of \cite{hollymanUnderstandingForecastReconciliation2021}, in that our approach averages not only different coherent forecasts, but also over hierarchies with completely different middle level series.
+Note that forecast combination here differs from that of \cite{hollymanUnderstandingForecastReconciliation2021}, in that our approach averages not only different coherent forecasts, but also across hierarchies with completely different middle level series.
 This is possible since only coherent bottom and top level forecasts are averaged and evaluated.
-\clearpage
+
 In summary, this paper presents four main contributions:
@@
 The rest of the paper is organized as follows.
-Section~\ref{sec:setup} describes the experimental setup including the datasets used, the reconciliation methods employed, the clustering techniques considered, and the rolling window evaluation with associated forecast performance metrics.
-Section~\ref{sec:natural} investigates RQ1, in particular the performance of the natural hierarchy compared to the two-level hierarchy.
-The permutation approach used throughout the paper is also introduced at this juncture.
-Section~\ref{sec:clustering} evaluate the performance of different clustering approaches in answering RQ2 and RQ3 via two empirical studies.
+Section~\ref{sec:methodology} describes the trace minimization reconciliation methods employed and the clustering-based hierarchical time series augmentation techniques considered.
+Section~\ref{sec:cluster} first introduces the two datasets used, and then investigates RQ1, in particular the performance of cluster hierarchy compared to natural hierarchy and two-level hierarchy.
+Section~\ref{sec:permutation} introduces the novel permutation approach, followed by the investigation of RQ2 via evaluating the performance of natural hierarchy and the best performing cluster hierarchy compared to their respective random twins.
 To avoid the concern that clusters found in the empirical datasets are spurious, a simulation study is considered in Section~\ref{sec:simulation}.
-Section~\ref{sec:combination} covers the forecast combination approaches raised in RQ4.
+Section~\ref{sec:combination} covers the forecast combination approach raised in RQ3.
 Section~\ref{sec:conclusion} concludes this paper with discussions on the findings and outlines future research directions.
+Data and code for reproducing the results in this paper are available at \url{https://github.com/AngelPone/project_hierarchy}.
 
@@
 
-\section{Experiment setup}\label{sec:setup}
-
-\subsection{Dataset description}
+\section{Methodology}\label{sec:methodology}
+
+\subsection{Hierarchical forecasting and reconciliation methods}
+
+%We propose a general hierarchical time series augmentation framework, in which new time series are constructed by aggregating subsets of bottom-level series. 
+%Such subsets can be formed according to  results of time series clustering, attributes of the time series or other expert knowledge.
+
+Hierarchical data can be characterized as being made up of bottom level series and their aggregates.
+In general, we consider a hierarchy with $n$ time series stacked into a vector $\boldsymbol{y}_t$.
+Let $\boldsymbol{b}_t$ denote the $m$ bottom level series, $\boldsymbol{a}_t$ denote the top level series, and $\boldsymbol{c}_t$ denote $k$ middle level series.
+The top level and bottom level will be common to all hierarchies we consider, and are augmented by middle level series.
+These middle level series can be formed according to attributes of the time series or in a data-driven fashion using time series clustering.
+The series are linked through an $(m+k+1)\times m$ summing matrix
+
+%$\boldsymbol{S}$, which can be decomposed into an identity matrix $\boldsymbol{I}_m$ and two aggregation matrices $\boldsymbol{A}$ and $\boldsymbol{C}$ consisting of $0$ and $1$, such that, 
+\[
+  \boldsymbol{y}_t = \boldsymbol{S}\boldsymbol{b}_t = \begin{bmatrix}
+    \boldsymbol{A} \\\boldsymbol{C} \\ \boldsymbol{I}_m 
+  \end{bmatrix}  \boldsymbol{b}_t = \begin{bmatrix}
+      \boldsymbol{a}_t \\ \boldsymbol{c}_t \\\boldsymbol{b}_t
+  \end{bmatrix},
+\]
+where, $\boldsymbol{C}$ consists of zeros and ones that encode the aggregation, \textit{i.e.}, $c_{ij}=1$ if bottom level series $j$ is included in middle level series $i$, and zero otherwise.
+The top level series aggregates all bottom levels, \textit{i.e.}, $\boldsymbol{A} = \mathbf{1}_{1\times m}$, which is a row of ones.
+
+%where $\boldsymbol{A}$ and  $\boldsymbol{C}$ represent the mappings from bottom-level time series to the given aggregated time series and constructed time series, respectively. 
+%Each row of $\boldsymbol{C}$ corresponds to a subset of bottom-level series. The values $c_i, i=1,\dots,m$, indicate whether the $i$-th bottom-level series belongs to the subset.
+% In the case of a two-level hierarchy, we simply have $\mathbf{A} = \mathbf{1}_{1\times m}$.
+%We consider a two-level given hierarchy throughout this paper, where $\mathbf{A} = \mathbf{1}_{1\times m}$.
+
+%\subsection{Trace minimization forecast reconciliation approach}
+
+%Forecast reconciliation is a statistical technique aimed to improve the overall forecasts accuracy across different series in a hierarchical setting.
+It is a post-forecasting step that ensures the coherence of forecasts for all series in the hierarchy.
+Well-recognized regression types of reconciliation include the Ordinary Least Square (OLS) method proposed by \cite{hyndmanOptimalCombinationForecasts2011}, and the trace minimization (MinT) method proposed by \cite{wickramasuriyaOptimalForecastReconciliation2019}.
+%Forecast reconciliation is a hierarchical forecasting which first generates base forecasts for all time series in the hierarchy, and then reconciles the base forecasts via regression (\citealp{hyndmanOptimalCombinationForecasts2011}) or trace minimization (MinT, \citealp{wickramasuriyaOptimalForecastReconciliation2019}).
+%It is well-known for the ability to produce coherent and more accurate forecasts, which has been exploited in several perspectives, such as forecast combination (\citealp{hollymanUnderstandingForecastReconciliation2021}) or projection (\citealp{panagiotelisForecastReconciliationGeometric2021}).
+%In this subsection, we describe the process of generating coherent forecasts using the MinT approach, which will be employed throughout this paper.
+
+% Consider a given hierarchy with $n$ time series with $m$ of them at the bottom level.
+Let vectors $\boldsymbol{b}_t$, $\boldsymbol{a}_t$, and $\boldsymbol{y}_t$ represent observations  at time $t$ of the bottom level, the aggregated levels (\textit{i.e.}, middle and top levels), and the entire hierarchy, respectively.
+% The vectors are linked through an $n\times m$ summing matrix $\boldsymbol{S}$, which can be decomposed into an identity matrix $\boldsymbol{I}_m$ and a constraint matrix $\boldsymbol{A}$ consisting of $0$ and $1$, such that,
+% \[
+%   \boldsymbol{y}_t = \boldsymbol{S}\boldsymbol{b}_t = \begin{bmatrix}
+%     \boldsymbol{A} \\ \boldsymbol{I}_m 
+%   \end{bmatrix}  \boldsymbol{b}_t = \begin{bmatrix}
+%       \boldsymbol{a}_t \\ \boldsymbol{b}_t
+%   \end{bmatrix},
+% \]
+% where $\boldsymbol{A}$ represents the mapping from bottom-level time series to aggregated-level time series.
+In the case of a two-level hierarchy, we simply have $\mathbf{A} = \mathbf{1}_{1\times m}$.
+
+%To produce $h$-step-ahead forecasts based on $T$ historic observations, we would first produce $h$-step-ahead unreconciled (or ``base'') forecasts $\hat{\boldsymbol{y}}_{T+h}$.
+Note that there are different ways to compute such forecasts.
+In this paper, we adopt the Exponential Smoothing (ETS) method, a well-known univariate forecasting model widely used in both research and practice \citep{ForecastingExponentialSmoothing}.
+%The \code{forecast} (\citealp{forecast}) package in {R} (\citealp{R}) is implemented to produce base forecasts for each time series in the hierarchy.
+%Subsequently, the MinT reconciliation method is applied to produce coherent forecasts:
+%\[
+%    \tilde{\boldsymbol{y}}_{T+h} = \boldsymbol{S}(\boldsymbol{S}'\boldsymbol{W}_h^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}_h^{-1}\hat{\boldsymbol{y}}_{T+h},
+%\]
+%where $\boldsymbol{W}_h$ is the covariance matrix of $h$-step-ahead forecast errors.
+The shrinkage method is employed to obtain the estimator of $\boldsymbol{W}_h$ \citep{wickramasuriyaOptimalForecastReconciliation2019}.
+%is considered throughout this paper.
+%Several estimators of $\boldsymbol{W}_h$ were proposed in \cite{wickramasuriyaOptimalForecastReconciliation2019}.
+%such as the OLS estimator, variance scaling, structural scaling estimator, and shrinkage estimator.
+% due to its ability to account for covariance in forecast errors.
+
+For the purposes of this paper, all forecasting is carried out as a two-step process.
+First, so-called \textit{base} forecasts are produced for all series in the hierarchy and stacked into an $n$-vector $\hat{\bm{y}}$, where subscripts are suppressed for brevity.
+For base forecasts, we use the Exponential Smoothing (ETS) method \citep{ForecastingExponentialSmoothing}, implemented using the \code{forecast} (\citealp{forecast}) package in {R} (\citealp{R}).
+Alternative methods such as ARIMA models were also considered, but this choice had very little impact on the overall conclusions.
+
+The base forecasts generated in this first step, do not have the property that bottom level forecasts add up to forecasts of the aggregates, \textit{i.e.}, they are \textit{incoherent}.
+Therefore, forecast reconciliation is used as a post-forecasting step to ensure coherence of forecasts for all series in the hierarchy.
+In general, reconciliation takes the form of projecting the base forecasts as
+\[
+    \tilde{\boldsymbol{y}} = \boldsymbol{S}(\boldsymbol{S}'\boldsymbol{W}_h^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}_h^{-1}\hat{\boldsymbol{y}},
+\]
+where $\tilde{\boldsymbol{y}}$ are the \textit{reconciled} forecasts and $\boldsymbol{W}_h$ is the covariance matrix of $h$-step-ahead forecast errors.
+For reconciliation, we use the MinT method \citep{wickramasuriyaOptimalForecastReconciliation2019}, which involves plugging in a shrinkage estimator for $\boldsymbol{W}_h$.
+Although alternatives were considered, including approaches that assume $\boldsymbol{W}_h$ is diagonal or an identity matrix \citep{hyndmanOptimalCombinationForecasts2011}, this choice has little impact on our main conclusions.
+
+%\subsection{Grouping-based forecast reconciliation}
+%\subsection{Augmenting hierarchical time series through clustering} 
+\subsection{Time series clustering} 
+\label{sec:clustering}
+
+%\textbf{HOW TO AUGMENT THE HIERARCHY}
+%\subsection{Cluster hierarchy construction approach}
+
+To the best of our knowledge, four studies have attempted to improve forecast accuracy in a reconciliation setting by constructing middle levels of the hierarchy using time series clustering.
+\cite{pangHierarchicalElectricityTime2018} detect consumption patterns of electricity smart meter data based on X-means clustering algorithm, while \cite{pangHierarchicalElectricityTime2022} propose several alternative clustering methods to group similar electricity and solar power time series.
+\cite{liForecastReconciliationApproach2019} apply agglomerative hierarchical clustering to cause-of-death time series, and
+\cite{matteraImprovingOutofSampleForecasts2023} utilize Partition Around Medoids algorithms to unveil underlying structures in stock price indexes. 
+However, these studies are limited in scope as they focus on a few  clustering techniques. 
+%\todo{Should we move to intro?}
+%construct hierarchies through clustering algorithms and 
+Inspired by the comprehensive overview of time series clustering by \cite{aghabozorgiTimeseriesClusteringDecade2015a}, we consider various approaches based on three key components, namely \textit{time series representations}, \textit{distance measures}, and \textit{clustering algorithms}.
+%Our framework for creating a clustering approach is as follows: we first choose a time series representation, which can be the raw time series, the in-sample forecast error, features of the time series, or features of the in-sample forecast error.
+We then select a distance measure, either Euclidean distance or dynamic time warping.
+Once the representation and the distance measure are determined, we choose a clustering algorithm, either $k$-medoids or agglomerative hierarchical clustering, to form clusters in the dataset.
+In total, we consider 12 different clustering approaches in our experiments.
+%, and evaluation measures.
+
+% Time series clustering is an essential technique that finds applications across various domains, including finance (\citealp{DIAS2015852}), energy (\citealp{pangHierarchicalElectricityTime2018}), robotics (\citealp{gopalapillaiExperimentationAnalysisTime2014}), and others.
+It is commonly used to identify similar patterns within time series datasets, aiding in applications such as anomaly detection, pattern discovery, and recommendation.
+
+\paragraph{\textbf{Time series representations}}
+
+The time series representation refers to the object that acts as an input for time series clustering. %that provide diverse perspectives on the same dataset.
+% Considering the impracticality of exploring every conceivable time series representation, we focus on four key ones: raw time series without any transformation (hereafter referred to as ``time series''), in-sample one-step-ahead forecast error, features of time series, and features of in-sample one-step-ahead forecast error.
+Our first candidate for the representation is raw time series itself, due to its simplicity and broad applicability.
+%However, a crucial element contributing to the success of the MinT method lies in estimating the covariance matrix of base forecast errors based on in-sample one-step-ahead forecast error. 
+We also consider the in-sample one-step-ahead forecast error as a representation of the time series, since a key step in MinT reconciliation is to estimate the $\boldsymbol{W}_h$ matrix.
+%to examine how the structure within the error series influences reconciliation performance.
+It is important to note that raw time series and in-sample error representations are standardized to eliminate the impact of scale variations.
+%This is done by normalizing each series by subtracting its mean and then dividing by the standard error.
+
+A potential shortcoming to using the time series or forecast error as a representation is their high dimensionality, which is equal to the sample size of the training data.
+To address this concern, low dimension summaries of ``features'' can be considered.
+Features have been used in the context
+%Features, widely employed in capturing time series characteristics, play a pivotal role in various time series applications, including 
+time series clustering by \cite{tianoFeatTSFeaturebasedTime2021}, and for forecasting by \cite{wangUncertaintyEstimationFeaturebased2022} and \cite{ liFeaturebasedIntermittentDemand2023}. 
+We consider features of both the raw time series and the in-sample forecast error as representations.
+After filtering out the features that are constant across all series, we select $56$ features.\footnote{The list and descriptions of features are available in the online GitHub repository.} These time series features are calculated by the \code{tsfeatures} (\citealp{tsfeatures}) package in R.
+%have been applied in several feature-based forecasting studies, \textit{e.g.}, \cite{montero-mansoFFORMAFeaturebasedForecast2020}.
+To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation.
+%\sout{These representations allow us to gain insights into the diverse aspects of hierarchical time series data}.
+
+\paragraph{\textbf{Distance measures}}
+
+All clustering algorithms we consider require a distance to be defined between the objects that act as inputs to the algorithm.
+%Distance measures serve as crucial tools for assessing the similarity between two series, which in turn significantly influence the clustering results.
+We consider two widely applied distance measures: Euclidean distance and dynamic time warping (DTW).
+When employing Euclidean distance, dimension reduction is necessary due to the curse of dimensionality.
+%, which acts as the dimension over which Euclidean distance is computed in our applications.
+%Failure to undertake dimension reduction may result in undesirable clustering outcomes due to the curse of dimensionality. 
+To address this, we perform Principal Component Analysis (PCA), extracting the first few principal components that collectively explain at least 80\% of the variance within the representations.
+
+Unlike Euclidean distance, DTW is not as sensitive to the curse of dimensionality (\citealp{sakoeDynamicProgrammingAlgorithm1978}).
+Instead of performing one-to-one point comparisons, DTW accommodates time series of varying lengths through many-to-one comparisons.
+This flexible approach allows for the recognition of time series with similar shapes, even in the presence of signal transformations such as shifting and/or scaling.
+
+\paragraph{\textbf{Clustering algorithms}}
+%\sout{Clustering algorithms, such as partitioning, hierarchical, grid-based, and model-based approaches,  identify clusters by optimizing specific objective functions} \citep{aghabozorgiTimeseriesClusteringDecade2015a}.
+%, or applying heuristics.
+%These functions are calculated based on chosen time series representations and distance measures.
+In this paper, we focus on two clustering algorithms, namely $k$-medoids and agglomerative hierarchical clustering.
+These algorithms are implemented using the \texttt{cluster} (\citealp{cluster}) package in R.
+{The $k$-medoids algorithm aims to minimize the total distance between all observations within a cluster and their respective cluster median.} This is implemented using the partitioning around medoids (PAM) method (\citealp{PartitioningMedoidsProgram1990}).
+%Unlike $k$-means which employs the mean vector of samples as the cluster center, $k$-medoids selects one observation within each cluster as the center. 
+Following the recommendation of \cite{PartitioningMedoidsProgram1990}, we determine the optimal number of clusters using the average silhouette width (ASW), which is a commonly used index in cluster validation \citep[see \textit{e.g.},][]{shutaywi2021silhouette}.
+%ASW assesses the quality of clustering results by measuring the proximity of samples within a cluster compared to neighboring clusters.
+%Given a clustering result, the silhouette width for the $i$th sample is calculated as 
+%\[
+%  SW(i) = \frac{b(i)-a(i)}{\max\{a(i), b(i)\}},  
+%\]
+%where $a(i)$ represents the average distance of the $i$th observation to others in the same cluster, and $b(i)$ is the average distance to observations in the cluster nearest to observation excluding the cluster that observation $i$ is assigned to.
+A higher silhouette width indicates greater proximity to observations within the same cluster than to those in neighboring clusters.
+The ASW is the average of silhouette width across all observation.
+We select the clustering result that maximizes the ASW by iterating over all possible numbers of clusters.
+However, ASW has the limitation of being undefined when there is only one cluster.
+%\textbf{Gap statistics (\citealp{tibshiraniEstimatingNumberClusters2002}) can be used to address this limitation, but it is incompatible with DTW.}
+
+Agglomerative hierarchical clustering initializes each observation in its own cluster, and then merges the nearest two clusters in a stepwise fashion until all observations form a single cluster.
+We employ Ward's linkage (\citealp{murtaghWardHierarchicalAgglomerative2014a}) which defines the nearest clusters as those that minimize the increase in within-cluster variance at each step.
+Applying hierarchical clustering to $m$ bottom-level series results in a binary hierarchical tree with ($2m-1$) nodes, all of which are retained as middle level series.
+
+\begin{figure}[h!]
+    \centering
+    \vspace{0.2in}
+    \includegraphics[width=0.46\textwidth]{figures/pamcluster.pdf}
+    \hspace{1cm}
+    \includegraphics[width=0.46\textwidth]{figures/aggcluster.pdf}
+    \caption{\label{fig:cluster_example}Example clustering results of two clustering algorithms.
+Left panel displays example for $k$-medoids algorithm, and right panel displays example for agglomerative hierarchical clustering algorithm.}
+\end{figure}
+Figure~\ref{fig:cluster_example} illustrates two examples of hierarchies generated by $k$-medoids and agglomerative clustering algorithms, on the left and right panels respectively.
+The corresponding two-level hierarchy would have four bottom-level series and one top-level series.
+% \sout{These examples highlight the distinct behaviors of the two algorithms.}
+Note that, $k$-medoids constructs a simple hierarchy with a single middle level, while hierarchical clustering generates multiple nested middle levels. 
+In general, $k$-medoids produces a hierarchy with fewer middle levels and middle level series compared to hierarchical clustering.
+As the number of bottom-level series increases, these differences become increasingly pronounced, with potential implications for forecast reconciliation.
+
+In summary, we employ 12 time series clustering approaches which are derived from combinations of four time series representations, two distance measures, and two clustering algorithms.
+The names and details of these approaches are listed in Table~\ref{tab:P3_methods}.
+Note that all methods using DTW, have either the raw time series or forecast errors as representations, since DTW is not compatible with time series features.
+\\
+
+\begin{table}[h!]
+\caption{\label{tab:P3_methods} Details of the 12 clustering approaches considered.}
+\centering
+\resizebox{\textwidth}{!}{
+\begin{tabular}{rcrrr}
+    \toprule
+    Approach & Dimension reduction & Representation & Distance measure & Clustering algorithm  \\ \midrule
+    TS-EUC-ME &  Yes & Time series  & Euclidean & $k$-medoids \\
+    ER-EUC-ME & Yes& In-sample  error  & Euclidean & $k$-medoids \\
+    TSF-EUC-ME & Yes& Time series features  & Euclidean & $k$-medoids \\
+    ERF-EUC-ME & Yes& In-sample error features  & Euclidean & $k$-medoids \\
+    TS-EUC-HC & Yes& Time series  & Euclidean & Hierarchical   \\ 
+    ER-EUC-HC & Yes& In-sample error  & Euclidean & Hierarchical   \\ 
+    TSF-EUC-HC & Yes& Time series features  & Euclidean & Hierarchical   \\ 
+    ERF-EUC-HC & Yes& In-sample error features  & Euclidean & Hierarchical  \\
+    TS-DTW-ME & No& Time series  & DTW & $k$-medoids \\
+    TS-DTW-HC & No& In-sample error  & DTW & Hierarchical  \\
+    ER-DTW-ME & No& Time series  & DTW & $k$-medoids \\
+    ER-DTW-HC & No& In-sample error  & DTW & Hierarchical 
+     \\\bottomrule
+\end{tabular}}
+\end{table}
+
+%The four time series representations need to perform dimension reduction when using Euclidean distance. 
+%Combing the four dimension reduced representations with two clustering algorithms results in the first eight clustering approaches. 
+%The first eight approaches require dimension reduction via PCA, while the last four approaches use either the raw time-series or forecast errors, 
+%must take temporal data as an input.
+%the last four approaches 
+%Note that features of raw time series and in-sample forecast error are not temporal data, thus incompatible with DTW.
+Therefore, the last four approaches are derived from combinations of two temporal representations (\textit{i.e.}, raw time series and in-sample error), DTW, and two clustering algorithms.
+
+\section{Improving forecast performance via hierarchy augmentation}\label{sec:cluster}
+\subsection{Data description}
 
 We conduct our experiments on two empirical datasets throughout this paper.
-The first one is the monthly Australian domestic tourism dataset, covering the period from January 1998 to December 2016.
-The data is recorded as ``visitor nights'', representing the total number of nights spent by Australians away from home.
+The first is the monthly Australian domestic tourism dataset, covering the period from January 1998 to December 2016.\footnote{Please refer to Section 4 of \cite{wickramasuriyaOptimalForecastReconciliation2019} for an in-depth explanation of this dataset.} The data is recorded as ``visitor nights'', representing the total number of nights spent by Australians away from home.
 In this dataset, the total visitor nights of Australia is geographically disaggregated into seven states and territories, which are further divided into $27$ zones, and then into $76$ regions.
@@
 Overall, this dataset comprises a total of $555$ time series with $304$ of those at the bottom level.
-Section 4 of \cite{wickramasuriyaOptimalForecastReconciliation2019} provided an in-depth explanation of this dataset.
+In the case of tourism data, the first two or three letters of the series name indicate geographical zones or regions, and the last three denote travel purposes.
+For example, ``\textit{AAAHol}'' represents the visitor nights spent for holiday in the ``Sydney'' region.
 
@@
 
-Figures~\ref{fig:tourism} and~\ref{fig:mortality} illustrate the top-level series and four bottom-level series for the tourism and mortality datasets, respectively. 
-In the case of tourism data, the first three letters indicate geographical regions, and the last three denote travel purposes.
-For example, ``\textit{BEEHol}'' represents the visitor nights spent for holiday in the `Spa Country' region.
-As mentioned before, the death series are coded based on the ICD 113 Cause List.
-From the figures, we can see that the mortality dataset generally exhibits strong seasonality and trend, whereas the tourism dataset displays greater volatility and less obvious seasonal and trend components.
-We can also see that the patterns observed at the bottom level can be very different from those at the top and middle levels.
+%\textbf{italic or double quotation mark} Italic is better I think
+
+The top-level series, one selected middle-level series, and three selected bottom-level series are illustrated in Figures~\ref{fig:tourism} and~\ref{fig:mortality} for the tourism and mortality datasets, respectively.
+%As mentioned before, the death series are coded based on the ICD 113 Cause List. 
+Both figures exhibit more regular and apparent trend and seasonality for series at a higher level of aggregation, while bottom-level series are noisier and prone to outliers. 
+Comparing the datasets to one another, the mortality dataset generally exhibits stronger seasonality and trend, whereas the tourism dataset displays greater volatility.
+Table~\ref{tab:features} summarizes three features of each dataset, with larger values indicating more ``signal'' relative to ``noise''.
+These are: the Holt Winters seasonal smoothing parameter; the lag 12 autocorrelation coefficient; and the strength of trend measured as the proportion of variance explained by the trend component in an STL decomposition.
+Table~\ref{tab:features} supports the conclusions made by visualizing the time series of the data, which is that the tourism data are noisier and less regular with respect to trend and seasonality.
+
+%Figures~\ref{fig:tourism} and~\ref{fig:mortality} illustrate the top-level series, one middle-level series, and three selected bottom-level series for the tourism and mortality datasets, respectively.
+%As mentioned before, the death series are coded based on the ICD 113 Cause List. 
+%We can see that the patterns observed at the bottom level can be very different from those at the top and middle levels, for both datasets. 
+%Furthermore, the mortality dataset generally exhibits strong seasonality and trend, whereas the tourism dataset displays greater volatility but less obvious seasonal and trend components.
 
@@
 
-\begin{figure}
+\begin{figure}[h!]
     \centering
     \includegraphics[width=\textwidth]{figures/tourism.pdf}
+    \vspace{-0.35in}
     \caption{Visualization of selected time series from the tourism dataset.
-``AEB'', ``BAB'', ``BEB'', and ``BEE'' represent the regions `New England North West`, `Peninsula', `Western Grampians` and ``Spa Country'', respectively.
-``Bus'', ``Oth'', ``Vis'' and ``Hol'' denote travel purposes ``Business'', ``Other'', ``Visit'' and ``Holiday'', respectively.}
+``AA'', ``AEB'', ``BEB'', and ``BEE'' represent the zone ``Metro NSW'', and the regions ``New England North West'', ``Western Grampians'', and ``Spa Country'', respectively.
+``Bus'', ``Vis'', and ``Hol'' denote travel purposes ``Business'', ``Visit'', and ``Holiday'', respectively.}
     \label{fig:tourism}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/mortality.pdf}
-    \caption{{Visualization of selected time series from the death count dataset.} ``GR113-051'',  ``GR113-063'', ``GR113-085'', and ``GR113-091'' denote ``Parkinson disease'', ``All other forms of chronic ischemic heart disease'', ``Asthma'', and ``Diseases of appendix'', respectively.}
+\begin{figure}[h!]
+    \centering
+    \vspace{-0.2in}\includegraphics[width=\textwidth]{figures/mortality.pdf}
+    \vspace{-0.35in}
+    \caption{{Visualization of selected time series from the death count dataset.} ``GR113-019'', ``GR113-051'',  ``GR113-063'', and ``GR113-085'' denote ``Malignant neoplasms'', ``Parkinson disease'', ``All other forms of chronic ischemic heart disease'', and ``Asthma'', respectively.}
+    \vspace{-0.2in}
     \label{fig:mortality}
@@
 
-\subsection{Trace minimization forecast reconciliation approach}
-
-In this subsection, we describe the process of generating coherent forecasts using the trace minimization (MinT) reconciliation approach \citep{wickramasuriyaOptimalForecastReconciliation2019}, which will be employed throughout this paper.
-Consider a given hierarchy with $n$ time series and $m$ of them being in the bottom level.
-Let vectors $\boldsymbol{b}_t$, $\boldsymbol{a}_t$, and $\boldsymbol{y}_t$ represent observations of the bottom level, the aggregated levels (\textit{i.e.} middle and top levels), and the entire hierarchy at time $t$, respectively.
-They are linked through an $n\times m$ summing matrix $\boldsymbol{S}$, which can be decomposed into an identity matrix $\boldsymbol{I}_m$ and a constraint matrix $\boldsymbol{A}$ consisting of $0$ and $1$, such that,
-\[
-  \boldsymbol{y}_t = \boldsymbol{S}\boldsymbol{b}_t = \begin{bmatrix}
-    \boldsymbol{A} \\ \boldsymbol{I}_m 
-  \end{bmatrix}  \boldsymbol{b}_t = \begin{bmatrix}
-      \boldsymbol{a}_t \\ \boldsymbol{b}_t
-  \end{bmatrix},
-\]
-where $\boldsymbol{A}$ represents the mapping from bottom-level time series to aggregated-level time series.
-
-Assume our objective is to make $h$-step-ahead forecasts based on $T$ historic observations, we would first produce $h$-step-ahead unreconciled (or ``base'') forecasts $\hat{\boldsymbol{y}}_{T+h}$.
-Note that there are many different ways to compute such forecasts.
-In this paper, we adopt the Exponential Smoothing (ETS) method, a well-known univariate forecasting model widely used in both academia and industry \citep{ForecastingExponentialSmoothing}.
-The \code{forecast} (\citealp{forecast}) package in {R} (\citealp{R}) is implemented to produce base forecasts for each time series in the hierarchy.
-Subsequently, the MinT reconciliation method is applied to produce coherent forecasts:
-\[
-    \tilde{\boldsymbol{y}}_{T+h} = (\boldsymbol{S}'\boldsymbol{W}_h^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}_h^{-1}\hat{\boldsymbol{y}}_{T+h},
-\]
-where $\boldsymbol{W}_h$ is the covariance matrix of $h$-step-ahead forecast errors, which is estimated using the MinT shrinkage estimator based on the in-sample one-step-ahead forecast errors (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
-
-%\subsection{Grouping-based forecast reconciliation}
-\subsection{Augmenting hierarchical time series through clustering}
-
-%DELETE
-
-%Instead of a We use the term ``augmentation'' to denote the process of creating middle-level series by aggregating subsets of bottom-level series.
-leading to a modified hierarchical time series $\boldsymbol{y}^c_t$, which can be represented as:
-%leading to a modified hierarchical time series $\boldsymbol{y}^c_t$, which can be represented as:
+%In Table~\ref{tab:features}, we summarize three features of the bottom-level series for the two datasets, including the strength of trend defined in \cite{tsfeatures}, the seasonality smoothing  parameter of the Holt-Winters model (\citealp{holtForecastingSeasonalsTrends2004}), and the first order seasonal auto-correlation coefficient.
+%function (ACF),
+%The strength of trend is defined as 
 %\[
-%   \boldsymbol{y}^c_t = \boldsymbol{S}^c\boldsymbol{b}_t = \begin{bmatrix}
-%        \boldsymbol{A}' &
-%        \boldsymbol{C}_1 &
-%        \cdots &
-%        \boldsymbol{C}_K &
-%        \boldsymbol{I}_m
-    %\end{bmatrix}'\boldsymbol{b}_t,
+%\text{Strength of trend} = 1-\frac{\text{Var}(e_t)}{\text{Var}(f_t+e_t)},
 %\]
-%where each $\boldsymbol{C}_k$ represents a newly created middle-level series, formed by aggregating a subset of bottom-level series $\boldsymbol{b}_t$.
-The vector $\boldsymbol{C}_k$ is of $m$-dimensional and its elements $c_{k, i} \in \{0, 1\}, i=1,\dots m$ indicate whether the $i$-th bottom-level series belongs to the aggregated subset.
-Notably, different augmentation approaches can result in different hierarchies with varying numbers of new middle-level series $K$.
-
-%After new hierarchies are constructed, we produce $h$-step-ahead base forecasts based on $T$ observations for each time series in the new hierarchy, and apply forecast reconciliation with MinT shrinkage estimator to obtain reconciled forecasts $\tilde{\boldsymbol{y}}^c_{T+h}$.
-Given our specific interest in the performance of the two-level hierarchy, we extract reconciled forecasts of the two-level hierarchy from $\tilde{\boldsymbol{y}}_{T+h}^c$, \textit{i.e.},
-%\[
-%  \tilde{\boldsymbol{y}}_{T+h} = \tilde{\boldsymbol{y}}^c_{T+h, 1:(n-m) \cup (n + K - m + 1): (n+K)}.
-%\]
-
-%\subsection{Cluster hierarchy construction approach}
-
-To the best of our knowledge, the following studies are the exclusive examples in the literature that propose to integrate forecast reconciliation with hierarchy construction via time series clustering.
-\cite{pangHierarchicalElectricityTime2018} detect consumption patterns of electricity smart meter data based on X-means clustering algorithm, while \cite{pangHierarchicalElectricityTime2022} propose a multiple alternative clustering method to group similar electricity and solar power time series.
-\cite{liForecastReconciliationApproach2019} apply agglomerative clustering to cause-of-death time series, and
-\cite{matteraImprovingOutofSampleForecasts2023} utilize Partition Around Medoids algorithms to unveil underlying structures in stock price indexes. 
-These studies demonstrate superior forecast performance of the clustering-based hierarchies compared to the natural hierarchy or the two-level hierarchy.
-However, these studies are limited in scope as they focus on a small number of  clustering techniques. 
-%construct hierarchies through clustering algorithms and
-
-Inspired by the comprehensive overview of time series clustering by \cite{aghabozorgiTimeseriesClusteringDecade2015a}, we consider various approaches based on three key components, namely time series representations, distance measures, and clustering algorithms.
-Our framework for creating a clustering approach is as follows: we first choose a time series representation, which can be the raw time series, the in-sample forecast error, features of the time series, or features of the in-sample forecast error.
-We then select a distance measure, either Euclidean distance or dynamic time warping.
-Once the representation and the distance measure are determined, we choose a clustering algorithm, either $k$-medoids or agglomerative hierarchical clustering, to form clusters in the dataset.
-In total, we consider 12 different clustering approaches in our experiments.
-%, and evaluation measures.
-
-% Time series clustering is an essential technique that finds applications across various domains, including finance (\citealp{DIAS2015852}), energy (\citealp{pangHierarchicalElectricityTime2018}), robotics (\citealp{gopalapillaiExperimentationAnalysisTime2014}), and others.
-It is commonly used to identify similar patterns within time series datasets, aiding in applications such as anomaly detection, pattern discovery, and recommendation.
-
-\subsubsection{Time series representations}
-
-The first step of time series clustering is to find appropriate time series representations.
-Time series representations transform time series data into another space through techniques like feature extraction or dimension reduction.
-By utilizing diverse time series representations, we are able to obtain distinct clusters which offer varied perspectives on the same dataset.
-Considering the impracticality of exploring every conceivable time series representation, we focus on four key ones: raw time series without any transformation (hereafter referred to as ``time series''), in-sample one-step-ahead forecast error, features of time series, and features of in-sample one-step-ahead forecast error.
-The inclusion of raw time series is motivated by its simplicity and broad applicability.
-A crucial element contributing to the success of the MinT method lies in estimating the covariance matrix of base forecast errors based on in-sample one-step-ahead forecast error.
-Hence, we consider in-sample one-step-ahead forecast error as a representation to examine how the structure within the error series influences reconciliation performance.
-Raw time series and in-sample error representations are standardized to eliminate the impact of scale variations.
-This is done by normalizing each series by subtracting its mean and then dividing by the standard error.
-
-Features, widely employed in capturing time series characteristics across literature, play a pivotal role in various time series applications, including clustering (\citealp{tianoFeatTSFeaturebasedTime2021}) and forecasting (\citealp{wangUncertaintyEstimationFeaturebased2022, liFeaturebasedIntermittentDemand2023}).
-In our exploration, we incorporate features of both raw time series and in-sample forecast error as representations.
-The included time series features, calculated by the \code{tsfeatures} (\citealp{tsfeatures}) in R, have been applied in several feature-based forecasting studies, \textit{e.g.}, \cite{montero-mansoFFORMAFeaturebasedForecast2020}.
-Notably, to the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation literature.
-These representations allow us to gain insights into the diverse aspects of hierarchical time series data.
-
-\subsubsection{Distance measures}
-
-Distance measures serve as crucial tools for assessing the similarity/dissimilarity between two series, significantly influencing the clustering results.
-We consider two widely applied distance measures: Euclidean distance and dynamic time warping (DTW).
-Due to the limited number of time series in comparison to the high dimensionality of individual time series (\textit{i.e.}, the length of time series and the number of time series features) in our applications, dimension reduction on the aforementioned representations becomes imperative when employing Euclidean distance.
-Failure to undertake dimension reduction may result in undesirable clustering outcomes due to the curse of dimensionality.
-To address this, we perform Principal Component Analysis (PCA), extracting the first few principal components that collectively explain at least 80\% of the variance within the representations.
-
-In contrast, DTW (\citealp{sakoeDynamicProgrammingAlgorithm1978}), exhibits reduced sensitivity to the curse of dimensionality.
-Unlike Euclidean distance, which performs one-to-one point comparisons, DTW accommodates time series of varying lengths through many-to-one comparisons.
-This flexible approach allows for the recognition of time series with similar shapes, even in the presence of signal transformations such as shifting and/or scaling.
-
-\subsubsection{Clustering algorithms}
-Clustering algorithms, such as partitioning, hierarchical, grid-based, model-based clustering, among others, identify clusters by optimizing specific objective functions (\citealp{aghabozorgiTimeseriesClusteringDecade2015a}).
-These functions are calculated based on chosen time series representations and distance measures.
-In this paper, we focus on two prevalent approaches, $k$-medoids and agglomerative hierarchical clustering.
-The $k$-medoids algorithm, a classical partitioning clustering method, aims to minimize the total distance between all samples within a cluster and their respective cluster centers.
-Unlike $k$-means which employs the mean vector of samples as the cluster center, $k$-medoids selects one sample within the cluster as the center. 
-Specifically, we adopt the $k$-medoids variant, partitioning around medoids (PAM, \citealp{PartitioningMedoidsProgram1990}).
-Following the recommendation of \cite{PartitioningMedoidsProgram1990}, we determine the optimal number of cluster using the average silhouette width (ASW), a popular cluster validation index.
-ASW assesses the quality of clustering results by measuring the proximity of samples within a cluster compared to neighboring clusters.
-Given a clustering result, the silhouette width for the $i$th sample is calculated as 
-\[
-  SW(i) = \frac{b(i)-a(i)}{\max\{a(i), b(i)\}},  
-\]
-where $a(i)$ represents the average distance of the $i$th sample to others in the same cluster, and $b(i)$ is the average distance to samples in the nearest cluster it is not assigned to.
-A higher silhouette width indicates greater proximity to samples within the same cluster than to those in neighboring clusters.
-The ASW is the average of silhouette widths across all samples.
-We select the clustering result that maximizes the ASW by iterating over all possible numbers of clusters.
-However, ASW has the limitation of being undefined when there is only one cluster.
-
-On the other hand, agglomerative hierarchical clustering begins by considering each sample as a cluster, and then gradually merges clusters until all samples forms a single cluster.
-Recall that $m$ represents the number of bottom level series.
-This process results in a binary hierarchical tree with ($2m-1$) nodes.
-We employ Ward's linkage (\citealp{murtaghWardHierarchicalAgglomerative2014a}) to merge clusters, minimizing the increase of within-cluster variances at each step.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/pamcluster.pdf}
-    \hspace{1cm}
-    \includegraphics[width=0.45\textwidth]{figures/aggcluster.pdf}
-    \caption{\label{fig:cluster_example}Example clustering results of two clustering algorithms.
-Left panel displays example for $k$-medoids algorithm, and right panel displays example for agglomerative hierarchical clustering algorithm.}
-\end{figure}
-Illustrated in Figure~\ref{fig:cluster_example} are two example hierarchies generated by $k$-medoids and agglomerative clustering algorithms for an original hierarchy with four bottom-level series and one total series.
-These examples highlight the distinct behaviors of the two algorithms.
-Firstly, $k$-medoids constructs a simple hierarchy with a single middle level, while hierarchical clustering generates multiple nested middle levels. 
-Secondly, $k$-medoids produces a hierarchy with the same number of series as the optimal number of clusters, whereas hierarchical clustering yields multiple middle levels with ($m-2$) series.
-As the number of bottom-level series increases, the structural differences become increasingly significant, and we aim to investigate how these differences influence the performance of forecast reconciliation.
-
-In summary, we employ 12 time series clustering approaches which are derived from combinations of four time series representations, two distance measures, and two clustering algorithms.
-The names and details of these approaches are listed in Table~\ref{tab:P3_methods}.
-The four time series representations need to perform dimension reduction when using Euclidean distance.
-Combing the four dimension reduced representations with two clustering algorithms results in the first eight clustering approaches.
-Note that features of raw time series and in-sample forecast error are not temporal data, thus incompatible with DTW.
-Therefore, the last four approaches are derived from combinations of two temporal representations (\textit{i.e.}, raw time series and in-sample error), DTW, and two clustering algorithms.
-After filtering out the features that are constant across all series, $56$ features are reserved.
-The list and descriptions of features are available in the supplementary materials.
-The $k$-medoids and hierarchical clustering algorithms are implemented using the \texttt{cluster} (\citealp{cluster}) package in R.
+%where $e_t$ and $f_t$ are residuals component and smoothed trend component obtained by the STL decomposition of the time series (\citealp{tsfeatures}).
+%We can confirm our earlier observations that the mortality dataset has stronger trend and seasonality compared to the tourism dataset in general.
 
 \begin{table}[h!]
-\caption{\label{tab:P3_methods} Details of the 12 clustering approaches considered.}
-\centering
-\resizebox{\textwidth}{!}{
-\begin{tabular}{lcrrr}
-    \toprule
-    Approaches & Dimension reduction & Representation & Distance measure & Clustering algorithms  \\ \midrule
-    TS-EUC-ME &  Yes & Time series  & Euclidean & $k$-medoids \\
-    ER-EUC-ME & Yes& In-sample error  & Euclidean & $k$-medoids \\
-    TSF-EUC-ME & Yes& Time series features  & Euclidean & $k$-medoids \\
-    ERF-EUC-ME & Yes& In-sample error features  & Euclidean & $k$-medoids \\
-    TS-EUC-HC & Yes& Time series  & Euclidean & hierarchical   \\ 
-    ER-EUC-HC & Yes& In-sample error  & Euclidean & hierarchical   \\ 
-    TSF-EUC-HC & Yes& Time series features  & Euclidean & hierarchical   \\ 
-    ERF-EUC-HC & Yes& In-sample error features  & Euclidean & hierarchical  \\
-    TS-DTW-ME & No& Time series  & DTW & $k$-medoids \\
-    TS-DTW-HC & No& In-sample error  & DTW & hierarchical  \\
-    ER-DTW-ME & No& Time series  & DTW & $k$-medoids \\
-    ER-DTW-HC & No& In-sample error  & DTW & hierarchical 
-     \\\bottomrule
-\end{tabular}}
+    \centering
+    \caption{\label{tab:features}Trend and seasonality features for the tourism  and mortality dataset.}
+    \begin{tabular}{lrr}\toprule
+        Feature & tourism &  mortality\\ \midrule
+        Strength of trend & 0.1559 & 0.7574 \\
+        Seasonality smoothing parameter & 0.0002 & 0.0202 \\ 
+        Seasonal auto-correlation coefficient &0.1814  &0.6523  \\ 
+ \bottomrule
+    \end{tabular}
 \end{table}
+%of Holt-Winters model
 
@@
 
-We investigate the impact of clustering on forecast reconciliation via a systematic comparison of the forecast accuracy based on different hierarchies. 
+%We investigate the impact of hierarchical on forecast reconciliation by comparing the forecast accuracy across different hierarchies. 
 %time series clustering techniques in Table \ref{tab:P3_methods}.
 %This comparison incorporates a diverse set of time series representations, distance measures, and clustering algorithms to provide a more thorough understanding of their impact on forecast performance.\\
-To evaluate the accuracy of reconciled forecasts based on a given hierarchical structure, we first calculate Root Mean Squared Scaled Error (RMSSE, \citealp{makridakisM5AccuracyCompetition2022}) for each series.
+%For a fair comparison, only bottom and top level forecasts are included evaluated. 
+%To evaluate the accuracy of reconciled forecasts,  
+%based on a given hierarchical structure, 
+To measure forecast accuracy, we first calculate the Root Mean Squared Scaled Error (RMSSE, \citealp{makridakisM5AccuracyCompetition2022}), for each series.
+Letting $\breve y_t$ be any forecast of $y_t$, we define RMSSE as
+
+\[
+RMSSE = \sqrt{\frac{\frac{1}{h}\displaystyle\sum_{t=T+1}^{T+h}(y_t-\breve y_{t})^2}{\frac{1}{T-12}\displaystyle\sum_{t=13}^T (y_t - y_{t-12})^2}} .
+\]
+
 RMSSE is symmetric, independent of the data scale, and thus suitable for evaluating hierarchical forecasts (\citealp{athanasopoulosEvaluationHierarchicalForecasts2023}).
-It is defined as follows:
-\[
-RMSSE = \sqrt{\frac{\frac{1}{h}\displaystyle\sum_{t=T+1}^{T+h}(y_t-\hat y_{t})^2}{\frac{1}{T-12}\displaystyle\sum_{t=13}^T (y_t - y_{t-12})^2}},
-\]
-where $\hat y_t$ is the reconciled forecast or base forecast of series $y_t$.
-It should be note that the denominator of our RMSSE measure is not exactly same as that in \cite{makridakisM5AccuracyCompetition2022}.
-We use the in-sample mean squared error of the seasonal naive method because the time series in our applications exhibit monthly seasonality.
-Then, we take average RMSSE of all forecasts in $\tilde{\boldsymbol{y}}_{T+h}$ as measure for the hierarchy.
-
-To rigorously validate our hypothesis, we utilize the rolling window strategy to evaluate the performance of different approaches on both datasets.
-We begin by producing and evaluating $12$-steps-ahead coherent forecasts using the first $96$ observations.
-The training set is then increased by one observation and new forecasts are obtained.
-The procedure is repeated until the last $12$ observations are used for evaluation.
-Finally, we can obtain $121$ RMSSE (January 2006 - January 2016) for the tourism dataset and $145$ RMSSE (January 2007 - January 2019) for the mortality dataset.
-Two approaches are utilized to compare and present the performance of various approaches on two datasets.
-The first one is to calculate average RMSSE across all evaluation windows, while the second involves Multiple Comparison with the Best (MCB) test (\citealp{koningM3CompetitionStatistical2005}), which computes the average ranks of different approaches across all evaluation windows and assess whether they are statistically different.
-
-\section{Natural hierarchy}\label{sec:natural}
-
-\subsection{Natural hierarchy vs two-level hierarchy}
-\label{subsec:n_vs_twolevel}
-In this subsection, we compare the performance of the natural hierarchy against the two-level hierarchy to address the first research question.
-We expect that natural hierarchy would demonstrate superior performance over the two-level hierarchy, as more time series are included in the reconciliation process.
-Following the evaluation procedure introduced in Section~\ref{subsec:evaluation}, Table~\ref{tab:P1} compares forecast accuracy of the natural hierarchy and the two-level hierarchy on tourism and mortality datasets.
-Average RMSSE is calculated across all evaluation windows.
-%in terms of average RMSSE across all evaluation windows. 
-The asterisk in table indicates significant difference according to MCB test.
-Table~\ref{tab:P1} shows that natural hierarchy significantly outperforms the two-level hierarchy on both datasets.
-It confirms our hypothesis that natural hierarchy improves forecast performance over a two-level hierarchy.
-
-\begin{table}[h!]
-    \centering
-    \caption{\label{tab:P1} Performance of natural and two-level hierarchies in terms of average RMSSE ($\times 10^{-2}$) across all evaluation windows on both datasets.
+It should be noted that the denominator of our RMSSE measure slightly differs from that used in \cite{makridakisM5AccuracyCompetition2022}; we replace the naive forecast, with the seasonal naive forecast since the time series in our applications exhibit monthly seasonality.
+As a single measure of accuracy, we take the average RMSSE across all series.
+Since we will be comparing hierarchies with different structures (thus different middle level series), this average only includes top and bottom level series, both of which are guaranteed to be present in all hierarchies.
+
+%To rigorously validate our hypothesis, we utilize the expanding window strategy to evaluate the performance of different approaches.
+For both datasets, starting with the first $96$ observations, we produce $12$-step-ahead forecasts.
+The training window is then increased by one observation and new forecasts are obtained.
+This procedure is repeated until the training window comprises all but the  last $12$ observations.
+Finally, we can obtain $121$ $12$-step-ahead forecasts (January 2006 - January 2016) for the tourism dataset and $145$ $12$-step-head forecasts (January 2007 - January 2019) for the mortality dataset.
+%Then we calculate the RMSSE for each of the expanding windows and take the average.
+%the reconciled forecasts.
+
+%Two approaches are utilized to summarise the overall performance across all evaluation windows.
+The first is to calculate average RMSSE across all evaluation windows.
+The second involves the Multiple Comparison with the Best (MCB) test (\citealp{koningM3CompetitionStatistical2005}), which computes the average ranks of different approaches across all evaluation windows and assess whether they are statistically different.
+
+We utilize the expanding window strategy to evaluate the performance of different approaches with a forecast horizon of 12 months (one year).
+For both datasets, the first window contains $96$ training observations.
+The training window is then increased by one observation and new 12-step ahead forecasts are obtained.
+This procedure is repeated until the training window comprises all but the  last $12$ observations.
+This results in $121$ $12$-step-ahead forecasts (January 2006 - January 2016) for the tourism dataset and $145$ $12$-step-head forecasts (January 2007 - January 2019) for the mortality dataset.
+%Then we calculate RMSSE for each of the reconciled forecasts.
+
+To assess whether differences in forecast performance are statistically significant, we employ the Multiple Comparison with the Best (MCB) test (\citealp{koningM3CompetitionStatistical2005}).
+This test is based on the average ranks of different approaches across all evaluation windows and controls for multiple comparisons.
+
+% \subsection{Natural hierarchy vs two-level hierarchy}
+% \label{subsec:n_vs_twolevel}
+% In this subsection, we compare the performance of natural hierarchy against the two-level hierarchy to address the first research question.
+We expect that the natural hierarchy would demonstrate superior performance over the two-level hierarchy, as more time series are included in the reconciliation process.
+% \begin{table}[h!]
+%     \centering
+%     \caption{\label{tab:P1} Performance of natural and two-level hierarchies in terms of average RMSSE across all evaluation windows on both datasets.
 Column-wise minimum values are displayed in bold.
 Asterisk (*) indicates significant difference according to MCB test.}
-    \begin{tabular}{lll}
-    \toprule
-        Method & tourism & mortality \\ \midrule
-        Natural & $\bold{69.13}^*$ & $\bold{75.01}^*$ \\ 
-        Two-level & $69.43$ & $75.28$ \\ \bottomrule
+%     \begin{tabular}{lll}
+%     \toprule
+%         Method & tourism & mortality \\ \midrule
+%         Base & $0.6945$ & $0.7530$ \\
+%         Two-level & $0.6943$ & $0.7528$ \\ 
+%         Natural & $\bold{0.6913}^*$ & $\bold{0.7501}^*$ \\ \bottomrule
+%     \end{tabular}
+
+% \end{table}
+
+% Following the evaluation procedure introduced in Section~\ref{subsec:evaluation}, Table~\ref{tab:P1} compares forecast accuracy of the natural hierarchy, the two-level hierarchy and base forecasts on tourism and mortality datasets.
+Average RMSSE is calculated across all evaluation windows.
+% %in terms of average RMSSE across all evaluation windows. 
+% The asterisk in table indicates significant difference according to MCB test.
+% It is shown that the natural hierarchy significantly outperforms the two-level hierarchy and base forecasts on both datasets.
+It confirms our hypothesis that natural hierarchy improves forecast performance over a two-level hierarchy.
+
+\subsection{Cluster hierarchies vs benchmarks}
+\label{subsec:cluster_vs_benchmarks}
+
+Table~\ref{tab:P3_rmsse} compares the accuracy of reconciled forecasts when using hierarchies obtained from the $12$ clustering-based hierarchies outlined in Table~\ref{tab:P3_methods}.
+The base forecasts, as well as the reconciled forecasts from the two-level hierarchy (only containing top- and bottom- level time series) and from the natural hierarchy, are included as benchmarks.
+%using the evaluation process described in Section~\ref{subsec:evaluation}.  
+The MCB test results are presented in Figure~\ref{fig:P3_mcb_benchmark}.
+
+\begin{table}[h!]
+    \centering
+\caption{\label{tab:P3_rmsse}Performance of cluster hierarchies and benchmark hierarchies in terms of average RMSSE across all evaluation windows on both datasets.
+Column-wise minimum values are displayed in bold.}
+\begin{tabular}{lrr}\toprule
+    Approach & tourism & mortality \\ \midrule
+    Base & 0.6945 & 0.7530 \\ 
+    Two-level & 0.6944 & 0.7528 \\ 
+    Natural & 0.6913 & 0.7501 \\ 
+    TS-EUC-ME & 0.6939 & 0.7528 \\ 
+    ER-EUC-ME & 0.6938 & 0.7530 \\ 
+    TSF-EUC-ME & 0.6938 & 0.7549 \\ 
+    ERF-EUC-ME & 0.6942 & 0.7532 \\ 
+    TS-EUC-HC & 0.6922 & 0.7540 \\ 
+    ER-EUC-HC & 0.6920 & 0.7507 \\ 
+    \textbf{TSF-EUC-HC} & \textbf{0.6909} & 0.7509 \\ 
+    ERF-EUC-HC & 0.6910 & 0.7501 \\ 
+    TS-DTW-ME & 0.6940 & 0.7528 \\ 
+    \textbf{TS-DTW-HC} & 0.6911 & \textbf{0.7496} \\ 
+    ER-DTW-ME & 0.6942 & 0.7531 \\ 
+    ER-DTW-HC & 0.6912 & 0.7532 \\ \bottomrule
 \end{tabular}
@@
 
-\subsection{Permutation of the natural hierarchy}
-\label{subsec:permutation}
-
-There are two potential contributors to the improvement in accuracy achieved by the natural hierarchy. First, natural hierarchy could tend to group time series with similar attributes together. 
-It is possible that these series share similar trend and seasonality pattern, similar features, strong correlations, or others, resulting in middle-level series with strong signals and easy to forecast.
-Thus, total and bottom-level series can borrow strength from these middle-level series during reconciliation. 
-We refer to this aspect as ``grouping''.
-Second, there are more series and more base forecasts to be combined during reconciliation, which leads to reduced uncertainty (\citealp{petropoulosExploringSourcesUncertainty2018a}) and improved reconciled forecasts.
-How the series are grouped is however irrelevant.
-We refer to this aspect as ``structure''.
-
-To systematically explore these two aspects, we introduce a permutation hierarchy construction method.
-Given a hierarchy tree, such as the natural hierarchy, the proposed approach constructs new hierarchies by randomly permuting the leaves.
-Recall that $\boldsymbol{A}$ is matrix consisting of $0$ and $1$ and represents the mapping from bottom-level time series to aggregated-level time series.
-In other words, it shuffles the columns of the constraint matrix $\boldsymbol{A}$ of the given hierarchy.
-This method yields random ``twin'' hierarchies with the same tree structure but different groupings.
-By generating forecasts using the twin hierarchies, we are able to eliminate the influence of grouping and focus specifically on structure. 
-If the random twin hierarchies significantly outperform the original counterpart, it suggests that structure holds greater importance than grouping, and vice versa.
-Figure~\ref{fig:aggcluster_random} shows an example of this approach, where the right hierarchy is a ``twin'' of the left hierarchy.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/aggcluster_random.pdf}
-
-    \[
-    \begin{bmatrix}
-    1 & 1 & 1 & 1\\
-    1 & 1 & 1 & 0 \\
-    1 & 1 & 0 & 0 \\
-    & I_4 & & 
-    \end{bmatrix}
-    \quad
-    \rightarrow
-    \quad
-    \begin{bmatrix}
-    1 & 1 & 1 & 1\\
-    0 & 1 & 1 & 1 \\
-    0 & 1 & 0 & 1 \\
-    & I_4 & & 
-    \end{bmatrix}
-    \]
-
-\caption{\label{fig:aggcluster_random}Examples of permutation of a given hierarchy.
-Right hierarchy is obtained by shuffling the leaves of left hierarchy.
-The upper part displays the hierarchy trees, and the lower part displays the corresponding summing matrices.}
-\end{figure}
-
-\subsection{Natural hierarchy versus its twins}
-\label{subsec:n_vs_pn}
-
-This subsection compares the performance of natural hierarchy and its random twins on mortality and tourism datasets.
-For each dataset, we first randomly generate $100$ permutations of the bottom-level series, which are applied to the natural hierarchy, producing $100$ twin hierarchies.
-Performances of natural hierarchy and its twins are compared using the evaluation process described in Section~\ref{subsec:evaluation}.
-
-Figures~\ref{fig:P2_tourism} and~\ref{fig:P2_mortality} display the MCB test results for the tourism dataset and mortality, respectively. 
-In order to save space, we only display the average rank labels for the natural hierarchy and $5$ twins.
-The grey zone indicates the confidence interval of the average rank of natural hierarchy.
-Any hierarchy whose confidence interval does not overlap with the grey zone is either significantly better or worse than the natural hierarchy.
-
-It is immediately clear that across both datasets, the natural hierarchy shows no significant outperformance compared to its random twins. 
-On the tourism dataset, it ranks the $5$th, performing indistinguishably from $32$ twins but significantly better than the remaining $68$.
-On the other hand, the performance difference is much smaller for the mortality dataset, where most twins perform insignificantly from the natural hierarchy.
-There are even three twin hierarchies significantly better than natural hierarchy.
-These results suggest that the natural hierarchy of tourism dataset may be ``smarter'' compared to that of mortality dataset.
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/hierarchy_rmsse/tourism/P2_natural_vs_pn_h12.pdf}
-    \caption{\label{fig:P2_tourism}Average ranks and 95\% confidence intervals for natural hierarchy and its $100$ twins on the tourism dataset.}
-\end{figure}
-
-\begin{figure}[!ht]
-    \centering    \includegraphics[width=0.8\textwidth]{figures/hierarchy_rmsse/mortality/P2_natural_vs_pn_h12.pdf}
-    \caption{\label{fig:P2_mortality}Average ranks and 95\% confidence intervals for natural hierarchy and its $100$ twins on the mortality dataset.}
-\end{figure}
-
-\section{Clustering-based hierarchy}
-\label{sec:clustering}
-
-Given that ``structure'' of natural hierarchy is the primary contributor to the performance improvement, we are interested in if better groupings can be constructed via clustering and become more critical than structure.
-We first review existing literature on clustering-based forecast reconciliation, and then describe the clustering techniques involved in our paper, followed by empirical results on mortality and tourism dataset.
-
-\subsection{Cluster hierarchies vs benchmarks}
-\label{subsec:P3_benchmark}
-Table~\ref{tab:P3_rmsse} shows the accuracy of benchmarks and $12$ cluster hierarchies in terms of average RMSSE across all evaluation windows using the evaluation process described in Section~\ref{subsec:evaluation}.
-The MCB test results are presented in Figure~\ref{fig:P3_mcb_benchmark}.
-On the tourism dataset, all cluster hierarchies outperform the two-level hierarchy, with ten showing significant improvement.
-While on the mortality dataset, only five cluster hierarchies surpass the two-level hierarchy in average RMSSE and eight do so in terms of average ranks. 
-However, none of these differences are statistically significant. 
-The inferiority of three $k$-medoids based cluster hierarchies highlights the importance of choosing an appropriate clustering technique.
-\begin{table}[h!]
-    \centering
-    \caption{\label{tab:P3_rmsse}Performance of cluster hierarchies and benchmark hierarchies in terms of average RMåSSE($\times 10^{-2}$) across all evaluation windows on both datasets.
-Column-wise minimum values are displayed in bold.}
-    \begin{tabular}{lll}
-    \toprule
-        Method & tourism & mortality \\ \midrule
-        Base & 69.452 & 75.295 \\ 
-        Two-level & 69.437 & 75.281 \\ 
-        Natural & 69.132 & 75.008 \\ 
-        TS-HC-EUC & 69.224 & 75.396 \\ 
-        TS-HC-DTW & 69.108 & \textbf{74.959} \\ 
-        TS-ME-EUC & 69.392 & 75.279 \\ 
-        TS-ME-DTW & 69.404 & 75.278 \\ 
-        TSF-HC-EUC & \textbf{69.086} & 75.091 \\ 
-        TSF-ME-EUC & 69.385 & 75.488 \\ 
-        ER-HC-EUC & 69.196 & 75.068 \\ 
-        ER-HC-DTW & 69.121 & 75.324 \\ 
-        ER-ME-EUC & 69.380 & 75.303 \\ 
-        ER-ME-DTW & 69.420 & 75.308 \\ 
-        ERF-HC-EUC & 69.099 & 75.010 \\ 
-        ERF-ME-EUC & 69.417 & 75.325 \\ \bottomrule
-    \end{tabular}
-\end{table}
-
-\begin{table}[!ht]
-    \centering
-    \caption{\label{tab:P3_features}Four trend and seasonality features for the tourism dataset and mortality dataset.}
-    \begin{tabular}{lll}\toprule
-        Features & mortality & tourism \\ \midrule
-        $\gamma$ parameter of Holt-Winters model & 0.0202 & 0.000165 \\ 
-        The first order seasonal ACF & 0.652 & 0.181 \\ 
-        Strength of trend & 0.757 & 0.156 \\ \bottomrule
-    \end{tabular}
-\end{table}
-
-The varying performance of cluster hierarchies across two datasets can be attributed to the unique characteristics of their bottom-level series.
-The tourism dataset, as shown in Figure~\ref{fig:tourism}, predominately contains volatile and noisy bottom-level time series with weak trend and seasonality.
-Creating new middle-level time series in this context helps elucidate the underlying pattern which can not be easily captured by bottom-level base forecasting models.
-On the other hand, bottom-level series in mortality dataset exhibit stronger trend and seasonality patterns, making creating middle-level series less beneficial.
-Table~\ref{tab:P3_features} summarises several features computed using available data in the last evaluation window, confirming the stronger seasonality and trend presence in the bottom level of mortality dataset.
-Note that the values are computed by averaging features for all bottom-level time series.
-The strength of trend is defined as
-\[
-\text{Strength of trend} = 1-\frac{\text{Var}(e_t)}{\text{Var}(f_t+e_t)},
-\]
-where $e_t$ and $f_t$ are residuals component and smoothed trend component obtained by STL decomposition of the time series (\citealp{tsfeatures}).
-
-\begin{table}[h!]
-    \centering
-    \caption{\label{tab:P3_number_series}Average number of middle-level time series for $k$-medoids-based, hierarchical-clustering-based and natural hierarchy in both datasets.}
-    \begin{tabular}{lll}
-    \toprule
-        Approach & mortality & tourism \\ \midrule
-     Natural & 21 & 250 \\ 
-        $k$-medoids clustering & 6.78 & 20.99 \\ 
-        Hierarchical clustering & 96 & 302 \\ \bottomrule
-    \end{tabular}
-\end{table}
-
-The hierarchies based on hierarchical clustering outperforms the hierarchies based on $k$-medoids when using the same representation and distance metric, e.g., ``TSF-HC-EUC'' outperforms ``TSF-ME-EUC''.
-This superiority is attributed to hierarchical clustering generating a greater number of middle-level time series than $k$-medoids, significantly enhancing the benefits of enriched structure.
-Table~\ref{tab:P3_number_series} summarises average number of middle-level series across all evaluation windows for natural, $k$-medoids-based and hierarchical clustering-based hierarchy. 
-Interestingly, the natural hierarchy shows competitive accuracy compared to hierarchical clustering-based hierarchies on both datasets, despite having fewer middle-level series.
-Regarding the superiority of any specific representation or distance metric, no consistent findings emerge.
-
-\begin{figure}
-    \centering
+We have the following observations from Table~\ref{tab:P3_rmsse} and Figure \ref{fig:P3_mcb_benchmark}.
+In terms of average RMSSE, for both datasets, the base forecasts provide the worst forecast performance.
+The natural hierarchies provide better results than the base forecasts and the two-level hierarchies, and comparable results with cluster hierarchies.
+In the case of the tourism dataset, all twelve clustering-based hierarchies outperform the simple two-level hierarchy.
+For ten out of twelve of these methods, the prediction intervals for the average ranks do not overlap with the two-level hierarchy, indicating significantly superior performance.
+For the mortality dataset, five cluster hierarchies surpass the two-level hierarchy in terms of average RMSSE.
+However,  not even the best clustering method is significantly more accurate than the two-level hierarchy based on the MCB test.
+%Across both datasets, the methods based on hierarchical clustering tend to outperform those based on $k$-medoids clustering, highlighting the importance of choosing an appropriate clustering technique.
+
+\begin{figure}[h!]
+    \centering
+    %\vspace{-0.1in}
     \includegraphics[width=0.45\textwidth]{figures/hierarchy_rmsse/tourism/P3_mcb_benchmarks_h12.pdf}
@@
 
+The varying performance of cluster hierarchies across two datasets can be attributed to the unique characteristics of their bottom-level series.
+The tourism dataset, as shown in Figure~\ref{fig:tourism}, predominately contains volatile and noisy bottom-level time series with weak trend and seasonality (see also in  Table~\ref{tab:features}).
+Arguably, creating new middle-level time series in this context helps elucidate the underlying pattern which can not be easily captured by bottom-level base forecasting models due to a low signal-to-noise ratio.
+On the other hand, the bottom-level series in mortality dataset exhibit stronger trend and seasonality patterns, meaning that the addition of middle-level series is less beneficial.
+
+\begin{table}[h!]
+    \centering
+    \caption{\label{tab:P3_number_series}Average number of middle-level time series resulting from $k$-medoids clustering, hierarchical clustering, and the natural hierarchy for both datasets.}
+    \begin{tabular}{lrr}
+    \toprule
+        Approach &  tourism& mortality \\ \midrule
+     Natural &250  & 21 \\ 
+        $k$-medoids clustering &  21&  7\\ 
+        Hierarchical clustering &302   & 96\\ \bottomrule
+    \end{tabular}
+\end{table}
+%20.99&  6.78
+
+We also observe that the hierarchies constructed via hierarchical clustering algorithms outperform the hierarchies based on $k$-medoids when using the same representation and distance metric.
+As an example, ``TSF-EUC-HC'' outperforms ``TSF-EUC-ME''.
+This superior performance can be attributed to hierarchical clustering generating a greater number of middle-level time series than $k$-medoids.
+%, significantly enhancing the benefits of enriched structure.
+Table~\ref{tab:P3_number_series} summarizes the average number of middle-level series across all evaluation windows for natural, $k$-medoids, and hierarchical clustering hierarchies. 
+Interestingly, the natural hierarchy shows competitive accuracy compared to hierarchical clustering methods on both datasets, despite having fewer middle-level series.
+However, it should be noted that natural hierarchies may not always exist.
+Regarding the superiority of any specific representation or distance metric, no consistent findings emerge.
+It shows that while it is possible to improve forecast accuracy via clustering, the performance of different clustering methods largely depends on the specific data in consideration.
+
+%\section{Investigating driving factors: grouping and structure}
+
+\section{Disentangling  grouping and structure}
+\label{sec:permutation}
+
+These results in Section~\ref{subsec:cluster_vs_benchmarks} raise the question of why hierarchies augmented with middle levels improve upon the two-level hierarchy.
+There are two possible explanations.
+On the one hand, it could be argued that by ``grouping'' together series with similar characteristics, certain signals are enhanced, leading to improved forecasting performance.
+%It is possible that by aggregating those series that share similar trends, seasonal patterns, or features, we enhance the signals in the middle-level series and improve their forecastability.
+Consequently, the total and bottom-level series can borrow strength from these middle-level series during the reconciliation process.
+%The second possible explanation assumes that it is the ``structure'' -- number of middle-level series, the depth of the hierarchy, the distribution of group sizes in the middle layer(s), or a combination of all these factors, that lead to the improved forecast accuracy.
+On the other hand, the exact grouping of times series is relatively inconsequential.
+Alternatively, it could be argued that the improved forecasting performance is a by-product of the ``structure'' of the hierarchy, \textit{i.e.} the number of middle-level series, the depth of the hierarchy, the distribution of group sizes in the middle layer(s), or a combination of all these factors.
+\subsection{Permutation hierarchy construction}
+\label{subsec:permutation}
+
+%there are more series and more base forecasts to be combined during reconciliation, which leads to reduced uncertainty (\citealp{petropoulosExploringSourcesUncertainty2018a}) and improved reconciled forecasts.
+
+To assess whether ``grouping'' or ``structure'' has relatively more importance, we consider a procedure based on permutation.
+For ease of exposition, we will describe this procedure for the natural hierarchy, although it is applied equally to hierarchies where middle level series are constructed using clustering algorithms.
+First, the structure of the natural hierarchy is kept fixed.
+A new ``twin'' hierarchy is constructed by randomly permuting the bottom level series\footnote{This can also be achieved by shuffling the columns of $\boldsymbol{C}$.}.
+An example is shown in Figure~\ref{fig:aggcluster_random}.
+
+%To further explore these two concepts, we introduce a method for constructing permutation hierarchies.
+%Given a hierarchy tree, such as the natural hierarchy, the proposed approach constructs new hierarchies by randomly permuting the leaf nodes of the hierarchy.
+Recall that $\boldsymbol{A}$ is a matrix consisting of $0$ and $1$, and represents the mapping from bottom-level time series to aggregated-level time series.
+The idea behind permuting a given hierarchy is to shuffle the columns of matrix $\boldsymbol{A}$ of the original hierarchy.
+This method creates random ``twin'' hierarchies with the same tree structure but different groupings rules.
+%By comparing forecast accuracy across permuted hierarchies, we are able to eliminate the influence of grouping and focus specifically on the structure of the hierarchy. 
+%If the random twin hierarchies significantly outperform the original counterpart, it suggests that structure holds greater importance than grouping, and vice versa.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/aggcluster_random.pdf}
+\caption{\label{fig:aggcluster_random}Examples of a given hierarchy and its ``twin''. }
+\end{figure}
+
+Suppose the forecast performance of the natural hierarchy can be explained by ``grouping''.
+In this case, the ``twin'' hierarchy, with a grouping formed at random, should perform significantly worse than the natural hierarchy.
+Alternatively, suppose the ``twin'' performs similarly to the natural hierarchy.
+In this case, the critical factor in improved forecast performance is the structure of the hierarchy, which is the same for both the natural hierarchy and its twin.
+To rule out the possibility that a random twin with exceptionally good (or bad) grouping is generated by chance, in all cases we consider 100 random twin hierarchies.
+
+%Figure~\ref{fig:aggcluster_random} shows an example of permutation hierarchy construction, where the right hand side hierarchy is obtained by shuffling the leaves of left hand side hierarchy.
+The upper part displays the hierarchy trees, and the lower part displays the corresponding summing matrices.
+%is a ``twin'' of the left hierarchy.\\
+%For the corresponding changes in matrix $\boldsymbol{A}$, we have the following results:
+
+ %   \[
+ %   \begin{bmatrix}
+ %   1 & 1 & 1 & 1\\
+ %   1 & 1 & 1 & 0 \\
+ %   1 & 1 & 0 & 0 \\
+ %   & I_4 & & 
+ %   \end{bmatrix}
+ %   \quad
+ %   \rightarrow
+ %   \quad
+ %   \begin{bmatrix}
+ %   1 & 1 & 1 & 1\\
+ %   0 & 1 & 1 & 1 \\
+ %   0 & 1 & 0 & 1 \\
+ %   & I_4 & & 
+ %   \end{bmatrix}
+ %   \]
+%\vspace{0.01in}
+
+\subsection{Natural hierarchy vs its twins}
+
+\label{subsec:n_vs_pn}
+
+%This subsection compares the performance of natural hierarchy and its random twins on mortality and tourism datasets.
+%For each dataset, we randomly generate $100$ permutations of the leaf nodes in the natural hierarchy, producing $100$ twin hierarchies.
+Performances of natural hierarchy and its twins are compared using the MCB test described in Section~\ref{subsec:evaluation}.
+
+Figure~\ref{fig:P2_tourism} compares the natural hierarchy to 100 twins using the MCB test.
+For brevity, we only display the average rank labels for the natural hierarchy and $5$ of its twin hierarchies\footnote{Note that ``82 - 73.74'' represents that the $82$nd permutation of the hierarchy which has an average rank of 73.74.
+The same convention applies to the labels of the $y$-axis for Figures \ref{fig:P3_tourism_c_vs_pc},  \ref{fig:simu_P3_benchmarks}, and \ref{fig:P4_a_vs_pa}.}.
+The figure is adjusted so that the gray band is around the 95\% confidence interval for the natural hierarchy rather than the best performing twin.
+Any hierarchies whose confidence interval overlaps with the gray zone is not significantly better or worse than the natural hierarchy.
+
+\begin{figure}[h!]
+    \centering
+\includegraphics[width=0.47\textwidth]{figures/hierarchy_rmsse/tourism/P2_natural_vs_pn_h12.pdf}
+    \centering    \includegraphics[width=0.47\textwidth]{figures/hierarchy_rmsse/mortality/P2_natural_vs_pn_h12.pdf}
+    \caption{\label{fig:P2_tourism}Average ranks and 95\% confidence intervals for natural hierarchy and its $100$ twins, tourism dataset (left) and mortality dataset(right).}
+\end{figure}
+
+It is clear that for both datasets, the natural hierarchy does not significantly outperform a large proportion of its random twins. 
+On the tourism dataset, the natural hierarchy ranks the $5$th.
+Its performance is statistically indistinguishable from 32 of its twins, but significantly better than the remaining 68.
+The difference in forecast performance for the natural hierarchy and its twins is even less pronounced for the mortality dataset.
+As shown in right panel of Figure~\ref{fig:P2_tourism}, the performance of the natural hierarchy is statistically indistinguishable from most of its twins and, there are three twin hierarchies significantly better than the natural hierarchy.
+%\textbf{These results suggest that the natural hierarchy of tourism dataset may be ``smarter'' compared to that of mortality dataset.}
+In both datasets, and particularly for the mortality dataset, we conclude that the ``structure'' of the natural hierarchy is the primary contributor to the improvement in forecast accuracy over the two-level hierarchy.
+
 \subsection{Cluster hierarchy vs its twins}
@@
 
-Results in Section~\ref{subsec:P3_benchmark} demonstrate that cluster hierarchy is able to improve forecast performance compared to natural hierarchy and two-level hierarchy. 
-We are also interested in how ``structure'' and ``grouping'' contribute to these improvements.
+The result in Section \ref{subsec:n_vs_pn} suggesting that ``structure'' is a more important contributor to ``grouping'' may arise since the grouping for the natural hierarchy is not selected in a data-driven fashion.
+%selected according to characteristics of the data, rather than in a data-driven fashion.}
+To assess whether clustering methods select a better ``grouping'', we compare the best-performing clustering-based hierarchies (TSF-EUC-HC and TS-DTW-HC for tourism and mortality, respectively) with their random twins.
+Recall that Section~\ref{subsec:cluster_vs_benchmarks} demonstrates that the clustering methods can outperform the natural hierarchy and two-level hierarchy.
+%We are also interested in how ``structure'' and ``grouping'' contribute to these improvements.
 Following the comparison in Section~\ref{subsec:n_vs_pn}, we compare the best performing cluster hierarchy with its $100$ random twins.
-Note that we choose the best performing approach according to average RMSSE shown in Table~\ref{tab:P3_rmsse}.
-
-The MCB test results for the tourism dataset and mortality dataset are shown in Figure~\ref{fig:P3_tourism_c_vs_pc} and Figure~\ref{fig:P3_mortality_c_vs_pc}, respectively.
+%Note that we choose the best performing approach according to average RMSSE shown in Table~\ref{tab:P3_rmsse}.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.47\textwidth]{figures/hierarchy_rmsse/tourism/P3_cluster_vs_pc_h12.pdf}
+    \includegraphics[width=0.47\textwidth]{figures/hierarchy_rmsse/mortality/P3_cluster_vs_pc_h12.pdf}
+    %best performing cluster hierarchy
+    \caption{\label{fig:P3_tourism_c_vs_pc}Average ranks and 95\% confidence intervals for best performing clustering approach and its $100$ twins, tourism dataset (left) and mortality dataset (right).}
+\end{figure}
+
+The MCB test results for the tourism dataset and mortality dataset are shown in Figure~\ref{fig:P3_tourism_c_vs_pc}.
 We observe that in both datasets, the best performing clustering approach does not yield significantly better results than its random twins. 
-Indicatively, the best cluster approach of mortality dataset ranks nearly in the middle of its random twins, indicating that structure instead of grouping dominates the performance. 
-However, the best cluster approach of tourism dataset ranks first and significantly outperforms $70$ of its random twins. This suggests a combination effect of grouping and structure.
-
-Overall, Table~\ref{tab:P3_rmsse}, Figures~\ref{fig:P3_tourism_c_vs_pc} and \ref{fig:P3_mortality_c_vs_pc} suggest that while it is possible to construct a ``smart'' hierarchical structure that improves forecast reconciliation performance, this possibility highly depends on the dataset characteristic and the time series cluster methods employed, making it a challenging objective to achieve.
+The best cluster approach of mortality dataset ranks nearly in the middle of its random twins, indicating that once again structure rather than grouping is the main driver of improvement in forecast accuracy.
+On the other hand, the best performing clustering method for the tourism data is statistically indistinguishable from 30 of its random twins, despite being the best in terms of the mean ranks.
+One can argue that for tourism dataset, a data-driven method for grouping time series plays a more prominent role in forecast improvement.
+%does appear to contribute the .
+%be a major contributor.
+This may be attributed to the noisier nature of bottom level tourism data, suggesting that similar weak signals are strengthened when aggregated.
+However, there is still roughly a 30\% chance that a random twin performs similarly, once again highlighting that structure is the main contributor to improved forecast performance.
+
+%Overall, Table~\ref{tab:P3_rmsse} and Figure~\ref{fig:P3_tourism_c_vs_pc} suggest that while it is possible to construct a ``smart'' hierarchical structure that improves forecast reconciliation performance, this possibility highly depends on the dataset characteristic and the time series cluster methods employed, making it a challenging objective to achieve.
 On the other hand, no matter the ``smarter'' hierarchy is construed or not, enriched structure contributes to the performance improvement.
 
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.7\textwidth]{figures/hierarchy_rmsse/tourism/P3_cluster_vs_pc_h12.pdf}
-    \caption{\label{fig:P3_tourism_c_vs_pc}Average ranks and 95\% confidence intervals for best performing cluster hierarchy TSF-HC-EUC and its $100$ twins on the tourism dataset.}
-\end{figure}
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.7\textwidth]{figures/hierarchy_rmsse/mortality/P3_cluster_vs_pc_h12.pdf}
-    \caption{\label{fig:P3_mortality_c_vs_pc}Average ranks and 95\% confidence intervals for best performing cluster hierarchy TS-HC-DTW and its $100$ twins on the mortality dataset.}
-\end{figure}
-
+%\section{Investigating driving factors: simulation cases}
 \section{Simulation study}
 \label{sec:simulation}
-
-The experiments in Section~\ref{sec:clustering} show the difficulty of constructing a smart hierarchy through clustering.
-However, it is possible that the clustering approaches we used are unable to detect clusters underlying the dataset.
-In this section, we simulate a scenario where ideal clusters can be detected and investigate how the two factors affect performance in this secenario.
+%The experiments in Section~\ref{sec:clustering} show the difficulty of constructing a smart hierarchy through clustering. 
+The main conclusion of Section~\ref{sec:permutation} is that hierarchies with more middle level series improve forecast accuracy due to structure rather than grouping.
+In so far as grouping may be a factor, this may be due to aggregating similar weak signals into stronger signals.
+To further test this conjecture, we consider a simulation study.
+Time series are generated that form clear clusters according to their trend and seasonality.
+These are then aggregated into middle level series, based on the known characteristics of each time series.
+The purpose of this is two-fold.
+First, in a simulated setting, the ``true'' clusters can be known, which guards against the risk that a given clustering algorithm fails to identify the correct clusters.
+Second, a simulation study guards against the shortcoming of any cluster analysis, namely that clusters will always be found even where they are not present.
+Such spurious clusters may explain the similar forecasting performance of cluster-based hierarchies with their randomly permuted twins.
+The simulation study thus sets up an ideal scenario, where grouping can potentially dominate structure as the factor explaining improved forecast performance.
+
+%The experiments in Section~\ref{subsec:cluster_vs_benchmarks} and Section~\ref{subsec:P3_c_vs_pc} illustrate the potential of using clustering-based methods to construct hierarchies for further improvement in forecast accuracy.
+
+%However, no evidence was found that clustering-based hierarchies are significantly better than the natural hierarchies.
+To avoid the concern that clusters found in the empirical datasets are spurious, we now consider a simulation study such that the `ground truth clusters' are known.
+%However, it is possible that the clustering approaches we used are unable to detect clusters underlying the dataset. 
+%In this section, we simulate a scenario where ideal clusters can be detected and investigate how the two factors affect performance in this scenario.
 
@@
 
-We assume the bottom-level time series follow an additive time series pattern with a data generating process described as follows:
+We construct $m=120$ bottom-level time series in an additive manner, each following a data generating process described as follows:
 \begin{equation}
@@
     \begin{aligned}
-    Y_t &= L_t + S_t + \xi_t \\
-    S_t &= S_{t~\text{mod}~s} \\
-    L_t &= \alpha t + \varepsilon_t,
+    Y_t &= L_t + S_t + \xi_t, \\
+        L_t &= \alpha t + \varepsilon_t,\\
+    S_t &= \begin{cases}\beta\quad\textrm{if $t-\delta$ is even}\\\gamma\quad\textrm{if $t-\delta$ is odd}\end{cases}\,,
     \end{aligned}
 \end{equation}
-where $L_t$ represents the trend term which increases or decreases over time at a slope of $\alpha$.
-The seasonal component, denoted by $S_t$, is repeating and deterministic with a cycle of length $s$.
-Both $\xi_t$ and $\varepsilon_t$ are white noises.
-
-Instead of employing cluster algorithms, we artificially craft $6$ ideal clusters by manipulating the directions of the trend components and patterns of the seasonal components.
-The configurations for each cluster can be found in Table~\ref{table:simu_params}.
-To simulate an increasing trend, we set the slope $\alpha$ to $0.001$, and for a decreasing trend, we set $\alpha$ to $-0.002$.
+where $L_t$ represents the trend term that increases or decreases over time with slope $\alpha$.
+We set $\alpha$ to 0.001, $-0.002$, and 0 so that exactly one third of the bottom level series have increasing, decreasing, and no trend respectively.
+The seasonal pattern is determined by $S_t$.
+It is deterministic with a seasonal period of 2, hitting a peak $\beta$ drawn uniformly from [2, 3], and a trough $\gamma$ drawn uniformly from [0, 1].
+The parameter $\delta$ controls whether a time series has its seasonal peak for odd values of $t$ or even values of $t$, which we refer to as ``odd'' and ``even'' seasonality respectively.
+We set $\delta=0$ (even seasonality) for exactly half of the series and $\delta=0$ (odd seasonality) for the other half of the series.
+Both $\xi_t$ and $\varepsilon_t$ are white noise with the variance of $\xi_t$ set to 0.25 and the variance of $\varepsilon_t$ set to $2.5\times 10^{-5}$ and $4.9\times 10^{-5}$ for increasing trend and decreasing trend, respectively.
+The combination of three different trends with two different patterns of seasonality leads to six clusters as described in Table~\ref{table:simu_params}.% For series with no trend, $L_t$ = 0, and there is no $\varepsilon_t$.
+%\todo{What about no trend?
+For no trend, $L_t$ = 0, there is no $\varepsilon_t$}.
+
+\begin{table}[h!]
+\caption{\label{table:simu_params}Parameter setting for all clusters in the simulation experiments.}
+\centering
+\begin{tabular}{lcccccc}\toprule
+& Cluster 1 & Cluster 2 & Cluster 3 & Cluster 4 & Cluster 5 & Cluster 6 \\ \midrule
+Trend & Increase & Increase & None & None & Decrease & Decrease \\
+Seasonality & Odd & Even & Odd & Even & Odd & Even  \\
+    \bottomrule
+\end{tabular}
+\end{table}
+
+For each series, we generate $144$ observations, with the last $12$ observations reserved for evaluation.
+Figure~\ref{fig:simu_emps} displays typical time series from each cluster, while Figure~\ref{fig:simu_pca} is a scatterplot of the first two principal components of the series.
+It is clear that the simulation design generates distinct clusters.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\textwidth]{figures/simu_example.pdf}
+\caption{\label{fig:simu_emps}Example time series for each cluster in the simulation experiments.}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.65\textwidth]{figures/simu_pca.pdf}
+    \caption{\label{fig:simu_pca}Visualization of the generated time series in the simulation experiments.}
+\end{figure}
+
+Various schemes for constructing middle level series can be considered and are summarized in Table~\ref{tab:7}.
+Middle level series can be constructed according to the value of the $\alpha$ parameter, leading to three clusters, or according to whether the series has a trend or no trend, leading to two clusters.
+In Table~\ref{tab:7}, these are referred to as Cluster-trend1 and Cluster-trend2 respectively.
+Middle level series can also be formed on the basis of seasonality (Cluster-season), leading to two clusters, or according to both trend and seasonality leading to six clusters (Cluster-trend-season).
+
+%To simulate an increasing trend, we set the slope $\alpha$ to $0.001$, and for a decreasing trend, we set $\alpha$ to $-0.002$.
 The variances of the associate white noise $\varepsilon_t$ are set to $2.5\times 10^{-5}$ and $4.9\times 10^{-5}$ for increasing trend and decreasing trend, respectively.
@@
 The variance of $\xi_t$ is set to $0.25$.
-We generate monthly time series data, ensuring that each cluster contains $20$ distinct time series.
-For each series, we generate $144$ observations, and the last $12$ observations are reserved for evaluation purpose.
-Figure~\ref{fig:simu_emps} displays example time series from each cluster, while Figure~\ref{fig:simu_pca} visualizes these generated time series based on the first two principal components extracted from principal component analysis of the series.
-
-\begin{table}
-\caption{\label{table:simu_params}Parameter setting for all clusters in the simulation experiments.}
-\centering
-\begin{tabular}{lcccccc}\toprule
-& Cluster 1 & Cluster 2 & Cluster 3 & Cluster 4 & Cluster 5 & Cluster 6 \\
-Trend & Increase & Increase & None & None & Decrease & Decrease \\
-Seasonality & Odd & Even & Odd & Even & Odd & Even  \\
-    \bottomrule
+
+%We generate $120$ bottom level series, ensuring that each cluster contains $20$ distinct time series.
+
+%\subsection{Hierarchy construction}
+
+%We consider a two-level hierarchy with a total of $120$ bottom-level series and a single aggregated series.
+In addition, we examine four cluster hierarchies.
+Note that we consider multiple cluster hierarchies in order to reflect the real-world scenario where a variety of clustering techniques may be employed.
+The first cluster hierarchy, ``Cluster-predefined'', forms six middle-level series according to the predefined clusters.
+We then merge clusters with the same trend pattern, resulting in the cluster hierarchy with three clusters, denoted by ``Cluster-trend1''.
+Similarly, we construct cluster hierarchies ``Cluster-trend2'' and ``Cluster-season'' based on the presence of the trend term and seasonal peak positioning, resulting in $2$ and $3$ middle-level series, respectively.
+%Table~\ref{tab:7} summarizes the five approaches.
+
+\begin{table}[h!]
+    \centering
+    \caption{\label{tab:simu_methods}Four clustering approaches used in the simulation experiments.}
+    \begin{tabular}{ll}\toprule
+        Approach & Description \\ \midrule
+%        Two-level &  A  two-level hierarchy consisting of only bottom and top levels. \\ 
+        Cluster-trend-season & Hierarchy based on trend and seasonal pattern. \\
+        Cluster-trend1 &  Hierarchy based on trend (positive/negative/none). \\
+        Cluster-trend2 & Hierarchy based on trend/no trend. \\
+        Cluster-season & Hierarchy based on seasonal pattern (odd/even). \\\bottomrule
+    \end{tabular}
+    \label{tab:7}
+\end{table}
+
+\subsection{Results}
+\label{sec:simu_res}
+
+We replicate the simulation $500$ times and follow the evaluation procedure introduced in Section~\ref{subsec:evaluation}.
+Table~\ref{tab:simu_P3} reports the average RMSSE across all hierarchies, and
+Figure~\ref{fig:simu_P3_benchmarks} presents the MCB test results.
+The results reveal that most approaches perform better than the base forecasts and the two-level hierarchy.
+This outcome indicates that hierarchy construction generally improves forecast reconciliation performance, corroborating our findings reported in Section~\ref{subsec:cluster_vs_benchmarks}.
+Clustering only on the basis of trend yields the best performance, however all clustering schemes are statistically indistinguishable from one another.
+
+\begin{table}[h!]
+    \centering
+    \caption{\label{tab:simu_P3}Performance of cluster hierarchies and benchmark hierarchies in terms of average RMSSE in simulation. Column-wise minimum values are displayed in bold.}
+    \begin{tabular}{lc}\toprule
+        Approach & Average RMSSE \\ \midrule
+        Base & 0.7764 \\ 
+        Two-level & 0.5971 \\ 
+        Cluster-trend-season & 0.5963 \\ 
+        Cluster-trend1 & \textbf{0.5962} \\ 
+        Cluster-trend2 & 0.5965 \\ 
+        Cluster-season & 0.5965 \\ \bottomrule
     \end{tabular}
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/simu_example.pdf}
-\caption{\label{fig:simu_emps}Example time series for each cluster in the simulation experiments.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{figures/simu_pca.pdf}
-    \caption{\label{fig:simu_pca}Visualization of the generated time series in the simulation experiments.}
-\end{figure}
-
-\subsection{Hierarchies construction}
-
-We consider a two-level hierarchy with a total of $120$ bottom-level series and a single aggregated series, labelled as ``Two-level''.
-In addition, we examine four cluster hierarchies.
-Note that we consider multiple cluster hierarchies in order to reflect the real-world scenario where a variety of clustering techniques may be employed.
-The first cluster hierarchy, ``Cluster'', forms six middle-level series according to the predefined ideal clusters.
-We then merge clusters with the same trend pattern, resulting in the cluster hierarchy with three clusters, denoted by ``Cluster-trend1''.
-Similarly, we construct cluster hierarchies ``Cluster-trend2'' and ``Cluster-season'' based on the presence of the trend term and seasonal peak positioning, resulting in $2$ and $3$ middle-level series, respectively.
-Table~\ref{table:simu_params} summarizes the five approaches.
-
-\begin{table}[]
-    \centering
-    \begin{tabular}{ll}\toprule
-        Approaches & Description \\ \midrule
-        Two-level &  The original two-level hierarchy. \\ 
-        Cluster & Cluster hierarchy based on ideal clustering. \\
-        Cluster-trend1 & Cluster hierarchy based on trend patterns. \\
-        Cluster-trend2 & Cluster hierarchy based on existence of trend component. \\
-        Cluster-season & Cluster hierarchy based on seasonality patterns. \\\bottomrule
-    \end{tabular}
-    \caption{\label{tab:simu_methods}Five approaches used in the simulation experiments.}
-\end{table}
-
-\subsection{Results}
-\label{sec:simu_res}
-
-We repeat the simulation $500$ times and evaluate the results on these $500$ hierarchies following the evaluation procedure introduced in Section~\ref{subsec:evaluation}.
-Table~\ref{tab:simu_P3} reports the average RMSSE across all hierarchies, and
-Figure~\ref{fig:simu_P3_benchmarks} presents the MCB test results.
-The results reveal that most approaches perform better than the base forecasts and the original two-level hierarchy.
-This outcome indicates that hierarchy construction generally improves forecast reconciliation performance, corroborating our findings reported in Section~\ref{sec:clustering}.
-Interestingly, the ideal cluster ``Cluter'' achieves second rank, indicating that optimal clustering does not necessarily translate into the best forecast reconciliation performance.
-
-Furthermore, we are interested in structure or grouping contributes more to the performance improvements.
-Again, following the random hierarchy construction procedure described in Section~\ref{subsec:permutation}, we compare the ideal cluster with its $100$ random twins.
+\begin{figure}[h!]
+    \centering
+    \vspace{0.1in}\includegraphics[width=0.7\textwidth]{figures/hierarchy_rmsse/simulation/P3_mcb.pdf}
+   \vspace{-0.1in}
+\caption{\label{fig:simu_P3_benchmarks}Average ranks and 95\% confidence intervals for four cluster hierarchies and two benchmarks in simulation based on MCB test.}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+\includegraphics[width=0.8\textwidth]{figures/hierarchy_rmsse/simulation/P3_c_vs_pc.pdf}
+    \vspace{-0.1in}
+    \caption{Average ranks and 95\% confidence intervals for four the ideal hierarchy and its 100 random twins in simulation based on MCB test.}
+%    \vspace{-0.2in}
+    \label{fig:simu_P3_c_vs_pc}
+\end{figure}
+
+Having constructed clearly demarcated clusters, we now compare the six cluster hierarchy against 100 of its random twins.
 The MCB test result is shown in Figure~\ref{fig:simu_P3_c_vs_pc}.
-Even if the optimal cluster can be obtained in this simulation, the results are similar to what we found on the mortality dataset, showing that  structure plays a greater role in improving the forecast reconciliation performance.
-It enforces our belief that the reason of clustering improving performance depends on the dataset characteristics.
-
-\begin{table}[!ht]
-    \centering
-    \caption{\label{tab:simu_P3}Performance of cluster hierarchies and benchmark hierarchies in terms of average RMSSE($\times 10^{-2}$) in simulation.
-Column-wise minimum values are displayed in bold.}
-    \begin{tabular}{ll}\toprule
-        Method & RMSSE \\ \midrule
-        Base & 77.64 \\ 
-        Two-level & 59.71 \\ 
-        Cluster & 59.63 \\ 
-        Cluster-trend1 & \textbf{59.62} \\ 
-        Cluster-trend2 & 59.65 \\ 
-        Cluster-season & 59.65 \\ \bottomrule
+Using the known clusters yields a performance somewhere in the middle of the 100 twins that is statistically indistinguishable from nearly all twins.
+%\todo{is it really all of them?
+Yes.
+In the MCB plot, all elements indistinguishable from the target element (here the Cluster-predefined) have red points}.
+This arguably provides the most compelling evidence so far on whether improvements in forecast accuracy can be attributed to structure or grouping.
+It is the process of forming any middle-level series that is more important than aggregating similar time series.
+This result holds not only for our empirical studies, but also for an example specifically designed to have distinct, known clusters as illustrated in this section.
+
+  %\vspace{-0.4in}
+
+%\section{Improving performance via forecast combination}
+\section{Forecast combination}
+\label{sec:combination}
+
+The results in Sections~\ref{sec:cluster} and~\ref{sec:simulation} highlight the potential of improving forecast reconciliation performance through the construction of new middle levels series using time series clustering.
+The selection of the best performing combination of time series representation, distance measure, and clustering algorithm remains an open question.
+Since the best cluster-based method will heavily depend on the characteristics of the data, %and forecasting method used to obtain bottom level series,
+we consider averaging forecasts across different hierarchies, as an alternative to hierarchy selection.
+This is supported by substantial research and empirical evidence in favor of forecast combination over selection (see \textit{e.g.}, \citealp{elliottForecastingEconomicsFinance2016}).
+Specifically, the reconciled forecasts from multiple hierarchies are combined using equal weights (\citealp{wangForecastCombinations50year2022}), \textit{i.e.},
+\[
+  \tilde{\boldsymbol{y}}_{T+h}^{\text{comb}} = \frac{1}{l} \sum_{j=1}^l \tilde{\boldsymbol{y}}_{T+h}^j.
+\] 
+We note that this average can only be carried out using series that are common to all hierarchies, in our case, the top and bottom levels.
+In this case, since all elements of the average are coherent, any linear combination of these forecasts will also be coherent.
+
+%While it is possible to employ more complex methods to determine ``optimal'' weights, we adhere to equally-weighted combination due to its simplicity and well-known efficacy (\citealp{wangForecastCombinations50year2022}).
+
+%Following the evaluation procedure introduced in Section~\ref{subsec:evaluation,
+
+\begin{table}
+    \centering
+    \caption{\label{tab:P4_RMSSE}Average RMSSE across six approaches. Column-wise minimum values are displayed in bold.}
+    \begin{tabular}{lcc}\toprule
+       Approach & tourism & mortality \\ \midrule
+        Base & 0.6945 & 0.7530 \\ 
+        Two-level & 0.6944 & 0.7528 \\ 
+        Natural & 0.6913 & 0.7501 \\ 
+        TS-DTW-HC & 0.6911 & 0.7496 \\ 
+        TSF-EUC-HC & 0.6909 & 0.7509 \\ 
+        Combination & \textbf{0.6902} & \textbf{0.7423} \\ \bottomrule
     \end{tabular}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{figures/hierarchy_rmsse/simulation/P3_mcb.pdf}
-    \caption{\label{fig:simu_P3_benchmarks}Average ranks and 95\% confidence intervals for four cluster hierarchies and two benchmarks in simulation based on MCB test.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/hierarchy_rmsse/simulation/P3_c_vs_pc.pdf}
-    \caption{Average ranks and 95\% confidence intervals for four the ideal hierarchy and its 100 random twins in simulation based on MCB test.}
-    \label{fig:simu_P3_c_vs_pc}
-\end{figure}
-
-\section{Combination hierarchies}
-\label{sec:combination}
-
-The results in Section~\ref{sec:clustering} and Section~\ref{sec:simulation} highlights the possibility of improving forecast reconciliation performance by constructing new middle levels through time series clustering.
-However, this possibility highly depends on the dataset characteristics and time series approaches used.
-Therefore, the classical problem of selecting the optimal clustering approaches arises.
-Considering the substantial research and empirical evidences in favor of forecast combination over selection (see e.g., \citealp{elliottForecastingEconomicsFinance2016}), we suggest employing combination of forecasts from multiple cluster hierarchies to avoid the uncertainty associated with identifying a best cluster approach.
-Specifically, the reconciled forecasts from multiple hierarchies are combined using equal weights, i.e.,
-\[
-  \tilde{\boldsymbol{y}}_{T+h}^{\text{comb}} = \frac{1}{l} \sum_{j=1}^l \tilde{\boldsymbol{y}}_{T+h}^j.
-\] Note that the resulted forecasts are still coherent. 
-While it is possible to employ more complex methods to determine ``optimal'' weights, we adhere to equally-weighted combination due to its simplicity and well-known efficacy (\citealp{wangForecastCombinations50year2022}).
-
-Following the evaluation procedure introduced in Section~\ref{subsec:evaluation},
+% \clearpage
+
 Table~\ref{tab:P4_RMSSE} presents the accuracy in terms of average RMSSE across all evaluation windows for both datasets.
-Note that we only present accuracies of three benchmarks, the best cluster hierarchies and the combination hierarchy to save space.
+Note that for brevity we only present results for three benchmarks (base, two-level, and natural), the best cluster hierarchy (TS-DTW-HC for the mortality data and TSF-EUC-HC for the tourism data) and the combination hierarchy.
 The MCB test results are shown in Figure~\ref{fig:P4_bench_mcb}.
-As expected, we observe that on both datasets, forecast combination future improves forecast performance compared to the best performing cluster hierarchy. 
-The improvement on the mortality dataset is more pronounced, with forecast combination significantly outperforms all other approaches.
-\begin{table}[!ht]
-    \centering
-    \caption{\label{tab:P4_RMSSE}Performance in terms of average RMSSE($\times 10^{-2}$) on both datasets. Column-wise minimum values are displayed in bold.}
-    \begin{tabular}{lcc}\toprule
-        Method & tourism & mortality \\ \midrule
-        Base & 69.452 & 75.295 \\ 
-        Two-level & 69.437 & 75.281 \\ 
-        Natural & 69.132 & 75.008 \\ 
-        TS-HC-DTW & 69.108 & 74.959 \\ 
-        TSF-HC-EUC & 69.086 & 75.091 \\ 
-        Combination & \textbf{69.019} & \textbf{74.234} \\ \bottomrule
-    \end{tabular}
-\end{table}
-
-\begin{figure}[!h]
-    \centering
+As expected, we observe that on both datasets, forecast combination improves forecast performance compared to any single hierarchy. 
+The improvement on the mortality dataset is more pronounced, with forecast combination significantly outperforming all other approaches.
+
+\begin{figure}[h!]
+    \centering
+    %\vspace{-0.2in}
     \includegraphics[width=0.45\textwidth]{figures/hierarchy_rmsse/tourism/P4_benchmarks_h12.pdf}
@@
 
-We are also interested in if combination of cluster hierarchies significantly differ from its random twins.
-We propose to extend the permutation hierarchy generation approach introduced in Section~\ref{subsec:permutation} to combination hierarchy.
-First, we apply the same permutations of bottom-level series used in Section~\ref{subsec:P3_c_vs_pc} to all other cluster hierarchies.
-Then for each of the $100$ permutations, the twelve reconciled forecasts obtained from corresponding random twins of cluster hierarchies are combined through equally-weighted combination, resulting $100$ random twins of combination hierarchy.
-The results of MCB test for combination hierarchy and its $100$ random twins on the mortality dataset are presented in Figure~\ref{fig:P4_a_vs_pa}.
-It is not surprising that the combination hierarchy ranks $100$th, given that even the best-performing cluster hierarchy failed to demonstrate absolute superiority.
-This comparison is conducted solely on the mortality dataset, as computing random twins for all cluster hierarchies on the tourism dataset is time-consuming.
-\begin{figure}[h!]
-\vspace{-0.1in}
-    \centering
-    \includegraphics[width=0.75\textwidth]{figures/hierarchy_rmsse/mortality/P4_average_vs_pa_h12.pdf}
-    \caption{\label{fig:P4_a_vs_pa} Average ranks and 95\% confidence intervals for combination of twelve cluster hierarchies and its $100$ random twins on mortality dataset based on MCB test.}
-\end{figure}
-
-\clearpage 
-\newpage
+We also consider how the question of grouping versus structure plays out in the case of combinations by extending the permutation approach introduced in Section~\ref{subsec:permutation}.
+We do so by first permuting the labels of the bottom level series while keeping the hierarchy fixed.
+The same permutation is used for all hierarchies in a combination.
+This is then repeated 100 times, yielding 100 ``twins'' of the combination forecast.
+%First, we apply the same permutations of bottom-level series used in Section~\ref{subsec:P3_c_vs_pc} to all other cluster hierarchies.
+%Then for each of the $100$ permutations, the twelve reconciled forecasts obtained from corresponding random twins of cluster hierarchies are combined through equally-weighted combination, resulting $100$ random twins of combination hierarchy.
+
+The results of MCB test for the combination and its $100$ random twins are presented in Figure~\ref{fig:P4_a_vs_pa} for the mortality dataset\footnote{Note that this experiment has been conducted only on the mortality dataset, as computing random twins for all cluster hierarchies on the tourism dataset is too computationally expensive.}.
+Similar to the results in Section~\ref{sec:permutation}, we find evidence that a large number of random twins do not perform significantly worse than an approach based on clustering.
+In fact, out of the 100 twins, the combination only performs better than a single twin.
+This provides the last piece of compelling evidence that the grouping of similar time series, contributes less to improved forecast performance than structure.
+
+\begin{figure}[h!]
+%\vspace{-0.15in}
+    \centering
+    \includegraphics[width=0.6\textwidth]{figures/hierarchy_rmsse/mortality/P4_average_vs_pa_h12.pdf}
+    \vspace{-0.1in}\caption{\label{fig:P4_a_vs_pa} Average ranks and 95\% confidence intervals for combination of twelve cluster hierarchies and its $100$ random twins on mortality dataset based on MCB test.}
+\end{figure}
+%\clearpage 
+%\newpage
 
@@
 
-\section{Discussion and Conclusion}
+\section{Conclusion}
 \label{sec:conclusion}
 
-This paper extends the current body of research on clustering-based forecast reconciliation by introducing a general hierarchical forecasting framework, incorporating three distinct approaches: cluster hierarchies, random hierarchies, and combination hierarchies.
-In contrast to the focused scope of previous studies, our approach to cluster hierarchies involves a broader exploration.
-We examine four time series representations, employ two distance measures, and utilize two clustering algorithms.
-This comprehensive method differs significantly from the existing literature, which typically concentrates on specific clustering implementations.
-We also introduce two innovative random hierarchy construction methods to investigate what drives the performance enhancements in cluster hierarchies.
+This paper thoroughly investigates the issue of constructing hierarchies for forecast reconciliation, with the goal of improving forecast accuracy.
+This issue is particularly important in the absence of a predefined natural hierarchy.
+Rather than focus on a single clustering algorithm, we consider a more general framework, incorporating three distinct approaches: cluster hierarchies, permutation hierarchies, and combination hierarchies.
+Unsurprisingly, no single method emerges as superior for all datasets, although hierarchical clustering, which by construction leads to a larger number of clusters, tends to outperform $k$-mediods clustering.
+
+This naturally begs the question, of why adding more middle level series can improve forecast performance.
+We devise a method that keeps the hierarchy fixed while permuting the bottom level series, yielding ``twin'' hierarchies.
+The bottom-level series that aggregate to a single middle level series are thus chosen at random.
+Across different datasets and settings, an overwhelmingly large number of twins, perform not significantly worse, or even better, than a hierarchy selected using clustering.
+This suggests that the improved forecast performance arises not from grouping similar times series together, but rather from features related to the structure of the hierarchy, \textit{e.g.} the larger number of middle level series.
+We find similar results from a simulation study where clusters are predefined.
+%, as well as for combinations of hierarchies.
+%This rules out the possibility that our empirical results arise due to spurious clusters or the poor performance of a single clustering method.
+This eliminates the possibility that our empirical results arise due to  spurious clusters or the inadequate performance of a single clustering method.
+%Our empirical and simulation studies provided answers to four important research questions.
+Firstly, we find that the natural hierarchy improves forecast performance compared to both the two-level hierarchy and base forecast.
+%Secondly, cluster hierarchies have the potential to further improve  performance, despite the best-performing approach varying depending on specific datasets.
+%These results align with findings in previous literature on this topic (\citealp{liForecastReconciliationApproach2019, pangHierarchicalElectricityTime2018, pangHierarchicalElectricityTime2022, matteraImprovingOutofSampleForecasts2023}).
+%However, in contrast to the focused scope of previous studies, we involve a broader exploration, including four time series representations, two distance measures, and two clustering algorithms.
+
+%To investigate the driving factors behind performance improvements in natural hierarchy and cluster hierarchies, specifically ``strcuture'' and ``groupings'', we propose an innovative permutation approach that constructs random ``twin'' hierarchies.
+%Comparing natural or cluster hierarchies with their twins allows us to disentangle the impact of ``groupings''.
+The results from two empirical datasets and simulations indicate that while certain cluster hierarchies further improve performance, they do not demonstrate a definitive priority over their twins, particularly in the case of the mortality dataset.
+Therefore, ``structure'', such as number of middle-level time series and depth of the hierarchy, usually has a more substantial influence on forecast performance.
+Our main practical recommendation is to use multiple clustering methods and combine forecasts across these methods using equal weights combination. 
+This mitigates the uncertainty of selecting the best clustering approach and is shown to significantly outperform all benchmarks across both datasets that we consider.
+%One could also extend this idea to averaging over random twins, although we note that any averaging approach incurs a computation cost in needing to obtain base forecasts for more middle level series.
+One could also extend this idea to averaging over random twins.
+However, it's worth noting that any averaging approach incurs a computation cost as it requires obtaining base forecasts for additional middle-level series.
+% We also introduce an innovative random hierarchy construction method to investigate what drives the performance enhancements in cluster hierarchies.
 These random hierarchies help isolate the effect of clustering, allowing us to focus on the benefits derived from the structure alone.
-Furthermore, we propose combination hierarchies to mitigate uncertainties inherent in random hierarchies.
-
-Our simulation study is constructed around two scenarios, each based on different base forecasting models.
+% Furthermore, we propose combination hierarchies to mitigate uncertainties inherent in random hierarchies.
+
+% Our simulation study is constructed around two scenarios, each based on different base forecasting models.
 The first scenario highlights the value of the structure, evident in the high-ranking performance of random combination hierarchies.
@@
 
-Empirical studies on two datasets support our simulation findings.
+% Empirical studies on two datasets support our simulation findings.
 In the tourism dataset, the inferior base forecasts at the bottom level lead to all cluster hierarchies surpassing the original hierarchy, with four outperforming the combination of random hierarchies, which is used to demonstrate the impact of enriched structure.
@@
 Future research based on our study could proceed in several promising directions.
-Firstly, our experiments were concentrated on total-level and bottom-level series.
+%Firstly, our experiments were concentrated on total-level and bottom-level series.
 In practical applications, it might be necessary to include specific middle levels or evaluate the entire hierarchy.
 This could lead to the exploration of different hierarchy approaches, such as clustering middle-level series rather than bottom-level ones.
-Although we used equally-weighted combinations in this study, there's potential for applying more sophisticated methods to improve performance.
-The extensive literature on forecast combination, including advanced methods for calculating weights, offers numerous possibilities for enhancement (refer to \citealp{wangForecastCombinations50year2022} for an in-depth review).
-
+For example, while we used equally-weighted combinations in this study, there is  potential to apply more sophisticated forecast combination methods to improve performance.
+The extensive literature on forecast combination, including advanced methods for calculating weights, could also be considered (refer to \citealp{wangForecastCombinations50year2022} for an in-depth review).
 % In Section~\ref{sec:combination}, we discuss the implications of combining multiple hierarchical structures on the uncertainty in estimating the covariance matrix of base forecast errors.
@@
 In this context, innovative solutions like the regularized forecast reconciliation approach, as proposed by \cite{bentaiebRegularizedRegressionHierarchical2019a}, and alternative estimators of the covariance matrix, such as those suggested by \cite{pritulargaStochasticCoherencyForecast2021} could be highly beneficial.
-
-In both our simulation and empirical studies, the combination of random hierarchies displayed competitive results compared to clustering-based methods.
+% In both our simulation and empirical studies, the combination of random hierarchies displayed competitive results compared to clustering-based methods.
 However, the efficacy of this approach in scenarios with an extremely large number of bottom-level series remains uncertain.
@@
 It's plausible to enhance forecastability at the middle level by creating series through general linear combinations.
-
-Finally, our study was centered around point forecast reconciliation and cross-sectional hierarchy.
+%Finally, our study was centered around point forecast reconciliation and cross-sectional hierarchy.
 However, the field of probabilistic forecast reconciliation has recently gained significant interest, as evidenced by research like \cite{panagiotelisProbabilisticForecastReconciliation2023} and \cite{jeonProbabilisticForecastReconciliation2019}.
@@
 This approach could provide deeper insights and more robust forecast reconciliation methods, particularly in scenarios where uncertainty and variability are significant factors.
-Another promising direction for extending our methodologies lies in exploring temporal (\citealp{athanasopoulosForecastingTemporalHierarchies2017}) and cross-temporal hierarchies (\citealp{girolimettoCrosstemporalProbabilisticForecast2023a}).
+Also, our results are based on cross-sectional data, this could be extended to explore temporal (\citealp{athanasopoulosForecastingTemporalHierarchies2017}) and cross-temporal hierarchies (\citealp{girolimettoCrosstemporalProbabilisticForecast2023a}).
+Finally, more work could be carried out to understand whether some middle levels contribute more to forecast accuracy than others, and accordingly ``pruning'' the less useful middle level series.
 

### 2024-04-15 manuscript/coverletter.tex
submit to IJF

\documentclass[a4paper,11pt]{article}

%%%%%%%%%%%%%%%%%% Non-Latin Languages Support %%%%%%%%%%%%%%%%%%%%%%%
% \usepackage[adobefonts,nocap]{ctex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[twoside]{geometry}
\geometry{verbose,tmargin=2.0cm,bmargin=5.5cm,lmargin=2.0cm,rmargin=2.0cm}
% \usepackage[raggedright]{titlesec}

\usepackage{graphicx}
\usepackage[unicode=true]{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue}

\usepackage{multirow}

%% Line spacing
\usepackage{setspace}
\onehalfspace

%% Fancy symbols
\usepackage{marvosym}

%% Fonts
\usepackage[ugaramond]{mathdesign}
% \usepackage{inconsolata}

%% Fancy header and footer
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}

\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.4pt}

\fancyfoot[L]{ \texttt{School of Economics and Management\\ Beihang University\\ 37 Xueyuan Road, Beijing, 100191, China}}

%\fancyfoot[C]{\vspace{2.0cm} \thepage~/~\pageref{LastPage}}

\fancyfoot[R]{\texttt{\url{https://sem.buaa.edu.cn}\\ \url{https://www.buaa.edu.cn}\\Tel: +86 10 82317839}}

\begin{document} \thispagestyle{fancy}

\begin{tabular}{ll}
  \multirow{7}{*}{\hspace{4cm}\hspace{0.18\textwidth}}
  & Bohan Zhang \\
  & School of Economics and Management \\
  & Beihang University\\
  & 100191 Beijing, China\\
  & \Email~\texttt{zhangbohan@buaa.edu.cn} \\
  & \Pointinghand~\texttt{\url{https://bohan-zhang.com/}}\\
  & \\
  & \today
\end{tabular}

\vspace{1.5cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Dear Editor,
\vspace{1cm}

Please find the attached manuscript entitled ``Constructing hierarchical time series through clustering: Is there an optimal way for forecasting?'' by Bohan Zhang, Anastasios Panagiotelis, and Han Li, which we wish to submit for publication as a regular article in \emph{International Journal of Forecasting}.  No conflict of interest exists in the submission of this manuscript, and the manuscript is approved by all authors for publication. We confirm that the work is original research that has not been published previously and is not under consideration for publication elsewhere.

In this paper, we extend existing work that uses time series clustering to construct hierarchies, with the goal of improving forecast accuracy, in three ways. First, we investigate multiple approaches to clustering, and find that cluster-based hierarchies lead to improvements in forecast accuracy relative to two-level hierarchies. Second, we devise an approach based on random permutation of hierarchies. In doing so, we find that improvements in forecast accuracy that accrue from using clustering do not arise from grouping together similar series but from the structure of the hierarchy. Third, we propose an approach based on averaging forecasts across hierarchies constructed using different clustering methods, that is shown to outperform any single clustering method. All analysis is carried out on two benchmark datasets and a simulated dataset. Our findings provide new insights into the role of hierarchy construction in forecast reconciliation and offer valuable guidance on forecasting practice.

We hope that the manuscript meets the standards of your journal. Thank you for your consideration.

\vspace{1cm}

\noindent Sincerely,
\bigskip
%\noindent \includegraphics[width=3cm]{/home/fli/Documents/Signatures/Signature-EN}

\noindent Bohan Zhang

\end{document}

### 2024-04-15 R/permute_process_mortality.R

@@ -1,26 +1,0 @@
-
-nl2tibble <- function(x) {
-  output <- vector("list", 6)
-  names(output) <- c("representor", "cluster", "distance", "S", "rf", "other")
-  
-  for (i in seq_along(x)) {
-    for (n in names(x[[i]])) {
-      if (is.character(x[[i]][[n]])) {
-        output[[n]] <- append(output[[n]], x[[i]][[n]])
-      } else {
-        output[[n]] <- append(output[[n]], list(x[[i]][[n]]))
-      }
-    }
-  }
-  tibble::as_tibble(output)
-}
-
-for (i in 0:119) {
-  print(i)
-  dt <- readRDS(sprintf("tourism/ets/batch_%s.rds", i))
-  cluster <- sapply(dt$nl, function(x){x$cluster})
-  idx_to_remove <- which(startsWith(cluster, "permute-hcluster"))[101:600]
-  dt$nl <- dt$nl[-idx_to_remove]
-  stopifnot(length(dt$nl) == 964)
-  saveRDS(dt, sprintf("tourism/ets/batch_%s.rds", i))
-}

### 2024-04-15 R/run_base.R

@@ -1,6 +1,6 @@
 args <- commandArgs(trailingOnly = TRUE)
 path <- args[[1]]
-bfmethod <- args[[2]]
+bfmethod <- "ets"
 
 num.cores <- 8
 
@@ -31,10 +31,11 @@ for (batch in 0:batch_length) {
   }
   forecast_horizon <- min(c(time_length - 96 - batch, 12))
   data <- hts(rbind(rep(1, m), diag(m)),
-               bts = dt$data[1:(96+batch), (n-m+1):n],
-               tts = dt$data[(96+batch+1):(96+batch+forecast_horizon), (n-m+1):n])
+    bts = dt$data[1:(96 + batch), (n - m + 1):n],
+    tts = dt$data[(96 + batch + 1):(96 + batch + forecast_horizon), (n - m + 1):n]
+  )
 
-  data <- hts.basef(data, bfmethod, h=forecast_horizon, frequency=12)
+  data <- hts.basef(data, bfmethod, h = forecast_horizon, frequency = 12)
 
   print(paste0(Sys.time(), "computing features ..."))
   data <- features.compute(data, frequency = frequency)
@@ -47,7 +48,7 @@ for (batch in 0:batch_length) {
     cluster_input <- get(paste0("representator.", strsplit(representor, "-")[[1]][1]))(data, dr = endsWith(representor, "-dr"))
     distance_method <- get(paste0("distance.", distance))
     distance_mat <- matrix(0, m, m)
-    lst <- foreach(row=1:m, .packages = c("dtw")) %dopar% {
+    lst <- foreach(row = 1:m, .packages = c("dtw")) %dopar% {
       output <- c()
       for (col in 1:row) {
         dis <- distance_method(cluster_input[, row], cluster_input[, col])
@@ -63,6 +64,6 @@ for (batch in 0:batch_length) {
     data$distance <- DISTANCEMAT
   }
   data <- add_nl(data, NULL, "", "", "")
-  data <- add_nl(data, dt$S[2:(n-m),], representor = "", distance = "", cluster = "natural")
+  data <- add_nl(data, dt$S[2:(n - m), ], representor = "", distance = "", cluster = "natural")
   saveRDS(data, store_path)
 }

### 2024-04-15 R/run_nl.R

@@ -1,6 +1,6 @@
 args <- commandArgs(trailingOnly = TRUE)
 path <- args[[1]]
-bfmethod <- args[[2]]
+bfmethod <- "ets"
 
 num.cores <- 8
 
@@ -31,46 +31,58 @@ DISTANCES2 <- rep("dtw", 2)
 for (batch in 0:batch_length) {
   store_path <- sprintf("%s/%s/batch_%s.rds", path, bfmethod, batch)
   data <- readRDS(store_path)
-  cluster <- sapply(data$nl, function(x){x$cluster})  
+  cluster <- sapply(data$nl, function(x) {
+    x$cluster
+  })
   if ("Kmedoids-dr" %in% cluster) {
     next
   }
 
   for (i in seq_along(REPRESENTORS)) {
     print(sprintf("%s KMedoids dr %s * %s ", Sys.time(), REPRESENTORS[i], DISTANCES[i]))
-    nl <- build_level(hts = data, representor = REPRESENTORS[i],
-                      distance = DISTANCES[i],
-                      cluster = cluster.kmedoids,
-                      n_clusters = 1:(m - 1))
+    nl <- build_level(
+      hts = data, representor = REPRESENTORS[i],
+      distance = DISTANCES[i],
+      cluster = cluster.kmedoids,
+      n_clusters = 1:(m - 1)
+    )
     data <- add_nl(data, nl$S, REPRESENTORS[i], DISTANCES[i], "Kmedoids-dr",
-                   other = nl$info)
+      other = nl$info
+    )
   }
-  
+
   for (i in seq_along(REPRESENTORS2)) {
     print(sprintf("%s KMedoids %s * %s ", Sys.time(), REPRESENTORS2[i], DISTANCES2[i]))
-    nl <- build_level(hts = data, representor = REPRESENTORS2[i],
-                      distance = DISTANCES2[i],
-                      cluster = cluster.kmedoids,
-                      n_clusters = 1:(m - 1))
+    nl <- build_level(
+      hts = data, representor = REPRESENTORS2[i],
+      distance = DISTANCES2[i],
+      cluster = cluster.kmedoids,
+      n_clusters = 1:(m - 1)
+    )
     data <- add_nl(data, nl$S, REPRESENTORS2[i], DISTANCES2[i], "Kmedoids",
-                   other = nl$info)
+      other = nl$info
+    )
   }
 
   # hierarchical clustering dimension reduction
   for (i in seq_along(REPRESENTORS)) {
[…]

### 2024-04-15 R/run_nlf.R

@@ -1,6 +1,6 @@
 args <- commandArgs(trailingOnly = TRUE)
 path <- args[[1]]
-bfmethod <- args[[2]]
+bfmethod <- "ets"
 
 num.cores <- 8
 source("R/construct_hierarchy.R", chdir = T)
@@ -21,10 +21,9 @@ for (batch in 0:(batch_length)) {
   print(sprintf("%s batch %s ....", Sys.time(), batch))
   store_path <- sprintf("%s/%s/batch_%s.rds", path, bfmethod, batch)
   data <- readRDS(store_path)
-  
+
   forecast_horizon <- min(c(12, time_length - 96 - batch))
-  data <- hts.nlf(data, bfmethod, frequency=frequency, h=forecast_horizon)
-  
+  data <- hts.nlf(data, bfmethod, frequency = frequency, h = forecast_horizon)
+
   saveRDS(data, store_path)
 }
-

### 2024-04-15 R/run_nlr.R

@@ -1,52 +1,0 @@
-args <- commandArgs(trailingOnly = TRUE)
-path <- args[[1]]
-bfmethod <- args[[2]]
-
-num.cores <- 8
-set.seed(20231019)
-
-cl <- parallel::makeCluster(num.cores)
-doParallel::registerDoParallel(cl)
-
-source("R/construct_hierarchy.R", chdir = T)
-
-
-dt <- readRDS(sprintf("%s/data.rds", path))
-n <- NROW(dt$S)
-m <- NCOL(dt$S)
-print(sprintf("%s dataset has %s series and %s bottom series", path, n, m))
-time_length <- NROW(dt$data)
-forecast_horizon <- 12
-frequency <- 12
-batch_length <- time_length - 96 - forecast_horizon
-
-# load dataset
-for (batch in 0:batch_length) {
-  store_path <- sprintf("%s/%s/batch_%s.rds", path, bfmethod, batch)
-  data <- readRDS(store_path)
-  
-  for (i in 1:50) {
-    ncluster <- 15
-    S <- cluster.random(data$distance$ts$dtw, n_clusters = ncluster)[[1]]
-    data <- add_nl(data, S, "", "", paste0("random-", ncluster))
-  }
-  
-  newS <- dt$S[2:(n-m), ]
-  
-  for (i in 1:50) {
-    S <- newS[, sample(m, m)]
-    data <- add_nl(data, S, "", "", "random-natural")
-  }
-  
-  saveRDS(data, store_path)
-}
-
-
-
-
-
-
-
-
-
-

### 2024-04-15 R/run_permute.R

@@ -12,7 +12,7 @@ n <- NROW(dt$S)
 m <- NCOL(dt$S)
 print(sprintf("%s dataset has %s series and %s bottom series", path, n, m))
 time_length <- NROW(dt$data)
-forecast_horizon <- as.integer(args[[2]])
+forecast_horizon <- 12
 frequency <- 12
 batch_length <- time_length - 96 - forecast_horizon
 

### 2024-04-15 R/run_series_summary.R

@@ -1,89 +1,0 @@
-source("R/run_nls.R")
-library(dplyr)
-library(ggplot2)
-library(Matrix)
-library(tsutils)
-
-source("R/metrics.R")
-source("R/expr_utils.R")
-
-# natural vs two-level
-P1 <- function(dt, path, type = "series", conf.level = 0.95) {
-  
-  
-  path <- sprintf("manuscript/figures/%s_rmsse/%s/P1_natural_vs_twolevel_h%s.pdf", type, path, forecast_horizon)
-  
-  mcb_(dt %>% filter(method %in% c("Natural", "Two-level", "Base")), type = type, 
-       plot_type = "orig", file_path = path, conf.level = conf.level)
-}
-
-# natural vs its randomization
-P2 <- function(dt, path, type = "series", conf.level = 0.95) {
-  path <- sprintf("manuscript/figures/%s_rmsse/%s/P2_natural_vs_pn_h%s.pdf", type, path, forecast_horizon)
-  
-  mcb_(dt %>% 
-         filter(cluster == "natural" | startsWith(cluster, "permute-natural")),
-       type = type, plot_type = "custom", file_path = path, mar=c(4,14,3,2), 
-       target = "Natural", conf.level = conf.level)
-}
-
-
-
-P3 <- function(dt, path, type = "series", conf.level = 0.95) {
-  
-  file_path <- sprintf("manuscript/figures/%s_rmsse/%s/P3_mcb_benchmarks_h%s.pdf", type, path, forecast_horizon)
-  mcb_(dt %>% 
-         filter(!startsWith(cluster, "permute"), cluster != "average"),
-       type = type, plot_type = "orig", file_path = file_path, conf.level = conf.level)
-  
-  
-  bench_rmsse <- dt %>%
-    filter(representor != "", !startsWith(cluster, "permute")) %>%
-    rowwise() %>%
-    mutate(rmsse = mean(rmsse)) %>%
-    select(representor, distance, cluster, method, batch, rmsse) %>%
-    group_by(representor, distance, cluster, method) %>%
-    summarise(rmsse = mean(rmsse), .groups = "drop") %>%
-    arrange(rmsse)
-
-  best_ <- bench_rmsse[1, ]
-  file_path <- sprintf("manuscript/figures/%s_rmsse/%s/P3_cluster_vs_pc_h%s.pdf", type, path, forecast_horizon)
-  mcb_(dt %>% 
[…]

### 2024-04-15 R/run_summary_mcs.r

@@ -1,221 +1,0 @@
-source("R/run_nls.R")
-library(dplyr)
-library(ggplot2)
-library(Matrix)
-library(tsutils)
-library(MCS)
-
-source("R/metrics.R")
-source("R/expr_utils.R")
-
-
-cl <- parallel::makeCluster(8)
-
-method_name <- function(representor, distance, cluster) {
-  representor <- strsplit(representor, "-")[[1]][1]
-  representor <- ifelse(!is.na(representor), switch(representor,
-    error = "ER-",
-    error.features = "ERF-",
-    ts = "TS-",
-    ts.features = "TSF-"
-  ), "")
-  distance <- ifelse(distance == "", "",
-    switch(distance,
-      euclidean = "EUC",
-      dtw = "DTW"
-    )
-  )
-  cluster <- strsplit(cluster, "-")[[1]][1]
-  cluster <- ifelse(
-    !is.na(cluster),
-    switch(cluster,
-      natural = "Natural",
-      Kmedoids = "-ME",
-      hcluster = "-HC",
-      base = "Base",
-      "average" = "Combination"
-    ),
-    "Two-level"
-  )
-  paste0(representor, distance, cluster)
-}
-
-mcs_hierarchy_rmsse <- function(orig, rand, name, alpha) {
-  orig_rmsse <- orig %>%
-    rowwise() %>%
-    mutate(rmsse = mean(rmsse)) %>%
-    arrange(batch) %>%
-    pull(rmsse)
-
-  rand_rmsse <- rand %>%
-    rowwise() %>%
-    mutate(rmsse = mean(rmsse)) %>%
-    arrange(batch, cluster) %>%
-    tidyr::nest(rmsse = -"cluster") %>%
-    pull(rmsse) %>%
-    lapply(function(x) {
-      x %>%
-        arrange(batch) %>%
-        pull(rmsse)
-    }) %>%
-    do.call(cbind, .)
-
-  all_rmsse <- cbind(orig_rmsse, rand_rmsse)
-  colnames(all_rmsse) <- c(name, 1:100)
-  MCSprocedure(all_rmsse, alpha = alpha, cl=cl)
-}
-
-
-# natural vs two-level
-P1 <- function(dt, path, alpha) {
-  a <- dt$dtb %>%
-    filter(cluster %in% c("natural", "")) %>%
-    mutate(method = ifelse(cluster == "natural", "Natural", "Two-level")) %>%
[…]

### 2024-04-15 R/summary.R

@@ -1,457 +1,0 @@
-args <- commandArgs(trailingOnly = TRUE)
-path <- args[[1]]
-bfmethod <- args[[2]]
-
-
-dt <- readRDS(sprintf("%s/%s/eval.rds", path, bfmethod))
-dt_orig <- readRDS(sprintf("%s/%s/batch_0.rds", path, bfmethod))
-dt_names <- readRDS(sprintf("%s/names.rds", path))
-source("R/run_nls.R")
-library(dplyr)
-library(ggplot2)
-library(Matrix)
-
-
-
-nemenyi <- function (data, conf.level = 0.95, sort = c(TRUE, FALSE), plottype = c("vline", 
-                                                                       "none", "mcb", "vmcb", "line", "matrix"), select = NULL, 
-          labels = NULL, ...) 
-{
-  sort <- sort[1]
-  plottype <- match.arg(plottype, c("vline", "none", "mcb", 
-                                    "vmcb", "line", "matrix"))
-  if (length(dim(data)) != 2) {
-    stop("Data must be organised as methods in columns and observations in rows.")
-  }
-  data <- as.matrix(data)
-  data <- na.exclude(data)
-  rows.number <- nrow(data)
-  cols.number <- ncol(data)
-  if (!is.null(select) && (select > cols.number)) {
-    select <- NULL
-  }
-  if (plottype != "none") {
-    sort <- TRUE
-  }
-  if (is.null(labels)) {
-    labels <- colnames(data)
-    if (is.null(labels)) {
-      labels <- 1:cols.number
-    }
-  }
-  else {
-    labels <- labels[1:cols.number]
-  }
-  fried.pval <- stats::friedman.test(data)$p.value
-  if (fried.pval <= 1 - conf.level) {
-    fried.H <- "Ha: Different"
-  }
-  else {
-    fried.H <- "H0: Identical"
-  }
-  r.stat <- stats::qtukey(conf.level, cols.number, Inf) * sqrt((cols.number * 
-                                                                  (cols.number + 1))/(12 * rows.number))
-  ranks.matrix <- t(apply(data, 1, function(x) {
-    rank(x, na.last = "keep", ties.method = "average")
-  }))
-  ranks.means <- colMeans(ranks.matrix)
-  ranks.intervals <- rbind(ranks.means - r.stat, ranks.means + 
-                             r.stat)
-  if (sort == TRUE) {
-    order.idx <- order(ranks.means)
-  }
-  else {
-    order.idx <- 1:cols.number
-  }
[…]

### 2024-04-15 manuscript/titlepage.tex
submit to IJF

--- 2023-12-15 manuscript/manuscript.tex
@@
 \usepackage{geometry}
+\usepackage{todonotes}
+\usepackage{hyperref}
+\usepackage{ulem}
 \usepackage{subfig}
@@
 \setcounter{MaxMatrixCols}{20}
+\usepackage{enumitem}
+% \usepackage[pagewise]{lineno}
 
@@
 
-% ADDING LINENUMBERS FOR REVIEWING:
-% \usepackage{lineno}
-
 \begin{document}
@@
 
-  \title{On the performance of hierarchy construction: impacts of structure and clustering}
+  %\title{On the performance of hierarchy construction: impacts of structure and clustering}
+\title{Constructing hierarchical time series through clustering: \\Is there an optimal way for forecasting?}
 
@@
 \author[label3]{Han Li}
-  \address[label3]{Centre for Actuarial Studies, Department of Economics, The University of Melbourne, Australia}
-
-  \begin{abstract}
-
-    Forecast reconciliation has attracted significant research interest in recent years, with most studies relying on pre-defined hierarchies based on time series metadata.
-With the goal of forecast performance in mind, we extend the existing literature on clustering-based reconciliation approach by proposing a novel framework based on hierarchy construction approaches.
-This framework offers three variants: cluster hierarchies, random hierarchies, and combination hierarchies.
-Utilizing the proposed approaches, we investigate the individual contributions of two primary factors, namely clustering and enriched structure, to the performance of forecast reconciliation.
-Through a simulation study and experiments on two real-world datasets, we demonstrate the practical efficacy of hierarchy construction approaches.
-Our findings provide new insights into the dynamics between clustering and enriched structure, significantly enriching our understanding of forecast reconciliation.
-
-  \end{abstract}
-
-  \begin{keyword}
-  Forecasting \sep
-  Hierarchical time series \sep
-  Clustering \sep
-  Hierarchy construction \sep
-  Forecast combination
-  \end{keyword}
+\address[label3]{Department of Economics, The University of Melbourne, VIC 3010, Australia}
 
 \end{frontmatter}
-
-%\clearpage
-\newpage
-% \linenumbers
-
-\section{Introduction}
-
-Hierarchical time series (HTS) has various important applications ranging from supply chain management (\citealp{syntetosSupplyChainForecasting2016}) to tourism (\citealp{kourentzesCrosstemporalCoherentForecasts2019}), electrical load (\citealp{jeonProbabilisticForecastReconciliation2019}), retail demand (\citealp{makridakisM5AccuracyCompetition2022}) forecasting.
-In recent decades, there has been an increasing interest in hierarchical forecasting, primarily driven by the success of the optimal reconciliation framework (\citealp{hyndmanOptimalCombinationForecasts2011,wickramasuriyaOptimalForecastReconciliation2019, panagiotelisProbabilisticForecastReconciliation2023}).
-Unlike the traditional approaches such as bottom-up and top-down, which generate coherent forecasts using forecasts from a single level, the reconciliation framework optimally combine base forecasts of all series in HTS.
-Numerous case studies in the literature demonstrate that reconciliation approaches not only yield coherent forecasts but also enhance overall forecast performance (\citealp{AthanasopoulosForecastReconciliationReview2023}).
-
-The primary objective of hierarchical forecasting is to produce coherent forecasts for the series within a given HTS, which we refer to as \textit{original hierarchy}, ensuring that decision-makers at different levels of the hierarchy can analyze and make informed decisions based on aligned expectations for the future.
-Consequently, the majority of existing research in forecast reconciliation literature experiments on the original hierarchy, which is typically formed according to inherent attributes of the bottom-level series, such as geographical location, gender, product category, travel purpose, and others.
-This limitation is evident in the absence of any discussion regarding cluster-based approaches in the recent comprehensive review of forecast reconciliation by \cite{AthanasopoulosForecastReconciliationReview2023}.
-However, the question arises as to whether the original hierarchy is the optimal structure and whether better structure can be constructed when pursuing superior forecast performance.
-This inquiry serves as the key motivation behind the investigation presented in this paper.
-
-Two observations have been consistently demonstrated in empirical studies on forecast reconciliation.
-First, the accuracy of base forecasts, which are influenced by the individual time series characteristics within the hierarchy, critically affects the overall performance of reconciliation.
-Second, performance improvements achieved through reconciliation do not occur across all levels of the hierarchy.
-In fact, gains for some series often come at the expense of others.
-These observations have motivated researchers to explore the idea of enriching the original hierarchy by introducing new time series via clustering analysis.
-The rationale behind this approach lies in grouping time series with similar patterns together, thereby creating parent time series with stronger signals and consequently, improved forecastability.
-Ideally, the original series can ``borrow strength'' from the newly created series, leading to improved performance across all levels.
-For example, \cite{pangHierarchicalElectricityTime2022} propose a multiple alternative clustering method to group similar electricity and solar power time series.
-In a similar vein, \cite{matteraImprovingOutofSampleForecasts2023} utilize Partition Around Medoids algorithms to unveil underlying structures in stock price indexes, while \cite{liForecastReconciliationApproach2019} apply agglomerative clustering to cause-of-death time series.
-These studies construct new hierarchies through clustering algorithms and demonstrate superior forecast performance compared to reconciliation without clustering, aligning with similar ideas from other research (e.g., \citealp{huberClusterbasedHierarchicalDemand2017, pangHierarchicalElectricityTime2018}).
-However, they are limited in scope as they concentrate solely on a specific time series clustering technique.
-To comprehensively investigate the effectiveness of clustering-based hierarchies, our approach involves a systematic comparison of multiple time series clustering techniques.
-This comparison incorporates a diverse set of time series representations, distance measures and clustering algorithms to provide a more thorough understanding of their impact on forecast performance.
-
-Despite the intuitive appeal of clustering algorithms in forming parent time series with improved forecastability, uncertainties persist.
-Even if time series with superior forecastability are constructed, such improvements do not guarantee enhanced reconciliation performance, given the inherent uncertainty in estimating covariance matrices of base forecast errors (\citealp{pritulargaStochasticCoherencyForecast2021}).
-Therefore, the conclusion that clustering technique is the primary contributor to forecast performance improvement is not straightforward.
-The observed improvement could also be attributed to the enriched structure itself, where a larger set of series is optimally combined to obtain the reconciled forecasts, leading to reduced model uncertainty and data uncertainty.
-To address these concerns, we propose a random hierarchy construction approach.
-By randomly constructing ``twin'' hierarchies with the same tree structure but different permutations of bottom-level series as a contrast to a clustering-based hierarchy, we are able to isolate the influence of clustering algorithms.
-This allows us to inspect the individual contributions of the enriched structure and clustering technique to forecast reconciliation performance.
-
-Randomness technique is commonly integrated with forecast combination approaches in the forecasting literature.
-An illustrative instance is found in the work of \cite{bergmeirBaggingExponentialSmoothing2016}, who leverage a bootstrap aggregation (bagging) technique to improve the performance of exponential smoothing models.
-This involves combining forecasts derived from bootstrapped versions of the time series, demonstrating consistent superior performance on the M3 dataset.
-Additionally, \cite{petropoulosExploringSourcesUncertainty2018a} explore three sources of uncertainty, model uncertainty (data uncertainty and parameter uncertainty), and conclude that the efficacy of bagging technique stems from model uncertainty.
-To address the uncertainty introduced by random hierarchies, we propose a method that combines reconciled forecasts derived from multiple random hierarchies, assigning equal weights to each.
-Furthermore, for a fair comparison with clustering algorithms, we include an equally weighted combination of reconciled forecasts obtained from multiple cluster-based hierarchies.
-
-This paper presents four main contributions:
-
-\begin{itemize}
-  \item We introduce a novel hierarchical forecast reconciliation framework centered on hierarchy construction.
-Within this framework, we explore and compare three distinct approaches: cluster hierarchies, random hierarchies, and combination hierarchies.
-  \item In contrast to existing literature that often focuses on a single clustering technique, our study systematically investigates the effectiveness of various time series clustering implementations.
-This investigation involves the incorporation of four time series representations, two distance measures, and two clustering algorithms.
-  \item Through a simulation study featuring an artificial example, we illustrate a scenario wherein the enriched structure, rather than clustering, emerges as the primary contributor to forecast reconciliation performance.
-Another scenario highlights the importance of carefully selecting a clustering technique.
-  \item We conduct experiments using two real-life datasets - the Australian tourism dataset and the U.S.
-cause-of-death mortality dataset.
-The results demonstrate the superior performance of hierarchy construction approaches, especially the combination hierarchies.
-Our research provides valuable insights into why clustering-based approaches enhance forecast reconciliation performance and offers guidance on the selection of hierarchy construction methods.
-\end{itemize}
-
-The rest of the paper is organized as follows.
-In section~\ref{sec:method} we introduce the proposed framework, elaborating on three approaches: cluster hierarchies, random hierarchies and combination hierarchies.
-The simulation study is presented in Section~\ref{sec:simulation}, while Section~\ref{sec:emp} details empirical experiments conducted on the Australian tourism dataset and U.S.
-mortality dataset.
-Finally, Section~\ref{sec:conclusion} concludes this paper with discussions on the findings and outlines future research directions.
-
-\section{Methodology}
-\label{sec:method}
-
-In this section, we illustrate the proposed framework for hierarchy construction.
-We begin by introducing the necessary notations, followed by detailed explanation of the overall framework.
-The three subsections followed present cluster hierarchies (Section~\ref{sec:cluster}), random hierarchies (Section~\ref{sec:random}) and combination hierarchies (Section~\ref{sec:combination}), respectively.
-Section~\ref{sec:reconciliation} describes the procedure for reconciliation and evaluation.
-
-Given the original hierarchy, let $m$ and $n$ denote the number of time series in the bottom level and the hierarchy, respectively.
-Vectors $\boldsymbol{b}_t$ and $\boldsymbol{y}_t$ represent observations of bottom level and hierarchy at time $t$.
-They are linked through an $n\times m$ summing matrix $\boldsymbol{S}$, which can be decomposed into an identity matrix $\boldsymbol{I}_m$ and a constraint matrix $\boldsymbol{A}$, i.e.,
-\[
-  \boldsymbol{y}_t = \boldsymbol{S}\boldsymbol{b}_t = \begin{bmatrix}
-    \boldsymbol{A} \\ \boldsymbol{I}_m 
-  \end{bmatrix}  \boldsymbol{b}_t,
-\]
-where $\boldsymbol{A}$ represents the mapping from bottom-level time series to upper-level time series.
-While HTS can accommodate general linear constraints, this paper focuses specifically on the most common aggregation constraints, where the matrix $\boldsymbol{A}$ consists solely of $0$ and $1$.
-We define hierarchy construction as the process of creating ``new middle-level series'', resulting in a modified HTS $\boldsymbol{y}^c_t$, which can be represented as:
-\[
-    \boldsymbol{y}^c_t = \boldsymbol{S}^c\boldsymbol{b}_t = \begin{bmatrix}
-        \boldsymbol{A} \\
-        \boldsymbol{C}_1' \\
-        \vdots \\
-        \boldsymbol{C}_K' \\
-        \boldsymbol{I}_m
-    \end{bmatrix}\boldsymbol{b}_t,
-\] 
-where each $\boldsymbol{C}_k$ represents a newly created middle-level series, formed by aggregating a subset of bottom-level series $\boldsymbol{b}_t$.
-The vector $\boldsymbol{C}_k$ is of $m$-dimensional and its elements $c_{k, i} \in \{0, 1\}, i=1,\dots m$ indicate whether the $i$-th bottom-level series belongs to the aggregated subset.
-Notably, different hierarchy construction approaches can result in different hierarchies with varying numbers of new middle-level series $K$.
-In this paper, we introduce and compare three hierarchy construction approaches: cluster hierarchies, random hierarchies and combination hierarchies, which are detailed in the following subsections.
-
-\subsection{Cluster hierarchies}
-\label{sec:cluster}
-
-Cluster hierarchies are constructed based on clustering analyzes of the bottom-level time series. 
-\cite{aghabozorgiTimeseriesClusteringDecade2015a} comprehensively summarize the four key components of time series clustering: time series representations, distance measures, clustering algorithms and evaluation.
-Within our framework, the first three components are directly involved in the hierarchy construction process.
-The fourth component, including forecast reconciliation and evaluation of reconciled forecasts of the original hierarchy, will be detailed in Section~\ref{sec:reconciliation}.
-
-\subsubsection*{Time series representations}
-
-Time series representations transform raw time series into another space through techniques like feature extraction or dimension reduction.
-By utilizing diverse time series representations, we are able to obtain distinct clusters which offer varied perspectives on the same dataset.
-For example, \cite{pangHierarchicalElectricityTime2022} adopt Symbolic Aggregate approXimation (SAX) representation of time series, while \cite{liForecastReconciliationApproach2019} conduct their analysis on the normalized age-time mortality matrix.
-However, the lack of theoretical evidence regarding the relationship between specific groupings within an HTS and forecast reconciliation performance makes the selection of time series representations a challenging task.
-To address this gap, we explore the use of multiple time series representations and discern potential correlations between the resulting hierarchical structure and the efficacy of forecast reconciliation.
-
-Considering the impracticality of exploring every conceivable time series representation, we focus on four key ones: raw time series, in-sample one-step-ahead forecast error, features of time series, and features of in-sample one-step-ahead forecast error.
-The inclusion of raw time series is motivated by its simplicity and broad applicability.
-A crucial element contributing to the success of the minimum trace method proposed by \cite{wickramasuriyaOptimalForecastReconciliation2019} lies in estimating the covariance matrix of base forecast errors based on in-sample one-step-ahead forecast error.
-Hence, we consider in-sample one-step-ahead forecast error as a representation to examine how the structure within the error series influences reconciliation performance.
-Raw time series and in-sample error representations are standardized on a per-series basis to eliminate the impact of scale variations.
-Features, widely employed in capturing time series characteristics across literature, play a pivotal role in various time series applications, including clustering (\citealp{tianoFeatTSFeaturebasedTime2021}) and forecasting (\citealp{wangUncertaintyEstimationFeaturebased2022, liFeaturebasedIntermittentDemand2023}).
-In our exploration, we incorporate features of both raw time series and in-sample forecast error as representations.
-Notably, to the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation literature.
-These representations allow us to glean insights into the diverse aspects of hierarchical time series data and enhance our understanding of how different structures contribute to the forecast reconciliation performance.
-
-\subsubsection*{Distance measures}
-
-Distance measures serve as crucial tools for assessing the similarity/dissimilarity between two series, forming the foundation for clustering algorithms to detect clusters within datasets.
-In the context of time series clustering, we consider two widely applied distance measures: Euclidean distance and dynamic time warping (DTW).
-
-Due to the limited number of time series in comparison to the high dimensionality of individual time series (i.e., the length of time series and the number of time series features) in our applications, dimension reduction on the aforementioned representations becomes imperative when employing Euclidean distance.
-Failure to undertake dimension reduction may result in undesirable clustering outcomes due to the curse of dimensionality.
-To address this, we perform Principal Component Analysis (PCA), extracting the first few principal components that collectively explain at least 80\% of the variance within the data.
-
-In contrast, DTW (\citealp{sakoeDynamicProgrammingAlgorithm1978}), exhibits reduced sensitivity to the curse of dimensionality.
-Unlike Euclidean distance, which performs one-to-one point comparisons, DTW accommodates time series of varying lengths through many-to-one comparisons.
-This flexible approach allows for the recognition of time series with similar shapes, even in the presence of signal transformations such as shifting and/or scaling.
-
-\subsubsection*{Clustering algorithms}
-\label{sec:clustering}
-
-Regarding clustering algorithms, we focus on two prevalent approaches, k-Medoids and agglomerative hierarchical clustering.
-The k-Medoids algorithm, a classical partitioning clustering method, aims to minimize the total distance between all samples within a cluster and their respective cluster centers.
-Unlike k-Means, which employs the mean vector of samples as the cluster center, k-Medoids selects one sample within the cluster as the center. 
-Specifically, we adopt the k-Medoids variant, partitioning around medoids (PAM, \citealp{PartitioningMedoidsProgram1990}).
-Following the recommendation of \cite{PartitioningMedoidsProgram1990}, we determine the optimal number of cluster using the average silhouette width (ASW), a popular cluster validation index.
-ASW assesses the quality of clustering results by measuring the proximity of samples within a cluster compared to neighboring clusters.
-Given a clustering result, the silhouette width for the $i$th sample is calculated as 
-\[
-  SW(i) = \frac{b(i)-a(i)}{\max\{a(i), b(i)\}},  
-\]
-where $a(i)$ represents the average distance of the $i$th sample to others in the same cluster, and $b(i)$ is the average distance to samples in the nearest cluster it is not assigned to.
-A higher silhouette width indicates greater proximity to samples within the same cluster than to those in neighboring clusters.
-The ASW is the average of silhouette widths across all samples.
-We select the clustering result that maximizes the ASW by iterating over all possible numbers of clusters.
-However, ASW has the limitation of being undefined when there is only one cluster.
-Gap statistics (\citealp{tibshiraniEstimatingNumberClusters2002}) can be used to address this limitation, but it is incompatible with DTW.
-
-Agglomerative hierarchical clustering begins by considering each sample as a cluster, and then gradually merges clusters until all samples forms a single cluster. 
-This process results in a binary hierarchical tree with $2m-1$ nodes.
-We employ Ward's linkage (\citealp{murtaghWardHierarchicalAgglomerative2014a}) to merge clusters, minimizing the increase of within-cluster variances at each step.
-
-New middle-level series are constructed according to the clustering results.
-For each cluster, we obtain the corresponding aggregation vector $\boldsymbol{C} = [c_{1}, \dots, c_{m}]'$, where $c_{i}$ is $1$ if the $i$-th bottom-level series belongs to the cluster and $0$ otherwise.
-Illustrated in Figure~\ref{fig:cluster_example} are two example hierarchies generated by k-Medoids and agglomerative clustering algorithms for an original hierarchy with four bottom-level series and one total series.
-These examples highlight the distinct behaviors of the two algorithms.
-Firstly, k-Medoids constructs a simple hierarchy with a single middle level, while hierarchical clustering generates multiple nested middle levels. 
-Secondly, k-Medoids produces a hierarchy with the same number of series as the optimal number of clusters, whereas hierarchical clustering yields multiple middle levels with $m-2$ series.
-As the number of bottom-level series increases, the structural differences become increasingly significant, and we aim to investigate how these differences influence the performance of forecast reconciliation.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.3\textwidth]{figures/pamcluster.pdf}
-    \hspace{1cm}
-    \includegraphics[width=0.3\textwidth]{figures/aggcluster.pdf}
-    \caption{\label{fig:cluster_example}Example clustering results of two clustering algorithms.
-Left panel displays example for k-Medoids algorithm, and right panel displays example for agglomerative hierarchical clustering algorithm.}
-\end{figure}
-
-\subsection{Random hierarchies}
-\label{sec:random}
-
-Cluster hierarchies can potentially affect forecast performance in two aspects.
-First, clustering analysis creates time series that is easy to forecast, allowing original series to borrow strength.
-The accuracy decrease during reconciliation occurs on the newly created time series instead of the original series.
-Secondly, the enriched structure reduce data and model uncertainty within the base forecasts of bottom level, leading to improved reconciled forecasts.
-
-To systematically explore these two aspects, we introduce two randomized methods for constructing hierarchies.
-These methods allow us to eliminate the influence of clustering and focus specifically on investigating the second aspect.
-The first approach generates hierarchies akin to those produced by k-Medoids clustering algorithms.
-Given $m$ bottom-level series and the number of groups $k$, it first randomly assigns $ \lfloor \frac{m}{k}\rfloor$ number of series to each group.
-The remaining $m -  k\times\lfloor\frac{m}{k}\rfloor$ series are then shuffled and assigned to the first $m -  k\times\lfloor\frac{m}{k}\rfloor$ groups one by one.
-This straightforward yet efficient approach constructs a three-level random hierarchy, ensuring the numbers of bottom-level series of these groups  are as nearly equal as possible, allowing us to focus solely on the impact of enriched structure on the forecast reconciliation performance.
-
-The second approach generates random hierarchies based on a given hierarchy, such as one constructed from clustering results.
-Given a hierarchy tree, it creates new hierarchies by randomly permuting the leaf nodes.
-In other words, it shuffles the columns of the constraint matrix $\boldsymbol{A}$ of the given hierarchy.
-This method yields a random ``twin'' hierarchy with the same tree structure but different groupings.
-If the randomized version of a cluster hierarchy significantly outperforms its original counterpart, it suggests that the second aspect holds greater importance than the first, and vice versa.
-Figure~\ref{fig:aggcluster_random} shows an example of this approach.
-The left hierarchy is the hierarchy shown in right panel of Figure~\ref{fig:cluster_example} The right hierarchy is an example of a random ``twin'' hierarchy.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{figures/aggcluster_random.pdf}
-    \caption{\label{fig:aggcluster_random}Examples of randomization of a given hierarchy. Right hierarchy is obtained by shuffling the leaf nodes of left hierarchy.}
-\end{figure}
-
-\subsection{Combination hierarchies}
-\label{sec:combination}
-
-To mitigate the uncertainty introduced by random hierarchies, we propose to combine multiple hierarchies.
-This strategy involves two primary methods.
-The first method focuses on combining the structures of these hierarchies.
-Assume there are $l$ hierarchies in the combination pool, it does so by constructing a new HTS with a summing matrix, which is a composite of the constraint matrices $\boldsymbol{A}_1, \dots, \boldsymbol{A}_l$ of  these hierarchies, along with the original constraint matrix $\boldsymbol{A}$ and the identity matrix $\boldsymbol{I}_m$.
-The summing matrix is thus represented as:
-\[
-  \boldsymbol{S} = \begin{bmatrix}
-    \boldsymbol{A} \\ \boldsymbol{A}_1 \\ \vdots \\ \boldsymbol{A}_l \\ \boldsymbol{I}_m
-  \end{bmatrix}.  
-\] An example of this approach is seen in the work of \cite{pangHierarchicalElectricityTime2022}, where multiple clusterings obtained from k-Means algorithms with different number of clusters are combined.
-However, this method faces challenges, particularly as the number of hierarchies in the combination pool increases, which not only raises computational time but also amplifies the uncertainty in estimating the covariance matrix.
-To address this concern, \cite{pangHierarchicalElectricityTime2022} impose sparse penalty to select ideal clusters that are helpful for reconciliation.
-
-Given the complexities of the first method, our paper concentrates on the second approach, which combines reconciled forecasts from different hierarchies.
-Firstly, we produce reconciled forecasts for each hierarchy.
-The reconciled forecasts of the original series are then extracted and combined using equal weights.
-Note that the resulted forecasts are still coherent.
-While it is possible to employ more complex methods to determine ``optimal'' weights, we adhere to equally-weighted combination due to its simplicity and well-known efficacy (\citealp{wangForecastCombinations50year2022}).
-
-\subsection{Forecast reconciliation and evaluation}
-\label{sec:reconciliation}
-
-This subsection introduces the forecast reconciliation approach used in our paper.
-Assume we are making $h$-step-ahead forecasts based on $T$ historic observations for a given hierarchy $\boldsymbol{y}^c$, which could be the original hierarchy, a cluster hierarchy or a random hierarchy.
-We first produce $h$-step-ahead base forecasts $\hat{\boldsymbol{y}}^c_{T+h}$ using arbitrary forecasting models for each time series in the hierarchy.
-Subsequently, the minimum trace (MinT, \citealp{wickramasuriyaOptimalForecastReconciliation2019}) reconciliation method is applied to produce coherent forecasts:
-\[
-    \tilde{\boldsymbol{y}}_{T+h}^c = (\boldsymbol{S}'\boldsymbol{W}_h^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}_h^{-1}\hat{\boldsymbol{y}}_{T+h}^c,
-\]
-where the superscript $c$ of $\boldsymbol{S}^c$ is omitted for ease of expression.
-$\boldsymbol{W}_h$ is the covariance matrix of $h$-step-ahead forecast errors.
-We employ the shrinkage estimator of $\boldsymbol{W}_h$ proposed by \cite{wickramasuriyaOptimalForecastReconciliation2019}, which estimates the covariance matrix based on the in-sample one-step-ahead forecast errors.
-Specifically, it sets  $\boldsymbol{W}_h = \lambda \hat{\boldsymbol{W}}_{1,D} + (1-\lambda)\hat{\boldsymbol{W}}_1$, where $\hat{\boldsymbol{W}}_1$ is the unbiased sample covariance estimator of the in-sample one-step-ahead forecast errors.
-$\hat{\boldsymbol{W}}_{1,D}$ is a diagonal matrix comprising the diagonal entries of $\hat{\boldsymbol{W}}_1$.
-$\lambda$ is a shrinkage intensity parameter proposed in \cite{SchaferStrimmer2005}.
-
-Given our specific interest in the performance of the original series, we extract reconciled forecasts of the original series from $\tilde{\boldsymbol{y}}_{T+h}^c$, i.e.,
-\[
-  \tilde{\boldsymbol{y}}_{T+h} = \tilde{\boldsymbol{y}}^c_{T+h, 1:(n-m) \cup (n_c - m + 1): n_c},
-\]
-where $n_c$ is the number of time series in the hierarchy.
-For combination hierarchies, the reconciled forecasts from $l$ hierarchies in the combination pool are equally combined to obtain the final forecasts, i.e.,
-\[
-  \tilde{\boldsymbol{y}}_{T+h}^{\text{comb}} = \frac{1}{l} \sum_{j=1}^l \tilde{\boldsymbol{y}}_{T+h}^j.
-\]
-Finally, these forecasts are used for evaluating the performance of different approaches.
-
-\section{Simulation}
-\label{sec:simulation}
-
-Recall our hypothesis positing that the performance of cluster hierarchies is influenced predominantly by two aspects.
-The first aspect is the generation of accurate base forecasts by the newly created time series, while the second aspect is attributable to the enriched structure.
-In this section, we simulate two artificial scenarios using the same dataset but varying base forecasting models.
-The first scenario is designed to demonstrate a context where the second aspect plays a dominant role.
-Conversely, the second scenario is constructed to illustrate a situation where the first aspect is the predominant factor.
-
-\subsection{Simulation design}
-
-\subsubsection*{Time series generation}
-
-We assume the bottom-level time series follow an additive time series pattern with a data generating process described as follows:
-\begin{equation}
-    \label{simu:DGP}
-    \begin{aligned}
-    Y_t &= L_t + S_t + \xi_t \\
-    S_t &= S_{t~\text{mod}~s} \\
-    L_t &= a t + \varepsilon_t,
-    \end{aligned}
-\end{equation}
-where $L_t$ represents the trend term which increases or decreases over time at a slope of $a$.
-The seasonal component, denoted by $S_t$, is repeating and deterministic with a cycle of length $s$.
-Both $\xi_t$ and $\varepsilon_t$ are white noises.
-
-Instead of employing cluster algorithms, we artificially craft $6$ ideal clusters by manipulating the directions of the trend components and patterns of the seasonal components.
-The configurations for each cluster can be found in Table~\ref{table:simu_params}.
-To simulate an increasing trend, we set the slope $a$ to $0.001$, and for a decreasing trend, we set $a$ to $-0.002$.
-The variances of the associate white noise $\varepsilon_t$ are set to $2.5\times 10^{-5}$ and $4.9\times 10^{-5}$ for increasing trend and decreasing trend, respectively.
-For series without trend (``None''), the trend component $L_t$ is set to zero.
-The terms ``Even'' and ``Odd'' in our setup refer to the positioning of seasonal peak.
-Specifically, ``Even'' seasonality means that peaks occur at even-numbered positions (e.g., $2, 4, \dots$) of seasonal cycle, with the reverse being true for ``Odd'' seasonality.
-The values of these seasonal peaks and troughs are randomly drawn from uniform distributions within the ranges of $[2, 3]$ and $[0,1]$, respectively.
-The variance of $\xi_t$ is set to $0.25$.
-We generate monthly time series data, ensuring that each cluster contains $20$ distinct time series.
-For each series, we generate $144$ observations, and the last $12$ observations are reserved for evaluation purpose.
-Figure~\ref{fig:simu_emps} displays example time series from each cluster, while Figure~\ref{fig:simu_pca} visualizes these generated time series based on the first two principal components extracted from principal component analysis of the series.
-
-\begin{table}
-\caption{\label{table:simu_params}Parameter setting for all clusters in the simulation experiments.}
-\centering
-\begin{tabular}{lcccccc}\toprule
-& Cluster 1 & Cluster 2 & Cluster 3 & Cluster 4 & Cluster 5 & Cluster 6 \\
-Trend & Increase & Increase & None & None & Decrease & Decrease \\
-Seasonality & Odd & Even & Odd & Even & Odd & Even  \\
-    \bottomrule
-\end{tabular}
-\end{table}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/simu_example.pdf}
-\caption{\label{fig:simu_emps}Example time series for each cluster in the simulation experiments.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.6\textwidth]{figures/simu_pca.pdf}
-    \caption{\label{fig:simu_pca}Visualization of the generated time series in the simulation experiments.}
-\end{figure}
-
-\subsubsection*{Hierarchies construction}
-
-We consider an original hierarchy with a total of $120$ bottom-level series and a single aggregated series, labelled as ``C0''.
-In addition, we examine four cluster hierarchies and two combination hierarchies.
-Note that we consider multiple cluster hierarchies in order to reflect the real-world scenario where a variety of clustering techniques may be employed.
-The first cluster hierarchy, ``C1'', forms six middle-level series according to the predefined ideal clusters.
-We then merge clusters with the same trend pattern, resulting in the cluster hierarchy with three clusters, denoted by ``C2''.
-Similarly, we construct cluster hierarchies ``C3'' and ``C4'' based on the presence of the trend term and seasonal peak positioning, resulting in $2$ and $3$ middle-level series, respectively.
-Combination hierarchy ``A1'' combines reconciled forecasts obtained from all four cluster hierarchies (``C1'' to ``C4'') using equal weights.
-Moreover, by shuffling the bottom-level series within the cluster hierarchy ``C1'', we generate random ``twin'' hierarchies, as described in Section~\ref{sec:random}.
-The second combination hierarchy ``A2'' combines reconciled forecasts from ten random ``twin'' hierarchies using equal weights.
-
-\subsubsection*{Forecasting}
-
-Given the generated hierarchies, we construct two distinct scenarios, each employing different base forecasting models.
-In the first scenario, exponential smoothing (ETS, \citealp{ForecastingExponentialSmoothing}) is used to generate base forecasts for all time series in hierarchies.
-This setup simulates a context where raw time series are used as time series representations for clustering.
-In the second scenario, we apply the historic mean for generating base forecasts for the bottom-level series, while continuing to use ETS for other time series in hierarchies.
-This approach ensures that the in-sample forecast errors exhibit patterns similar to those of the raw time series, simulating the scenario where in-sample forecast errors are considered as time series representations for clustering.
-Furthermore, this scenario aims to verify the proposition that the original series can borrow strength from the newly created series.
-We refer to these scenarios as ``clustering by time series'' and ``clustering by error'', respectively.
-
-\subsection{Evaluation}
-\label{sec:simu_eval}
-
-Recalling that our purpose is to improve forecast performance of the original series, our evaluation focuses exclusively on reconciled forecasts of the total-level and bottom-level series. 
-Firstly, we employ the Root Mean Squared Error (RMSE) as our accuracy metric for forecasts of individual time series. 
-To ensure robustness and reliability in our findings, we conduct the simulation $500$ times, resulting in a comprehensive evaluation set comprising $500\times 121$ RMSEs for each hierarchy. 
-Multiple comparisons with the best (MCB) test is then applied to compute the average ranks of the seven hierarchies as well as the base forecasts, and to determine whether the performance differences are statistically different (\citealp{tsutils}).
-
-\subsection{Results}
-\label{sec:simu_res}
-
-Figure~\ref{fig:simu_mcb} presents the MCB test results for both scenarios.
-The results reveal that in both scenarios, most approaches perform better than the base forecasts and the original two-level hierarchy ``C0''.
-This outcome indicates that hierarchy construction generally improves forecast reconciliation performance, corroborating similar findings reported in existing literature, such as those by \cite{pangHierarchicalElectricityTime2022,liForecastReconciliationApproach2019} and \cite{matteraImprovingOutofSampleForecasts2023}.
-
-In the ``clustering by time series'' scenario, the ideal cluster ``C1'' achieves a $4$th rank, indicating that optimal clustering does not necessarily translate into the best forecast reconciliation performance.
-On the other hand, ``C1'' ranks $1$st in the ``clustering by error'' scenarios and demonstrates superior performance over other clustering approaches and its randomized counterpart.
-This finding implies that in this scenario, the created series based on clustering, as opposed to enriched structure, plays a crucial role in improving forecast performance.
-However, it is important to recognize that such scenarios may be uncommon in practical applications due to careful modeling of base forecasts.
-Thus, the in-sample forecast errors in practice may not exhibit clear patterns as those observed in this simulation, leading to clustering with more uncertainty.
-Additionally, the varying  performance of ``C1'' across two scenarios highlight the significance of carefully selecting time series representations when constructing new middle levels using clustering algorithms.
-
-Regard the combination hierarchies, it is noteworthy that the equally weighted combination of ten random hierarchies achieves first rank in the first scenario.
-Meanwhile, the equally weighted combination of four clustering hierarchies ranks third in both scenarios.
-These outcomes suggest that forecast combination can further improve forecast performance of both random hierarchies and cluster hierarchies.
-Interestingly, in the first scenario, the combination of random hierarchies outperforms the combination of cluster hierarchies in.
-This implies that the enriched structure has a more significant impact on forecast performance in this context.
-We argue that this outcome can be attributed to the already high quality of base forecasts, as indicated by the close relative ranks of the various approaches.
-When the base forecasts are sufficiently accurate, the added value of reconciliation through complex hierarchical structures might be limited, while combination of hierarchies further improves performance by dealing with data and model uncertainty.
-
-In summary, our simulation effectively illustrates two distinct scenarios, each highlighting a separate factor contributing to the performance improvement offered by hierarchy contribution approaches.
-However, it is crucial to acknowledge that both scenarios represent simplified, somewhat exaggerated representations of practical situations.
-The actual practice of forecasting involves careful modeling, but is also impacted by ubiquitous model misspecification, which adds complexity that isn't fully captured in these artificial scenarios.
-To further validate and explore the effectiveness of various methodologies, we will conduct experiments on two real-world applications, thereby offering a more practical and nuanced understanding of these approaches.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/simu_mcb1.pdf}
-    \includegraphics[width=0.45\textwidth]{figures/simu_mcb2.pdf}
-    \caption{\label{fig:simu_mcb}Average ranks and 95\% confidence intervals based on the MCB Test for the $8$ approaches in the two scenarios of the simulation experiments.
-Left panel displays test results for the ``clustering by time series'' scenario and right panel displays test results for the ``clustering by error'' scenario.}
-\end{figure}
-
-\section{Empirical studies}
-\label{sec:emp}
-\subsection{Datasets}
-
-We analyze two datasets in our empirical studies.
-The first dataset is the monthly Australian domestic tourism dataset, covering the period from January 1998 to December 2016.
-The tourism demand of Australia is geographically disaggregated into seven states and territories, which are further divided into $27$ zones and $76$ regions.
-Additionally, each geographical series is divided by four travel purposes (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
-Overall, this dataset comprises a total of $555$ time series with $304$ of those at the bottom level.
-
-The second dataset focuses on causes of death in the United States, using the ICD 10 coding system.
-We obtain monthly cause-specific death count data from the Center for Disease Control and Prevention (CDC) for the period between 1999 and 2019.
-The coding system inherently forms an unbalanced hierarchy containing $137$ time series, with $113$ of those being bottom-level series.
-To address issues with suppressed data values, we combine causes that contain missing values and share a parent cause.
-The death counts for these combined categories are calculated by subtracting the death counts of sibling causes from the death counts of their parent cause.
-This processing results in a refined dataset that includes $120$ time series with $98$ at the bottom level.
-
-\subsection{Experiment design}
-
-In our analysis of the two datasets, we focus specifically on the total-level and bottom-level series rather than evaluating all levels of the given hierarchies.
-These two-level hierarchies are referred to as ``original hierarchy'', serving as our benchmark.
-The given hierarchy, referred to as ``natural hierarchy'', is considered as one way of hierarchy construction that is based on metadata of the time series.
-We demonstrate that for the purpose of forecast performance, the natural hierarchy may not be the most effective hierarchical structure.
-
-Regarding cluster hierarchies, we employ twelve time series techniques which are derived from combinations of four time series representations, two distance measures and two clustering algorithms.
-The names and details of these approaches are listed in Table~\ref{tab:emp_method}.
-The four time series representations need to perform dimension reduction when using Euclidean distance, as we have discussed in Section~\ref{sec:clustering}.
-Combing the four dimension reduced representations with two clustering algorithms results in the first eight clustering approaches.
-Features of raw time series and in-sample forecast error are not temporal data, thus incompatible with DTW.
-The last four approaches are derived from combinations of two temporal representations, two clustering algorithms and DTW.
-
-\begin{table}
-\caption{\label{tab:emp_method} Hierarchy construction approaches used in empirical studies.}
-\centering
-\resizebox{\textwidth}{!}{
-\begin{tabular}{ccccc}
-    \toprule
-    Approaches & Representation & Dimension reduction & Distance measure & Clustering algorithms  \\
-    TS-MED & Raw time series & Yes & Euclidean & k-Medoids \\
-    ER-MED & In-sample error & Yes & Euclidean & k-Medoids \\
-    TSF-ME & Raw time series features & Yes & Euclidean & k-Medoids \\
-    ERF-ME & In-sample error features & Yes & Euclidean & k-Medoids \\
-    TS-HC & Raw time series & Yes & Euclidean & hierarchical clustering  \\ 
-    ER-HC & In-sample error & Yes & Euclidean & hierarchical clustering  \\ 
-    TSF-HC & Raw time series features & Yes & Euclidean & hierarchical clustering  \\ 
-    ERF-HC & In-sample error features & Yes & Euclidean & hierarchical clustering  \\
-    TS-MED-DTW & Time series & No & DTW & k-Medoids \\
-    TS-HC-DTW & In-sample error & No & DTW & hierarchical clustering \\
-    ER-MED-DTW & Time series & No & DTW & k-Medoids \\
-    ER-HC-DTW & In-sample error & No & DTW & hierarchical clustering 
-     \\\bottomrule
-\end{tabular}}
-\end{table}
-
-Additionally, we explore three combination hierarchies.
-The first one, referred to as ``FC-R'', implements the first random hierarchy construction approach outlined in Section~\ref{sec:random}.
-Here, we set the number of groups $k$ to $15$, an arbitrary number chosen with the goal of creating a moderate number of groups, each containing a moderate number of series.
-We repeat this process to create ten similar hierarchies and combine their reconciled forecasts using equal weights.
-This approach is employed to verify the hypothesis that hierarchy construction can improve forecast reconciliation performance.
-The second combination hierarchy, denoted by ``FC-N'', adopts the alternative random hierarchy construction approach also discussed in Section~\ref{sec:random}.
-Specifically, we randomly create ten ``twin'' hierarchies of the natural hierarchy, to evaluate our argument that the natural hierarchy might not be the optimal hierarchy in terms of forecast performance.
-The third combination hierarchy, labelled by ``FC-C'', involves an equally-weighted combination of the reconciled forecasts obtained from the $12$ cluster hierarchies shown in Table~\ref{tab:emp_method}.
-This approach aims to demonstrate that the performance of hierarchy construction approaches can be further enhanced through forecast combination.
-
-The time series features used in this experiment are calculated using the \texttt{tsfeatures} package (\citealp{tsfeatures}) for R (\citealp{R}).
-After filtering out the features that are constant across all series, $56$ features are reserved.
-The k-Medoids and hierarchical clustering algorithms are implemented using the \texttt{cluster} (\citealp{cluster}) package for R.
-The base forecasts are generated using the automatic ETS models, which are then reconciled using the minimum trace method with shrinkage estimator.
-
-To rigorously validate our hypothesis, we utilize the rolling window strategy to evaluate the performance of different approaches on both datasets.
-We begin by fitting base forecasting models using the first $96$ observations.
-Then we calculate time series representations and construct new hierarchies, either through clustering or random approaches, and then forecast $12$ steps ahead.
-After that, the training set is increased by one observation and new forecasts are obtained.
-The procedure is repeated until the last $12$ observations are used for evaluation.
-Finally, we can obtain $121$ $12$-step-ahead forecasts for the tourism dataset and $144$ $12$-step-ahead forecasts for the mortality dataset.
-
-We compare the forecast performance of the twelve cluster hierarchies, three combination hierarchies as well as the natural hierarchy, the original two-level hierarchy and base forecasts.
-Same as the evaluation measure described in Section~\ref{sec:simu_eval}, we first calculate RMSE for each of the $12$-step-ahead forecasts, resulting in $144 \times 99$ RMSE values for the mortality dataset and $121 \times 305$ RMSE values for the tourism dataset for each approach.
-We then conduct the MCB test on these RMSE values to statistically assess the differences in forecast accuracy.
-
-\subsection{Results}
-
-The MCB test results for the tourism dataset and mortality dataset are shown in Figure~\ref{fig:tourism_mcb} and Figure~\ref{fig:mortality_mcb}, respectively.
-For both datasets, most hierarchy construction approaches outperform both base forecasts and the two-level hierarchy.
-The first combination approach ``FC-R'' achieves third rank on the mortality dataset eighth rank on the tourism dataset.
-These results demonstrate that hierarchy construction can enhance forecast performance, further supporting the findings in our simulation and the literature.
-
-In both datasets, the evidence suggests that the natural hierarchy may not be optimal for performance.
-The equally weighted combination of "twin" hierarchies derived from the natural hierarchy (``FC-N'') outperform the natural hierarchy itself, supporting this hypothesis.
-This finding reinforces our belief that better hierarchical structures can be constructed, as evidenced by the superior performance of some cluster hierarchies on the tourism dataset.
-Most cluster hierarchies outperform the original two-level hierarchy on both datasets, further demonstrating the effectiveness of clustering approaches.
-However, three exceptions on the mortality dataset highlight the importance of choosing an appropriate clustering technique.
-
-Interestingly, unlike the simulation where either clustering or enriched structure play the primary role in performance improvement, both factors contribute to better forecasts in the two real-world datasets.
-First, the randomized natural hierarchy ``FC-N'' outperform all  cluster hierarchies and the natural hierarchy on both datasets, showcasing the benefit of enriched structure.
-Second, the equally weighted combination of cluster hierarchies achieves the top rank, demonstrating the effectiveness of clustering techniques.
-Furthermore, the impressive performance of the three combination hierarchies underscores the potential of combining forecasts from multiple hierarchies for even greater accuracy.
-This suggests that the impact of combination may even more significant than the individual contributions of clustering and enriched structure.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/tourism_mcb.pdf}
-    \caption{\label{fig:tourism_mcb}Average ranks and 95\% confidence intervals based on the MCB Test for the $18$ approaches on the tourism dataset.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/mortality_mcb.pdf}
-    \caption{\label{fig:mortality_mcb}Average ranks and 95\% confidence intervals based on the MCB Test for the $18$ approaches on the mortality dataset.}
-\end{figure}
-
-The approach based on hierarchical clustering outperforms the approach based on k-Medoids on the tourism dataset when using the same representation and distance metric, e.g., ``TSF-HC'' significantly outperforms ``TSF-ME''.
-However, this is not consistently observed for every combination of representation and distance metric on the mortality dataset.
-We believe this discrepancy is due to different time series patterns at the bottom level of these two datasets.
-In the case of the mortality dataset, we combine rare causes of death that have suppressed values and record death counts at a national level.
-As a result, most series at the bottom level exhibit strong seasonality and trend.
-On the other hand, in the tourism dataset, the tourism demand is disaggregated for both travel purposes and geographical regions.
-This leads to numerous bottom-level series with high volatility and many zeros, making them more challenging to forecast.
-Therefore, having a hierarchy with more middle-level series can be more advantageous for reconciliation in the tourism dataset compared to the mortality dataset.
-Additionally, we suspect that the inferior performance of ``FC-R'' on the tourism dataset may be partly attributed to an insufficient number of middle-level series.
-
-In most cases, the in-sample error representation outperforms the time series representation when using the same distance metric and clustering algorithms.
-However, this performance difference is not as significant as what was observed in Section~\ref{sec:simu_res}.
-Intuitively, hierarchies constructed based on clustering in-sample error should be similar to random hierarchies when all base models are correctly specified.
-However, due to ubiquitous model misspecification in practice, vague patterns emerge in the in-sample error, which leads to contradictory results.
-
-\subsubsection*{Effect of number of random hierarchies}
-
-In our previous experiments, we set the number of random hierarchies in ``FC-R'' and ``FC-N'' to $10$ for fair comparisons with ``FC-C''.
-However, we believe that increasing the number of random hierarchies could further enhance performance.
-In this subsection, we explore the effects of using 20 and 50 random hierarchies, referred to as ``FC-N-20'', ``FC-N-50'', ``FC-R-20'', and ``FC-R-50''.
-We compare these variations with ``FC-R'', ``FC-C'', and ``FC-N'' using the same evaluation procedure described earlier.
-The results from the MCB test are presented in Figure~\ref{fig:number_mcb}, where the left panel shows results on the tourism dataset and the right panel displays results on the mortality dataset.
-
-Generally, we observe that forecast performance improves as the number of random hierarchies increases, except for ``FC-N-20'' and ``FC-N'' on the mortality dataset.
-Surprisingly, on the tourism dataset, ``FC-N-50'' performs slightly better than ``FC-C''.
-It is important to note that employing more random hierarchies comes at a cost of increased computational resources.
-Therefore, one must carefully consider trade-offs between efficiency and performance when making decisions.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{figures/tourism_number_mcb.pdf}
-\includegraphics[width=0.45\textwidth]{figures/mortality_number_mcb.pdf}
-\caption{\label{fig:number_mcb}Average ranks and 95\% confidence intervals based on the MCB Test of different number of random hierarchies on two datasets.
-Left and right panels display test results on tourism dataset and mortality dataset, respectively.}
-\end{figure}
-
-\section{Discussion and Conclusion}
-\label{sec:conclusion}
-
-This paper extends the current body of research on clustering-based forecast reconciliation by introducing a general hierarchical forecasting framework, incorporating three distinct approaches: cluster hierarchies, random hierarchies, and combination hierarchies.
-In contrast to the focused scope of previous studies, our approach to cluster hierarchies involves a broader exploration.
-We examine four time series representations, employ two distance measures, and utilize two clustering algorithms.
-This comprehensive method differs significantly from the existing literature, which typically concentrates on specific clustering implementations.
-We also introduce two innovative random hierarchy construction methods to investigate what drives the performance enhancements in cluster hierarchies.
-These random hierarchies help isolate the effect of clustering, allowing us to focus on the benefits derived from the enriched structure alone.
-Furthermore, we propose combination hierarchies to mitigate uncertainties inherent in random hierarchies.
-
-Our simulation study is constructed around two scenarios, each based on different base forecasting models.
-The first scenario highlights the value of the enriched structure, evident in the high-ranking performance of random combination hierarchies.
-Enriched structure can further improve forecast performance when the base forecasts are of high quality.
-The second scenario demonstrates the efficacy of clustering-based approaches, particularly when the base forecasts at the bottom level are less accurate.
-
-Empirical studies on two datasets support our simulation findings.
-In the tourism dataset, the inferior base forecasts at the bottom level lead to all cluster hierarchies surpassing the original hierarchy, with four outperforming the combination of random hierarchies, which is used to demonstrate the impact of enriched structure.
-In contrast, the superior performance of two random combination hierarchies in the mortality dataset highlights the effectiveness of enriched structure.
-These results imply that the dominant factor, whether it is the enriched structure or clustering, varies depending on the dataset's characteristics, the base forecasting models, and other variables.
-Overall, our findings suggest that hierarchy construction approaches generally enhance performance, and combining these approaches leads to further improvements.
-
-Future research based on our study could proceed in several promising directions.
-Firstly, our experiments were concentrated on total-level and bottom-level series.
-In practical applications, it might be necessary to include specific middle levels or evaluate the entire hierarchy.
-This could lead to the exploration of different hierarchy approaches, such as clustering middle-level series rather than bottom-level ones.
-Although we used equally-weighted combinations in this study, there's potential for applying more sophisticated methods to improve performance.
-The extensive literature on forecast combination, including advanced methods for calculating weights, offers numerous possibilities for enhancement (refer to \citealp{wangForecastCombinations50year2022} for an in-depth review).
-
-In Section~\ref{sec:combination}, we discuss the implications of combining multiple hierarchical structures on the uncertainty in estimating the covariance matrix of base forecast errors.
-Our conclusion was to opt for forecast combination rather than combining the structures of the hierarchies.
-However, a systematic exploration of these two strategies, combining hierarchical structures and combining forecasts, presents an intriguing area for future research.
-Specifically, addressing the challenge of uncertainty due to high dimensionality in the combination of hierarchical structures is possible.
-In this context, innovative solutions like the regularized forecast reconciliation approach, as proposed by \cite{bentaiebRegularizedRegressionHierarchical2019a}, and alternative estimators of the covariance matrix, such as those suggested by \cite{pritulargaStochasticCoherencyForecast2021} could be highly beneficial.
-
-In both our simulation and empirical studies, the combination of random hierarchies displayed competitive results compared to clustering-based methods.
-However, the efficacy of this approach in scenarios with an extremely large number of bottom-level series remains uncertain.
-In such cases, a partially random approach might be more effective.
-For instance, initially generating random hierarchies, identifying those with superior performance, and then constructing partially random hierarchies based on these well-performing structures could be a viable strategy.
-Another intriguing possibility is the integration of both clustering and random approaches.
-Moreover, our study focused specifically on the aggregation of bottom-level series, which may have constrained the potential of middle-level series.
-It's plausible to enhance forecastability at the middle level by creating series through general linear combinations.
-
-Finally, our study was centered around point forecast reconciliation and cross-sectional hierarchy.
-However, the field of probabilistic forecast reconciliation has recently gained significant interest, as evidenced by research like \cite{panagiotelisProbabilisticForecastReconciliation2023} and \cite{jeonProbabilisticForecastReconciliation2019}.
-Applying hierarchy construction approaches to probabilistic forecast reconciliation presents a novel and potentially fruitful research avenue.
-This approach could provide deeper insights and more robust forecast reconciliation methods, particularly in scenarios where uncertainty and variability are significant factors.
-Another promising direction for extending our methodologies lies in exploring temporal (\citealp{athanasopoulosForecastingTemporalHierarchies2017}) and cross-temporal hierarchies (\citealp{girolimettoCrosstemporalProbabilisticForecast2023a}).
 
@@
 Bohan Zhang is supported by the international joint doctoral education fund of Beihang University.
+Han Li is supported by the Australian Research Council Discovery Projects funding scheme (DP220100090).
 
-\begingroup
-\setstretch{1.15}
-\bibliographystyle{agsm}
-\bibliography{references.bib}
-\endgroup
+\section*{Declaration of competing interest}
+
+The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
 

### 2024-05-21 slides/slides.tex
add slides for ISF2024

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

\documentclass[aspectratio=169]{beamer}

\setbeamertemplate{caption}[numbered]
\usepackage{times}

%\usepackage{textpos}
\mode<presentation> {

	% The Beamer class comes with a number of default slide themes
	% which change the colors and layouts of slides. Below this is a list
	% of all the themes, uncomment each in turn to see what they look like.

	%\usetheme{default}
	%\usetheme{AnnArbor}
	%\usetheme{Antibes}
	%\usetheme{Bergen}
	%\usetheme{Berkeley}
	%\usetheme{Berlin}
	\usetheme{Boadilla}
	%\usetheme{CambridgeUS}
	%\usetheme{Copenhagen}
	%\usetheme{Darmstadt}
	%\usetheme{Dresden}
	%\usetheme{Frankfurt}
	%\usetheme{Goettingen}
	%\usetheme{Hannover}
	%\usetheme{Ilmenau}
	%\usetheme{JuanLesPins}
	%\usetheme{Luebeck}
	%\usetheme{Madrid}
	%\usetheme{Malmoe}
	%\usetheme{Marburg}
	%\usetheme{Montpellier}
	%\usetheme{PaloAlto}
	%\usetheme{Pittsburgh}
	%\usetheme{Rochester}
	%\usetheme{Singapore}
	%\usetheme{Szeged}
	%\usetheme{Warsaw}

	% As well as themes, the Beamer class has a number of color themes
	% for any slide theme. Uncomment each of these in turn to see how it
	% changes the colors of your current slide theme.

	%\usecolortheme{albatross}
	%\usecolortheme{beaver}
	%\usecolortheme{beetle}
	%\usecolortheme{crane}
	\usecolortheme{dolphin}
	%\usecolortheme{dove}
	%\usecolortheme{fly}
	%\usecolortheme{lily}
	%\usecolortheme{orchid}
	%\usecolortheme{rose}
	%\usecolortheme{seagull}
	%\usecolortheme{seahorse}
	%\usecolortheme{whale}
	%\usecolortheme{wolverine}
	\usefonttheme{serif}
	\usepackage[utf8]{inputenc}
	\usepackage{mathptmx}
	\usepackage{amsmath}
	\usepackage{amsfonts}
	\usepackage{amssymb}
	\usepackage{color}
	\usepackage{url}
        \usepackage{wrapfig}
	\usepackage{multirow}
	\usepackage{multicol}
	\usepackage{booktabs}
	\usepackage{graphicx}
	\usepackage{array}
	\usepackage{arydshln}
	\usepackage{mathtools}
	\usepackage{chngpage}
	\usepackage{url}
	\usepackage{setspace}
	\usepackage{bigstrut}
	\usepackage{tabularx}
	\usepackage{bm}
	\usepackage{bigstrut}
        \usepackage{epsfig}
        \usepackage{epstopdf}
        \usepackage{hyperref}
        \usepackage{amsfonts,amsmath,bbm,bm,xcolor,booktabs,hyperref,amsthm}
	%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
	%\setbeamertemplate{footline}[pagenumber] % To replace the footer line in all slides with a simple slide count uncomment this line

	\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
}
\usepackage{bigstrut}
\usepackage{caption}
\usepackage{subfig}
\usepackage{float}
\usepackage{graphicx} % Allows including images
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{natbib}
\usepackage{setspace}
\usepackage{comment}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{bigstrut}
\usepackage{lscape,tikz-qtree}
\usetikzlibrary{arrows,shapes,positioning,shadows,trees}

\graphicspath{{figures/}}

\newcounter{researchquestion}
\setcounter{researchquestion}{0}

% Define the environment for the research questions
\newenvironment{researchquestion}{%
    \refstepcounter{researchquestion}%
    \par\medskip\noindent%
    \textbf{RQ\theresearchquestion.}~%
}{\medskip}

\linespread{1}
\newenvironment{myenv}[1]
{\begin{spacing}{#1}}
	{\end{spacing}}

\AtBeginSection[]
{
	%\ifthenelse{\boolean{sectiontoc}}{
	%    \begin{frame}<beamer>{Gliederung}
	%      \tableofcontents[currentsection]
	%    \end{frame}
	%  }
	%\newcommand{\toclesssection}[1]{
	%  \setboolean{sectiontoc}{false}
	%  \section{#1}
	%  \setboolean{sectiontoc}{true}
	%}

	%\begin{frame}[noframenumbering]  
	%	\frametitle{Outline} \tableofcontents[currentsection, subsectionstyle=hide] 
	%\end{frame}

	%\addtocounter{framenumber}{-1}
}

\AtBeginSection[]
{\begin{frame}

  \frametitle{Outline} \tableofcontents[currentsection, subsectionstyle=hide]

\end{frame}
\addtocounter{framenumber}{-1}
}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

	%\begin{frame}
	%\frametitle{Overview} % Table of contents slide, comment this block out to remove it
	%\tableofcontents % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
	%\end{frame}

	%----------------------------------------------------------------------------------------
	%	PRESENTATION SLIDES
	%----------------------------------------------------------------------------------------

	%------------------------------------------------

\title[Constructing hierarchical time series through clustering]{Constructing hierarchical time series through clustering: \\Is there an optimal way for forecasting?}
%\vspace{8mm}
%\author{{\bf Han Li$^*$ and Colin O'Hare$^{\dagger}$} \vspace{6mm}\\\vspace{0.05cm} \small $^*$ARC Centre of Excellence in Population Ageing Research (CEPAR), UNSW \vspace{2mm}\\ \small $^\dagger$Department of Econometrics and Business Statistics, Monash University}

\vspace{-8in}

\author[Bohan Zhang]{Bohan Zhang$^{1}$, Anastasios Panagiotelis$^{2}$, and Han Li$^{3}$} % Your name
	\institute[] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
	%{\small {$^1$ \small  Department of Statistics and Department of Mathematics\\ \textbf{Purdue University}}\\ 
	 %\vskip 0.2cm	
  	{\small {$^1$ \small School of Economics and Management, Beihang University}
   \vskip 0.2cm
	\small {$^2$ Discipline of Business Analytics, Business School, University of Sydney}	
    \vskip 0.2cm
  	\small {$^3$ \small Centre for Actuarial Studies, Department of Economics, University of Melbourne}
   \vskip 0.5cm
\textbf{The 44th International Symposium on Forecasting, Dijon, France}
}
	\date{30 June - 3 July, 2024} % Date, can be changed to a custom date

	%\logo{\includegraphics[height=0.7cm]{Figures/logo_all.png}\vspace{-0.3cm}}

%	\logo{\includegraphics[height=3.5cm]{Doc1}\vspace{-2cm}}

\begin{document}

\begin{frame}
\titlepage
% \vspace{0.3cm}

\end{frame}

% \begin{frame}{Outline of the presentation}
% 	\large
% 	\begin{enumerate}
% 		\item \color {blue} What are we trying to measure, and why?
% 		\vspace{0.08in}
%             \item Data description
%             \vspace{0.08in}
% 		\item \color {blue} What modelling procedures are used?
%   		\begin{itemize}
% 		\vspace{0.02in}
% 			\item Standardisation and smoothing
% 		\vspace{0.02in}
% 			\item Linear regression and time series modelling
% 		\vspace{0.02in}
% 			\item Forecast reconciliation
% 		\end{itemize}
% 		\vspace{0.02in}
% 		\item \color {blue} What do the results look like?\vspace{0.08in}		
% 		\item \color {blue} Questions and discussions

% 		%\vspace{0.08in}
% 		%\item  \color {blue}

% 	\end{enumerate}
% \end{frame}

%------------------------------------------------

\begin{frame}{Outline of the presentation}

\tableofcontents 
\end{frame}

\section{Hierarchical forecasting and forecast reconciliation}

\begin{frame}{Hierarchical forecasting and forecast reconciliation}
\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{hts.png}    
\end{figure}
\vspace{-0.7cm}
\begin{itemize}
    \item (Cross-sectional) Hierarchical time series is multivariate time series whose observations at time $t$ respect \textbf{aggregation constraints}.
    \item Hierarchical forecasting produces \textit{coherent} forecasts for hierarchical time series.
    \item Forecast reconciliation projects incoherent base forecasts of all time series onto the coherent subspace (\citealp{panagiotelisForecastReconciliationGeometric2021}).
\end{itemize}

\end{frame}

\begin{frame}{Forecast reconciliation: the forecast combination perspective}

	\begin{itemize}
		\item Forecast reconciliation can be interpreted from the forecast combination perspective (\citealp{hollymanUnderstandingForecastReconciliation2021,difonzoForecastCombinationbasedForecast2024}).
		\item Reconciled forecasts are weighted combination of ``direct'' and ``indirect'' base forecasts. 
		\[
			\tilde{y}_{AA} = w_1 \hat y_{AA} + w_2 (\hat y_{A} -\hat y_{AB}) + w_3 (\hat y_{Total} - \hat y_{AB} - \hat y_{BA} - \hat y_{BB})
		\]

		\item Could we employ {\color{red} more ``indirect'' forecasts} and improve forecast accuracy?
		\begin{itemize}
			\item Add middle-level series.
		\end{itemize}
		\item Could we find {\color{red} more accurate ``indirect'' forecasts} and improve forecast accuracy?
		\begin{itemize}
			\item Cluster similar time series (\citealp{liForecastReconciliationApproach2019,pangHierarchicalElectricityTime2022,matteraImprovingOutofSampleForecasts2023}).
			\item The rationale behind clustering lies in grouping time series with similar patterns together, thereby creating middle-level series with enhanced signals and consequently, improved forecastability.
		\end{itemize}
	\end{itemize}

	\end{frame}

%------------------------------------------------
\section{Research questions}
%------------------------------------------------

\begin{frame}{Research questions}
	\begin{researchquestion}
		In terms of forecast performance, can {\color{red} the use of middle level series lead to improvement} compared to a two-level hierarchy (consisting of only top and bottom time series)? If so, is it possible to {\color{red} construct hierarchies in a data-driven way} that leads to further improvements in forecast accuracy?
	\end{researchquestion}

	\begin{figure}
		\centering
		\includegraphics[width=0.45\textwidth]{RQ1-l.png}
		\includegraphics[width=0.45\textwidth]{RQ1-r.png}
	\end{figure}

	\begin{itemize}
		\item Does creating ``Agg''s improve forecast accuracy?
		\item How to construct ``Agg''s in a data-driven approach?
	\end{itemize}

\end{frame}

\begin{frame}{Research questions}

	The increased accuracy when using data-driven approach may be attributed to two factors.

	\begin{itemize}
		\item {\color{red} Grouping}: some correct subsets of series are chosen to form new middle-level series.
		\item {\color{red} Structure}: the number of middle-level series, the depth of the hierarchy, and the distribution of group sizes in the middle layer(s).
	\end{itemize}

	\begin{researchquestion}
		Should the improved accuracy of clustering-based methods be attributed to grouping together similar time series, or to the structure of the hierarchy?
	\end{researchquestion}
\end{frame}

\begin{frame}{Research questions}

	With {\color{red} multiple hierarchies available} and inspired by the forecast combination literature (\citealp{wangForecastCombinations50year2022}), we consider the last research question:

	\begin{researchquestion}
		Does an equally-weighted combination of reconciled forecasts derived from multiple hierarchies improve forecast reconciliation performance?
	\end{researchquestion}
\end{frame}

\section{Time series clustering-based forecast reconciliation}

\begin{frame}{Time series clustering-based forecast reconciliation}
	To the best of our knowledge, four studies have attempted to improve forecast accuracy in a reconciliation setting by constructing middle levels of the hierarchy using time series clustering.

	\begin{itemize}
		\item \cite{pangHierarchicalElectricityTime2018} and \cite{pangHierarchicalElectricityTime2022} propose to employ K-means algorithm to group similar electricity and solar power time series.
		\item \cite{liForecastReconciliationApproach2019} apply agglomerative hierarchical clustering to cause-of-death time series.
		\item \cite{matteraImprovingOutofSampleForecasts2023} utilize Partition Around Medoids algorithms to unveil underlying structures in stock price indexes.
	\end{itemize}

	We consider various approaches based on three key components, namely {\color{red} time series representations}, {\color{red} distance measures}, and {\color{red} clustering algorithms}.
\end{frame}

\begin{frame}{Time series representations}

	The time series representation refers to the object that acts as an input for time series clustering. We consider four representations:
	\begin{itemize}
		\item {\color{red} Raw time series}.
		\item {\color{red} In-sample one-step-ahead forecast error}. A key step in MinT reconciliation is to estimate $\boldsymbol{W}_h$ based on in-sample forecast error.
		\item {\color{red} Time series features of raw time series}.
		\item {\color{red} Time series features of in-sample one-step-ahead forecast error}. 
		\begin{itemize}
			\item Features are low dimensional representation of time series, and have been used in various tasks such as clustering and forecasting.
			\item $56$ features calculated by the \texttt{tsfeatures} package in R are included.
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Distance measures}

	All clustering algorithms we consider require a distance to be defined between the objects that act as inputs to the algorithm.

	We consider two widely applied distance measures: {\color{red} Euclidean distance} (combined with PCA to reduce dimensionality) and {\color{red} dynamic time warping (DTW)}.

\end{frame}

\begin{frame}{Clustering algorithms}
	We focus on two clustering algorithms:

	\begin{itemize}
		\item {\color{red} Partitioning around medoids}, which is an algorithm to find a local minimum for the $k$-medoids problem.
		\item {\color{red} Agglomerative hierarchical clustering} with Ward's linkage.
	\end{itemize}

	\begin{figure}
		\centering
		\includegraphics[width=0.35\textwidth]{pamcluster.pdf}
		\includegraphics[width=0.35\textwidth]{aggcluster.pdf}
	\end{figure}

	\begin{itemize}
		\item PAM (left) constructs {\color{red} a simple hierarchy with a single middle level}, while hierarchical clustering (right) generates {\color{red} multiple nested middle levels}.
		\item As the number of bottom-level series increases, these differences become increasingly pronounced, with potential implications for forecast reconciliation.
	\end{itemize}
\end{frame}

\begin{frame}{Summary}
	\begin{table}[h!]
		\caption{\label{tab:P3_methods} Details of the 12 clustering approaches considered.}
		\centering
		\resizebox{\textwidth}{!}{
		\begin{tabular}{rcrrr}
			\toprule
			Approach & Dimension reduction & Representation & Distance measure & Clustering algorithm  \\ \midrule
			TS-EUC-ME &  Yes & Time series  & Euclidean & $k$-medoids \\
			ER-EUC-ME & Yes& In-sample  error  & Euclidean & $k$-medoids \\
			TSF-EUC-ME & Yes& Time series features  & Euclidean & $k$-medoids \\
			ERF-EUC-ME & Yes& In-sample error features  & Euclidean & $k$-medoids \\
			TS-EUC-HC & Yes& Time series  & Euclidean & Hierarchical   \\ 
			ER-EUC-HC & Yes& In-sample error  & Euclidean & Hierarchical   \\ 
			TSF-EUC-HC & Yes& Time series features  & Euclidean & Hierarchical   \\ 
			ERF-EUC-HC & Yes& In-sample error features  & Euclidean & Hierarchical  \\
			TS-DTW-ME & No& Time series  & DTW & $k$-medoids \\
			TS-DTW-HC & No& In-sample error  & DTW & Hierarchical  \\
			ER-DTW-ME & No& Time series  & DTW & $k$-medoids \\
			ER-DTW-HC & No& In-sample error  & DTW & Hierarchical 
			 \\\bottomrule
		\end{tabular}}
		\end{table}
\end{frame}

\section{Data description}

\begin{frame}{Australian tourism dataset}
	\begin{figure}
		\includegraphics[width=0.8\textwidth]{../manuscript/figures/tourism.pdf}
	\end{figure}
	\begin{itemize}
		\item Monthly Australian domestic tourism dataset, covering the period from January 1998 to December 2016 (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
		\item Consists of $555$ time series with $304$ of those at the bottom level. The middle-level series are constructed based on state, region, city and travel purpose.
	\end{itemize}

\end{frame}

\begin{frame}{U.S. cause-of-death count dataset}
	\begin{figure}
		\includegraphics[width=0.8\textwidth]{../manuscript/figures/mortality.pdf}
	\end{figure}
	\begin{itemize}
		\item Monthly cause-specific death count data of U.S. for the period between January 1999 and December 2019.
		\item Consists of $120$ time series, with $98$ of those being bottom-level series. The middle-level series are constructed based on major cause-of-death groups.
	\end{itemize}
\end{frame}

\section{Improving forecast performance via hierarchy augmentation}

\begin{frame}{Evaluation}

	\begin{itemize}
		\item We employ the expanding window strategy, resulting in $121$ $12$-step-ahead forecasts for tourism dataset, and $145$ $12$-step-ahead forecasts for mortality dataset.
		\item We only focus on the total series and bottom-level series.
		\item Forecast accuracy is evaluated based on average RMSSE of all time series (total and bottom).
		\item {\color{red} Three benchmarks}: Base forecast, Two-level hierarchy (total and bottom), Natural hierarchy (constructed based on attributes of the bottom-level series)
	\end{itemize}

\end{frame}

\begin{frame}{Cluster hierarchies vs benchmarks}

	\begin{figure}
		\centering
		\includegraphics[width=0.4\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P3_mcb_benchmarks_h12.pdf}
		\includegraphics[width=0.4\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P3_mcb_benchmarks_h12.pdf}
		\caption{Average ranks and 95\% confidence intervals for twelve cluster hierarchies and three benchmarks on tourism dataset (left) and mortality dataset (right) based on MCB test.}
	\end{figure}

\end{frame}

\begin{frame}{Cluster hierarchies vs benchmarks}

	\begin{itemize}
		\item The {\color{red} natural hierarchies} provide better results than the base forecasts and the two-level hierarchies, and {\color{red} comparable results with cluster hierarchies}.
		\item For tourism dataset, {\color{red} ten out of twelve} cluster hierarchies significantly outperform two-level hierarchy. However for mortality dataset, none of the cluster hierarchies significantly outperform two-level hierarchy.
		\begin{itemize}
			\item The performance of clustering-based forecast reconciliation depend on the characteristics of bottom-level series.
			\item The tourism dataset predominately contains {\color{red} volatile and noisy} bottom-level time series with weak trend and seasonality. 
			\item The bottom-level series in mortality dataset exhibit {\color{red} stronger trend and seasonality patterns}, meaning that the addition of middle-level series is less beneficial.
		\end{itemize}
		\item The hierarchies constructed via {\color{red} hierarchical clustering} algorithms outperform the hierarchies based on {\color{red} k-medoids }when using the same representation and distance metric.
	\end{itemize}
\end{frame}

\begin{frame}{Disentangling grouping and structure}
	To assess whether ``grouping'' or ``structure'' has relatively more importance, we propose to construct {\color{red}``twin'' hierarchies} constructed by {\color{red}randomly permuting the bottom-level series}.

	\begin{figure}
		\centering
		\includegraphics[width=0.8\textwidth]{../manuscript/figures/aggcluster_random.pdf}
		\caption{Examples of a given hierarchy and its “twin”.}
	\end{figure}
\end{frame}

\begin{frame}{Natural hierarchy vs its twins}

We construct $100$ twin hierarchies for each of the two natural hierarchies and compare their performance.

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P2_natural_vs_pn_h12.pdf}
	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P2_natural_vs_pn_h12.pdf}
	\caption{Average ranks and 95\% confidence intervals for natural hierarchy and its 100 twins, tourism dataset (left) and mortality dataset(right).}
\end{figure}

\end{frame}

\begin{frame}{Best cluster hierarchy vs its twins}

	We construct $100$ twin hierarchies for each of the two best cluster hierarchies and compare their performance.

	\begin{figure}
		\centering
		\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P3_cluster_vs_pc_h12.pdf}
		\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P3_cluster_vs_pc_h12.pdf}
		\caption{Average ranks and 95\% confidence intervals for the best cluster hierarchy and its 100 twins, tourism dataset (left) and mortality dataset(right).}
	\end{figure}

	\end{frame}

\begin{frame}{Disentangling grouping and structure}
	\begin{itemize}
		\item For mortality dataset,  the performances of the natural hierarchy and the best cluster hierarchy are statistically {\color{red} indistinguishable from most of their twins}. {\color{red} ``Structure'' is the primary contributor} to the improvement in forecast accuracy over the two-level hierarchy.
		\item For tourism dataset, both natural and best cluster hierarchies are  statistically indistinguishable from around $30$ of their twins, but significantly better than the remaining $70$.
		\item For tourism dataset, {\color{red} a data-driven method} for grouping time series plays {\color{red} a more prominent role} in forecast improvement. This may be attributed to the noisier nature of bottom level tourism data, suggesting that similar weak signals are strengthened when aggregated.
		\item However, there roughly a {\color{red} 30\% chance that a random twin performs similarly}, once again highlighting that structure is the main contributor to improved forecast performance.
	\end{itemize}
\end{frame}

\begin{frame}{Forecast combination}
	\begin{itemize}
		\item Although it is possible to significantly improve forecast performance through clustering, the {\color{red} selection of the best performing combination} of time series representation, distance measure, and clustering algorithm remains an open question.
		\item We consider {\color{red} averaging forecasts across different hierarchies}, as an alternative to hierarchy selection.
	\end{itemize}
\end{frame}

\begin{frame}{Forecast combination}
	\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P4_benchmarks_h12.pdf}
	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P4_benchmarks_h12.pdf}
	\caption{Average ranks and 95\% confidence intervals for all approaches on tourism dataset(left) and mortality dataset(right) based on MCB test}
	\end{figure}
	\begin{itemize}
		\item On both datasets, forecast combination improves forecast performance compared to any single hierarchy. The improvement on the mortality dataset is more pronounced.
	\end{itemize}
\end{frame}

\section{Conclusions}

\begin{frame}{Conclusions}
	\begin{itemize}
		\item We consider a general framework, incorporating three distinct approaches: cluster hierarchies, permutation hierarchies, and combination hierarchies.
		\item Although adding middle-level time series via clustering or natural hierarchy improve forecast accuracy over two-level hierarchy, {\color{red}the primary contributing factor varies across datasets}. For both datasets, ``structure'' plays an important role.
		\item Our main practical recommendation is to {\color{red}use multiple clustering methods and combine forecasts across these methods using equal weights combination}. This mitigates the uncertainty of selecting the best clustering approach and is shown to significantly outperform all benchmarks across both datasets that we consider.
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Questions and discussions}%{End of presentation}

	\vspace{-0.15in}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.5\textwidth]{end.jpg}
	%	\caption{\normalsize{ US mortality forecasts at age 85$+$ for the period 2018--2027}}
	%	\label{fig:US_totalforecast}
\end{figure}

\Large
\begin{center}
	%\color{blue}Thank you!\\
%	\vspace{-0.1in}
	\begin{itemize}
		\centering
	%	\item[] Any questions/comments/suggestions?
		\vspace{-0.05in}

		\item[] \small\color{purple}Contact email: {\color{blue}   zhangbohan@buaa.edu.cn}

  %\\
%		\color{purple}Research Gate page:  \textit{http://www.researchgate.net/profile/Han\_Li51}
	\end{itemize}
\end{center}

\end{frame}

\begin{frame}[noframenumbering]{References}
	\bibliographystyle{agsm}
	\bibliography{../manuscript/references.bib}		
\end{frame}

\end{document}

### 2024-09-03 R/expr_utils.R
update

@@ -1,68 +1,0 @@
-library(Matrix, quietly = TRUE)
-
-create_new_output <- function() {
-  output <- vector("list", 5)
-  names(output) <- c("representator", "distance", "cluster", "accuracy", "other")
-  output
-}
-
-
-
-output_pre <- function(output) {
-  as_tibble(output) %>% 
-    tidyr::unnest_longer(accuracy, values_to = "accuracy", indices_to = "accuracy_method") %>% 
-    tidyr::unnest_longer(accuracy, values_to = "accuracy", indices_to = "rf_method") %>% 
-    tidyr::unnest_wider(accuracy)
-}
-
-
-
-mcb_ <- function(orig, type, plot_type, target,
-                 file_path, mar = NULL, conf.level) {
-  orig_ <- orig %>%
-    select(method, rmsse, batch) %>%
-    tidyr::nest(rmsse = -c("method")) %>%
-    mutate_at("rmsse", purrr::map, function(g) {
-      g <- g %>% arrange(batch)
-      if (type == "hierarchy") {
-        return(list(sapply(g$rmsse, mean)))
-      } else {
-        return(list(do.call(c, g$rmsse)))
-      }
-    }) %>%
-    tidyr::unnest(rmsse)
-  
-  rmsse <- do.call(cbind, orig_$rmsse)
-  colnames(rmsse) <- orig_$method
-  pdf(file_path, width=8, height = 6)
-  if (plot_type == "custom") {
-    stopifnot(!is.null(mar))
-    par(mar = mar)
-    nemenyi(rmsse, plottype = "vmcb", target = target, conf.level = conf.level)
-  }
-  if (plot_type == "orig") {
-    tsutils::nemenyi(rmsse, plottype = "vmcb", conf.level = conf.level)
-  }
-  dev.off()
-}
-mcb_series_rmsse <- function(orig, rand, name) {
-  orig_rmsse <- orig %>%
-    arrange(batch) %>%
-    pull(rmsse) %>%
-    do.call(c, .)
-  rand_rmsse <-
-    rand %>%
-    arrange(batch, cluster) %>%
-    select(cluster, rmsse, batch) %>%
-    tidyr::nest(rmsse = -"cluster") %>%
-    mutate_at("rmsse", purrr::map, function(g) {
-      g <- g %>% arrange(batch)
-      list(do.call(c, g$rmsse))
-    }) %>%
[…]

### 2024-09-03 R/features.R

@@ -1,5 +1,5 @@
-get_number_series <- function(path, forecast_horizon = 12) {
-  dt <- readRDS(sprintf("%s/eval_cluster.rds", path, forecast_horizon))
+get_number_series <- function(path) {
+  dt <- readRDS(sprintf("%s/eval_cluster.rds", path))
   dt$dtb %>%
     filter(!startsWith(cluster, "permute")) %>%
     filter(!cluster %in% c("", "combination1", "combination2", "base")) %>%

### 2024-09-03 R/run_comb.R

@@ -1,5 +1,6 @@
-
-source("R/utils.R", chdir = T)
+args <- commandArgs(trailingOnly = TRUE)
+path <- args[[1]]
+source("R/utils.R")
 
 compute_comb1 <- function(batch) {
   nls <- Filter(function(x) {
@@ -39,20 +40,19 @@ compute_comb2 <- function(batch) {
   rf[,c(1, (NCOL(rf)-m+1):NCOL(rf))]
 }
 
-for (path in c("mortality")) {
-  files <- list.files(paste0(path, ""))
-  files <- files[startsWith(files, "batch")]
-  output <- list()
-  for (batch in 1:length(files)) {
-    print(sprintf("batch %s ...", batch))
-    store_path <- sprintf("%s/batch_%s.rds", path, batch-1)
-    dt <- readRDS(store_path)
-    comb1 <- compute_comb1(dt)
-    comb2 <- compute_comb2(dt)
-    output[[batch]] <- list(comb1, comb2)
-  }
-  saveRDS(output, sprintf("%s/combination.rds", path))
+
+files <- list.files(paste0(path, ""))
+files <- files[startsWith(files, "batch")]
+output <- list()
+for (batch in 1:length(files)) {
+  print(sprintf("batch %s ...", batch))
+  store_path <- sprintf("%s/batch_%s.rds", path, batch-1)
+  dt <- readRDS(store_path)
+  comb1 <- compute_comb1(dt)
+  comb2 <- compute_comb2(dt)
+  output[[batch]] <- list(comb1, comb2)
 }
+saveRDS(output, sprintf("%s/combination.rds", path))
 
 
 

### 2024-09-03 R/run_eval.R

@@ -1,90 +1,0 @@
-args <- commandArgs(trailingOnly = TRUE)
-path <- args[[1]]
-bfmethod <- "ets"
-
-dt <- readRDS(sprintf("%s/data.rds", path))
-n <- NROW(dt$S)
-m <- NCOL(dt$S)
-time_length <- NROW(dt$data)
-forecast_horizon <- 12
-frequency <- 12
-batch_length <- time_length - 96 - forecast_horizon
-
-
-
-
-hts.eval2 <- function(df, tts, bts, S, combination, base, comb_permute=NULL) {
-  tts <- tts %*% t(S)
-  bts <- bts %*% t(S)
-  
-  df <- add_row(df, representor="", cluster="combination1", 
-                distance="", S=NULL, 
-                rf=list(list(mint=combination[[1]])), other=NULL) 
-  
-  df <- add_row(df, representor = "", cluster="combination2", S=NULL, 
-                distance = "",
-                rf=list(list(mint=combination[[2]])), other=NULL)
-  
-  if (!is.null(comb_permute)) {
-    for (i in 1:100) {
-      df <- add_row(df, representor="", cluster=paste0("permute-combination1-", i),
-                    distance="", S=NULL, rf=list(list(mint=comb_permute[[i]])), other=NULL)
-    }
-  }
-  
-  
-  df[["rmsse"]] <- lapply(iterators::iter(df$rf), function(g) {
-      c <- g[['mint']][, 2:(m+1),drop=FALSE]
-      c <- c %*% t(S)
-      sapply(1:NCOL(c), function(x) { metric.rmsse(tts[,x], c[,x], bts[,x]) })
-  })
-  
-  
-  basef_middle <- furrr::future_map(as.list(iterators::iter(bts[,2:(n-m)], by="column")),
-                                    \(x) as.numeric(f.ets(x, 12, 12)$basef))
-  basef_middle <- do.call(cbind, basef_middle)
-  basef <- cbind(base[,1], basef_middle, base[,2:(m+1)])
-  basef_rmsse <- sapply(1:NCOL(bts),
-                             function(x) {
-                               metric.rmsse(tts[,x], basef[,x], bts[,x])
-                             } )
-  
-  df <- add_row(df, representor="", cluster="base", distance="",
-                S=NULL, rf=NULL, rmsse=list(basef_rmsse))
-  df
-}
-
-
-
-library(dplyr)
[…]

### 2024-09-03 R/run_eval_cluster.R

@@ -1,14 +1,7 @@
 args <- commandArgs(trailingOnly = TRUE)
 path <- args[[1]]
 
-source("R/utils.R", chdir = T)
-dt <- readRDS(sprintf("%s/data.rds", path))
-n <- NROW(dt$S)
-m <- NCOL(dt$S)
-time_length <- NROW(dt$data)
-forecast_horizon <- 12
-frequency <- 12
-batch_length <- time_length - 96 - forecast_horizon + 1
+source("R/utils.R")
 
 
 
@@ -48,15 +41,16 @@ dtb <- NULL
 
 combination <- readRDS(sprintf("%s/combination.rds", path))
 for (batch in 0:(batch_length-1)) {
-  print(sprintf("%s, %s", Sys.time(), batch))
   store_path <- sprintf("%s/batch_%s.rds", path, batch)
   data <- readRDS(store_path)
-  data_tibble <- nl2tibble(data$nl)
+  data_tibble <- nl2tibble(data$nl) %>%
+    filter(!startsWith(cluster, "permute"))
   data_tibble <- hts.eval(data_tibble, data$tts, data$bts, dt$S, combination[[batch+1]], data$basef)
   
   data_tibble <- data_tibble %>% select(-rf, -other) %>% mutate(batch = batch)
   dtb <- rbind(dtb, data_tibble)
 }
+
 
 #' mcb all cluster hierarchies, grouped, base, natural, two-level
 bench_rmsse <- dtb %>%
@@ -68,7 +62,7 @@ bench_rmsse <- dtb %>%
 
 stopifnot(NROW(bench_rmsse) == batch_length * 16)
 
-pdf(sprintf("manuscript/figures/%s/mcb_benchmarks.pdf", path), 8, 6)
+pdf(sprintf("manuscript/figures/%s/Figure4_mcb_benchmarks.pdf", path), 8, 6)
 par(mex = 1.1)
 bench_rmsse %>%
   rowwise() %>%
@@ -90,7 +84,7 @@ bench_rmsse <- dtb %>%
 
 stopifnot(NROW(bench_rmsse) == batch_length * 17)
 
-pdf(sprintf("manuscript/figures/%s/mcb_combination.pdf", path), 8, 6)
+pdf(sprintf("manuscript/figures/%s/Figure12_mcb_combination.pdf", path), 8, 6)
 par(mex = 1.1)
 bench_rmsse %>%
   rowwise() %>%
@@ -109,6 +103,7 @@ methods <- c(
[…]

### 2024-09-03 R/run_nl.R

@@ -1,17 +1,7 @@
 args <- commandArgs(trailingOnly = TRUE)
 path <- args[[1]]
 
-source("R/utils.R", chdir = T)
-
-
-dt <- readRDS(sprintf("%s/data.rds", path))
-n <- NROW(dt$S)
-m <- NCOL(dt$S)
-time_length <- NROW(dt$data)
-forecast_horizon <- 12
-frequency <- 12
-batch_length <- time_length - 96 - forecast_horizon + 1
-
+source("R/utils.R")
 
 REPRESENTORS <- c("ts-dr", "error-dr", "ts.features-dr", "error.features-dr")
 DISTANCES <- rep("euclidean", 4)

### 2024-09-03 R/run_nlf.R

@@ -1,16 +1,7 @@
 args <- commandArgs(trailingOnly = TRUE)
 path <- args[[1]]
 
-source("R/utils.R", chdir = T)
-
-
-dt <- readRDS(sprintf("%s/data.rds", path))
-n <- NROW(dt$S)
-m <- NCOL(dt$S)
-time_length <- NROW(dt$data)
-forecast_horizon <- 12
-frequency <- 12
-batch_length <- time_length - 96 - forecast_horizon + 1
+source("R/utils.R")
 
 for (batch in 0:(batch_length-1)) {
   print(sprintf("%s batch %s ....", Sys.time(), batch))

### 2024-09-03 R/run_nls.R

@@ -1,172 +1,0 @@
-# Calculate average RMSE to compare with mint paper
-nl2tibble <- function(x) {
-  output <- vector("list", 6)
-  names(output) <- c("representor", "cluster", "distance", "S", "rf", "other")
-  
-  for (i in seq_along(x)) {
-    for (n in names(x[[i]])) {
-      if (is.character(x[[i]][[n]])) {
-        output[[n]] <- append(output[[n]], x[[i]][[n]])
-      } else {
-        output[[n]] <- append(output[[n]], list(x[[i]][[n]]))
-      }
-    }
-  }
-  tibble::as_tibble(output)
-}
-
-avg_measure_fn <- function(dt, rf_method = "mint", metric = "rmse") {
-  n <- length(dt$base$rmse[[1]])
-  base <- dt$base %>% pull(metric) %>% 
-    do.call(rbind, .) %>%
-    colMeans()
-  dt$dtb %>% 
-    nest(!!metric := -c("representor", "distance", "cluster")) %>% 
-    mutate_at(metric, purrr::map, function(x){
-      x <- arrange(x, batch)
-      x %>% pull(metric) %>%
-        lapply(function (z) z[[rf_method]]) %>%
-        do.call(rbind, .) %>% colMeans()
-    }) %>%
-    add_row(representor = "", distance = "", cluster="base", !!metric  := list(base)) %>%
-    rowwise() %>%
-    mutate(total = get(metric)[1], bottom = mean(get(metric)[2:n])) %>%
-    arrange(total)
-}
-
-rank_compare <- function(dt, methods_df = NULL, measure="rmse", rf_method = "mint", filter_random = FALSE) {
-  if (is.null(methods_df)) {
-    if (filter_random) {
-      methods_random <- dt$dtb %>% select(representor, distance, cluster) %>% 
-        filter(cluster %in% c("random-15-50", "hcluster-random-50", "random-natural")) %>% 
-        unique()
-    } else {
-      methods_random <- dt$dtb %>% select(representor, distance, cluster) %>% 
-        filter(grepl(cluster, "random", fixed = TRUE)) %>% 
-        unique()
-    }
-    methods_dr <- dt$dtb %>% select(representor, distance, cluster) %>% filter(endsWith(cluster, "-dr")) %>% unique()
-    methods_natural <- dt$dtb %>% select(representor, distance, cluster) %>%
[…]

### 2024-09-03 R/run_permute.R

@@ -4,15 +4,7 @@ path <- args[[1]]
 set.seed(20231019)
 
 
-source("R/utils.R", chdir = T)
-
-dt <- readRDS(sprintf("%s/data.rds", path))
-n <- NROW(dt$S)
-m <- NCOL(dt$S)
-time_length <- NROW(dt$data)
-forecast_horizon <- 12
-frequency <- 12
-batch_length <- time_length - 96 - forecast_horizon + 1
+source("R/utils.R")
 
 REPRESENTORS <- c("ts-dr", "error-dr", "ts.features-dr", "error.features-dr")
 DISTANCES <- rep("euclidean", 4)

### 2024-09-03 R/run_summary_permute.R

@@ -107,7 +107,8 @@ write(sprintf("The best cluster ranks %s in its 100 twins, significantly better 
 
 if (path == "mortality") {
   # calculate combination of twin hierarchies
-  pdf(sprintf("manuscript/figures/%s/comb_vs_pc.pdf", path), 6, 8)
+  pdf(sprintf("manuscript/figures/%s/comb_vs_pc.pdf", path), 8, 6)
+  par(mar=c(4,14,3,2))
   mcb <- mcb_hierarchy_rmsse(
     dt %>% filter(cluster == "combination1"),
     dt %>% filter(startsWith(cluster, "permute-combination1")),

### 2024-09-03 R/utils.R

@@ -147,24 +147,51 @@ hts.nlf <- function(htst, h, frequency) {
     return(htst)
   }
   
-  rfs <- future_map(htst$nl[idx2forecast], function(x) {
-    # two-level hierarchy
-    if (is.null(x$S)) {
-      return(list(
-        rf = reconcile.mint(rbind(rep(1, m), diag(m)), htst$basef, htst$resid)
-      ))
+  smat2sstr <- function(S) {
+    S_str <- c()
+    for (i in 1:NROW(S)) {
+      S_str <- c(S_str, do.call(paste0, as.list(S[i,])))
     }
-    mid_ts <- htst$bts %*% t(as.matrix(x$S))
-    mid_forecasts <- 
-      map(as.list(iterators::iter(mid_ts, by="column")), \(x) f.ets(x, h=h, frequency=frequency))
-    S <- rbind(rep(1, m), as.matrix(x$S), diag(m))
-    basef <- cbind(htst$basef[,1,drop=FALSE],
-                   do.call(cbind, map(mid_forecasts, "basef")),
-                   htst$basef[,2:NCOL(htst$basef)])
-    resid <- cbind(htst$resid[,1,drop=FALSE],
-                   do.call(cbind, map(mid_forecasts, "resid")),
-                   htst$resid[,2:NCOL(htst$resid)])
-    list(rf=reconcile.mint(S, basef, resid), basef=do.call(cbind, map(mid_forecasts, "basef")))
+    S_str
+  }
+  
+  S <- do.call(rbind, lapply(htst$nl[idx2forecast], function(g) { g$S }))
+  S_str <- smat2sstr(as.matrix(S))
+  fcasts <- list()
+  
+  for (idx in seq_along(S_str)) {
+    if (S_str[idx] %in% names(fcasts)) {
+      next
+    } else {
+      fcasts[[S_str[idx]]] <- S[idx, ]
+    }
+  }
+  S_toforecast <- do.call(rbind, fcasts)
+  allts <- htst$bts %*% t(S_toforecast)
+  bf <- future_map(as.list(iterators::iter(allts, by = "column")),
+                   \(x) f.ets(x, h, frequency))
+  names(bf) <- names(fcasts)
+  
+  rfs <- map(htst$nl[idx2forecast], function(nl) {
+    
+    S_nl <- NULL
+    if (!is.null(nl$S)) {
[…]

### 2024-09-03 manuscript/figures/aggcluster_random.tex
update

@@
 
-    \node(A1)[draw, circle, minimum size=0.2cm]{};
-    \node(B1)[draw, circle, minimum size=0.2cm, below left=0.5cm of A1]{};
+    \node(B1)[draw, circle, minimum size=0.2cm]{};
+    \node(A1)[draw, circle, minimum size=0.2cm, above right=0.3cm and 1.2cm of B1]{};
+    \node(F1)[draw, circle, minimum size=0.2cm, below left=0.55cm and 0.5cm of B1]{1};
+    \node(H1)[draw, circle, minimum size=0.2cm, below right=0.55cm and 0.5cm of B1]{2};
 
-    \node(D1)[draw, circle, minimum size=0.2cm, below left=0.5cm of B1]{};
-    \node(F1)[draw, circle, minimum size=0.2cm, below left=0.5cm of D1]{1};
-    \node(G1)[draw, circle, minimum size=0.2cm, below right=0.5cm of D1]{2};
-    \node(E1)[draw, circle, minimum size=0.2cm, right=0.8727922cm of G1]{3};
-    \node(C1)[draw, circle, minimum size=0.2cm, right=0.8727922cm of E1]{4};
+    \node(E1)[draw, circle, minimum size=0.2cm, below right=0.3cm and 1.2cm of A1]{};
+    \node(I1)[draw, circle, minimum size=0.2cm, below left=0.55cm and 0.5cm of E1]{3};
+    \node(G1)[draw, circle, minimum size=0.2cm, below=0.4cm of E1]{4};
+    \node(K1)[draw, circle, minimum size=0.2cm, below right=0.55cm and 0.5cm of E1]{5};
 
-    \draw (A1) -- (B1) -- (D1) -- (F1);
-    \draw (D1) -- (G1);
-    \draw (B1) -- (E1);
-    \draw (A1) -- (C1);
+    \draw (A1) -- (B1) -- (F1);
+    \draw (H1) -- (B1);
+    \draw (A1) -- (E1) -- (G1);
+    \draw (K1) -- (E1) -- (I1);
 
-    \node(A)[draw, circle, minimum size=0.2cm, right=5cm of A1]{};
-    \node(B)[draw, circle, minimum size=0.2cm, below left=0.5cm of A]{};
+    \node(B)[draw, circle, minimum size=0.2cm, right=6cm of B1]{};
+    \node(A)[draw, circle, minimum size=0.2cm, above right=0.3cm and 1.2cm of B]{};
+    \node(F)[draw, circle, minimum size=0.2cm, below left=0.55cm and 0.5cm of B]{2};
 
-    \node(D)[draw, circle, minimum size=0.2cm, below left=0.5cm of B]{};
-    \node(F)[draw, circle, minimum size=0.2cm, below left=0.5cm of D]{4};
-    \node(G)[draw, circle, minimum size=0.2cm, below right=0.5cm of D]{3};
-    \node(E)[draw, circle, minimum size=0.2cm, right=0.8727922cm of G]{1};
-    \node(C)[draw, circle, minimum size=0.2cm, right=0.8727922cm of E]{2};
+    \node(H)[draw, circle, minimum size=0.2cm, below right=0.55cm and 0.5cm of B]{4};
 
-    \draw (A) -- (B) -- (D) -- (F);
-    \draw (D) -- (G);
-    \draw (B) -- (E);
-    \draw (A) -- (C);
+    \node(E)[draw, circle, minimum size=0.2cm, below right=0.3cm and 1.2cm of A]{};
+    \node(I)[draw, circle, minimum size=0.2cm, below left=0.55cm and 0.5cm of E]{1};
+    \node(G)[draw, circle, minimum size=0.2cm, below=0.4cm of E]{5};
+    \node(K)[draw, circle, minimum size=0.2cm, below right=0.55cm and 0.5cm of E]{3};
+
+    \draw (A) -- (B) -- (F);
+    \draw (H) -- (B);
+    \draw (A) -- (E) -- (G);
+    \draw (K) -- (E) -- (I);
 

### 2024-09-03 manuscript/manuscript.tex
update

@@
 \usepackage{enumitem}
+% \usepackage[pagewise]{lineno}
 
@@
 
-  \author[label1]{Bohan Zhang\corref{cor1}}
-  \address[label1]{School of Economics and Management, Beihang University, Beijing, China}
-  \ead{zhangbohan@buaa.edu.cn}
-  \cortext[cor1]{Corresponding author.}
-  \author[label2]{Anastasios Panagiotelis}
-  \address[label2]{The University of Sydney Business School, NSW 2006, Australia}
-  \author[label3]{Han Li}
-  \address[label3]{Department of Economics, The University of Melbourne, VIC 3010, Australia}
+%   \author[label1]{Bohan Zhang\corref{cor1}}
+%   \address[label1]{School of Economics and Management, Beihang University, Beijing, China}
+%   \ead{zhangbohan@buaa.edu.cn}
+%   \cortext[cor1]{Corresponding author.}
+%   \author[label2]{Anastasios Panagiotelis}
+%   \address[label2]{The University of Sydney Business School, NSW 2006, Australia}
+%   \author[label3]{Han Li}
+%   \address[label3]{Department of Economics, The University of Melbourne, VIC 3010, Australia}
 
@@
 
-    %the dynamics between ``grouping'' and ``structure'', which lead to an improved understanding of forecast reconciliation.\\
-
   \end{abstract}
@@
   Forecast reconciliation \sep
-  Hierarchical time series \sep
   Clustering \sep
   Hierarchy construction \sep
-  Forecast combination
+  Forecast combination \sep
+  Mortality \sep
+  Tourism flows
   \end{keyword}
@@
 Section~\ref{sec:conclusion} concludes this paper with discussions on the findings and outlines future research directions.
-Data and code for reproducing the results in this paper are available at \url{https://github.com/AngelPone/project_hierarchy}.
+% Data and code for reproducing the results in this paper are available at \url{https://github.com/AngelPone/project_hierarchy}.
 
@@
 We consider features of both the raw time series and the in-sample forecast error as representations.
-After filtering out the features that are constant across all series, we select $56$ features.\footnote{The list and descriptions of features are available in the online GitHub repository.} These time series features are calculated by the \code{tsfeatures} (\citealp{tsfeatures}) package in R.
+After filtering out the features that are constant across all series, we select $56$ features calculated by the \code{tsfeatures} (\citealp{tsfeatures}) package in R.
 %have been applied in several feature-based forecasting studies, \textit{e.g.}, \cite{montero-mansoFFORMAFeaturebasedForecast2020}.
@@
 
+% \section*{Acknowledgements}
+
+% Bohan Zhang is supported by the international joint doctoral education fund of Beihang University.
+Han Li is supported by the Australian Research Council Discovery Projects funding scheme (DP220100090)
+
 \clearpage 
@@
 
-%\section*{Acknowledgements}
-
-%Bohan Zhang is supported by the international joint doctoral education fund of Beihang University.
-
+% \nolinenumbers
 \begingroup

### 2024-09-03 Revision1/R1.tex
update

--- 2024-04-07 manuscript/manuscript.tex
@@
 
-  \author[label1]{Bohan Zhang\corref{cor1}}
-  \address[label1]{School of Economics and Management, Beihang University, Beijing, China}
-  \ead{zhangbohan@buaa.edu.cn}
-  \cortext[cor1]{Corresponding author.}
-  \author[label2]{Anastasios Panagiotelis}
-  \address[label2]{The University of Sydney Business School, NSW 2006, Australia}
-  \author[label3]{Han Li}
-  \address[label3]{Department of Economics, The University of Melbourne, VIC 3010, Australia}
+  % \author[label1]{Bohan Zhang\corref{cor1}}
+  % \address[label1]{School of Economics and Management, Beihang University, Beijing, China}
+  % \ead{zhangbohan@buaa.edu.cn}
+  % \cortext[cor1]{Corresponding author.}
+  % \author[label2]{Anastasios Panagiotelis}
+  % \address[label2]{The University of Sydney Business School, NSW 2006, Australia}
+  % \author[label3]{Han Li}
+  % \address[label3]{Department of Economics, The University of Melbourne, VIC 3010, Australia}
 
@@
 A limitation in the overwhelming majority of forecast reconciliation studies is that the structure of the hierarchy is taken as \textit{given}.
-This structure usually includes \textit{bottom level series}, an overall aggregate or \textit{top level series}, with various aggregation schemes used to construct \textit{middle level series}.
+This structure usually includes \textit{bottom level series}, an overall aggregate or \textit{top level series}, with various aggregation schemes used to construct \textit{middle-level series}.
 Typically, middle levels are formed according to inherent attributes of the bottom-level series, such as geographical location, gender, product category, travel purpose, and others.
@@
 Moreover, a predefined natural hierarchy may not always exist in hierarchical settings, underscoring the importance of a hierarchical construction framework for forecasting purposes.
-It should be noted that very little attention has been paid to whether middle level series can be constructed in a way that leads to further improvements in forecast accuracy relative to a given natural hierarchy.
-To the best of our knowledge, only \cite{pangHierarchicalElectricityTime2018}, \cite{liForecastReconciliationApproach2019}, \cite{pangHierarchicalElectricityTime2022}, and \cite{matteraImprovingOutofSampleForecasts2023} have attempted to \textit{construct} middle level series in a data-driven way which ultimately improved forecast accuracy.
-However, all of these works use time series clustering to construct hierarchies in a manner that is somewhat ad hoc.
+It should be noted that very little attention has been paid to whether middle-level series can be constructed in a way that leads to further improvements in forecast accuracy relative to a given natural hierarchy.
+{\color{purple}To the best of our knowledge, only \cite{yang2017reconciling}, \cite{pangHierarchicalElectricityTime2018}, \cite{liForecastReconciliationApproach2019}, \cite{pangHierarchicalElectricityTime2022}, \cite{cini2023graph}, and \cite{matteraImprovingOutofSampleForecasts2023} have attempted to \textit{construct} middle-level series in a data-driven way which ultimately improved forecast accuracy.
+} However, all of these works use time series clustering to construct hierarchies in a manner that is somewhat ad hoc.
 Our work conducts a more thorough investigation of issues faced when  constructing hierarchical structures in forecast reconciliation.
@@
 
-\begin{researchquestion} In terms of forecast performance, can the use of middle level series lead to improvement compared to a two-level hierarchy (consisting of only top and bottom time series)?
+\begin{researchquestion} In terms of forecast performance, can the use of middle-level series lead to improvement compared to a two-level hierarchy (consisting of only top and bottom time series)?
 If so, is it possible to construct hierarchies in a data-driven way that leads to further improvements in forecast accuracy?
@@
 %\begin{researchquestion}
-%    If the use of middle level series in the ``natural'' hierarchy can lead to improvement in forecast accuracy, is it possible to construct hierarchies in a data-driven way that leads to further improvements in forecast accuracy?
+%    If the use of middle-level series in the ``natural'' hierarchy can lead to improvement in forecast accuracy, is it possible to construct hierarchies in a data-driven way that leads to further improvements in forecast accuracy?
 %\end{researchquestion}
@@
 The models used to obtain base forecasts and the reconciliation method are fixed throughout the experiments.
-Using both empirical datasets, as well as a simulation study, we find evidence that constructing hierarchies via clustering can lead to improved forecasting performance, although the optimal clustering method depends on the dataset characteristics.% \textbf{We use the same base forecasting model and reconciliation method through this paper}.
+Using both empirical datasets, as well as a simulation study, we find evidence that constructing hierarchies via clustering can lead to improved forecasting performance, although the optimal clustering method depends on the dataset as well as the base forecasting and reconciliation method.% \textbf{We use the same base forecasting model and reconciliation method through this paper}.
 
@@
 Indeed, clustering methods may only work in so far as they generate a larger number of base forecasts.
-This argument would be consistent with the interpretation of reconciliation as a forecast combination of ``direct'' and ``indirect'' forecasts (\citealp{hollymanUnderstandingForecastReconciliation2021}), since more middle-level series implies a greater number of indirect forecasts in the combination.
-This leads to our second research question:
+{\color{purple}This argument would be consistent with the interpretation of reconciliation as a forecast combination of ``direct'' and ``indirect'' forecasts (\citealp{hollymanUnderstandingForecastReconciliation2021, di2024forecast}), since more middle-level series implies a greater number of indirect forecasts in the combination.} This leads to our second research question:
 
 \begin{researchquestion}
-    Should the improved accuracy of clustering-based methods be attributed to grouping together similar time series, or to the structure of the hierarchy? %including the number of middle level series?
+    Should the improved accuracy of clustering-based methods be attributed to grouping together similar time series, or to the structure of the hierarchy? %including the number of middle-level series?
 \end{researchquestion}
@@
 
-Note that forecast combination here differs from that of \cite{hollymanUnderstandingForecastReconciliation2021}, in that our approach averages not only different coherent forecasts, but also across hierarchies with completely different middle level series.
+Note that forecast combination here differs from that of \cite{hollymanUnderstandingForecastReconciliation2021}, in that our approach averages not only different coherent forecasts, but also across hierarchies with completely different middle-level series.
 This is possible since only coherent bottom and top level forecasts are averaged and evaluated.
@@
 Section~\ref{sec:conclusion} concludes this paper with discussions on the findings and outlines future research directions.
-Data and code for reproducing the results in this paper are available at \url{https://github.com/AngelPone/project_hierarchy}.
+Data and code for reproducing the results in this paper are available at \url{https://github.com/Purity3-cyber/constructing_hierarchies}.
 
@@
 
-Hierarchical data can be characterized as being made up of bottom level series and their aggregates.
+Hierarchical data can be characterised as being made up of bottom level series and their aggregates.
 In general, we consider a hierarchy with $n$ time series stacked into a vector $\boldsymbol{y}_t$.
-Let $\boldsymbol{b}_t$ denote the $m$ bottom level series, $\boldsymbol{a}_t$ denote the top level series, and $\boldsymbol{c}_t$ denote $k$ middle level series.
-The top level and bottom level will be common to all hierarchies we consider, and are augmented by middle level series.
-These middle level series can be formed according to attributes of the time series or in a data-driven fashion using time series clustering.
+Let $\boldsymbol{b}_t$ denote the $m$ bottom level series, $\boldsymbol{a}_t$ denote the top level series, and $\boldsymbol{c}_t$ denote $k$ middle-level series.
+The top level and bottom level will be common to all hierarchies we consider, and are augmented by middle-level series.
+These middle-level series can be formed according to attributes of the time series or in a data-driven fashion using time series clustering.
 The series are linked through an $(m+k+1)\times m$ summing matrix
-
 %$\boldsymbol{S}$, which can be decomposed into an identity matrix $\boldsymbol{I}_m$ and two aggregation matrices $\boldsymbol{A}$ and $\boldsymbol{C}$ consisting of $0$ and $1$, such that, 
@@
   \end{bmatrix}  \boldsymbol{b}_t = \begin{bmatrix}
-      \boldsymbol{a}_t \\ \boldsymbol{c}_t \\\boldsymbol{b}_t
+      {\color{purple}a_t} \\ \boldsymbol{c}_t \\\boldsymbol{b}_t
   \end{bmatrix},
 \]
-where, $\boldsymbol{C}$ consists of zeros and ones that encode the aggregation, \textit{i.e.}, $c_{ij}=1$ if bottom level series $j$ is included in middle level series $i$, and zero otherwise.
+where, $\boldsymbol{C}$ consists of zeros and ones that encode the aggregation, \textit{i.e.}, $c_{ij}=1$ if bottom level series $j$ is included in middle-level series $i$, and zero otherwise.
 The top level series aggregates all bottom levels, \textit{i.e.}, $\boldsymbol{A} = \mathbf{1}_{1\times m}$, which is a row of ones.
@@
 For the purposes of this paper, all forecasting is carried out as a two-step process.
-First, so-called \textit{base} forecasts are produced for all series in the hierarchy and stacked into an $n$-vector $\hat{\bm{y}}$, where subscripts are suppressed for brevity.
+First, so called \textit{base} forecasts are produced for all series in the hierarchy and stacked into an $n$-vector $\hat{\bm{y}}$, where subscripts are suppressed for brevity.
 For base forecasts, we use the Exponential Smoothing (ETS) method \citep{ForecastingExponentialSmoothing}, implemented using the \code{forecast} (\citealp{forecast}) package in {R} (\citealp{R}).
@@
 
-The base forecasts generated in this first step, do not have the property that bottom level forecasts add up to forecasts of the aggregates, \textit{i.e.}, they are \textit{incoherent}.
+The base forecasts generated in this first step, do not have the property that bottom level forecasts add up to forecasts of the aggregates , \textit{i.e.}, they are \textit{incoherent}.
 Therefore, forecast reconciliation is used as a post-forecasting step to ensure coherence of forecasts for all series in the hierarchy.
 In general, reconciliation takes the form of projecting the base forecasts as
+\vspace{-0.1in}
 \[
-    \tilde{\boldsymbol{y}} = \boldsymbol{S}(\boldsymbol{S}'\boldsymbol{W}_h^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}_h^{-1}\hat{\boldsymbol{y}},
+  \color{purple}  \tilde{\boldsymbol{y}} = \boldsymbol{S}(\boldsymbol{S}'\boldsymbol{W}^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}^{-1}\hat{\boldsymbol{y}},
+  \vspace{-0.15in}
 \]
-where $\tilde{\boldsymbol{y}}$ are the \textit{reconciled} forecasts and $\boldsymbol{W}_h$ is the covariance matrix of $h$-step-ahead forecast errors.
-For reconciliation, we use the MinT method \citep{wickramasuriyaOptimalForecastReconciliation2019}, which involves plugging in a shrinkage estimator for $\boldsymbol{W}_h$.
-Although alternatives were considered, including approaches that assume $\boldsymbol{W}_h$ is diagonal or an identity matrix \citep{hyndmanOptimalCombinationForecasts2011}, this choice has little impact on our main conclusions.
+where $\tilde{\boldsymbol{y}}$ are the \textit{reconciled} forecasts and $\boldsymbol{W}$ is the covariance matrix of base forecast errors.
+{\color{purple}For reconciliation, we use the MinT method \citep{wickramasuriyaOptimalForecastReconciliation2019} implemented using the \texttt{FoReco} (\citealp{FoReco}) package in R, which involves plugging in a shrinkage estimator for $\boldsymbol{W}$.}Although alternatives were considered, including approaches that assume $\boldsymbol{W}$ is diagonal or an identity matrix \citep{hyndmanOptimalCombinationForecasts2011}, this choice has little impact on our main conclusions.
+{\color{purple}Despite the importance of non-negativity in practical scenarios such as demand forecasting, our study does not enforce non-negative forecasts for two reasons.
+First, the proportion of negative forecasts is minimal in our applications (0.25\% in the tourism dataset and 0.2\% in the mortality dataset).
+Second, introducing non-negativity constraints would significantly increase the computational cost of our experiments.
+It should be noted that the framework proposed in our paper could be applied using any reconciliation approach, including those that guarantee non-negative forecasts.}
 
@@
 
-To the best of our knowledge, four studies have attempted to improve forecast accuracy in a reconciliation setting by constructing middle levels of the hierarchy using time series clustering.
-\cite{pangHierarchicalElectricityTime2018} detect consumption patterns of electricity smart meter data based on X-means clustering algorithm, while \cite{pangHierarchicalElectricityTime2022} propose several alternative clustering methods to group similar electricity and solar power time series.
+%To the best of our knowledge,
+
+%four studies
+
+{\color{purple}Only a handful of studies have attempted to improve forecast accuracy in a reconciliation setting by constructing middle levels of the hierarchy using time series clustering.
+\cite{yang2017reconciling} employ spatial $k$-means clustering methods to assign distributed photovoltaics  to their nearest transmission grid bus locations for reconciliation purposes.} \cite{pangHierarchicalElectricityTime2018} detect consumption patterns of electricity smart meter data based on X-means clustering algorithm, while \cite{pangHierarchicalElectricityTime2022} propose several alternative clustering methods to group similar electricity and solar power time series.
 \cite{liForecastReconciliationApproach2019} apply agglomerative hierarchical clustering to cause-of-death time series, and
 \cite{matteraImprovingOutofSampleForecasts2023} utilize Partition Around Medoids algorithms to unveil underlying structures in stock price indexes.
-However, these studies are limited in scope as they focus on a few  clustering techniques. 
+{\color{purple} \cite{cini2023graph} took an end-to-end approach from which clusters can be extracted together with hierarchical forecasts.}
+However, these studies are limited in scope as they focus on a small number of  clustering techniques. 
 %\todo{Should we move to intro?}
@@
 % Considering the impracticality of exploring every conceivable time series representation, we focus on four key ones: raw time series without any transformation (hereafter referred to as ``time series''), in-sample one-step-ahead forecast error, features of time series, and features of in-sample one-step-ahead forecast error.
-Our first candidate for the representation is raw time series itself, due to its simplicity and broad applicability.
+{\color{purple} Our first candidate for the representation, due to its simplicity and broad applicability, is the time series itself without any processing or additional features.
+We refer to this as the raw time series.}
 %However, a crucial element contributing to the success of the MinT method lies in estimating the covariance matrix of base forecast errors based on in-sample one-step-ahead forecast error. 
-We also consider the in-sample one-step-ahead forecast error as a representation of the time series, since a key step in MinT reconciliation is to estimate the $\boldsymbol{W}_h$ matrix.
+We also consider the in-sample one-step-ahead forecast error as a representation of the time series, since a key step in MinT reconciliation is to estimate the $\boldsymbol{W}$ matrix.
 %to examine how the structure within the error series influences reconciliation performance.
@@
 To address this concern, low dimension summaries of ``features'' can be considered.
-Features have been used in the context
+Features have been used in the context {\color{purple} of}
 %Features, widely employed in capturing time series characteristics, play a pivotal role in various time series applications, including 
@@
 %have been applied in several feature-based forecasting studies, \textit{e.g.}, \cite{montero-mansoFFORMAFeaturebasedForecast2020}.
-To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation.
+{\color{purple}To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the clustering-based hierarchy construction process.\footnote{We acknowledge that in-sample forecast error and time series features have been used in the computation of base forecasts or in the reconciliation process \citep[see][]{wickramasuriyaOptimalForecastReconciliation2019}.}}
+%To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation.
 %\sout{These representations allow us to gain insights into the diverse aspects of hierarchical time series data}.
@@
 %Unlike $k$-means which employs the mean vector of samples as the cluster center, $k$-medoids selects one observation within each cluster as the center. 
-Following the recommendation of \cite{PartitioningMedoidsProgram1990}, we determine the optimal number of clusters using the average silhouette width (ASW), which is a commonly used index in cluster validation \citep[see \textit{e.g.},][]{shutaywi2021silhouette}.
+Following the recommendation of \cite{PartitioningMedoidsProgram1990}, we determine the optimal number of clusters using the average silhouette width (ASW), which is a commonly used index in cluster validation \citep[see \textit{e.g.}, ][]{shutaywi2021silhouette}.
 %ASW assesses the quality of clustering results by measuring the proximity of samples within a cluster compared to neighboring clusters.
@@
 
-Agglomerative hierarchical clustering initializes each observation in its own cluster, and then merges the nearest two clusters in a stepwise fashion until all observations form a single cluster.
+Agglomerative hierarchical clustering initialises each observation in its own cluster, and then merges the nearest two clusters in a stepwise fashion until all observations form a single cluster.
 We employ Ward's linkage (\citealp{murtaghWardHierarchicalAgglomerative2014a}) which defines the nearest clusters as those that minimize the increase in within-cluster variance at each step.
-Applying hierarchical clustering to $m$ bottom-level series results in a binary hierarchical tree with ($2m-1$) nodes, all of which are retained as middle level series.
-
-\begin{figure}[h!]
-    \centering
-    \vspace{0.2in}
-    \includegraphics[width=0.46\textwidth]{figures/pamcluster.pdf}
+Applying hierarchical clustering to $m$ bottom-level series results in a binary hierarchical tree with ($2m-1$) nodes, all of which are retained as middle-level series.
+
+\begin{figure}[h!]
+    \centering
+  %  \vspace{-0.1in}
+    \includegraphics[width=0.46\textwidth]{../manuscript/figures/pamcluster.pdf}
     \hspace{1cm}
-    \includegraphics[width=0.46\textwidth]{figures/aggcluster.pdf}
+    \includegraphics[width=0.46\textwidth]{../manuscript/figures/aggcluster.pdf}
     \caption{\label{fig:cluster_example}Example clustering results of two clustering algorithms.
@@
 \end{figure}
-Figure~\ref{fig:cluster_example} illustrates two examples of hierarchies generated by $k$-medoids and agglomerative clustering algorithms, on the left and right panels respectively.
-The corresponding two-level hierarchy would have four bottom-level series and one top-level series.
+
+{\color{purple}Figure~\ref{fig:cluster_example} illustrates two examples of hierarchies generated by $k$-medoids and agglomerative clustering algorithms, on the left and right panels respectively.
+The corresponding two-level hierarchy would have five bottom-level series and one top-level series.
 % \sout{These examples highlight the distinct behaviors of the two algorithms.}
-Note that, $k$-medoids constructs a simple hierarchy with a single middle level, while hierarchical clustering generates multiple nested middle levels. 
-In general, $k$-medoids produces a hierarchy with fewer middle levels and middle level series compared to hierarchical clustering.
+Note that, $k$-medoids constructs a simple hierarchy with a single middle level, while hierarchical clustering generates multiple nested middle levels.} 
+In general, $k$-medoids produces a hierarchy with fewer middle levels and middle-level series compared to hierarchical clustering.
 As the number of bottom-level series increases, these differences become increasingly pronounced, with potential implications for forecast reconciliation.
-
-In summary, we employ 12 time series clustering approaches which are derived from combinations of four time series representations, two distance measures, and two clustering algorithms.
-The names and details of these approaches are listed in Table~\ref{tab:P3_methods}.
-Note that all methods using DTW, have either the raw time series or forecast errors as representations, since DTW is not compatible with time series features.
-\\
-
 \begin{table}[h!]
@@
 
+In summary, we employ 12 time series clustering approaches which are derived from combinations of four time series representations, two distance measures, and two clustering algorithms.
+The names and details of these approaches are listed in Table~\ref{tab:P3_methods}.
+Note that all methods using DTW, have either the raw time series or forecast errors as representations, since DTW is not compatible with time series features.
+{\color{purple}In addition to these 12 clustering approaches, we also include a grouped hierarchy structure combining all aggregation constraints in matrix $\boldsymbol{S}$, which we refer to as ``grouped''.}
+
 %The four time series representations need to perform dimension reduction when using Euclidean distance. 
@@
 Additionally, each regional-level series is divided by four travel purposes.
-Overall, this dataset comprises a total of $555$ time series with $304$ of those at the bottom level.
+Overall, this dataset comprises a total of {\color{purple}$525$} unique time series with $304$ of those at the bottom level.
 In the case of tourism data, the first two or three letters of the series name indicate geographical zones or regions, and the last three denote travel purposes.
@@
 Comparing the datasets to one another, the mortality dataset generally exhibits stronger seasonality and trend, whereas the tourism dataset displays greater volatility.
-Table~\ref{tab:features} summarizes three features of each dataset, with larger values indicating more ``signal'' relative to ``noise''.
+Table~\ref{tab:features} summarises three features of each dataset, with larger values indicating more ``signal'' relative to ``noise''.
 These are: the Holt Winters seasonal smoothing parameter; the lag 12 autocorrelation coefficient; and the strength of trend measured as the proportion of variance explained by the trend component in an STL decomposition.
-Table~\ref{tab:features} supports the conclusions made by visualizing the time series of the data, which is that the tourism data are noisier and less regular with respect to trend and seasonality.
+Table~\ref{tab:features} supports the conclusions made by visualizing the time series of the data, which is that the tourism data are noisier and less regular with respect to trend and seasonality.\\
 
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/tourism.pdf}
-    \vspace{-0.35in}
+    \includegraphics[width=\textwidth]{../manuscript/figures/tourism.pdf}
+  %  \vspace{-0.35in}
     \caption{Visualization of selected time series from the tourism dataset.
@@
     \label{fig:tourism}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \vspace{-0.2in}\includegraphics[width=\textwidth]{figures/mortality.pdf}
-    \vspace{-0.35in}
-    \caption{{Visualization of selected time series from the death count dataset.} ``GR113-019'', ``GR113-051'',  ``GR113-063'', and ``GR113-085'' denote ``Malignant neoplasms'', ``Parkinson disease'', ``All other forms of chronic ischemic heart disease'', and ``Asthma'', respectively.}
-    \vspace{-0.2in}
-    \label{fig:mortality}
 \end{figure}
@@
 
+\begin{figure}[h!]
+    \centering
+    \vspace{0.2in}
+    %\vspace{-0.2in}
+    \includegraphics[width=\textwidth]{../manuscript/figures/mortality.pdf}
+    %\vspace{-0.35in}
+    \caption{{Visualization of selected time series from the death count dataset.} ``GR113-019'', ``GR113-051'',  ``GR113-063'', and ``GR113-085'' denote ``Malignant neoplasms'', ``Parkinson disease'', ``All other forms of chronic ischemic heart disease'', and ``Asthma'', respectively.}
+   % \vspace{-0.2in}
+    \label{fig:mortality}
+\end{figure}
+
 \subsection{Evaluation of forecast accuracy}
@@
 To measure forecast accuracy, we first calculate the Root Mean Squared Scaled Error (RMSSE, \citealp{makridakisM5AccuracyCompetition2022}), for each series.
-Letting $\breve y_t$ be any forecast of $y_t$, we define RMSSE as
+{\color{purple}We define RMSSE of the $h$-step-ahead forecasts, produced using the $j$-th method and conditioning on $T$ observations, of the $i$-th time series as
 
 \[
-RMSSE = \sqrt{\frac{\frac{1}{h}\displaystyle\sum_{t=T+1}^{T+h}(y_t-\breve y_{t})^2}{\frac{1}{T-12}\displaystyle\sum_{t=13}^T (y_t - y_{t-12})^2}} .
+RMSSE_{j, i} = \sqrt{\frac{\frac{1}{h}\displaystyle\sum_{t=T+1}^{T+h}(y_{t, i}-\breve y_{t, j, i})^2}{\frac{1}{T-12}\displaystyle\sum_{t=13}^T (y_{t, i} - y_{t-12, i})^2}},
 \]
-
-RMSSE is symmetric, independent of the data scale, and thus suitable for evaluating hierarchical forecasts (\citealp{athanasopoulosEvaluationHierarchicalForecasts2023}).
+where $\breve y_{t,j,i}$ be forecast of the $i$-th time series, generated by the $j$-th method, at time $t$.} RMSSE is symmetric, independent of the data scale, and thus suitable for evaluating hierarchical forecasts (\citealp{athanasopoulosEvaluationHierarchicalForecasts2023}).
 It should be noted that the denominator of our RMSSE measure slightly differs from that used in \cite{makridakisM5AccuracyCompetition2022}; we replace the naive forecast, with the seasonal naive forecast since the time series in our applications exhibit monthly seasonality.
 As a single measure of accuracy, we take the average RMSSE across all series.
-Since we will be comparing hierarchies with different structures (thus different middle level series), this average only includes top and bottom level series, both of which are guaranteed to be present in all hierarchies.
+Since we will be comparing hierarchies with different structures (thus different middle-level series), this average only includes top and bottom level series, both of which are guaranteed to be present in all hierarchies.
 
@@
 This test is based on the average ranks of different approaches across all evaluation windows and controls for multiple comparisons.
+{\color{purple} We implement the MCB test using the \code{tsutils} (\citealp{tsuitls}) R package}.
 
@@
     Natural & 0.6913 & 0.7501 \\ 
+    \color{purple}Grouped & 0.7068 & 0.8091\\
     TS-EUC-ME & 0.6939 & 0.7528 \\ 
@@
 However,  not even the best clustering method is significantly more accurate than the two-level hierarchy based on the MCB test.
-%Across both datasets, the methods based on hierarchical clustering tend to outperform those based on $k$-medoids clustering, highlighting the importance of choosing an appropriate clustering technique.
-
-\begin{figure}[h!]
-    \centering
-    %\vspace{-0.1in}
-    \includegraphics[width=0.45\textwidth]{figures/hierarchy_rmsse/tourism/P3_mcb_benchmarks_h12.pdf}
-    \includegraphics[width=0.45\textwidth]{figures/hierarchy_rmsse/mortality/P3_mcb_benchmarks_h12.pdf}
-    \caption{\label{fig:P3_mcb_benchmark}Average ranks and 95\% confidence intervals for twelve cluster hierarchies and three benchmarks on tourism dataset (left) and mortality dataset (right) based on MCB test.}
+{\color{purple}It should also be noted that the performance of the grouped hierarchy is much poorer compared to individual clustering hierarchies across both datasets.
+We suspect this may be a consequence of having too large a hierarchy, resulting in difficulty in estimating the covariance matrix $\boldsymbol{W}$ used as an input to MinT (\citealp{pritulargaStochasticCoherencyForecast2021}).}%Across both datasets, the methods based on hierarchical clustering tend to outperform those based on $k$-medoids clustering, highlighting the importance of choosing an appropriate clustering technique.
+
+\begin{figure}[h!]
+    \centering
+    \vspace{0.1in}
+    \includegraphics[width=0.45\textwidth]{../manuscript/figures/tourism/mcb_benchmarks.pdf}
+    \includegraphics[width=0.45\textwidth]{../manuscript/figures/mortality/mcb_benchmarks.pdf}
+    \caption{\label{fig:P3_mcb_benchmark}Average ranks and 95\% confidence intervals for {\color{purple} thirteen} cluster hierarchies and three benchmarks on tourism dataset (left) and mortality dataset (right) based on the MCB test.}
 \end{figure}
@@
 The tourism dataset, as shown in Figure~\ref{fig:tourism}, predominately contains volatile and noisy bottom-level time series with weak trend and seasonality (see also in  Table~\ref{tab:features}).
-Arguably, creating new middle-level time series in this context helps elucidate the underlying pattern which can not be easily captured by bottom-level base forecasting models due to a low signal-to-noise ratio.
-On the other hand, the bottom-level series in mortality dataset exhibit stronger trend and seasonality patterns, meaning that the addition of middle-level series is less beneficial.
+Arguably, creating new middle-level time series in this context helps elucidate the underlying pattern which can not be easily captured by bottom-level base forecasting models due to a low signal to noise ratio.
+On the other hand, the bottom-level series in mortality dataset exhibit stronger trend and seasonality patterns, meaning that the addition of middle-level series is less beneficial.\\
 
@@
 Table~\ref{tab:P3_number_series} summarizes the average number of middle-level series across all evaluation windows for natural, $k$-medoids, and hierarchical clustering hierarchies.
-Interestingly, the natural hierarchy shows competitive accuracy compared to hierarchical clustering methods on both datasets, despite having fewer middle-level series.
-However, it should be noted that natural hierarchies may not always exist.
 Regarding the superiority of any specific representation or distance metric, no consistent findings emerge.
 It shows that while it is possible to improve forecast accuracy via clustering, the performance of different clustering methods largely depends on the specific data in consideration.
+Interestingly, the natural hierarchy shows competitive accuracy compared to hierarchical clustering methods on both datasets, despite having fewer middle-level series.
+{\color{purple} The competitiveness of the natural hierarchy may be explained by factors other than similar series being combined together.
+For example, the natural hierarchy encodes prior information about the series, regarding common underlying shocks and dynamics for neighboring regions or similar causes of death.
+These may be more clearly detected and modeled in aggregate series.} However, it should be noted that natural hierarchies may not always exist.
+{\color{purple} For completeness, we further evaluate the forecast accuracy of middle-level time series, defined according to the natural hierarchy.
+For clustering-based hierarchies, we use a bottom-up approach.
+The results are consistent with our findings and are provided in the supplementary materials.
+}
 
@@
 To assess whether ``grouping'' or ``structure'' has relatively more importance, we consider a procedure based on permutation.
-For ease of exposition, we will describe this procedure for the natural hierarchy, although it is applied equally to hierarchies where middle level series are constructed using clustering algorithms.
+For ease of exposition, we will describe this procedure for the natural hierarchy, although it is applied equally to hierarchies where middle-level series are constructed using clustering algorithms.
 First, the structure of the natural hierarchy is kept fixed.
-A new ``twin'' hierarchy is constructed by randomly permuting the bottom level series\footnote{This can also be achieved by shuffling the columns of $\boldsymbol{C}$.}.
+A new ``twin'' hierarchy is then constructed by randomly permuting the bottom level series\footnote{This can also be achieved by shuffling the columns of $\boldsymbol{C}$.}.
 An example is shown in Figure~\ref{fig:aggcluster_random}.
+{\color{purple} In this figure, we begin with the hierarchy on the left hand side and shuffle the leaves (the nodes on the bottom labelled 1--5) to obtain the hierarchy on the right hand side.
+Note that none of the middle levels from the hierarchy on the left are retained.
+Instead, where the hierarchy on the left has a middle-level variable formed by adding node 1 and node 2, the corresponding node on the right would have a middle level that adds node 2 and node 4.
+%These middle level nodes are both shaded grey in the figure.
+If nodes are aggregated on the basis of similarity, this will no longer hold in the permuted hierarchy.
+For example, in the left hand side hierarchy, node 1 and node 2 may correspond to similar time series.
+However, after permutation, the same structure may no longer add similar time series (\textit{i.e.} node 2 and node 4 may not be similar).
+In this way, permutation retains the structure of a hierarchy while removing the effect of grouping similar time series together.}
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/aggcluster_random.pdf}
+    \includegraphics[width=0.9\textwidth]{../manuscript/figures/aggcluster_random.pdf}
 \caption{\label{fig:aggcluster_random}Examples of a given hierarchy and its ``twin''. }
@@
 The same convention applies to the labels of the $y$-axis for Figures \ref{fig:P3_tourism_c_vs_pc},  \ref{fig:simu_P3_benchmarks}, and \ref{fig:P4_a_vs_pa}.}.
-The figure is adjusted so that the gray band is around the 95\% confidence interval for the natural hierarchy rather than the best performing twin.
-Any hierarchies whose confidence interval overlaps with the gray zone is not significantly better or worse than the natural hierarchy.
-
-\begin{figure}[h!]
-    \centering
-\includegraphics[width=0.47\textwidth]{figures/hierarchy_rmsse/tourism/P2_natural_vs_pn_h12.pdf}
-    \centering    \includegraphics[width=0.47\textwidth]{figures/hierarchy_rmsse/mortality/P2_natural_vs_pn_h12.pdf}
+The figure is adjusted so that the grey band is around the 95\% confidence interval for the natural hierarchy rather than the best performing twin.
+Any hierarchies whose confidence interval overlaps with the grey zone is not significantly better or worse than the natural hierarchy.
+
+\begin{figure}[h!]
+    \centering
+\includegraphics[width=0.47\textwidth]{../manuscript/figures/tourism/natural_vs_pn.pdf}
+    \centering    \includegraphics[width=0.47\textwidth]{../manuscript/figures/mortality/natural_vs_pn.pdf}
     \caption{\label{fig:P2_tourism}Average ranks and 95\% confidence intervals for natural hierarchy and its $100$ twins, tourism dataset (left) and mortality dataset(right).}
@@
     \centering
-    \includegraphics[width=0.47\textwidth]{figures/hierarchy_rmsse/tourism/P3_cluster_vs_pc_h12.pdf}
-    \includegraphics[width=0.47\textwidth]{figures/hierarchy_rmsse/mortality/P3_cluster_vs_pc_h12.pdf}
+    \includegraphics[width=0.47\textwidth]{../manuscript/figures/tourism/cluster_vs_pc.pdf}
+    \includegraphics[width=0.47\textwidth]{../manuscript/figures/mortality/cluster_vs_pc.pdf}
     %best performing cluster hierarchy
@@
 %The experiments in Section~\ref{sec:clustering} show the difficulty of constructing a smart hierarchy through clustering. 
-The main conclusion of Section~\ref{sec:permutation} is that hierarchies with more middle level series improve forecast accuracy due to structure rather than grouping.
+The main conclusion of Section~\ref{sec:permutation} is that hierarchies with more middle-level series improve forecast accuracy due to structure rather than grouping.
 In so far as grouping may be a factor, this may be due to aggregating similar weak signals into stronger signals.
@@
 Time series are generated that form clear clusters according to their trend and seasonality.
-These are then aggregated into middle level series, based on the known characteristics of each time series.
+These are then aggregated into middle-level series, based on the known characteristics of each time series.
 The purpose of this is two-fold.
@@
 \centering
-\includegraphics[width=\textwidth]{figures/simu_example.pdf}
+\includegraphics[width=\textwidth]{../manuscript/figures/simu_example.pdf}
 \caption{\label{fig:simu_emps}Example time series for each cluster in the simulation experiments.}
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{figures/simu_pca.pdf}
+    \includegraphics[width=0.65\textwidth]{../manuscript/figures/simu_pca.pdf}
     \caption{\label{fig:simu_pca}Visualization of the generated time series in the simulation experiments.}
@@
 
-Various schemes for constructing middle level series can be considered and are summarized in Table~\ref{tab:7}.
-Middle level series can be constructed according to the value of the $\alpha$ parameter, leading to three clusters, or according to whether the series has a trend or no trend, leading to two clusters.
+Various schemes for constructing middle-level series can be considered and are summarised in Table~\ref{tab:7}.
+middle-level series can be constructed according to the value of the $\alpha$ parameter, leading to three clusters, or according to whether the series has a trend or no trend, leading to two clusters.
 In Table~\ref{tab:7}, these are referred to as Cluster-trend1 and Cluster-trend2 respectively.
-Middle level series can also be formed on the basis of seasonality (Cluster-season), leading to two clusters, or according to both trend and seasonality leading to six clusters (Cluster-trend-season).
+middle-level series can also be formed on the basis of seasonality (Cluster-season), leading to two clusters, or according to both trend and seasonality leading to six clusters (Cluster-trend-season).
 
@@
     \centering
-    \vspace{0.1in}\includegraphics[width=0.7\textwidth]{figures/hierarchy_rmsse/simulation/P3_mcb.pdf}
+    \vspace{0.1in}\includegraphics[width=0.7\textwidth]{../manuscript/figures/simulation/P3_mcb.pdf}
    \vspace{-0.1in}
@@
     \centering
-\includegraphics[width=0.8\textwidth]{figures/hierarchy_rmsse/simulation/P3_c_vs_pc.pdf}
+\includegraphics[width=0.8\textwidth]{../manuscript/figures/simulation/P3_c_vs_pc.pdf}
     \vspace{-0.1in}
@@
 \[
-  \tilde{\boldsymbol{y}}_{T+h}^{\text{comb}} = \frac{1}{l} \sum_{j=1}^l \tilde{\boldsymbol{y}}_{T+h}^j.
+  \tilde{\boldsymbol{y}}_{T+h}^{\text{comb}} = \frac{1}{l} \sum_{j=1}^l \tilde{\boldsymbol{y}}_{T+h}^j,
 \] 
+{\color{purple}where $l$ is the number of hierarchies considered in the forecast combination analysis.}
 We note that this average can only be carried out using series that are common to all hierarchies, in our case, the top and bottom levels.
 In this case, since all elements of the average are coherent, any linear combination of these forecasts will also be coherent.
+\\
 
@@
 
-\begin{table}
+\begin{table}[h!]
     \centering
@@
 
-% \clearpage
-
 Table~\ref{tab:P4_RMSSE} presents the accuracy in terms of average RMSSE across all evaluation windows for both datasets.
@@
     %\vspace{-0.2in}
-    \includegraphics[width=0.45\textwidth]{figures/hierarchy_rmsse/tourism/P4_benchmarks_h12.pdf}
-    \includegraphics[width=0.45\textwidth]{figures/hierarchy_rmsse/mortality/P4_benchmarks_h12.pdf}
+    \includegraphics[width=0.45\textwidth]{../manuscript/figures/tourism/mcb_combination.pdf}
+    \includegraphics[width=0.45\textwidth]{../manuscript/figures/mortality/mcb_combination.pdf}
     \caption{Average ranks and 95\% confidence intervals for all approaches on tourism dataset(left) and mortality dataset(right) based on MCB test.}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{figures/hierarchy_rmsse/mortality/P4_average_vs_pa_h12.pdf}
+    \includegraphics[width=0.6\textwidth]{../manuscript/figures/mortality/comb_vs_pc.pdf}
     \vspace{-0.1in}\caption{\label{fig:P4_a_vs_pa} Average ranks and 95\% confidence intervals for combination of twelve cluster hierarchies and its $100$ random twins on mortality dataset based on MCB test.}
@@
 %\newpage
-
-% \subsection{Results on simulation dataset}
-
-% Table~\ref{}, Figures~\ref{} and We apply these analyses on the simulation dataset, leading to
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.8\textwidth]{figures/hierarchy_rmsse/simulation/P4.pdf}
-%     \caption{}
-%     \label{fig:}
-% \end{figure}
 
@@
 
-This naturally begs the question, of why adding more middle level series can improve forecast performance.
+This naturally begs the question, of why adding more middle-level series can improve forecast performance.
 We devise a method that keeps the hierarchy fixed while permuting the bottom level series, yielding ``twin'' hierarchies.
-The bottom-level series that aggregate to a single middle level series are thus chosen at random.
+The bottom-level series that aggregate to a single middle-level series are thus chosen at random.
 Across different datasets and settings, an overwhelmingly large number of twins, perform not significantly worse, or even better, than a hierarchy selected using clustering.
-This suggests that the improved forecast performance arises not from grouping similar times series together, but rather from features related to the structure of the hierarchy, \textit{e.g.} the larger number of middle level series.
+This suggests that the improved forecast performance arises not from grouping similar times series together, but rather from features related to the structure of the hierarchy, \textit{e.g.} the larger number of middle-level series.
 We find similar results from a simulation study where clusters are predefined.
@@
 This mitigates the uncertainty of selecting the best clustering approach and is shown to significantly outperform all benchmarks across both datasets that we consider.
-%One could also extend this idea to averaging over random twins, although we note that any averaging approach incurs a computation cost in needing to obtain base forecasts for more middle level series.
+%One could also extend this idea to averaging over random twins, although we note that any averaging approach incurs a computation cost in needing to obtain base forecasts for more middle-level series.
 One could also extend this idea to averaging over random twins.
@@
 Also, our results are based on cross-sectional data, this could be extended to explore temporal (\citealp{athanasopoulosForecastingTemporalHierarchies2017}) and cross-temporal hierarchies (\citealp{girolimettoCrosstemporalProbabilisticForecast2023a}).
-Finally, more work could be carried out to understand whether some middle levels contribute more to forecast accuracy than others, and accordingly ``pruning'' the less useful middle level series.
-
-\clearpage 
-\newpage
-
-%\section*{Acknowledgements}
-
-%Bohan Zhang is supported by the international joint doctoral education fund of Beihang University.
+Finally, more work could be carried out to understand whether some middle levels contribute more to forecast accuracy than others, and accordingly ``pruning'' the less useful middle-level series.\\
+
+% \section*{Acknowledgements}
+
+% Bohan Zhang is supported by the international joint doctoral education fund of Beihang University.
+
+%\clearpage 
+%\newpage
 

### 2024-09-03 Revision1/supplementary.tex
update

\documentclass[12pt]{article}
\usepackage{booktabs, multicol, graphicx}
\usepackage{setspace}
\setstretch{1.2}
\usepackage[a4paper]{geometry}
\geometry{hscale=0.7,vscale=0.75,centering}

\begin{document}

\section*{Supplementary material}

%\begin{center}
%\setlength{\unitlength}{2cm}
%{\Large Supplementary materials}
%\end{center}
This supplementary material provides results on forecast performance of middle-level series defined by the natural hierarchy. For cluster hierarchies and two-level hierarchies where these middle-level series do not exist, we compute the middle-level forecasts using a bottom-up strategy. The average RMSSE based on different approaches for the tourism and mortality datasets are presented in Table~\ref{tab:P3_rmsse}. The MCB test results on middle-level series are shown in Figure~\ref{fig:mcb_middle}.\\

\begin{table}[h!]
\renewcommand\thetable{S.1}
    \centering
\caption{\label{tab:P3_rmsse}Performance of all approaches in terms of average RMSSE across all evaluation windows on both datasets. Column-wise minimum values are displayed in bold. ``Middle'' refers to middle-levels defined by the natural hierarchy. }
\vspace{0.1in}
\begin{tabular}{lcccccc}
\toprule
 Approach & \multicolumn{3}{c}{tourism} & \multicolumn{3}{c}{mortality} \\ 
 \cmidrule(lr){2-4} \cmidrule(lr){5-7}
 & Top & Middle & Bottom & Top & Middle & Bottom \\ \midrule
 Base & \textbf{0.869} & 0.732 & 0.694 & 0.761 & 0.744 & 0.753 \\
Two-level & 0.923 & 0.730 & 0.694 & 0.736 & 0.735 & 0.753 \\
Natural & 0.876 & \textbf{0.717} & 0.691 & 0.738 & 0.732 & 0.750 \\
Grouped & 0.831  & 0.721 & 0.706 & 0.798 & 0.783 & 0.750 \\
TS-EUC-ME & 0.900 & 0.727 & 0.693 & 0.728 & 0.735 & 0.753 \\
ER-EUC-ME & 0.918 & 0.727 & 0.693 & 0.741 & 0.740 & 0.753 \\
TSF-EUC-ME & 0.907 & 0.728 & 0.693 & 0.739 & 0.741 & 0.755 \\
ERF-EUC-ME & 0.909 & 0.729 & 0.694 & 0.733 & 0.738 & 0.753 \\
TS-EUC-HC & 0.874 & 0.719 & 0.692 & 0.740 & 0.730 & 0.754 \\
ER-EUC-HC & 0.890 & 0.719 & 0.691 & 0.746 & 0.732 & 0.751 \\
TSF-EUC-HC & 0.881 & 0.719 & 0.690 & 0.744 & 0.739 & 0.751 \\
TS-DTW-ME & 0.909 & 0.729 & 0.693 & \textbf{0.726} & 0.734 & 0.753 \\
TS-DTW-HC & 0.878 & 0.719 & 0.691 & 0.731 & 0.730 & 0.750 \\
ER-DTW-ME & 0.911 & 0.729 & 0.694 & 0.733 & 0.739 & 0.753 \\
ER-DTW-HC & 0.878 & 0.719 & 0.691 & 0.748 & 0.736 & 0.753 \\ 
Combination & 0.893 & 0.721 & \textbf{0.690} & 0.730 & \textbf{0.724} & \textbf{0.725} \\
\bottomrule\end{tabular}

\end{table}

\begin{figure}[h!]
\renewcommand\thefigure{S.1}
    \centering
    %\vspace{-0.1in}
    \includegraphics[width=0.5\textwidth]{../manuscript/figures/tourism/mcb_combination_middle.pdf}
    \includegraphics[width=0.5\textwidth]{../manuscript/figures/mortality/mcb_combination_middle.pdf}
    \caption{\label{fig:mcb_middle}Average ranks and 95\% confidence intervals for all approaches on middle level of tourism dataset (left) and mortality dataset (right) based on MCB test.}
\end{figure}

\end{document}

### 2024-09-03 simulation/simu.R

@@ -2,7 +2,7 @@ library(foreach)
 library(forecast)
 library(dplyr)
 library(ggplot2)
-source("R/reconciliation.R")
+source("R/utils.R")
 
 set.seed(43)
 

### 2024-09-03 simulation/simu_summary.R

@@ -1,8 +1,7 @@
 rm(list = ls())
 dt <- readRDS("simulation/simulation.rds")
 library(dplyr)
-source("R/metrics.R")
-source("R/expr_utils.R")
+source("R/utils.R")
 
 forecast_horizon <- 1
 
@@ -58,7 +57,7 @@ test <- function(mat, name) {
 }
 
 # natural hierarchy vs its counterpart
-pdf("manuscript/figures/hierarchy_rmsse/simulation/P3_c_vs_pc.pdf", width = 10, height = 5)
+pdf("manuscript/figures/simulation/P3_c_vs_pc.pdf", width = 10, height = 5)
 par(mar=c(4,18,3,2))
 natural_ <- evaluate_idx(best_hierarchy)
 natural_test <- test(cbind(natural_, evaluate_idx(permute_best)), "Cluster-trend-season")
@@ -127,7 +126,7 @@ calculate_comb <- function() {
 print("Evaluating comb ...")
 comb_rmsse <- calculate_comb()
 # # 51
-pdf("manuscript/figures/hierarchy_rmsse/simulation/P4.pdf", width = 8, height = 6)
+pdf("manuscript/figures/simulation/P4.pdf", width = 8, height = 6)
 comb_test <- test(comb_rmsse, "Combination")
 dev.off()
 
@@ -144,11 +143,11 @@ clusters_tbl <- data.frame(
 ) %>%
   arrange(rmsse) %>%
   mutate(rmsse = round(rmsse, digits = 2)) %>%
-  write.csv("manuscript/figures/hierarchy_rmsse/simulation/simulation_methods.csv")
+  write.csv("manuscript/figures/simulation/simulation_methods.csv")
 
   
 
-pdf("manuscript/figures/hierarchy_rmsse/simulation/P3_mcb.pdf", width = 8, height = 4)
+pdf("manuscript/figures/simulation/P3_mcb.pdf", width = 8, height = 4)
 tsutils::nemenyi(cluster_mat, plottype = "vmcb")
 dev.off()
 

### 2024-09-08 submission/supplementary.tex
update

--- 2024-09-03 Revision1/supplementary.tex
@@
 
-%\begin{center}
-%\setlength{\unitlength}{2cm}
-%{\Large Supplementary materials}
-%\end{center}
 This supplementary material provides results on forecast performance of middle-level series defined by the natural hierarchy.
@@
 
-\begin{table}[h!]
+\begin{table}[!h]
 \renewcommand\thetable{S.1}
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \renewcommand\thefigure{S.1}
     \centering
-    %\vspace{-0.1in}
-    \includegraphics[width=0.5\textwidth]{../manuscript/figures/tourism/mcb_combination_middle.pdf}
-    \includegraphics[width=0.5\textwidth]{../manuscript/figures/mortality/mcb_combination_middle.pdf}
+    \includegraphics[width=0.5\textwidth]{../figures/FigureS1_tourism_mcb_combination_middle.jpg}
+    \includegraphics[width=0.5\textwidth]{../figures/Figure12_mortality_mcb_combination.jpg}
     \caption{\label{fig:mcb_middle}Average ranks and 95\% confidence intervals for all approaches on middle level of tourism dataset (left) and mortality dataset (right) based on MCB test.}

### 2024-09-08 R/features.R

@@ -1,3 +1,4 @@
+library(dplyr)
 get_number_series <- function(path) {
   dt <- readRDS(sprintf("%s/eval_cluster.rds", path))
   dt$dtb %>%
@@ -14,7 +15,7 @@ get_number_series <- function(path) {
 
 rbind(get_number_series("mortality"), get_number_series("tourism")) %>%
   tidyr::pivot_wider(values_from = "S", names_from = "path") %>%
-  write.csv("manuscript/figures/n_series.csv")
+  write.csv("figures/Table4.csv")
 
 
 
@@ -47,4 +48,4 @@ tourism_features %>%
   group_by(features, path) %>%
   summarise(value = mean(value)) %>%
   tidyr::pivot_wider(names_from = "path", values_from = "value") %>%
-  write.csv("manuscript/figures/features.csv")
+  write.csv("figures/Table2.csv")

### 2024-09-08 R/run_eval_cluster.R

@@ -62,7 +62,7 @@ bench_rmsse <- dtb %>%
 
 stopifnot(NROW(bench_rmsse) == batch_length * 16)
 
-pdf(sprintf("manuscript/figures/%s/Figure4_mcb_benchmarks.pdf", path), 8, 6)
+jpeg(sprintf("figures/Figure4_%s_mcb_benchmarks.jpg", path), height = 600/1.3, width = 800/1.3)
 par(mex = 1.1)
 bench_rmsse %>%
   rowwise() %>%
@@ -84,7 +84,7 @@ bench_rmsse <- dtb %>%
 
 stopifnot(NROW(bench_rmsse) == batch_length * 17)
 
-pdf(sprintf("manuscript/figures/%s/Figure12_mcb_combination.pdf", path), 8, 6)
+jpeg(sprintf("figures/Figure12_%s_mcb_combination.jpg", path), height = 600/1.3, width = 800/1.3)
 par(mex = 1.1)
 bench_rmsse %>%
   rowwise() %>%
@@ -111,7 +111,7 @@ csv_ <- bench_rmsse %>% rowwise() %>%
   ungroup() %>%
   group_by(method, representor, distance, cluster) %>% summarise(rmsse = mean(rmsse))
 csv_[match(methods, csv_$method), c("method", "rmsse")] %>%
-  write.csv(sprintf("manuscript/figures/%s/Table3_Table8.csv", path))
+  write.csv(sprintf("figures/Table3_%s_Table8.csv", path))
 
 csv_ %>% filter(representor != "") %>%
   arrange(rmsse) -> csv_
@@ -128,7 +128,7 @@ bench_rmsse <- dtb %>%
   ungroup() %>%
   select(method, batch, top, middle, bottom)
 
-pdf(sprintf("manuscript/figures/%s/supply_figure_mcb_combination_middle.pdf", path), 8, 6)
+jpeg(sprintf("figures/FigureS1_%s_mcb_combination_middle.jpg", path), height = 600/1.3, width = 800/1.3)
 par(mex = 1.1)
 bench_rmsse %>%
   select(method, batch, middle) %>%
@@ -143,7 +143,7 @@ bench_rmsse <- bench_rmsse %>%
   summarise(across(c(top, middle, bottom), \(x) mean(x)))
 
 bench_rmsse[match(methods, bench_rmsse$method),] %>%
[…]

### 2024-09-08 R/run_summary_permute.R

@@ -53,7 +53,7 @@ acc <- function() {
 
 dt <- acc()
 
-pdf(sprintf("manuscript/figures/%s/natural_vs_pn.pdf", path), width = 8, height = 6)
+jpeg(sprintf("figures/Figure6_%s_natural_vs_pn.jpg", path), height = 600/1.3, width = 800/1.3)
 par(mar=c(4,14,3,2))
 natural_hierarchy <- mcb_hierarchy_rmsse(
   dt %>% filter(cluster == "natural"),
@@ -71,10 +71,10 @@ sig_worse <-
 
 write(sprintf("Natural ranks %s in its 100 twins, significantly better than %s, significantly worse than %s",
               rank, sig_better, sig_worse),
-      sprintf("manuscript/figures/%s/natural_vs_pn.txt", path))
+      sprintf("figures/%s_natural_vs_pn.txt", path))
 
 
-pdf(sprintf("manuscript/figures/%s/cluster_vs_pc.pdf", path), 8, 6)
+jpeg(sprintf("figures/Figure7_%s_cluster_vs_pc.jpg", path), height = 600/1.3, width = 800/1.3)
 par(mar=c(4,14,3,2))
 best_ <- readRDS(sprintf("%s/eval_cluster.rds", path))$best_
 best_name <- method_name(best_$representor, best_$distance, best_$cluster)
@@ -101,13 +101,13 @@ sig_worse <- length(which(itl2 < itl1[best_name]))
 
 write(sprintf("The best cluster ranks %s in its 100 twins, significantly better than %s, significantly worse than %s",
               rank, sig_better, sig_worse),
-      sprintf("manuscript/figures/%s/cluster_vs_pc.txt", path))
+      sprintf("figures/%s_cluster_vs_pc.txt", path))
 
 
 
 if (path == "mortality") {
   # calculate combination of twin hierarchies
-  pdf(sprintf("manuscript/figures/%s/comb_vs_pc.pdf", path), 8, 6)
+  jpeg(sprintf("figures/Figure13_%s_comb_vs_pc.jpg", path), height = 600/1.3, width = 800/1.3)
   par(mar=c(4,14,3,2))
   mcb <- mcb_hierarchy_rmsse(
     dt %>% filter(cluster == "combination1"),

### 2024-09-08 simulation/simu.R

@@ -2,9 +2,11 @@ library(foreach)
 library(forecast)
 library(dplyr)
 library(ggplot2)
-source("R/utils.R")
 
 set.seed(43)
+
+
+
 
 cl <- parallel::makeCluster(8)
 doParallel::registerDoParallel(cl)

### 2024-09-08 simulation/simu_summary.R

@@ -1,9 +1,14 @@
 rm(list = ls())
 dt <- readRDS("simulation/simulation.rds")
 library(dplyr)
-source("R/utils.R")
+source("simulation/utils.R")
 
 forecast_horizon <- 1
+
+
+metric.rmsse <- function(obs, pred, hist) {
+  sqrt(mean((obs - pred)^2) / mean(diff(hist, 12)^2))
+}
 
 rmsse <- function(pred, obs, hist) {
   obs <- cbind(rowSums(obs), obs)
@@ -57,7 +62,7 @@ test <- function(mat, name) {
 }
 
 # natural hierarchy vs its counterpart
-pdf("manuscript/figures/simulation/P3_c_vs_pc.pdf", width = 10, height = 5)
+jpeg("figures/Figure11.jpg", width = 600 *1.4, height = 300*1.4)
 par(mar=c(4,18,3,2))
 natural_ <- evaluate_idx(best_hierarchy)
 natural_test <- test(cbind(natural_, evaluate_idx(permute_best)), "Cluster-trend-season")
@@ -96,40 +101,6 @@ calculate_base <- function() {
   }))
 }
 
-calculate_comb <- function() {
-  if (file.exists("simulation/comb.rds")) {
-    return(readRDS("simulation/comb.rds"))
-  }
-  method_idx <- c(2, 303, 304, 305)
-  all_rmsse <- NULL
-  for (i in seq_along(dt$acc)) {
-    print(i)
-    tts <- t(dt$series[[i]][, 133:144])
-    bts <- t(dt$series[[i]][, 1:132])
-    f_orig_ <- apply(simplify2array(dt$acc[[i]][method_idx]), c(1, 2), mean)
-    f_permu_ <- lapply(1:100, function(j) {
-      apply(simplify2array(
-        dt$acc[[i]][c(permute_best[j], permute_trend[j], permute_season[j], permute_trend_exis[j])]
-      ), c(1, 2), mean)
-    })
-
-    rmsse_orig <- rmsse(f_orig_, tts, bts)
-    rmsse_permu_ <- sapply(iterators::iter(f_permu_), function(g) {
-      rmsse(g, tts, bts)
-    })
-    all_rmsse <- rbind(all_rmsse, c(rmsse_orig, rmsse_permu_))
-  }
-  saveRDS(all_rmsse, "simulation/comb.rds")
-  all_rmsse
-}
-
-print("Evaluating comb ...")
-comb_rmsse <- calculate_comb()
[…]

### 2024-09-08 Revision1/responseletter.tex

\documentclass{article}
    \usepackage[export]{adjustbox}
	\usepackage[english]{babel}%required allways
	\usepackage{booktabs, makecell}	%required for bookstyle tables, without these the tables will have to be redrawn
 \renewcommand\theadfont{\bfseries}
 \renewcommand{\cellalign}{cl}
	\usepackage{bm}
	\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{chngcntr}
	\usepackage{tikz}		% required for linestyle graphics
 %   \usepackage{tikz,pgfplots}	
	\usepackage{enumerate}
	\usepackage{float} 		% required for example and excercise styles
   % \usepackage{chicago}
	\usepackage[round]{natbib}
    \usepackage{epstopdf}
    \usepackage[toc,page]{appendix} % required for adding appendice
	\usepackage[intlimits]{amsmath}%provide option intlimits to
    \usepackage{amsfonts}
							% give boundaries of limits above/below integral sign
	\usepackage{rotating} 	%required for rotated tables
	\usepackage{graphicx} 	%required for including external graphics files
\usepackage{ae,aecompl}
\usepackage{amsmath,amsthm,amssymb,enumerate,mathrsfs}
        \numberwithin{equation}{section}
    \usepackage{epsfig}
\usepackage[pdftex]{hyperref}
	\usepackage{caption}
    \usepackage{multirow}
    \usepackage{epsfig}    %required to put multiple figures under one caption
    \usepackage{lscape}    % change the layout of single page to landscape
    \usepackage{caption}
  %  \usepackage{subcaption}%required to add sub-captions
    \usepackage{subfig}
    \usepackage{setspace}
    \usepackage{url}
    \usepackage{multirow}
    \usepackage{multicol}
    \usepackage{bigstrut}
    \usepackage{natbib}
    \usepackage{bbm}
		\usepackage[a4paper]{geometry}
    \doublespacing
		\geometry{hscale=0.7,vscale=0.75,centering}
\def\R{{\rm I} \negthinspace {\rm R}}
\renewcommand{\baselinestretch}{1.50}\normalsize
\setlength\parindent{0pt}
\theoremstyle{plain}
\newtheorem{ro}{Corollary}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}

\theoremstyle{definition}
\newtheorem{de}{Definition}
\newtheorem{lm}{Lemma}
\newtheorem{exm}{Example}
\theoremstyle{remark}
\newtheorem{Alg}{Algorithm}
\newtheorem{rem}{Remark}
\bibliographystyle{agsm}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue}
%\doublespace
\let\code=\texttt
\begin{document}

\begin{center}
%\maketitle
\setlength{\unitlength}{2cm}

{\Large Responses to Associate Editor and Referee's Comments \\[%
0pt]
\vspace{0.02in}
\large\textbf{Constructing hierarchical time series through clustering: \\Is there an optimal way for forecasting?}}
\end{center}

\noindent We greatly appreciate the time and effort the Associate Editor and the two referees have dedicated to reviewing our paper. The comments received are extremely insightful and have largely benefited the manuscript. We have revised the manuscript based on these comments and provided the following point-by-point response to the Associate Editor and two anonymous referees.
\vspace{-0.4in}
%\section*{\large Major points}
%We are glad that you find the topic important and interesting. 
%\medskip
%\medskip
\section*{Comments from the Associate Editor}
%\vspace{-0.1in}

\textit{The two reviewers find the paper well-written and a good fit for IJF - I agree. They provide some useful comments that will help the authors improve their manuscript, including the provision of additional consideration in the middle levels of the hierarchy in terms of hierarchy construction but also evaluation and a better description of the permutation algorithm. Overall, I think the comments can be fully addressed and I am looking forward to receiving a revised version of the paper.}

\medskip
\noindent \textbf{Authors' response:}
We express our gratitude to the Associate Editor for your guidance on the revision of this manuscript. In response to the suggestions and comments from the referees, we have conducted major and thorough revisions of the manuscript. Please see below a summary of the major changes we have made. %\\
\vspace{-0.03in}
\begin{itemize}
    \item We have enhanced the literature review by including more relevant studies in the discussion, thereby emphasizing the contribution of our research. This addresses Referee 1's comments. 
    \item We have conducted additional analyses on the performance of our methods on the intermediate levels defined by the natural hierarchies, where we used a bottom-up approach for clustering-based hierarchies. This addresses Referee 1's comments.

    \item We have included a grouped hierarchy structure, which combines the aggregation constraints of all the clustering-based hierarchies. This addresses Referee 1's comments.

    \item We have added a more detailed description of the permutation method in Section 4 of the manuscript. This addresses Referee 2's comments.

    \item We have included additional discussions in Section 3.3, on the competitive performance of the natural hierarchy in our studies. This addresses Referee 2's comments.

    \item {We have made our code and data available in a public GitHub repository to enable replication of the results presented in the manuscript. The repository can be accessed at: \url{https://github.com/Purity3-cyber/constructing_hierarchies}.}

\end{itemize}

In summary, the paper has greatly benefited from the insightful comments received. We hope that, the incorporation of these changes will now make the revised version suitable for \textit{International Journal of Forecasting}.

\clearpage 
\newpage

\section*{Comments from Referee 1}

% We appreciate your comments, and we are pleased that the referee acknowledged the significant challenges addressed in our research. Following the referee's guidance, we provide further clarifications and discussions which have made the paper more cohesive. We have also conducted additional analysis and comparisons, thereby emphasizing the contributions of the paper. Below, we present point-by-point responses to address your comments.

\subsection*{General considerations}

\textit{The paper presents an interesting analysis on the use of different cluster algorithms to enhance the forecast accuracy for hierarchical time series. The manuscript is generally clear and well written. My major comments will follow the order in which the topics are treated in the different sections of the manuscript. Then, a list of (possible) typos and minor corrections is brought to the authors’ attention.}

\medskip
\noindent \textbf{Response:} We appreciate the comments, and we are pleased that the referee finds the topic interesting and our paper well-written. Following the referee's guidance, we conduct further analyses and discussions which have made the paper more comprehensive. Below, we present point-by-point responses to address your comments.

\subsection*{Major Comments}
\textbf{Comment 1:} \textit{Page 2, rows 54--56. I would suggest the authors to include among the following citations to papers that make use of cluster methods to build a hierarchy also \cite{yang2017reconciling}
 and \cite{cini2023graph}.}

%Yang et al. (2017) and Cini et al. (2023).

\medskip
\noindent \textbf{Response:} {Thank you for this suggestion. In the revised manuscript, we have added the two citations in the relevant paragraph. } \\

\textbf{Comment 2:} \textit{Page 4, row 15. I would suggest adding ``, and \citealp{di2024forecast}''
immediately after ``\citealp{hollymanUnderstandingForecastReconciliation2021}''}.

\medskip
\noindent \textbf{Response:} {Thank you for this comment. In the revised manuscript, we have added the suggested citation in the relevant paragraph. } \\

\textbf{Comment 3:} \textit{Page 6, rows 50--57 and page 7, rows 1--6/40. The subscript $h$ is used to denote only the $h$-step-ahead covariance matrix $\boldsymbol{W}_h$ and not for the base forecasts $\hat{\boldsymbol{y}}$ or the reconciled forecasts $\tilde{\boldsymbol{y}}$. I would recommend keeping a uniform notation and omit the subscript in $\boldsymbol{W}_h$ since it is not the purpose of the authors to evaluate forecasts at different horizons.}

\medskip

\noindent \textbf{Response:} {Thank you for this suggestion. We have now omitted the subscript $h$ in $\boldsymbol{W}_h$.}\\

\textbf{Comment 4:} \textit{Page 7, row 1. The authors should use consistent R package citations throughout the paper: the package forecast for obtaining base forecasts was cited on page 6 row 37, the package tsfeatures for extracting features was cited on page 7 row 56, and the package cluster for clustering was cited on page 8 row 28. It would be appropriate to cite the package used for reconciliation.}

\medskip

\noindent \textbf{Response:}  {We appreciate this comment. In this paper, the \code{FoReco} package (\citealp{FoReco}) has been used for reconciliation. We have now cited the package and included it in the reference list. } \\

\textbf{Comment 5:} \textit{Page 7, row 58 and page 8 row 1. I would suggest that the authors clarify the claim ``To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation''. With regard to the in-sample forecast error in the reconciliation context, it is well-known that these are used in many studies to estimate the covariance matrix, as previously discussed (page 7, rows 38--40 ) and in \cite{wickramasuriyaOptimalForecastReconciliation2019}. Moreover, it should be specified that the time series features are exclusively employed in the clustering phase and not in the computation of base forecasts (as seen in machine learning models), or in the reconciliation process itself.}

\medskip
\noindent \textbf{Response:}  %{\color{red} utilize time series error and features to cluster time series in the context of forecast reconciliation.} \\
{Thank you for pointing this out. Following your suggestion, we have revised the sentence to make it clear that the in-sample forecast error and time series features are exclusively employed in the clustering phase. We have also acknowledged that these have been used by others in the computation of base forecasts and in the reconciliation process.}\\

\textbf{Comment 6:} \textit{Page 9, fig 1. I noticed that the graph in the right panel is very similar to the canonical structure of an aggregated curve presented in Fig 2 on page 583 of \cite{ghelasiHierarchicalForecastingAggregated2024}. I would recommend that the authors elaborate on this similarity.}

\medskip

\noindent \textbf{Response:} {Thank you for your comment. 
While the right panel in Figure 1 of our paper does resemble an aggregate curve from \cite{ghelasiHierarchicalForecastingAggregated2024}, this is only one example of what a structure found using hierarchical clustering could look like. In general, hierarchical clustering may yield structures that bear no resemblance to the aggregate curves of  \cite{ghelasiHierarchicalForecastingAggregated2024}. For example,  a binary tree structure. Therefore, we choose to omit the discussion of this reference to avoid confusion. Instead, we have changed the examples shown in Figure 1 in the revised manuscript.} \\

\textbf{Comment 7:} \textit{Section 3.1. There are some aspects related to the two datasets that should be further clarified:}
\begin{enumerate}
    \item \textit{Firstly, as for the ``tourism'' dataset, the authors refer to a total of 555 time series. However, six Australian zones are each formed by a single region (see Table 4 in \citealp{girolimettoCrosstemporalProbabilisticForecast2023a}), resulting in an unbalanced hierarchy of 525 unique nodes.}

    \noindent \textbf{Response:} {Thank you for pointing this out. There are indeed 525 unique nodes and we have revised the data description to reflect this. }
    \item \textit{Secondly, negative forecasts may be obtained in both datasets, but negative values are not interpretable in these settings. The authors should clarify how they handle negative forecasts in their analysis and whether they employ any of the solutions proposed by \cite{wickramasuriya2020optimal} and \cite{di2023spatio}.}

    \noindent \textbf{Response:} 
    {We appreciate this comment and acknowledge the importance of handling negative forecasts in practice. Our study did not enforce non-negative forecasts for two reasons. First, the proportion of negative forecasts is minimal in our applications. Only 0.25\% of forecasts in the tourism dataset are negative across all evaluation windows. The corresponding proportion in the mortality dataset is only 0.2\%. Second, introducing non-negativity constraints would significantly increase the computational cost of our experiments. Given these considerations, we did not incorporate methods for handling negative forecasts in our analysis. We now briefly discuss these reasons in the revised version of the manuscript. Finally, the framework proposed in our paper could be applied using any reconciliation approach, including those that guarantee non-negative forecasts. We now also make note of this point in the revised manuscript. }
\end{enumerate}

\medskip
\textbf{Comment 8:} \textit{Page 12 rows 17--25. I would suggest to be more precise in the notation of the accuracy index such that $RMSSE_{j,i}$ and $\check{y}_{t,j,h}$ where $j$ is the method used, $i$ is the series and $h$ the forecast horizons.}

\medskip

\noindent \textbf{Response:} {Thanks for the suggestion. We have revised the definition of RMSSE as follows.}

\textit{We define RMSSE of the $h$-step-ahead forecasts, produced using the $j$-th method and conditioning on $T$ observations, of the $i$-th time series as
\[
RMSSE_{j, i} = \sqrt{\frac{\frac{1}{h}\displaystyle\sum_{t=T+1}^{T+h}(y_{t, i}-\breve y_{t, j, i})^2}{\frac{1}{T-12}\displaystyle\sum_{t=13}^T (y_{t, i} - y_{t-12, i})^2}},
\]
where $\breve y_{t,j,i}$ be forecast of the $i$-th time series, generated by the $j$-th method, at time $t$.}\\

\textbf{Comment 9:} \textit{Section 3.2. I would suggest to adjust the evaluation of the forecast accuracy. The authors are limiting themselves to evaluating accuracy indices for only the series presented across all hierarchies (page 12 rows 39--40 ). However, a forecaster might also be interested in the natural middle levels (e.g., regions,
purpose of travels, . . . ) in order to support operational decision. Obviously, in the case of hierarchies formed by clusters, these intermediate levels do not have a straightforward operational interpretation, but the intermediate levels in the case of the natural hierarchy do. Additionally, the claims ``...top and bottom level series, both of which are guaranteed to be present in all hierarchies.'' (page 12 rows 38--39 ) should be clarified since any middle levels series can be obtain using a bottom-up strategy. Therefore, I suggest that the authors calculate the single, not only the total, RMSSE for the top series, the bottom series and the \textbf{natural middle levels series} in Table 3.}

\medskip

\noindent \textbf{Response:} %{\color{red}good idea} 
Thank you for your comment. We have followed your suggestion and computed results for the natural middle-levels across all methods. As you correctly point out, some middle level series will not be included in the base forecasts for clustering-based hierarchies. Therefore we adopt the bottom-up approach as you propose. Please refer to the results in Table \ref{tab:P3_rmsse} below, as a comparison with Table 3 and Table 8 of the revised manuscript. \\

\begin{table}[h!]
    \centering
\caption{\label{tab:P3_rmsse}Performance of all approaches in terms of average RMSSE across all evaluation windows on both datasets. Column-wise minimum values are displayed in bold. ``Middle'' refers to middle-levels defined by the natural hierarchy. }

\begin{tabular}{lcccccc}
\toprule
 Approach & \multicolumn{3}{c}{tourism} & \multicolumn{3}{c}{mortality} \\ 
 \cmidrule(lr){2-4} \cmidrule(lr){5-7}
 & Top & Middle & Bottom & Top & Middle & Bottom \\ \midrule
 Base & \textbf{0.869} & 0.732 & 0.694 & 0.761 & 0.744 & 0.753 \\
Two-level & 0.923 & 0.730 & 0.694 & 0.736 & 0.735 & 0.753 \\
Natural & 0.876 & \textbf{0.717} & 0.691 & 0.738 & 0.732 & 0.750 \\
Grouped & 0.831  & 0.721 & 0.706 & 0.798 & 0.783 & 0.750 \\
TS-EUC-ME & 0.900 & 0.727 & 0.693 & 0.728 & 0.735 & 0.753 \\
ER-EUC-ME & 0.918 & 0.727 & 0.693 & 0.741 & 0.740 & 0.753 \\
TSF-EUC-ME & 0.907 & 0.728 & 0.693 & 0.739 & 0.741 & 0.755 \\
ERF-EUC-ME & 0.909 & 0.729 & 0.694 & 0.733 & 0.738 & 0.753 \\
TS-EUC-HC & 0.874 & 0.719 & 0.692 & 0.740 & 0.730 & 0.754 \\
ER-EUC-HC & 0.890 & 0.719 & 0.691 & 0.746 & 0.732 & 0.751 \\
TSF-EUC-HC & 0.881 & 0.719 & 0.690 & 0.744 & 0.739 & 0.751 \\
TS-DTW-ME & 0.909 & 0.729 & 0.693 & \textbf{0.726} & 0.734 & 0.753 \\
TS-DTW-HC & 0.878 & 0.719 & 0.691 & 0.731 & 0.730 & 0.750 \\
ER-DTW-ME & 0.911 & 0.729 & 0.694 & 0.733 & 0.739 & 0.753 \\
ER-DTW-HC & 0.878 & 0.719 & 0.691 & 0.748 & 0.736 & 0.753 \\ 
Combination & 0.893 & 0.721 & \textbf{0.690} & 0.730 & \textbf{0.724} & \textbf{0.725} \\
\bottomrule\end{tabular}

\end{table}

We note that these additional results for the middle levels do not necessarily provide a ``fair'' comparison, since for clustering-based hierarchies, a bottom-up approach has been adopted.  In the case of tourism data, the natural hierarchy provides the best performance at the middle-level, which is not surprising. Nevertheless, the difference between the performance of the natural hierarchy and several cluster hierarchies is not significant. On the other hand, for mortality data, the combination approach provides the best performance across all methods, for both the middle and the bottom levels. {The MCB test results on middle-level series are shown in Figure \ref{fig:mcb_middle}.} These additional results are consistent with our previous findings and do not contradict our conclusions. For illustrative purposes, we will put these additional results in the supplementary materials and keep the format of Table 3 in the manuscript as it is.\\

\begin{figure}[h!]
    \centering
    %\vspace{-0.1in}
    \includegraphics[width=0.45\textwidth]{../manuscript/figures/tourism/mcb_combination_middle.pdf}
    \includegraphics[width=0.45\textwidth]{../manuscript/figures/mortality/mcb_combination_middle.pdf}
    \caption{\label{fig:mcb_middle}Average ranks and 95\% confidence intervals for all approaches on middle level of tourism dataset (left) and mortality dataset (right) based on MCB test.}
\end{figure}

\medskip
In principle, we could also consider taking the natural hierarchy as a starting point for hierarchy construction.
%We also note that if the natural hierarchy is taken as a starting point, 
However, there is some ambiguity on how to carry out clustering in this case. For example, clustering could be carried out on bottom level series and middle level series together or on each level of the hierarchy separately. We do not further investigate these issues since they lie beyond the scope of the current paper.\\

%{\color{purple} How do we construct middle-level forecasts based on the clustering hierarchies? Bottom ups for simplicity? }\\

\textbf{Comment 10:} \textit{Page 12 rows 58. If a package was used for computing the MCB test, consider citing it as done for the others R packages.}

\medskip

\noindent \textbf{Response:} {We appreciate this comment. In this paper, the \code{tsutils} (\citealp{tsuitls}) package has been used to conduct the MCB test. We have now cited the package and included it in the reference list. } \\

\textbf{Comment 11:} \textit{Page 14 rows 54--58. The authors repeatedly refer to the superior predictive capacity of hierarchies with a greater number of intermediate levels (see also page 15, rows 17--19, Page 18, rows 15--17, and page 24, rows 57--58 and page 25, rows 1 ). However, the hierarchies obtained through clustering share the top and bottom series, thus it might be useful to construct a grouped structure with all the ``cluster-based'' middle levels series. For example, Figure~\ref{fig:comment_fig} represents two hierarchies that share the top and the 5 bottom series.}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/comment_figure.png}
\caption{\label{fig:comment_fig}Two hierarchies that share the bottom level (in red) and the upper level (in white) series.}
\end{figure}
\vspace{-0.5cm}
\textit{We can then express the two summation matrices (see notation on page 6 ) as}
$\boldsymbol{S}_1=\left[\begin{matrix}\boldsymbol{A}\\\boldsymbol{C}_1\\\boldsymbol{I}_m\end{matrix}\right]$ \textit{and} $\boldsymbol{S}_2=\left[\begin{matrix}\boldsymbol{A}\\\boldsymbol{C}_2\\\boldsymbol{I}_m\end{matrix}\right]$ \textit{where} $\boldsymbol{C}_1=\left[\begin{matrix}
    1 & 1 & 0 & 0 & 0 \\
    0 & 0 & 1 & 1 & 1
\end{matrix}\right]$ and $\boldsymbol{C}_1=\left[\begin{matrix}
    1 & 0 & 0 & 1 & 0 \\
    0 & 0 & 1 & 0 & 1
\end{matrix}\right]$,
\textit{and we can write the} \\

\textit{grouped hierarchy as}
%\vspace{-0.2in}
\[
\boldsymbol{S}_g=\left[\begin{matrix}\boldsymbol{A} \\ \boldsymbol{C}_g \\ \boldsymbol{I}_m \end{matrix}\right] \quad\text{with}\quad \boldsymbol{C}_g =\left[\begin{matrix}
    \boldsymbol{C}_1 \\ \boldsymbol{C}_2
\end{matrix}\right] = \left[ \begin{matrix} 1 & 1 & 0 & 0 & 0 \\ 0 & 0 & 1 & 1 & 1 \\ 1 & 0 & 0 & 1 & 0 \\ 0 & 0 & 1 & 0 & 1 \end{matrix}\right].
\]
\textit{Obviously, possible duplicated series should be removed. Those we obtain a grouped hierarchy with number of middle level series $n_g$ such that $\min(n_1,n_2)\leq n_1+n_2$, where $n_1$ and $n_2$ are the number of middle level series for the ``simple'' hierarchies 1 and 2, respectively.}
\medskip

\textit{The only section where the authors consider all levels together is in the combination of reconciled forecasts in Section 6, while it would be interesting to understand if this grouped structure offers any benefit due to the increased number of middle level series.}

\medskip

\noindent \textbf{Response:} 
Thank you for the comment. We agree with the referee that it would be interesting to see if grouped structure can further improve forecast accuracy. We  have included a grouped hierarchy structure in our study, which combines the aggregation constraints of all 12 clustering-based hierarchies. Theses new results are shown in Table 3 of the revised manuscript, and also in Table \ref{tab:P2_rmsse}. We can see that the performance of the grouped hierarchy is much poorer compared to individual clustering hierarchies. We suspect this may be a consequence of having too large a hierarchy, resulting in difficulty in estimating the covariance matrix $\boldsymbol{W}$ used as an input to MinT (\citealp{pritulargaStochasticCoherencyForecast2021}).

% \begin{table}[h!]
%     \centering
% \caption{\label{tab:P3_rmsse}Performance of cluster hierarchies and benchmark hierarchies in terms of average RMSSE across all evaluation windows on both datasets. Column-wise minimum values are displayed in bold.}
% \begin{tabular}{lrr}\toprule
%     Approach & tourism & mortality \\ \midrule
%     Base & 0.6945 & 0.7530 \\ 
%     Two-level & 0.6944 & 0.7528 \\ 
%     Natural & 0.6913 & 0.7501 \\ 
%     \color{purple}Grouped & 0.7068 & 0.8091\\
%     TS-EUC-ME & 0.6939 & 0.7528 \\ 
%     ER-EUC-ME & 0.6938 & 0.7530 \\ 
%     TSF-EUC-ME & 0.6938 & 0.7549 \\ 
%     ERF-EUC-ME & 0.6942 & 0.7532 \\ 
%     TS-EUC-HC & 0.6922 & 0.7540 \\ 
%     ER-EUC-HC & 0.6920 & 0.7507 \\ 
%     \textbf{TSF-EUC-HC} & \textbf{0.6909} & 0.7509 \\ 
%     ERF-EUC-HC & 0.6910 & 0.7501 \\ 
%     TS-DTW-ME & 0.6940 & 0.7528 \\ 
%     \textbf{TS-DTW-HC} & 0.6911 & \textbf{0.7496} \\ 
%     ER-DTW-ME & 0.6942 & 0.7531 \\ 
%     ER-DTW-HC & 0.6912 & 0.7532 \\ \bottomrule
% \end{tabular}

% \end{table}

\begin{table}
    \centering
    \vspace{-0.8in}
\caption{\label{tab:P2_rmsse}Performance of cluster hierarchies and benchmark hierarchies in terms of average RMSSE across all evaluation windows on both datasets. Column-wise minimum values are displayed in bold.}
\begin{tabular}{lrr}\toprule
    Approach & tourism & mortality \\ \midrule
    Base & 0.6945 & 0.7530 \\ 
    Two-level & 0.6944 & 0.7528 \\ 
    Natural & 0.6913 & 0.7501 \\ 
    Grouped & 0.7068 & 0.8091\\
    TS-EUC-ME & 0.6939 & 0.7528 \\ 
    ER-EUC-ME & 0.6938 & 0.7530 \\ 
    TSF-EUC-ME & 0.6938 & 0.7549 \\ 
    ERF-EUC-ME & 0.6942 & 0.7532 \\ 
    TS-EUC-HC & 0.6922 & 0.7540 \\ 
    ER-EUC-HC & 0.6920 & 0.7507 \\ 
    \textbf{TSF-EUC-HC} & \textbf{0.6909} & 0.7509 \\ 
    ERF-EUC-HC & 0.6910 & 0.7501 \\ 
    TS-DTW-ME & 0.6940 & 0.7528 \\ 
    \textbf{TS-DTW-HC} & 0.6911 & \textbf{0.7496} \\ 
    ER-DTW-ME & 0.6942 & 0.7531 \\ 
    ER-DTW-HC & 0.6912 & 0.7532 \\ \bottomrule
\end{tabular}

\end{table}

\textbf{Comment 12:} \textit{Page 15 rows 34--44. The example used to explain the permutation strategy employs a natural hierarchy structure. However, Figure 5 utilizes a graphical structure typical of the cluster presented in Figure 1 on the right. I suggest that the authors consider the structure in Figure 1 on the left, which is more commonly and easily identifiable as a natural hierarchy.}

\medskip

\noindent \textbf{Response:} {Thank you for your advice. Following this comment, we have revised Figure 5 of the manuscript and we are now using the structure in Figure 1 on the left for illustrative purposes. }\\

\textbf{Comment 13:} \textit{Page 15 rows 36--41. The index $l$ is not specified.}

\medskip

\noindent \textbf{Response:} {Thank you for pointing this out. We have now defined index $l$ in the text, which is the total number of hierarchies included in the forecast combination. }

\medskip

\subsection*{Minor comments \& typos}

\begin{table}[ht]
    \centering
    \resizebox{\textwidth}{!}{
    \begin{tabular}{cc|c|l|l}
    \toprule
        \thead{Page} & \thead{Row} & \thead{Errata} &\thead{Corrige} & \thead{Note} \\
        \midrule
        6 & 17--24 & $\boldsymbol{a}_t$ & $a_t$ & Remove the bold for the scalar
values \\ \midrule
7 & 34/40 & raw & original & Coherent notation as proposed in page 3 row 41 \\\midrule
7 & 50 & context time series & context of time series & \\ \midrule
26 & 7 & A review.' & \makecell{A review’, International  \\ Journal  of Forecasting, \\40(2), 430--456.} & \\\bottomrule
    \end{tabular}}
\end{table}

\medskip

\noindent \textbf{Response:} We appreciate these comments and have made corrections accordingly.  
%{\color{red} raw time series and original time series are not the same concept.} 
{Please note that the ``raw'' and ``original'' time series refer to slightly different concepts, to advoid confusion, we have revised relevant sentences on page 7 to clarify our usage of ``raw''. }

\clearpage
\newpage

\section*{Comments from Referee 2}

We appreciate your comments and we are glad that the referee found our paper interesting and well-written. Following the referee's guidance, we have made clarifications on the permutation method, and added further discussions on the performance of the natural hierarchy. Below, we present point-by-point responses to address your comments.

\subsection*{General comments}

%\textit{An excellent, well written, interesting paper.}

\textbf{Comment 1:} \textit{I have one main point to make. I think that you could explain a little more clearly your work in section 4. Perhaps I am being a bit slow, but I really struggled with your description of what is going on when you discuss permuting an existing `natural' hierarchy. Surely you can only do this by disregarding or dropping some or of the `bottom' intermediate levels? Otherwise the hierarchy is fully specified and I cant see how you can randomly allocate bottom level series? If I am correct in this, please try to make this clear. If I am incorrect then perhaps you still need a much better description! I think this is quite unclear, however I can see where you are going in terms of ``grouping'' v ``structure''.... you could just clarify how you get there.}

\medskip

\noindent \textbf{Response:} We appreciate these comments.
We note that the structure of the hierarchy remains unchanged while all bottom level series are retained (they are simply permuted). In practice, \textit{all} middle level time series are dropped. When randomly shuffling the bottom level series, some middle level series of the natural hierarchy could be retained by chance, although this is highly unlikely. We understand where the confusion could arise, therefore we have revise the description of the permuted hierarchy in Section 4. In particular, we now work through the example in Figure 5 in detail, making it clear how the middle level series change as a result of the permutation. \\

%that and we thank you for bringing this to our attention. Add comment in text making it clear that the forecasts of small population states can only borrow strength if they have neighbours.

\textbf{Comment 2:} \textit{In terms of your broad conclusion it is interesting that the natural hierarchy performs more or less as well as the statistically generated ones. Obviously the natural hierarchy contains `prior' information\ldots which your statistical methods ignore. This may be a good reason why the natural hierarchy does well?}

\medskip

\noindent \textbf{Response:} Thank you for your comment. We fully agree with you that the natural hierarchy contains important prior information of the dataset, which may not have been taken into account in the clustering-based hierarchy construction. For example, tourist data from the same state are likely to be affected by common shocks and dynamics. This in turn, can potentially explain the competitive performance of the natural hierarchy compared to the other structures. In the revised manuscript, we have added this discussion in Sections 3.3.

\clearpage
\newpage

\bibliography{references.bib}
\end{document}

### 2024-09-08 Revision1/coverletter.tex

\documentclass[a4paper,12pt]{amsart}
\usepackage{natbib}
\usepackage{graphics, graphicx}
\usepackage{epstopdf}
\usepackage{float}
\usepackage{bm}
\usepackage{amsmath,amsfonts}
\usepackage{geometry}
\usepackage{amsmath,amsfonts,amssymb}
%\usepackage{amsmath,amsfonts,amssymb,stmaryrd,comment,tabularx, caption, rotating}
\usepackage{setspace,a4,times}
%\usepackage{harvard}
\usepackage{graphicx}
\usepackage{url}
\usepackage{morefloats}
\usepackage{float}
\usepackage{subfigure}
 \setlength{\topmargin}{-0.5cm}
% \setlength{\topskip}{1cm}
% \setlength{\headheight}{0cm}
% \setlength{\headsep}{0cm}
 \setlength{\oddsidemargin}{-0.2 cm}
 \setlength{\evensidemargin}{-0.2 cm}
 \setlength{\textwidth}{16cm}
 \setlength{\textheight}{25cm}
  %\setlength{\textheight}{25cm}
%\renewcommand{\baselinestretch}{2.0}
\geometry{top=3cm,bottom=2.5cm, left=3.4cm,right=3.4cm}
\setlength{\parindent}{0pt}
\linespread{1.35}
\newcommand{\bx}{\bm{x}}
\newcommand{\bv}{\bm{v}}
\newcommand{\bg}{\bm{g}}
\newcommand{\bbeta}{\bm{\beta}}
\newcommand{\bz}{\bm{z}}
\usepackage{color}

\doublespacing

\begin{document}

\begin{flushright}
Mr Bohan Zhang\\
Beihang University\\
School of Economics and Management\\%, Department of Economics\\
Xueyuan Road 37, Haidian District \\
Beijing, China\\
5 July 2024
\end{flushright}

%Professor David Blake and Professor Andrew Cairns\\
%Co-Editor\\
%Insurance: Mathematics and Economics\\
\bigskip
RE: ``Constructing hierarchical time series through clustering: Is there an optimal way for forecasting?''   \\

Dear Professor Fotios Petropoulos,\\

Thank you for giving us the opportunity to revise and resubmit this paper. We hope that the incorporation of the suggested changes will now make the revised paper suitable for \textit{International Journal of Forecasting}. We have addressed the comments from the Associate Editor and the two reviewers in separate files.    \\

We greatly appreciate the time and detail provided by you, and we look forward to your response.\\

Yours sincerely,\\
Bohan Zhang

\end{document}

### 2024-09-08 manuscript/figures/pamcluster.tex

@@
     % \node(start)[startstop]{Start};
-    \node(A)[draw, circle, minimum size=0.2cm]{};
-    \node(B)[draw, circle, minimum size=0.2cm, below left=0.9cm of A]{};
+    \node(B1)[draw, circle, minimum size=0.2cm]{};
+    \node(A1)[draw, circle, minimum size=0.2cm, above right=0.3cm and 0.9cm of B1]{};
+    \node(F1)[draw, circle, minimum size=0.2cm, below left=0.4cm and 0.5cm of B1]{};
+    \node(G1)[draw, circle, minimum size=0.2cm, below=0.3cm of B1]{};
+    \node(H1)[draw, circle, minimum size=0.2cm, below right=0.4cm and 0.5cm of B1]{};
 
-    \node(D)[draw, circle, minimum size=0.2cm, below right=0.9cm of A]{};
-    \node(F)[draw, circle, minimum size=0.2cm, below left=0.5cm of B]{};
-    \node(G)[draw, circle, minimum size=0.2cm, below right=0.5cm of B]{};
-    \node(E)[draw, circle, minimum size=0.2cm, below left =0.5cm of D]{};
-    \node(C)[draw, circle, minimum size=0.2cm, below right=0.5cm of D]{};
+    \node(E1)[draw, circle, minimum size=0.2cm, below right=0.3cm and 0.9cm of A1]{};
+    \node(I1)[draw, circle, minimum size=0.2cm, below left=0.4cm and 0.5cm of E1]{};
+    \node(K1)[draw, circle, minimum size=0.2cm, below right=0.4cm and 0.5cm of E1]{};
 
-    \draw (A) -- (B) -- (G);
-    \draw (A) -- (D);
-    \draw (B) -- (F);
-
-    \draw (D) -- (E);
-    \draw (D) -- (C);
+    \draw (A1) -- (B1) -- (F1);
+    \draw (H1) -- (B1) -- (G1);
+    \draw (A1) -- (E1);
+    \draw (K1) -- (E1) -- (I1);
 

### 2024-09-08 submission/submission.tex

--- 2024-09-03 Revision1/R1.tex
@@
 
-% \usepackage{natbib}
 \usepackage{amsfonts,amsmath,bbm,bm,xcolor,booktabs,hyperref,amsthm}
@@
 
-% Define a new counter for your research questions
 \newcounter{researchquestion}
@@
 
-% Define the environment for the research questions
 \newenvironment{researchquestion}{%
@@
 
-  %\title{On the performance of hierarchy construction: impacts of structure and clustering}
 \title{Constructing hierarchical time series through clustering: \\Is there an optimal way for forecasting?}
 
-  % \author[label1]{Bohan Zhang\corref{cor1}}
-  % \address[label1]{School of Economics and Management, Beihang University, Beijing, China}
-  % \ead{zhangbohan@buaa.edu.cn}
-  % \cortext[cor1]{Corresponding author.}
-  % \author[label2]{Anastasios Panagiotelis}
-  % \address[label2]{The University of Sydney Business School, NSW 2006, Australia}
-  % \author[label3]{Han Li}
-  % \address[label3]{Department of Economics, The University of Melbourne, VIC 3010, Australia}
+  \author[label1]{Bohan Zhang\corref{cor1}}
+  \address[label1]{School of Economics and Management, Beihang University, Beijing, China}
+  \ead{zhangbohan@buaa.edu.cn}
+  \cortext[cor1]{Corresponding author.}
+  \author[label2]{Anastasios Panagiotelis}
+  \address[label2]{The University of Sydney Business School, NSW 2006, Australia}
+  \author[label3]{Han Li}
+  \address[label3]{Department of Economics, The University of Melbourne, VIC 3010, Australia}
 
@@
 
-%\clearpage
 \newpage
-% \linenumbers
 
@@
 
-%The primary objective of hierarchical forecasting is to produce coherent forecasts for the series within a given HTS, which we refer to as \textit{original hierarchy}, ensuring that decision-makers at different levels of the hierarchy can analyze and make informed decisions based on aligned expectations for the future.
 A limitation in the overwhelming majority of forecast reconciliation studies is that the structure of the hierarchy is taken as \textit{given}.
@@
 It should be noted that very little attention has been paid to whether middle-level series can be constructed in a way that leads to further improvements in forecast accuracy relative to a given natural hierarchy.
-{\color{purple}To the best of our knowledge, only \cite{yang2017reconciling}, \cite{pangHierarchicalElectricityTime2018}, \cite{liForecastReconciliationApproach2019}, \cite{pangHierarchicalElectricityTime2022}, \cite{cini2023graph}, and \cite{matteraImprovingOutofSampleForecasts2023} have attempted to \textit{construct} middle-level series in a data-driven way which ultimately improved forecast accuracy.
+{To the best of our knowledge, only \cite{yang2017reconciling}, \cite{pangHierarchicalElectricityTime2018}, \cite{liForecastReconciliationApproach2019}, \cite{pangHierarchicalElectricityTime2022}, \cite{cini2023graph}, and \cite{matteraImprovingOutofSampleForecasts2023} have attempted to \textit{construct} middle-level series in a data-driven way which ultimately improved forecast accuracy.
 } However, all of these works use time series clustering to construct hierarchies in a manner that is somewhat ad hoc.
 Our work conducts a more thorough investigation of issues faced when  constructing hierarchical structures in forecast reconciliation.
-In particular, we address the following three research questions:%via time series clustering.
-%We also assess and disentangle the impact of
-
-%This limitation is evident in the absence of any discussion regarding cluster-based approaches in the recent comprehensive review of forecast reconciliation by \cite{AthanasopoulosForecastReconciliationReview2023}.
-However, the following questions arise when pursuing superior forecast performance, motivating the investigation presented in this paper.
+In particular, we address the following three research questions:
 
@@
 If so, is it possible to construct hierarchies in a data-driven way that leads to further improvements in forecast accuracy?
+\end{researchquestion}
 
-%In terms of forecast performance, is the natural hierarchy better than a two-level hierarchy (consisting of only top and bottom time series)? 
-%In terms of forecast performance, does the natural hierarchy outperform a two-level hierarchy of only top and bottom time series?
-\end{researchquestion}
-%\begin{researchquestion}
-%    If the use of middle-level series in the ``natural'' hierarchy can lead to improvement in forecast accuracy, is it possible to construct hierarchies in a data-driven way that leads to further improvements in forecast accuracy?
-%\end{researchquestion}
-
-%Two observations have been consistently demonstrated in empirical studies on forecast reconciliation.
-First, the accuracy of base forecasts, which are influenced by the individual time series characteristics within the hierarchy, critically affects the overall performance of reconciliation.
-For instance, \cite{panagiotelisForecastReconciliationGeometric2021} show that greater performance improvement can be achieved when bias correction for base forecasts is involved.
-%Under the reconciliation framework, improvements in accuracy for some series often come at the expense of others (see \citealp{pritulargaStochasticCoherencyForecast2021}).
 To investigate these questions, we consider two widely used empirical HTS datasets; the first is Australian tourism demand, the second, cause-of-death mortality data.
@@
 Indeed, clustering methods may only work in so far as they generate a larger number of base forecasts.
-{\color{purple}This argument would be consistent with the interpretation of reconciliation as a forecast combination of ``direct'' and ``indirect'' forecasts (\citealp{hollymanUnderstandingForecastReconciliation2021, di2024forecast}), since more middle-level series implies a greater number of indirect forecasts in the combination.} This leads to our second research question:
+{This argument would be consistent with the interpretation of reconciliation as a forecast combination of ``direct'' and ``indirect'' forecasts (\citealp{hollymanUnderstandingForecastReconciliation2021, di2024forecast}), since more middle-level series implies a greater number of indirect forecasts in the combination.} This leads to our second research question:
 
@@
 Our main finding is that hierarchies constructed using clustering methods do not significantly outperform their random ``twins'', leading to the conclusion that the driver of forecast improvement is the enlarged number of series in the hierarchy and/or its structure, rather than similarities between the time series.
-
-%Despite the intuitive appeal of clustering analysis, it is not straightforward to conclude that clustering itself is the primary contributor to the performance improvement illustrated in the literature.
-Except the factor of potentially accurate base forecasts of new series introduced by clustering, another factor  is the ``enriched structure'', meaning that a larger set of series is optimally combined to obtain the reconciled forecasts, leading to reduced model uncertainty and data uncertainty from forecast combination perspective (\citealp{hollymanUnderstandingForecastReconciliation2021}).
-The following question also motivates our research:
-%\begin{researchquestion}
-%Which factor, enriched structure or clustering, is the primary contributor to the performance improvement illustrated in clustering-based reconciliation approaches?
-%\end{researchquestion}
-
-%To address this question, we propose a random hierarchy construction approach.
-By randomly constructing ``twin'' hierarchies with the same tree structure but different permutations of bottom-level series as a contrast to a clustering-based hierarchy, we are able to isolate the influence of clustering algorithms.
-This allows us to inspect the individual contributions of the enriched structure and clustering technique to forecast reconciliation performance.
 
@@
 
-%Section~\ref{sec:related_work} reviews related work in time series clustering, forecast reconciliation and clustering-based forecast reconciliation.
-In Section~\ref{sec:method} we introduce the proposed framework, elaborating on three approaches: cluster hierarchies, random hierarchies and combination hierarchies.
-The simulation study is presented in Section~\ref{sec:simulation}, while Section~\ref{sec:emp} details empirical experiments conducted on the Australian tourism dataset and U.S.
-mortality dataset.
-Finally, Section~\ref{sec:conclusion} concludes this paper with discussions on the findings and outlines future research directions.
-
 \section{Methodology}\label{sec:methodology}
@@
 \subsection{Hierarchical forecasting and reconciliation methods}
-
-%We propose a general hierarchical time series augmentation framework, in which new time series are constructed by aggregating subsets of bottom-level series. 
-%Such subsets can be formed according to  results of time series clustering, attributes of the time series or other expert knowledge.
 
@@
 The series are linked through an $(m+k+1)\times m$ summing matrix
-%$\boldsymbol{S}$, which can be decomposed into an identity matrix $\boldsymbol{I}_m$ and two aggregation matrices $\boldsymbol{A}$ and $\boldsymbol{C}$ consisting of $0$ and $1$, such that, 
 \[
@@
   \end{bmatrix}  \boldsymbol{b}_t = \begin{bmatrix}
-      {\color{purple}a_t} \\ \boldsymbol{c}_t \\\boldsymbol{b}_t
+      {a_t} \\ \boldsymbol{c}_t \\\boldsymbol{b}_t
   \end{bmatrix},
@@
 The top level series aggregates all bottom levels, \textit{i.e.}, $\boldsymbol{A} = \mathbf{1}_{1\times m}$, which is a row of ones.
-
-%where $\boldsymbol{A}$ and  $\boldsymbol{C}$ represent the mappings from bottom-level time series to the given aggregated time series and constructed time series, respectively. 
-%Each row of $\boldsymbol{C}$ corresponds to a subset of bottom-level series. The values $c_i, i=1,\dots,m$, indicate whether the $i$-th bottom-level series belongs to the subset.
-% In the case of a two-level hierarchy, we simply have $\mathbf{A} = \mathbf{1}_{1\times m}$.
-%We consider a two-level given hierarchy throughout this paper, where $\mathbf{A} = \mathbf{1}_{1\times m}$.
-
-%\subsection{Trace minimization forecast reconciliation approach}
-
-%Forecast reconciliation is a statistical technique aimed to improve the overall forecasts accuracy across different series in a hierarchical setting.
-It is a post-forecasting step that ensures the coherence of forecasts for all series in the hierarchy.
-Well-recognized regression types of reconciliation include the Ordinary Least Square (OLS) method proposed by \cite{hyndmanOptimalCombinationForecasts2011}, and the trace minimization (MinT) method proposed by \cite{wickramasuriyaOptimalForecastReconciliation2019}.
-%Forecast reconciliation is a hierarchical forecasting which first generates base forecasts for all time series in the hierarchy, and then reconciles the base forecasts via regression (\citealp{hyndmanOptimalCombinationForecasts2011}) or trace minimization (MinT, \citealp{wickramasuriyaOptimalForecastReconciliation2019}).
-%It is well-known for the ability to produce coherent and more accurate forecasts, which has been exploited in several perspectives, such as forecast combination (\citealp{hollymanUnderstandingForecastReconciliation2021}) or projection (\citealp{panagiotelisForecastReconciliationGeometric2021}).
-%In this subsection, we describe the process of generating coherent forecasts using the MinT approach, which will be employed throughout this paper.
-
-% Consider a given hierarchy with $n$ time series with $m$ of them at the bottom level.
-Let vectors $\boldsymbol{b}_t$, $\boldsymbol{a}_t$, and $\boldsymbol{y}_t$ represent observations  at time $t$ of the bottom level, the aggregated levels (\textit{i.e.}, middle and top levels), and the entire hierarchy, respectively.
-% The vectors are linked through an $n\times m$ summing matrix $\boldsymbol{S}$, which can be decomposed into an identity matrix $\boldsymbol{I}_m$ and a constraint matrix $\boldsymbol{A}$ consisting of $0$ and $1$, such that,
-% \[
-%   \boldsymbol{y}_t = \boldsymbol{S}\boldsymbol{b}_t = \begin{bmatrix}
-%     \boldsymbol{A} \\ \boldsymbol{I}_m 
-%   \end{bmatrix}  \boldsymbol{b}_t = \begin{bmatrix}
-%       \boldsymbol{a}_t \\ \boldsymbol{b}_t
-%   \end{bmatrix},
-% \]
-% where $\boldsymbol{A}$ represents the mapping from bottom-level time series to aggregated-level time series.
-In the case of a two-level hierarchy, we simply have $\mathbf{A} = \mathbf{1}_{1\times m}$.
-
-%To produce $h$-step-ahead forecasts based on $T$ historic observations, we would first produce $h$-step-ahead unreconciled (or ``base'') forecasts $\hat{\boldsymbol{y}}_{T+h}$.
-Note that there are different ways to compute such forecasts.
-In this paper, we adopt the Exponential Smoothing (ETS) method, a well-known univariate forecasting model widely used in both research and practice \citep{ForecastingExponentialSmoothing}.
-%The \code{forecast} (\citealp{forecast}) package in {R} (\citealp{R}) is implemented to produce base forecasts for each time series in the hierarchy.
-%Subsequently, the MinT reconciliation method is applied to produce coherent forecasts:
-%\[
-%    \tilde{\boldsymbol{y}}_{T+h} = \boldsymbol{S}(\boldsymbol{S}'\boldsymbol{W}_h^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}_h^{-1}\hat{\boldsymbol{y}}_{T+h},
-%\]
-%where $\boldsymbol{W}_h$ is the covariance matrix of $h$-step-ahead forecast errors.
-The shrinkage method is employed to obtain the estimator of $\boldsymbol{W}_h$ \citep{wickramasuriyaOptimalForecastReconciliation2019}.
-%is considered throughout this paper.
-%Several estimators of $\boldsymbol{W}_h$ were proposed in \cite{wickramasuriyaOptimalForecastReconciliation2019}.
-%such as the OLS estimator, variance scaling, structural scaling estimator, and shrinkage estimator.
-% due to its ability to account for covariance in forecast errors.
 
@@
 \[
-  \color{purple}  \tilde{\boldsymbol{y}} = \boldsymbol{S}(\boldsymbol{S}'\boldsymbol{W}^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}^{-1}\hat{\boldsymbol{y}},
+    \tilde{\boldsymbol{y}} = \boldsymbol{S}(\boldsymbol{S}'\boldsymbol{W}^{-1}\boldsymbol{S})^{-1}\boldsymbol{S}'\boldsymbol{W}^{-1}\hat{\boldsymbol{y}},
   \vspace{-0.15in}
@@
 where $\tilde{\boldsymbol{y}}$ are the \textit{reconciled} forecasts and $\boldsymbol{W}$ is the covariance matrix of base forecast errors.
-{\color{purple}For reconciliation, we use the MinT method \citep{wickramasuriyaOptimalForecastReconciliation2019} implemented using the \texttt{FoReco} (\citealp{FoReco}) package in R, which involves plugging in a shrinkage estimator for $\boldsymbol{W}$.}Although alternatives were considered, including approaches that assume $\boldsymbol{W}$ is diagonal or an identity matrix \citep{hyndmanOptimalCombinationForecasts2011}, this choice has little impact on our main conclusions.
-{\color{purple}Despite the importance of non-negativity in practical scenarios such as demand forecasting, our study does not enforce non-negative forecasts for two reasons.
+{For reconciliation, we use the MinT method \citep{wickramasuriyaOptimalForecastReconciliation2019} implemented using the \texttt{FoReco} (\citealp{FoReco}) package in R, which involves plugging in a shrinkage estimator for $\boldsymbol{W}$.}Although alternatives were considered, including approaches that assume $\boldsymbol{W}$ is diagonal or an identity matrix \citep{hyndmanOptimalCombinationForecasts2011}, this choice has little impact on our main conclusions.
+{Despite the importance of non-negativity in practical scenarios such as demand forecasting, our study does not enforce non-negative forecasts for two reasons.
 First, the proportion of negative forecasts is minimal in our applications (0.25\% in the tourism dataset and 0.2\% in the mortality dataset).
@@
 
-%\subsection{Grouping-based forecast reconciliation}
-%\subsection{Augmenting hierarchical time series through clustering} 
 \subsection{Time series clustering} 
@@
 
-%\textbf{HOW TO AUGMENT THE HIERARCHY}
-%\subsection{Cluster hierarchy construction approach}
-
-%To the best of our knowledge,
-
-%four studies
-
-{\color{purple}Only a handful of studies have attempted to improve forecast accuracy in a reconciliation setting by constructing middle levels of the hierarchy using time series clustering.
+{Only a handful of studies have attempted to improve forecast accuracy in a reconciliation setting by constructing middle levels of the hierarchy using time series clustering.
 \cite{yang2017reconciling} employ spatial $k$-means clustering methods to assign distributed photovoltaics  to their nearest transmission grid bus locations for reconciliation purposes.} \cite{pangHierarchicalElectricityTime2018} detect consumption patterns of electricity smart meter data based on X-means clustering algorithm, while \cite{pangHierarchicalElectricityTime2022} propose several alternative clustering methods to group similar electricity and solar power time series.
@@
 \cite{matteraImprovingOutofSampleForecasts2023} utilize Partition Around Medoids algorithms to unveil underlying structures in stock price indexes.
-{\color{purple} \cite{cini2023graph} took an end-to-end approach from which clusters can be extracted together with hierarchical forecasts.}
+{ \cite{cini2023graph} took an end-to-end approach from which clusters can be extracted together with hierarchical forecasts.}
 However, these studies are limited in scope as they focus on a small number of  clustering techniques. 
-%\todo{Should we move to intro?}
-%construct hierarchies through clustering algorithms and 
 Inspired by the comprehensive overview of time series clustering by \cite{aghabozorgiTimeseriesClusteringDecade2015a}, we consider various approaches based on three key components, namely \textit{time series representations}, \textit{distance measures}, and \textit{clustering algorithms}.
-%Our framework for creating a clustering approach is as follows: we first choose a time series representation, which can be the raw time series, the in-sample forecast error, features of the time series, or features of the in-sample forecast error.
-We then select a distance measure, either Euclidean distance or dynamic time warping.
-Once the representation and the distance measure are determined, we choose a clustering algorithm, either $k$-medoids or agglomerative hierarchical clustering, to form clusters in the dataset.
-In total, we consider 12 different clustering approaches in our experiments.
-%, and evaluation measures.
-
-% Time series clustering is an essential technique that finds applications across various domains, including finance (\citealp{DIAS2015852}), energy (\citealp{pangHierarchicalElectricityTime2018}), robotics (\citealp{gopalapillaiExperimentationAnalysisTime2014}), and others.
-It is commonly used to identify similar patterns within time series datasets, aiding in applications such as anomaly detection, pattern discovery, and recommendation.
 
@@
 
-The time series representation refers to the object that acts as an input for time series clustering. %that provide diverse perspectives on the same dataset.
-% Considering the impracticality of exploring every conceivable time series representation, we focus on four key ones: raw time series without any transformation (hereafter referred to as ``time series''), in-sample one-step-ahead forecast error, features of time series, and features of in-sample one-step-ahead forecast error.
-{\color{purple} Our first candidate for the representation, due to its simplicity and broad applicability, is the time series itself without any processing or additional features.
+The time series representation refers to the object that acts as an input for time series clustering. 
+{ Our first candidate for the representation, due to its simplicity and broad applicability, is the time series itself without any processing or additional features.
 We refer to this as the raw time series.}
-%However, a crucial element contributing to the success of the MinT method lies in estimating the covariance matrix of base forecast errors based on in-sample one-step-ahead forecast error. 
 We also consider the in-sample one-step-ahead forecast error as a representation of the time series, since a key step in MinT reconciliation is to estimate the $\boldsymbol{W}$ matrix. 
-%to examine how the structure within the error series influences reconciliation performance.
 It is important to note that raw time series and in-sample error representations are standardized to eliminate the impact of scale variations.
-%This is done by normalizing each series by subtracting its mean and then dividing by the standard error.
 
@@
 To address this concern, low dimension summaries of ``features'' can be considered.
-Features have been used in the context {\color{purple} of}
-%Features, widely employed in capturing time series characteristics, play a pivotal role in various time series applications, including 
+Features have been used in the context { of}
 time series clustering by \cite{tianoFeatTSFeaturebasedTime2021}, and for forecasting by \cite{wangUncertaintyEstimationFeaturebased2022} and \cite{ liFeaturebasedIntermittentDemand2023}. 
@@
 After filtering out the features that are constant across all series, we select $56$ features.\footnote{The list and descriptions of features are available in the online GitHub repository.} These time series features are calculated by the \code{tsfeatures} (\citealp{tsfeatures}) package in R.
-%have been applied in several feature-based forecasting studies, \textit{e.g.}, \cite{montero-mansoFFORMAFeaturebasedForecast2020}.
-{\color{purple}To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the clustering-based hierarchy construction process.\footnote{We acknowledge that in-sample forecast error and time series features have been used in the computation of base forecasts or in the reconciliation process \citep[see][]{wickramasuriyaOptimalForecastReconciliation2019}.}}
-%To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation.
-%\sout{These representations allow us to gain insights into the diverse aspects of hierarchical time series data}.
+{To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the clustering-based hierarchy construction process.\footnote{We acknowledge that in-sample forecast error and time series features have been used in the computation of base forecasts or in the reconciliation process \citep[see][]{wickramasuriyaOptimalForecastReconciliation2019}.}}
 
@@
 All clustering algorithms we consider require a distance to be defined between the objects that act as inputs to the algorithm.
-%Distance measures serve as crucial tools for assessing the similarity between two series, which in turn significantly influence the clustering results.
 We consider two widely applied distance measures: Euclidean distance and dynamic time warping (DTW).
 When employing Euclidean distance, dimension reduction is necessary due to the curse of dimensionality.
-%, which acts as the dimension over which Euclidean distance is computed in our applications.
-%Failure to undertake dimension reduction may result in undesirable clustering outcomes due to the curse of dimensionality. 
 To address this, we perform Principal Component Analysis (PCA), extracting the first few principal components that collectively explain at least 80\% of the variance within the representations.
@@
 \paragraph{\textbf{Clustering algorithms}}
-%\sout{Clustering algorithms, such as partitioning, hierarchical, grid-based, and model-based approaches,  identify clusters by optimizing specific objective functions} \citep{aghabozorgiTimeseriesClusteringDecade2015a}.
-%, or applying heuristics.
-%These functions are calculated based on chosen time series representations and distance measures.
 In this paper, we focus on two clustering algorithms, namely $k$-medoids and agglomerative hierarchical clustering.
@@
 {The $k$-medoids algorithm aims to minimize the total distance between all observations within a cluster and their respective cluster median.} This is implemented using the partitioning around medoids (PAM) method (\citealp{PartitioningMedoidsProgram1990}).
-%Unlike $k$-means which employs the mean vector of samples as the cluster center, $k$-medoids selects one observation within each cluster as the center. 
 Following the recommendation of \cite{PartitioningMedoidsProgram1990}, we determine the optimal number of clusters using the average silhouette width (ASW), which is a commonly used index in cluster validation \citep[see \textit{e.g.}, ][]{shutaywi2021silhouette}.
-%ASW assesses the quality of clustering results by measuring the proximity of samples within a cluster compared to neighboring clusters.
-%Given a clustering result, the silhouette width for the $i$th sample is calculated as 
-%\[
-%  SW(i) = \frac{b(i)-a(i)}{\max\{a(i), b(i)\}},  
-%\]
-%where $a(i)$ represents the average distance of the $i$th observation to others in the same cluster, and $b(i)$ is the average distance to observations in the cluster nearest to observation excluding the cluster that observation $i$ is assigned to.
-A higher silhouette width indicates greater proximity to observations within the same cluster than to those in neighboring clusters.
-The ASW is the average of silhouette width across all observation.
-We select the clustering result that maximizes the ASW by iterating over all possible numbers of clusters.
-However, ASW has the limitation of being undefined when there is only one cluster.
-%\textbf{Gap statistics (\citealp{tibshiraniEstimatingNumberClusters2002}) can be used to address this limitation, but it is incompatible with DTW.}
 
@@
     \centering
-  %  \vspace{-0.1in}
-    \includegraphics[width=0.46\textwidth]{../manuscript/figures/pamcluster.pdf}
+    \includegraphics[width=0.46\textwidth]{../figures/Figure1_left.jpg}
     \hspace{1cm}
-    \includegraphics[width=0.46\textwidth]{../manuscript/figures/aggcluster.pdf}
+    \includegraphics[width=0.46\textwidth]{../figures/Figure1_right.jpg}
     \caption{\label{fig:cluster_example}Example clustering results of two clustering algorithms.
@@
 
-{\color{purple}Figure~\ref{fig:cluster_example} illustrates two examples of hierarchies generated by $k$-medoids and agglomerative clustering algorithms, on the left and right panels respectively.
+{Figure~\ref{fig:cluster_example} illustrates two examples of hierarchies generated by $k$-medoids and agglomerative clustering algorithms, on the left and right panels respectively.
 The corresponding two-level hierarchy would have five bottom-level series and one top-level series.
@@
 Note that all methods using DTW, have either the raw time series or forecast errors as representations, since DTW is not compatible with time series features.
-{\color{purple}In addition to these 12 clustering approaches, we also include a grouped hierarchy structure combining all aggregation constraints in matrix $\boldsymbol{S}$, which we refer to as ``grouped''.}
-
-%The four time series representations need to perform dimension reduction when using Euclidean distance. 
-%Combing the four dimension reduced representations with two clustering algorithms results in the first eight clustering approaches. 
-%The first eight approaches require dimension reduction via PCA, while the last four approaches use either the raw time-series or forecast errors, 
-%must take temporal data as an input.
-%the last four approaches 
-%Note that features of raw time series and in-sample forecast error are not temporal data, thus incompatible with DTW.
-Therefore, the last four approaches are derived from combinations of two temporal representations (\textit{i.e.}, raw time series and in-sample error), DTW, and two clustering algorithms.
+{In addition to these 12 clustering approaches, we also include a grouped hierarchy structure combining all aggregation constraints in matrix $\boldsymbol{S}$, which we refer to as ``grouped''.}
 
@@
 Additionally, each regional-level series is divided by four travel purposes.
-Overall, this dataset comprises a total of {\color{purple}$525$} unique time series with $304$ of those at the bottom level.
+Overall, this dataset comprises a total of {$525$} unique time series with $304$ of those at the bottom level.
 In the case of tourism data, the first two or three letters of the series name indicate geographical zones or regions, and the last three denote travel purposes.
@@
 As an example, \textit{Diseases of heart} (ICD code: I00--I09, I11, I13, I20--I51; 113 Cause List: GR113-054) is a middle-level series in the hierarchy, which contains bottom-level series \textit{Hypertensive heart disease} (I11; GR113-056) and \textit{Heart failure} (I50; GR113-067), among other circulatory diseases.
-% To address issues with suppressed data values, we combine causes that contain suppressed values and share a parent cause.
-The death counts for these combined categories are calculated by subtracting the death counts of sibling causes from the death counts of their parent causes.
-This processing results in a refined dataset that includes $120$ time series with $98$ at the bottom level.
-
-%\textbf{italic or double quotation mark} Italic is better I think
 
 The top-level series, one selected middle-level series, and three selected bottom-level series are illustrated in Figures~\ref{fig:tourism} and~\ref{fig:mortality} for the tourism and mortality datasets, respectively.
-%As mentioned before, the death series are coded based on the ICD 113 Cause List. 
 Both figures exhibit more regular and apparent trend and seasonality for series at a higher level of aggregation, while bottom-level series are noisier and prone to outliers. 
@@
 
-%Figures~\ref{fig:tourism} and~\ref{fig:mortality} illustrate the top-level series, one middle-level series, and three selected bottom-level series for the tourism and mortality datasets, respectively.
-%As mentioned before, the death series are coded based on the ICD 113 Cause List. 
-%We can see that the patterns observed at the bottom level can be very different from those at the top and middle levels, for both datasets. 
-%Furthermore, the mortality dataset generally exhibits strong seasonality and trend, whereas the tourism dataset displays greater volatility but less obvious seasonal and trend components.
-
-%Names of mortality series are ICD codes representing causes of deaths. For example, \code{GR113-085} represents deaths because of asthma.
-
 \begin{figure}[h!]
     \centering
-    \includegraphics[width=\textwidth]{../manuscript/figures/tourism.pdf}
-  %  \vspace{-0.35in}
+    \includegraphics[width=\textwidth]{../figures/Figure2.jpg}
     \caption{Visualization of selected time series from the tourism dataset.
@@
 \end{figure}
-
-%In Table~\ref{tab:features}, we summarize three features of the bottom-level series for the two datasets, including the strength of trend defined in \cite{tsfeatures}, the seasonality smoothing  parameter of the Holt-Winters model (\citealp{holtForecastingSeasonalsTrends2004}), and the first order seasonal auto-correlation coefficient.
-%function (ACF),
-%The strength of trend is defined as 
-%\[
-%\text{Strength of trend} = 1-\frac{\text{Var}(e_t)}{\text{Var}(f_t+e_t)},
-%\]
-%where $e_t$ and $f_t$ are residuals component and smoothed trend component obtained by the STL decomposition of the time series (\citealp{tsfeatures}).
-%We can confirm our earlier observations that the mortality dataset has stronger trend and seasonality compared to the tourism dataset in general.
 
@@
 \end{table}
-%of Holt-Winters model
 
@@
     \vspace{0.2in}
-    %\vspace{-0.2in}
-    \includegraphics[width=\textwidth]{../manuscript/figures/mortality.pdf}
-    %\vspace{-0.35in}
+    \includegraphics[width=\textwidth]{../figures/Figure3.jpg}
     \caption{{Visualization of selected time series from the death count dataset.} ``GR113-019'', ``GR113-051'',  ``GR113-063'', and ``GR113-085'' denote ``Malignant neoplasms'', ``Parkinson disease'', ``All other forms of chronic ischemic heart disease'', and ``Asthma'', respectively.}
-   % \vspace{-0.2in}
     \label{fig:mortality}
@@
 
-%We investigate the impact of hierarchical on forecast reconciliation by comparing the forecast accuracy across different hierarchies. 
-%time series clustering techniques in Table \ref{tab:P3_methods}.
-%This comparison incorporates a diverse set of time series representations, distance measures, and clustering algorithms to provide a more thorough understanding of their impact on forecast performance.\\
-%For a fair comparison, only bottom and top level forecasts are included evaluated. 
-%To evaluate the accuracy of reconciled forecasts,  
-%based on a given hierarchical structure, 
 To measure forecast accuracy, we first calculate the Root Mean Squared Scaled Error (RMSSE, \citealp{makridakisM5AccuracyCompetition2022}), for each series.
-{\color{purple}We define RMSSE of the $h$-step-ahead forecasts, produced using the $j$-th method and conditioning on $T$ observations, of the $i$-th time series as
+{We define RMSSE of the $h$-step-ahead forecasts, produced using the $j$-th method and conditioning on $T$ observations, of the $i$-th time series as
 
@@
 
-%To rigorously validate our hypothesis, we utilize the expanding window strategy to evaluate the performance of different approaches.
-For both datasets, starting with the first $96$ observations, we produce $12$-step-ahead forecasts.
-The training window is then increased by one observation and new forecasts are obtained.
-This procedure is repeated until the training window comprises all but the  last $12$ observations.
-Finally, we can obtain $121$ $12$-step-ahead forecasts (January 2006 - January 2016) for the tourism dataset and $145$ $12$-step-head forecasts (January 2007 - January 2019) for the mortality dataset.
-%Then we calculate the RMSSE for each of the expanding windows and take the average.
-%the reconciled forecasts.
-
-%Two approaches are utilized to summarise the overall performance across all evaluation windows.
-The first is to calculate average RMSSE across all evaluation windows.
-The second involves the Multiple Comparison with the Best (MCB) test (\citealp{koningM3CompetitionStatistical2005}), which computes the average ranks of different approaches across all evaluation windows and assess whether they are statistically different.
-
 We utilize the expanding window strategy to evaluate the performance of different approaches with a forecast horizon of 12 months (one year).
@@
 This results in $121$ $12$-step-ahead forecasts (January 2006 - January 2016) for the tourism dataset and $145$ $12$-step-head forecasts (January 2007 - January 2019) for the mortality dataset.
-%Then we calculate RMSSE for each of the reconciled forecasts.
 
@@
 This test is based on the average ranks of different approaches across all evaluation windows and controls for multiple comparisons.
-{\color{purple} We implement the MCB test using the \code{tsutils} (\citealp{tsuitls}) R package}.
-
-% \subsection{Natural hierarchy vs two-level hierarchy}
-% \label{subsec:n_vs_twolevel}
-% In this subsection, we compare the performance of natural hierarchy against the two-level hierarchy to address the first research question.
-We expect that the natural hierarchy would demonstrate superior performance over the two-level hierarchy, as more time series are included in the reconciliation process.
-% \begin{table}[h!]
-%     \centering
-%     \caption{\label{tab:P1} Performance of natural and two-level hierarchies in terms of average RMSSE across all evaluation windows on both datasets.
-Column-wise minimum values are displayed in bold.
-Asterisk (*) indicates significant difference according to MCB test.}
-%     \begin{tabular}{lll}
-%     \toprule
-%         Method & tourism & mortality \\ \midrule
-%         Base & $0.6945$ & $0.7530$ \\
-%         Two-level & $0.6943$ & $0.7528$ \\ 
-%         Natural & $\bold{0.6913}^*$ & $\bold{0.7501}^*$ \\ \bottomrule
-%     \end{tabular}
-
-% \end{table}
-
-% Following the evaluation procedure introduced in Section~\ref{subsec:evaluation}, Table~\ref{tab:P1} compares forecast accuracy of the natural hierarchy, the two-level hierarchy and base forecasts on tourism and mortality datasets.
-Average RMSSE is calculated across all evaluation windows.
-% %in terms of average RMSSE across all evaluation windows. 
-% The asterisk in table indicates significant difference according to MCB test.
-% It is shown that the natural hierarchy significantly outperforms the two-level hierarchy and base forecasts on both datasets.
-It confirms our hypothesis that natural hierarchy improves forecast performance over a two-level hierarchy.
+{ We implement the MCB test using the \code{tsutils} (\citealp{tsuitls}) R package}.
 
@@
 The base forecasts, as well as the reconciled forecasts from the two-level hierarchy (only containing top- and bottom- level time series) and from the natural hierarchy, are included as benchmarks.
-%using the evaluation process described in Section~\ref{subsec:evaluation}.  
 The MCB test results are presented in Figure~\ref{fig:P3_mcb_benchmark}.
@@
     Natural & 0.6913 & 0.7501 \\ 
-    \color{purple}Grouped & 0.7068 & 0.8091\\
+    Grouped & 0.7068 & 0.8091\\
     TS-EUC-ME & 0.6939 & 0.7528 \\ 
@@
 However,  not even the best clustering method is significantly more accurate than the two-level hierarchy based on the MCB test.
-{\color{purple}It should also be noted that the performance of the grouped hierarchy is much poorer compared to individual clustering hierarchies across both datasets.
-We suspect this may be a consequence of having too large a hierarchy, resulting in difficulty in estimating the covariance matrix $\boldsymbol{W}$ used as an input to MinT (\citealp{pritulargaStochasticCoherencyForecast2021}).}%Across both datasets, the methods based on hierarchical clustering tend to outperform those based on $k$-medoids clustering, highlighting the importance of choosing an appropriate clustering technique.
+{It should also be noted that the performance of the grouped hierarchy is much poorer compared to individual clustering hierarchies across both datasets.
+We suspect this may be a consequence of having too large a hierarchy, resulting in difficulty in estimating the covariance matrix $\boldsymbol{W}$ used as an input to MinT (\citealp{pritulargaStochasticCoherencyForecast2021}).}
 
@@
     \vspace{0.1in}
-    \includegraphics[width=0.45\textwidth]{../manuscript/figures/tourism/mcb_benchmarks.pdf}
-    \includegraphics[width=0.45\textwidth]{../manuscript/figures/mortality/mcb_benchmarks.pdf}
-    \caption{\label{fig:P3_mcb_benchmark}Average ranks and 95\% confidence intervals for {\color{purple} thirteen} cluster hierarchies and three benchmarks on tourism dataset (left) and mortality dataset (right) based on the MCB test.}
+    \includegraphics[width=0.45\textwidth]{../figures/Figure4_tourism_mcb_benchmarks.jpg}
+    \includegraphics[width=0.45\textwidth]{../figures/Figure4_mortality_mcb_benchmarks.jpg}
+    \caption{\label{fig:P3_mcb_benchmark}Average ranks and 95\% confidence intervals for { thirteen} cluster hierarchies and three benchmarks on tourism dataset (left) and mortality dataset (right) based on the MCB test.}
 \end{figure}
@@
 This superior performance can be attributed to hierarchical clustering generating a greater number of middle-level time series than $k$-medoids.
-%, significantly enhancing the benefits of enriched structure.
 Table~\ref{tab:P3_number_series} summarizes the average number of middle-level series across all evaluation windows for natural, $k$-medoids, and hierarchical clustering hierarchies.
@@
 Interestingly, the natural hierarchy shows competitive accuracy compared to hierarchical clustering methods on both datasets, despite having fewer middle-level series.
-{\color{purple} The competitiveness of the natural hierarchy may be explained by factors other than similar series being combined together.
+{ The competitiveness of the natural hierarchy may be explained by factors other than similar series being combined together.
 For example, the natural hierarchy encodes prior information about the series, regarding common underlying shocks and dynamics for neighboring regions or similar causes of death.
 These may be more clearly detected and modeled in aggregate series.} However, it should be noted that natural hierarchies may not always exist.
-{\color{purple} For completeness, we further evaluate the forecast accuracy of middle-level time series, defined according to the natural hierarchy.
+{ For completeness, we further evaluate the forecast accuracy of middle-level time series, defined according to the natural hierarchy.
 For clustering-based hierarchies, we use a bottom-up approach.
@@
 On the one hand, it could be argued that by ``grouping'' together series with similar characteristics, certain signals are enhanced, leading to improved forecasting performance.
-%It is possible that by aggregating those series that share similar trends, seasonal patterns, or features, we enhance the signals in the middle-level series and improve their forecastability.
-Consequently, the total and bottom-level series can borrow strength from these middle-level series during the reconciliation process.
-%The second possible explanation assumes that it is the ``structure'' -- number of middle-level series, the depth of the hierarchy, the distribution of group sizes in the middle layer(s), or a combination of all these factors, that lead to the improved forecast accuracy.
-On the other hand, the exact grouping of times series is relatively inconsequential.
 Alternatively, it could be argued that the improved forecasting performance is a by-product of the ``structure'' of the hierarchy, \textit{i.e.} the number of middle-level series, the depth of the hierarchy, the distribution of group sizes in the middle layer(s), or a combination of all these factors.
@@
 \label{subsec:permutation}
-
-%there are more series and more base forecasts to be combined during reconciliation, which leads to reduced uncertainty (\citealp{petropoulosExploringSourcesUncertainty2018a}) and improved reconciled forecasts.
 
@@
 An example is shown in Figure~\ref{fig:aggcluster_random}.
-{\color{purple} In this figure, we begin with the hierarchy on the left hand side and shuffle the leaves (the nodes on the bottom labelled 1--5) to obtain the hierarchy on the right hand side.
+{ In this figure, we begin with the hierarchy on the left hand side and shuffle the leaves (the nodes on the bottom labelled 1--5) to obtain the hierarchy on the right hand side.
 Note that none of the middle levels from the hierarchy on the left are retained.
@@
 
-%To further explore these two concepts, we introduce a method for constructing permutation hierarchies.
-%Given a hierarchy tree, such as the natural hierarchy, the proposed approach constructs new hierarchies by randomly permuting the leaf nodes of the hierarchy.
-Recall that $\boldsymbol{A}$ is a matrix consisting of $0$ and $1$, and represents the mapping from bottom-level time series to aggregated-level time series.
-The idea behind permuting a given hierarchy is to shuffle the columns of matrix $\boldsymbol{A}$ of the original hierarchy.
-This method creates random ``twin'' hierarchies with the same tree structure but different groupings rules.
-%By comparing forecast accuracy across permuted hierarchies, we are able to eliminate the influence of grouping and focus specifically on the structure of the hierarchy. 
-%If the random twin hierarchies significantly outperform the original counterpart, it suggests that structure holds greater importance than grouping, and vice versa.
-
 \begin{figure}[h!]
     \centering
-    \includegraphics[width=0.9\textwidth]{../manuscript/figures/aggcluster_random.pdf}
+    \includegraphics[width=0.9\textwidth]{../figures/aggcluster_random.pdf}
 \caption{\label{fig:aggcluster_random}Examples of a given hierarchy and its ``twin''. }
@@
 
-%Figure~\ref{fig:aggcluster_random} shows an example of permutation hierarchy construction, where the right hand side hierarchy is obtained by shuffling the leaves of left hand side hierarchy.
-The upper part displays the hierarchy trees, and the lower part displays the corresponding summing matrices.
-%is a ``twin'' of the left hierarchy.\\
-%For the corresponding changes in matrix $\boldsymbol{A}$, we have the following results:
-
- %   \[
- %   \begin{bmatrix}
- %   1 & 1 & 1 & 1\\
- %   1 & 1 & 1 & 0 \\
- %   1 & 1 & 0 & 0 \\
- %   & I_4 & & 
- %   \end{bmatrix}
- %   \quad
- %   \rightarrow
- %   \quad
- %   \begin{bmatrix}
- %   1 & 1 & 1 & 1\\
- %   0 & 1 & 1 & 1 \\
- %   0 & 1 & 0 & 1 \\
- %   & I_4 & & 
- %   \end{bmatrix}
- %   \]
-%\vspace{0.01in}
-
 \subsection{Natural hierarchy vs its twins}
@@
 \label{subsec:n_vs_pn}
-
-%This subsection compares the performance of natural hierarchy and its random twins on mortality and tourism datasets.
-%For each dataset, we randomly generate $100$ permutations of the leaf nodes in the natural hierarchy, producing $100$ twin hierarchies.
-Performances of natural hierarchy and its twins are compared using the MCB test described in Section~\ref{subsec:evaluation}.
 
@@
     \centering
-\includegraphics[width=0.47\textwidth]{../manuscript/figures/tourism/natural_vs_pn.pdf}
-    \centering    \includegraphics[width=0.47\textwidth]{../manuscript/figures/mortality/natural_vs_pn.pdf}
+    \includegraphics[width=0.47\textwidth]{../figures/Figure6_tourism_natural_vs_pn.jpg}
+    \centering    \includegraphics[width=0.47\textwidth]{../figures/Figure6_mortality_natural_vs_pn.jpg}
     \caption{\label{fig:P2_tourism}Average ranks and 95\% confidence intervals for natural hierarchy and its $100$ twins, tourism dataset (left) and mortality dataset(right).}
@@
 As shown in right panel of Figure~\ref{fig:P2_tourism}, the performance of the natural hierarchy is statistically indistinguishable from most of its twins and, there are three twin hierarchies significantly better than the natural hierarchy.
-%\textbf{These results suggest that the natural hierarchy of tourism dataset may be ``smarter'' compared to that of mortality dataset.}
 In both datasets, and particularly for the mortality dataset, we conclude that the ``structure'' of the natural hierarchy is the primary contributor to the improvement in forecast accuracy over the two-level hierarchy.
@@
 The result in Section \ref{subsec:n_vs_pn} suggesting that ``structure'' is a more important contributor to ``grouping'' may arise since the grouping for the natural hierarchy is not selected in a data-driven fashion.
-%selected according to characteristics of the data, rather than in a data-driven fashion.}
 To assess whether clustering methods select a better ``grouping'', we compare the best-performing clustering-based hierarchies (TSF-EUC-HC and TS-DTW-HC for tourism and mortality, respectively) with their random twins.
 Recall that Section~\ref{subsec:cluster_vs_benchmarks} demonstrates that the clustering methods can outperform the natural hierarchy and two-level hierarchy.
-%We are also interested in how ``structure'' and ``grouping'' contribute to these improvements.
-Following the comparison in Section~\ref{subsec:n_vs_pn}, we compare the best performing cluster hierarchy with its $100$ random twins.
-%Note that we choose the best performing approach according to average RMSSE shown in Table~\ref{tab:P3_rmsse}.
 
@@
     \centering
-    \includegraphics[width=0.47\textwidth]{../manuscript/figures/tourism/cluster_vs_pc.pdf}
-    \includegraphics[width=0.47\textwidth]{../manuscript/figures/mortality/cluster_vs_pc.pdf}
-    %best performing cluster hierarchy
+    \includegraphics[width=0.47\textwidth]{../figures/Figure7_tourism_cluster_vs_pc.jpg}
+    \includegraphics[width=0.47\textwidth]{../figures/Figure7_mortality_cluster_vs_pc.jpg}
     \caption{\label{fig:P3_tourism_c_vs_pc}Average ranks and 95\% confidence intervals for best performing clustering approach and its $100$ twins, tourism dataset (left) and mortality dataset (right).}
@@
 One can argue that for tourism dataset, a data-driven method for grouping time series plays a more prominent role in forecast improvement.
-%does appear to contribute the .
-%be a major contributor.
 This may be attributed to the noisier nature of bottom level tourism data, suggesting that similar weak signals are strengthened when aggregated.
@@
 
-%Overall, Table~\ref{tab:P3_rmsse} and Figure~\ref{fig:P3_tourism_c_vs_pc} suggest that while it is possible to construct a ``smart'' hierarchical structure that improves forecast reconciliation performance, this possibility highly depends on the dataset characteristic and the time series cluster methods employed, making it a challenging objective to achieve.
-On the other hand, no matter the ``smarter'' hierarchy is construed or not, enriched structure contributes to the performance improvement.
-
-%\section{Investigating driving factors: simulation cases}
 \section{Simulation study}
 \label{sec:simulation}
-%The experiments in Section~\ref{sec:clustering} show the difficulty of constructing a smart hierarchy through clustering. 
 The main conclusion of Section~\ref{sec:permutation} is that hierarchies with more middle-level series improve forecast accuracy due to structure rather than grouping.
@@
 
-%The experiments in Section~\ref{subsec:cluster_vs_benchmarks} and Section~\ref{subsec:P3_c_vs_pc} illustrate the potential of using clustering-based methods to construct hierarchies for further improvement in forecast accuracy.
-
-%However, no evidence was found that clustering-based hierarchies are significantly better than the natural hierarchies.
-To avoid the concern that clusters found in the empirical datasets are spurious, we now consider a simulation study such that the `ground truth clusters' are known.
-%However, it is possible that the clustering approaches we used are unable to detect clusters underlying the dataset. 
-%In this section, we simulate a scenario where ideal clusters can be detected and investigate how the two factors affect performance in this scenario.
-
 \subsection{Simulation design}
-
-%\subsubsection{Time series generation}
 
@@
 Both $\xi_t$ and $\varepsilon_t$ are white noise with the variance of $\xi_t$ set to 0.25 and the variance of $\varepsilon_t$ set to $2.5\times 10^{-5}$ and $4.9\times 10^{-5}$ for increasing trend and decreasing trend, respectively.
-The combination of three different trends with two different patterns of seasonality leads to six clusters as described in Table~\ref{table:simu_params}.% For series with no trend, $L_t$ = 0, and there is no $\varepsilon_t$.
-%\todo{What about no trend?
-For no trend, $L_t$ = 0, there is no $\varepsilon_t$}.
+The combination of three different trends with two different patterns of seasonality leads to six clusters as described in Table~\ref{table:simu_params}.
 
@@
 \centering
-\includegraphics[width=\textwidth]{../manuscript/figures/simu_example.pdf}
+\includegraphics[width=\textwidth]{../figures/Figure10.jpg}
 \caption{\label{fig:simu_emps}Example time series for each cluster in the simulation experiments.}
@@
     \centering
-    \includegraphics[width=0.65\textwidth]{../manuscript/figures/simu_pca.pdf}
+    \includegraphics[width=0.65\textwidth]{../figures/Figure11.jpg}
     \caption{\label{fig:simu_pca}Visualization of the generated time series in the simulation experiments.}
@@
 
-%To simulate an increasing trend, we set the slope $\alpha$ to $0.001$, and for a decreasing trend, we set $\alpha$ to $-0.002$.
-The variances of the associate white noise $\varepsilon_t$ are set to $2.5\times 10^{-5}$ and $4.9\times 10^{-5}$ for increasing trend and decreasing trend, respectively.
-For series without trend (``None''), the trend component $L_t$ is set to zero.
-The terms ``Even'' and ``Odd'' in our setup refer to the positioning of seasonal peak.
-Specifically, ``Even'' seasonality means that peaks occur at even-numbered positions (e.g., $2, 4, \dots$) of seasonal cycle, with the reverse being true for ``Odd'' seasonality.
-The values of these seasonal peaks and troughs are randomly drawn from uniform distributions within the ranges of $[2, 3]$ and $[0,1]$, respectively.
-The variance of $\xi_t$ is set to $0.25$.
-
-%We generate $120$ bottom level series, ensuring that each cluster contains $20$ distinct time series.
-
-%\subsection{Hierarchy construction}
-
-%We consider a two-level hierarchy with a total of $120$ bottom-level series and a single aggregated series.
-In addition, we examine four cluster hierarchies.
-Note that we consider multiple cluster hierarchies in order to reflect the real-world scenario where a variety of clustering techniques may be employed.
-The first cluster hierarchy, ``Cluster-predefined'', forms six middle-level series according to the predefined clusters.
-We then merge clusters with the same trend pattern, resulting in the cluster hierarchy with three clusters, denoted by ``Cluster-trend1''.
-Similarly, we construct cluster hierarchies ``Cluster-trend2'' and ``Cluster-season'' based on the presence of the trend term and seasonal peak positioning, resulting in $2$ and $3$ middle-level series, respectively.
-%Table~\ref{tab:7} summarizes the five approaches.
-
 \begin{table}[h!]
@@
         Approach & Description \\ \midrule
-%        Two-level &  A  two-level hierarchy consisting of only bottom and top levels. \\ 
         Cluster-trend-season & Hierarchy based on trend and seasonal pattern. \\
@@
     \centering
-    \vspace{0.1in}\includegraphics[width=0.7\textwidth]{../manuscript/figures/simulation/P3_mcb.pdf}
+    \vspace{0.1in}\includegraphics[width=0.7\textwidth]{../figures/Figure10.jpg}
    \vspace{-0.1in}
@@
     \centering
-\includegraphics[width=0.8\textwidth]{../manuscript/figures/simulation/P3_c_vs_pc.pdf}
+\includegraphics[width=0.8\textwidth]{../figures/Figure11.jpg}
     \vspace{-0.1in}
     \caption{Average ranks and 95\% confidence intervals for four the ideal hierarchy and its 100 random twins in simulation based on MCB test.}
-%    \vspace{-0.2in}
     \label{fig:simu_P3_c_vs_pc}
@@
 
-  %\vspace{-0.4in}
-
-%\section{Improving performance via forecast combination}
 \section{Forecast combination}
@@
 \] 
-{\color{purple}where $l$ is the number of hierarchies considered in the forecast combination analysis.}
+{where $l$ is the number of hierarchies considered in the forecast combination analysis.}
 We note that this average can only be carried out using series that are common to all hierarchies, in our case, the top and bottom levels.
@@
 \\
-
-%While it is possible to employ more complex methods to determine ``optimal'' weights, we adhere to equally-weighted combination due to its simplicity and well-known efficacy (\citealp{wangForecastCombinations50year2022}).
-
-%Following the evaluation procedure introduced in Section~\ref{subsec:evaluation,
 
@@
     \centering
-    %\vspace{-0.2in}
-    \includegraphics[width=0.45\textwidth]{../manuscript/figures/tourism/mcb_combination.pdf}
-    \includegraphics[width=0.45\textwidth]{../manuscript/figures/mortality/mcb_combination.pdf}
-    \caption{Average ranks and 95\% confidence intervals for all approaches on tourism dataset(left) and mortality dataset(right) based on MCB test.}
-    \label{fig:P4_bench_mcb}
+    \includegraphics[width=0.45\textwidth]{../figures/Figure12_tourism_mcb_combination.jpg}
+    \includegraphics[width=0.45\textwidth]{../figures/Figure12_mortality_mcb_combination.jpg}
+    \caption{\label{fig:P4_bench_mcb}Average ranks and 95\% confidence intervals for all approaches on tourism dataset(left) and mortality dataset(right) based on MCB test.}
 \end{figure}
@@
 This is then repeated 100 times, yielding 100 ``twins'' of the combination forecast.
-%First, we apply the same permutations of bottom-level series used in Section~\ref{subsec:P3_c_vs_pc} to all other cluster hierarchies.
-%Then for each of the $100$ permutations, the twelve reconciled forecasts obtained from corresponding random twins of cluster hierarchies are combined through equally-weighted combination, resulting $100$ random twins of combination hierarchy.
 
@@
 \begin{figure}[h!]
-%\vspace{-0.15in}
     \centering
-    \includegraphics[width=0.6\textwidth]{../manuscript/figures/mortality/comb_vs_pc.pdf}
+    \includegraphics[width=0.6\textwidth]{../figures/Figure13_mortality_comb_vs_pc.jpg}
     \vspace{-0.1in}\caption{\label{fig:P4_a_vs_pa} Average ranks and 95\% confidence intervals for combination of twelve cluster hierarchies and its $100$ random twins on mortality dataset based on MCB test.}
 \end{figure}
-%\clearpage 
-%\newpage
 
@@
 We find similar results from a simulation study where clusters are predefined.
-%, as well as for combinations of hierarchies.
-%This rules out the possibility that our empirical results arise due to spurious clusters or the poor performance of a single clustering method.
 This eliminates the possibility that our empirical results arise due to  spurious clusters or the inadequate performance of a single clustering method.
-%Our empirical and simulation studies provided answers to four important research questions.
-Firstly, we find that the natural hierarchy improves forecast performance compared to both the two-level hierarchy and base forecast.
-%Secondly, cluster hierarchies have the potential to further improve  performance, despite the best-performing approach varying depending on specific datasets.
-%These results align with findings in previous literature on this topic (\citealp{liForecastReconciliationApproach2019, pangHierarchicalElectricityTime2018, pangHierarchicalElectricityTime2022, matteraImprovingOutofSampleForecasts2023}).
-%However, in contrast to the focused scope of previous studies, we involve a broader exploration, including four time series representations, two distance measures, and two clustering algorithms.
 
-%To investigate the driving factors behind performance improvements in natural hierarchy and cluster hierarchies, specifically ``strcuture'' and ``groupings'', we propose an innovative permutation approach that constructs random ``twin'' hierarchies.
-%Comparing natural or cluster hierarchies with their twins allows us to disentangle the impact of ``groupings''.
-The results from two empirical datasets and simulations indicate that while certain cluster hierarchies further improve performance, they do not demonstrate a definitive priority over their twins, particularly in the case of the mortality dataset.
-Therefore, ``structure'', such as number of middle-level time series and depth of the hierarchy, usually has a more substantial influence on forecast performance.
 Our main practical recommendation is to use multiple clustering methods and combine forecasts across these methods using equal weights combination. 
@@
 However, it's worth noting that any averaging approach incurs a computation cost as it requires obtaining base forecasts for additional middle-level series.
-% We also introduce an innovative random hierarchy construction method to investigate what drives the performance enhancements in cluster hierarchies.
-These random hierarchies help isolate the effect of clustering, allowing us to focus on the benefits derived from the structure alone.
-% Furthermore, we propose combination hierarchies to mitigate uncertainties inherent in random hierarchies.
-
-% Our simulation study is constructed around two scenarios, each based on different base forecasting models.
-The first scenario highlights the value of the structure, evident in the high-ranking performance of random combination hierarchies.
-Structure can further improve forecast performance when the base forecasts are of high quality.
-The second scenario demonstrates the efficacy of clustering-based approaches, particularly when the base forecasts at the bottom level are less accurate.
-
-% Empirical studies on two datasets support our simulation findings.
-In the tourism dataset, the inferior base forecasts at the bottom level lead to all cluster hierarchies surpassing the original hierarchy, with four outperforming the combination of random hierarchies, which is used to demonstrate the impact of enriched structure.
-In contrast, the superior performance of two random combination hierarchies in the mortality dataset highlights the effectiveness of enriched structure.
-These results imply that the dominant factor, whether it is the enriched structure or clustering, varies depending on the dataset's characteristics, the base forecasting models, and other variables.
-Overall, our findings suggest that hierarchy construction approaches generally enhance performance, and combining these approaches leads to further improvements.
 
 Future research based on our study could proceed in several promising directions. 
-%Firstly, our experiments were concentrated on total-level and bottom-level series.
-In practical applications, it might be necessary to include specific middle levels or evaluate the entire hierarchy.
-This could lead to the exploration of different hierarchy approaches, such as clustering middle-level series rather than bottom-level ones.
 For example, while we used equally-weighted combinations in this study, there is  potential to apply more sophisticated forecast combination methods to improve performance.
 The extensive literature on forecast combination, including advanced methods for calculating weights, could also be considered (refer to \citealp{wangForecastCombinations50year2022} for an in-depth review).
-% In Section~\ref{sec:combination}, we discuss the implications of combining multiple hierarchical structures on the uncertainty in estimating the covariance matrix of base forecast errors.
-Our conclusion was to opt for forecast combination rather than combining the structures of the hierarchies.
-However, a systematic exploration of these two strategies, combining hierarchical structures and combining forecasts, presents an intriguing area for future research.
-Specifically, addressing the challenge of uncertainty due to high dimensionality in the combination of hierarchical structures is possible.
-In this context, innovative solutions like the regularized forecast reconciliation approach, as proposed by \cite{bentaiebRegularizedRegressionHierarchical2019a}, and alternative estimators of the covariance matrix, such as those suggested by \cite{pritulargaStochasticCoherencyForecast2021} could be highly beneficial.
-% In both our simulation and empirical studies, the combination of random hierarchies displayed competitive results compared to clustering-based methods.
-However, the efficacy of this approach in scenarios with an extremely large number of bottom-level series remains uncertain.
-In such cases, a partially random approach might be more effective.
-For instance, initially generating random hierarchies, identifying those with superior performance, and then constructing partially random hierarchies based on these well-performing structures could be a viable strategy.
-Another intriguing possibility is the integration of both clustering and random approaches.
-Moreover, our study focused specifically on the aggregation of bottom-level series, which may have constrained the potential of middle-level series.
-It's plausible to enhance forecastability at the middle level by creating series through general linear combinations.
-%Finally, our study was centered around point forecast reconciliation and cross-sectional hierarchy.
-However, the field of probabilistic forecast reconciliation has recently gained significant interest, as evidenced by research like \cite{panagiotelisProbabilisticForecastReconciliation2023} and \cite{jeonProbabilisticForecastReconciliation2019}.
-Applying hierarchy construction approaches to probabilistic forecast reconciliation presents a novel and potentially fruitful research avenue.
-This approach could provide deeper insights and more robust forecast reconciliation methods, particularly in scenarios where uncertainty and variability are significant factors.
+
 Also, our results are based on cross-sectional data, this could be extended to explore temporal (\citealp{athanasopoulosForecastingTemporalHierarchies2017}) and cross-temporal hierarchies (\citealp{girolimettoCrosstemporalProbabilisticForecast2023a}).
@@
 
-% \section*{Acknowledgements}
+\section*{Acknowledgements}
 
-% Bohan Zhang is supported by the international joint doctoral education fund of Beihang University.
+Bohan Zhang is supported by the Academic Excellence Foundation of Beihang University for PhD Students and international joint doctoral education fund of Beihang University, China.
+Han Li is supported by the Australian Research Council Discovery Projects funding scheme (DP220100090).
 
-%\clearpage 
-%\newpage
+\section*{Declaration of competing interest}
+
+The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
 

### 2024-09-08 submission/responseletter.tex
fix

--- 2024-09-08 Revision1/responseletter.tex
@@
 \noindent We greatly appreciate the time and effort the Associate Editor and the two referees have dedicated to reviewing our paper.
-The comments received are extremely insightful and have largely benefited the manuscript.
-We have revised the manuscript based on these comments and provided the following point-by-point response to the Associate Editor and two anonymous referees.
-\vspace{-0.4in}
-%\section*{\large Major points}
-%We are glad that you find the topic important and interesting. 
-%\medskip
-%\medskip
-\section*{Comments from the Associate Editor}
-%\vspace{-0.1in}
+We have provided a reproducibility package in \url{https://github.com/AngelPone/project_hierarchy}.
 
-\textit{The two reviewers find the paper well-written and a good fit for IJF - I agree.
-They provide some useful comments that will help the authors improve their manuscript, including the provision of additional consideration in the middle levels of the hierarchy in terms of hierarchy construction but also evaluation and a better description of the permutation algorithm.
-Overall, I think the comments can be fully addressed and I am looking forward to receiving a revised version of the paper.}
-
-\medskip
-\noindent \textbf{Authors' response:}
-We express our gratitude to the Associate Editor for your guidance on the revision of this manuscript.
-In response to the suggestions and comments from the referees, we have conducted major and thorough revisions of the manuscript.
-Please see below a summary of the major changes we have made.
-%\\
-\vspace{-0.03in}
-\begin{itemize}
-    \item We have enhanced the literature review by including more relevant studies in the discussion, thereby emphasizing the contribution of our research. This addresses Referee 1's comments. 
-    \item We have conducted additional analyses on the performance of our methods on the intermediate levels defined by the natural hierarchies, where we used a bottom-up approach for clustering-based hierarchies.
-This addresses Referee 1's comments.
-
-    \item We have included a grouped hierarchy structure, which combines the aggregation constraints of all the clustering-based hierarchies. This addresses Referee 1's comments.
-
-    \item We have added a more detailed description of the permutation method in Section 4 of the manuscript. This addresses Referee 2's comments.
-
-    \item We have included additional discussions in Section 3.3, on the competitive performance of the natural hierarchy in our studies. This addresses Referee 2's comments.
-
-    \item {We have made our code and data available in a public GitHub repository to enable replication of the results presented in the manuscript.
-The repository can be accessed at: \url{https://github.com/Purity3-cyber/constructing_hierarchies}.}
-
-\end{itemize}
-
-In summary, the paper has greatly benefited from the insightful comments received.
-We hope that, the incorporation of these changes will now make the revised version suitable for \textit{International Journal of Forecasting}.
-
-\clearpage 
 \newpage
@@
 
-% We appreciate your comments, and we are pleased that the referee acknowledged the significant challenges addressed in our research.
-Following the referee's guidance, we provide further clarifications and discussions which have made the paper more cohesive.
-We have also conducted additional analysis and comparisons, thereby emphasizing the contributions of the paper.
-Below, we present point-by-point responses to address your comments.
+\textit{I am satisfied with the revisions made by the authors in response to my comments. They have addressed all my suggestions thoroughly and clearly, improving the quality of the manuscript.}
 
-\subsection*{General considerations}
+\textbf{Response:} Thank you for your review and valuable comments.
 
-\textit{The paper presents an interesting analysis on the use of different cluster algorithms to enhance the forecast accuracy for hierarchical time series.
-The manuscript is generally clear and well written.
-My major comments will follow the order in which the topics are treated in the different sections of the manuscript.
-Then, a list of (possible) typos and minor corrections is brought to the authors’ attention.}
-
-\medskip
-\noindent \textbf{Response:} We appreciate the comments, and we are pleased that the referee finds the topic interesting and our paper well-written.
-Following the referee's guidance, we conduct further analyses and discussions which have made the paper more comprehensive.
-Below, we present point-by-point responses to address your comments.
-
-\subsection*{Major Comments}
-\textbf{Comment 1:} \textit{Page 2, rows 54--56.
-I would suggest the authors to include among the following citations to papers that make use of cluster methods to build a hierarchy also \cite{yang2017reconciling}
- and \cite{cini2023graph}.}
-
-%Yang et al. (2017) and Cini et al. (2023).
-
-\medskip
-\noindent \textbf{Response:} {Thank you for this suggestion. In the revised manuscript, we have added the two citations in the relevant paragraph. } \\
-
-\textbf{Comment 2:} \textit{Page 4, row 15. I would suggest adding ``, and \citealp{di2024forecast}''
-immediately after ``\citealp{hollymanUnderstandingForecastReconciliation2021}''}.
-
-\medskip
-\noindent \textbf{Response:} {Thank you for this comment. In the revised manuscript, we have added the suggested citation in the relevant paragraph. } \\
-
-\textbf{Comment 3:} \textit{Page 6, rows 50--57 and page 7, rows 1--6/40.
-The subscript $h$ is used to denote only the $h$-step-ahead covariance matrix $\boldsymbol{W}_h$ and not for the base forecasts $\hat{\boldsymbol{y}}$ or the reconciled forecasts $\tilde{\boldsymbol{y}}$.
-I would recommend keeping a uniform notation and omit the subscript in $\boldsymbol{W}_h$ since it is not the purpose of the authors to evaluate forecasts at different horizons.}
-
-\medskip
-
-\noindent \textbf{Response:} {Thank you for this suggestion. We have now omitted the subscript $h$ in $\boldsymbol{W}_h$.}\\
-
-\textbf{Comment 4:} \textit{Page 7, row 1.
-The authors should use consistent R package citations throughout the paper: the package forecast for obtaining base forecasts was cited on page 6 row 37, the package tsfeatures for extracting features was cited on page 7 row 56, and the package cluster for clustering was cited on page 8 row 28.
-It would be appropriate to cite the package used for reconciliation.}
-
-\medskip
-
-\noindent \textbf{Response:}  {We appreciate this comment.
-In this paper, the \code{FoReco} package (\citealp{FoReco}) has been used for reconciliation.
-We have now cited the package and included it in the reference list.
-} \\
-
-\textbf{Comment 5:} \textit{Page 7, row 58 and page 8 row 1.
-I would suggest that the authors clarify the claim ``To the best of our knowledge, we are the first to utilize in-sample forecast error and time series features as representations in the context of forecast reconciliation''.
-With regard to the in-sample forecast error in the reconciliation context, it is well-known that these are used in many studies to estimate the covariance matrix, as previously discussed (page 7, rows 38--40 ) and in \cite{wickramasuriyaOptimalForecastReconciliation2019}.
-Moreover, it should be specified that the time series features are exclusively employed in the clustering phase and not in the computation of base forecasts (as seen in machine learning models), or in the reconciliation process itself.}
-
-\medskip
-\noindent \textbf{Response:}  %{\color{red} utilize time series error and features to cluster time series in the context of forecast reconciliation.} \\
-{Thank you for pointing this out.
-Following your suggestion, we have revised the sentence to make it clear that the in-sample forecast error and time series features are exclusively employed in the clustering phase.
-We have also acknowledged that these have been used by others in the computation of base forecasts and in the reconciliation process.}\\
-
-\textbf{Comment 6:} \textit{Page 9, fig 1.
-I noticed that the graph in the right panel is very similar to the canonical structure of an aggregated curve presented in Fig 2 on page 583 of \cite{ghelasiHierarchicalForecastingAggregated2024}.
-I would recommend that the authors elaborate on this similarity.}
-
-\medskip
-
-\noindent \textbf{Response:} {Thank you for your comment. 
-While the right panel in Figure 1 of our paper does resemble an aggregate curve from \cite{ghelasiHierarchicalForecastingAggregated2024}, this is only one example of what a structure found using hierarchical clustering could look like.
-In general, hierarchical clustering may yield structures that bear no resemblance to the aggregate curves of  \cite{ghelasiHierarchicalForecastingAggregated2024}.
-For example,  a binary tree structure.
-Therefore, we choose to omit the discussion of this reference to avoid confusion.
-Instead, we have changed the examples shown in Figure 1 in the revised manuscript.} \\
-
-\textbf{Comment 7:} \textit{Section 3.1. There are some aspects related to the two datasets that should be further clarified:}
-\begin{enumerate}
-    \item \textit{Firstly, as for the ``tourism'' dataset, the authors refer to a total of 555 time series.
-However, six Australian zones are each formed by a single region (see Table 4 in \citealp{girolimettoCrosstemporalProbabilisticForecast2023a}), resulting in an unbalanced hierarchy of 525 unique nodes.}
-
-    \noindent \textbf{Response:} {Thank you for pointing this out. There are indeed 525 unique nodes and we have revised the data description to reflect this. }
-    \item \textit{Secondly, negative forecasts may be obtained in both datasets, but negative values are not interpretable in these settings.
-The authors should clarify how they handle negative forecasts in their analysis and whether they employ any of the solutions proposed by \cite{wickramasuriya2020optimal} and \cite{di2023spatio}.}
-
-    \noindent \textbf{Response:} 
-    {We appreciate this comment and acknowledge the importance of handling negative forecasts in practice.
-Our study did not enforce non-negative forecasts for two reasons.
-First, the proportion of negative forecasts is minimal in our applications.
-Only 0.25\% of forecasts in the tourism dataset are negative across all evaluation windows.
-The corresponding proportion in the mortality dataset is only 0.2\%.
-Second, introducing non-negativity constraints would significantly increase the computational cost of our experiments.
-Given these considerations, we did not incorporate methods for handling negative forecasts in our analysis.
-We now briefly discuss these reasons in the revised version of the manuscript.
-Finally, the framework proposed in our paper could be applied using any reconciliation approach, including those that guarantee non-negative forecasts.
-We now also make note of this point in the revised manuscript.
-}
-\end{enumerate}
-
-\medskip
-\textbf{Comment 8:} \textit{Page 12 rows 17--25.
-I would suggest to be more precise in the notation of the accuracy index such that $RMSSE_{j,i}$ and $\check{y}_{t,j,h}$ where $j$ is the method used, $i$ is the series and $h$ the forecast horizons.}
-
-\medskip
-
-\noindent \textbf{Response:} {Thanks for the suggestion. We have revised the definition of RMSSE as follows.}
-
-\textit{We define RMSSE of the $h$-step-ahead forecasts, produced using the $j$-th method and conditioning on $T$ observations, of the $i$-th time series as
-\[
-RMSSE_{j, i} = \sqrt{\frac{\frac{1}{h}\displaystyle\sum_{t=T+1}^{T+h}(y_{t, i}-\breve y_{t, j, i})^2}{\frac{1}{T-12}\displaystyle\sum_{t=13}^T (y_{t, i} - y_{t-12, i})^2}},
-\]
-where $\breve y_{t,j,i}$ be forecast of the $i$-th time series, generated by the $j$-th method, at time $t$.}\\
-
-\textbf{Comment 9:} \textit{Section 3.2.
-I would suggest to adjust the evaluation of the forecast accuracy.
-The authors are limiting themselves to evaluating accuracy indices for only the series presented across all hierarchies (page 12 rows 39--40 ).
-However, a forecaster might also be interested in the natural middle levels (e.g., regions,
-purpose of travels, .
-.
-.
-) in order to support operational decision.
-Obviously, in the case of hierarchies formed by clusters, these intermediate levels do not have a straightforward operational interpretation, but the intermediate levels in the case of the natural hierarchy do.
-Additionally, the claims ``...top and bottom level series, both of which are guaranteed to be present in all hierarchies.'' (page 12 rows 38--39 ) should be clarified since any middle levels series can be obtain using a bottom-up strategy.
-Therefore, I suggest that the authors calculate the single, not only the total, RMSSE for the top series, the bottom series and the \textbf{natural middle levels series} in Table 3.}
-
-\medskip
-
-\noindent \textbf{Response:} %{\color{red}good idea} 
-Thank you for your comment.
-We have followed your suggestion and computed results for the natural middle-levels across all methods.
-As you correctly point out, some middle level series will not be included in the base forecasts for clustering-based hierarchies.
-Therefore we adopt the bottom-up approach as you propose.
-Please refer to the results in Table \ref{tab:P3_rmsse} below, as a comparison with Table 3 and Table 8 of the revised manuscript.
-\\
-
-\begin{table}[h!]
-    \centering
-\caption{\label{tab:P3_rmsse}Performance of all approaches in terms of average RMSSE across all evaluation windows on both datasets.
-Column-wise minimum values are displayed in bold.
-``Middle'' refers to middle-levels defined by the natural hierarchy.
-}
-
-\begin{tabular}{lcccccc}
-\toprule
- Approach & \multicolumn{3}{c}{tourism} & \multicolumn{3}{c}{mortality} \\ 
- \cmidrule(lr){2-4} \cmidrule(lr){5-7}
- & Top & Middle & Bottom & Top & Middle & Bottom \\ \midrule
- Base & \textbf{0.869} & 0.732 & 0.694 & 0.761 & 0.744 & 0.753 \\
-Two-level & 0.923 & 0.730 & 0.694 & 0.736 & 0.735 & 0.753 \\
-Natural & 0.876 & \textbf{0.717} & 0.691 & 0.738 & 0.732 & 0.750 \\
-Grouped & 0.831  & 0.721 & 0.706 & 0.798 & 0.783 & 0.750 \\
-TS-EUC-ME & 0.900 & 0.727 & 0.693 & 0.728 & 0.735 & 0.753 \\
-ER-EUC-ME & 0.918 & 0.727 & 0.693 & 0.741 & 0.740 & 0.753 \\
-TSF-EUC-ME & 0.907 & 0.728 & 0.693 & 0.739 & 0.741 & 0.755 \\
-ERF-EUC-ME & 0.909 & 0.729 & 0.694 & 0.733 & 0.738 & 0.753 \\
-TS-EUC-HC & 0.874 & 0.719 & 0.692 & 0.740 & 0.730 & 0.754 \\
-ER-EUC-HC & 0.890 & 0.719 & 0.691 & 0.746 & 0.732 & 0.751 \\
-TSF-EUC-HC & 0.881 & 0.719 & 0.690 & 0.744 & 0.739 & 0.751 \\
-TS-DTW-ME & 0.909 & 0.729 & 0.693 & \textbf{0.726} & 0.734 & 0.753 \\
-TS-DTW-HC & 0.878 & 0.719 & 0.691 & 0.731 & 0.730 & 0.750 \\
-ER-DTW-ME & 0.911 & 0.729 & 0.694 & 0.733 & 0.739 & 0.753 \\
-ER-DTW-HC & 0.878 & 0.719 & 0.691 & 0.748 & 0.736 & 0.753 \\ 
-Combination & 0.893 & 0.721 & \textbf{0.690} & 0.730 & \textbf{0.724} & \textbf{0.725} \\
-\bottomrule\end{tabular}
-
-\end{table}
-
-We note that these additional results for the middle levels do not necessarily provide a ``fair'' comparison, since for clustering-based hierarchies, a bottom-up approach has been adopted.
-In the case of tourism data, the natural hierarchy provides the best performance at the middle-level, which is not surprising.
-Nevertheless, the difference between the performance of the natural hierarchy and several cluster hierarchies is not significant.
-On the other hand, for mortality data, the combination approach provides the best performance across all methods, for both the middle and the bottom levels.
-{The MCB test results on middle-level series are shown in Figure \ref{fig:mcb_middle}.} These additional results are consistent with our previous findings and do not contradict our conclusions.
-For illustrative purposes, we will put these additional results in the supplementary materials and keep the format of Table 3 in the manuscript as it is.\\
-
-\begin{figure}[h!]
-    \centering
-    %\vspace{-0.1in}
-    \includegraphics[width=0.45\textwidth]{../manuscript/figures/tourism/mcb_combination_middle.pdf}
-    \includegraphics[width=0.45\textwidth]{../manuscript/figures/mortality/mcb_combination_middle.pdf}
-    \caption{\label{fig:mcb_middle}Average ranks and 95\% confidence intervals for all approaches on middle level of tourism dataset (left) and mortality dataset (right) based on MCB test.}
-\end{figure}
-
-\medskip
-In principle, we could also consider taking the natural hierarchy as a starting point for hierarchy construction.
-%We also note that if the natural hierarchy is taken as a starting point, 
-However, there is some ambiguity on how to carry out clustering in this case.
-For example, clustering could be carried out on bottom level series and middle level series together or on each level of the hierarchy separately.
-We do not further investigate these issues since they lie beyond the scope of the current paper.\\
-
-%{\color{purple} How do we construct middle-level forecasts based on the clustering hierarchies? Bottom ups for simplicity? }\\
-
-\textbf{Comment 10:} \textit{Page 12 rows 58. If a package was used for computing the MCB test, consider citing it as done for the others R packages.}
-
-\medskip
-
-\noindent \textbf{Response:} {We appreciate this comment.
-In this paper, the \code{tsutils} (\citealp{tsuitls}) package has been used to conduct the MCB test.
-We have now cited the package and included it in the reference list.
-} \\
-
-\textbf{Comment 11:} \textit{Page 14 rows 54--58.
-The authors repeatedly refer to the superior predictive capacity of hierarchies with a greater number of intermediate levels (see also page 15, rows 17--19, Page 18, rows 15--17, and page 24, rows 57--58 and page 25, rows 1 ).
-However, the hierarchies obtained through clustering share the top and bottom series, thus it might be useful to construct a grouped structure with all the ``cluster-based'' middle levels series.
-For example, Figure~\ref{fig:comment_fig} represents two hierarchies that share the top and the 5 bottom series.}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=\textwidth]{figures/comment_figure.png}
-\caption{\label{fig:comment_fig}Two hierarchies that share the bottom level (in red) and the upper level (in white) series.}
-\end{figure}
-\vspace{-0.5cm}
-\textit{We can then express the two summation matrices (see notation on page 6 ) as}
-$\boldsymbol{S}_1=\left[\begin{matrix}\boldsymbol{A}\\\boldsymbol{C}_1\\\boldsymbol{I}_m\end{matrix}\right]$ \textit{and} $\boldsymbol{S}_2=\left[\begin{matrix}\boldsymbol{A}\\\boldsymbol{C}_2\\\boldsymbol{I}_m\end{matrix}\right]$ \textit{where} $\boldsymbol{C}_1=\left[\begin{matrix}
-    1 & 1 & 0 & 0 & 0 \\
-    0 & 0 & 1 & 1 & 1
-\end{matrix}\right]$ and $\boldsymbol{C}_1=\left[\begin{matrix}
-    1 & 0 & 0 & 1 & 0 \\
-    0 & 0 & 1 & 0 & 1
-\end{matrix}\right]$,
-\textit{and we can write the} \\
-
-\textit{grouped hierarchy as}
-%\vspace{-0.2in}
-\[
-\boldsymbol{S}_g=\left[\begin{matrix}\boldsymbol{A} \\ \boldsymbol{C}_g \\ \boldsymbol{I}_m \end{matrix}\right] \quad\text{with}\quad \boldsymbol{C}_g =\left[\begin{matrix}
-    \boldsymbol{C}_1 \\ \boldsymbol{C}_2
-\end{matrix}\right] = \left[ \begin{matrix} 1 & 1 & 0 & 0 & 0 \\ 0 & 0 & 1 & 1 & 1 \\ 1 & 0 & 0 & 1 & 0 \\ 0 & 0 & 1 & 0 & 1 \end{matrix}\right].
-\]
-\textit{Obviously, possible duplicated series should be removed.
-Those we obtain a grouped hierarchy with number of middle level series $n_g$ such that $\min(n_1,n_2)\leq n_1+n_2$, where $n_1$ and $n_2$ are the number of middle level series for the ``simple'' hierarchies 1 and 2, respectively.}
-\medskip
-
-\textit{The only section where the authors consider all levels together is in the combination of reconciled forecasts in Section 6, while it would be interesting to understand if this grouped structure offers any benefit due to the increased number of middle level series.}
-
-\medskip
-
-\noindent \textbf{Response:} 
-Thank you for the comment.
-We agree with the referee that it would be interesting to see if grouped structure can further improve forecast accuracy.
-We  have included a grouped hierarchy structure in our study, which combines the aggregation constraints of all 12 clustering-based hierarchies.
-Theses new results are shown in Table 3 of the revised manuscript, and also in Table \ref{tab:P2_rmsse}.
-We can see that the performance of the grouped hierarchy is much poorer compared to individual clustering hierarchies.
-We suspect this may be a consequence of having too large a hierarchy, resulting in difficulty in estimating the covariance matrix $\boldsymbol{W}$ used as an input to MinT (\citealp{pritulargaStochasticCoherencyForecast2021}).
-
-% \begin{table}[h!]
-%     \centering
-% \caption{\label{tab:P3_rmsse}Performance of cluster hierarchies and benchmark hierarchies in terms of average RMSSE across all evaluation windows on both datasets.
-Column-wise minimum values are displayed in bold.}
-% \begin{tabular}{lrr}\toprule
-%     Approach & tourism & mortality \\ \midrule
-%     Base & 0.6945 & 0.7530 \\ 
-%     Two-level & 0.6944 & 0.7528 \\ 
-%     Natural & 0.6913 & 0.7501 \\ 
-%     \color{purple}Grouped & 0.7068 & 0.8091\\
-%     TS-EUC-ME & 0.6939 & 0.7528 \\ 
-%     ER-EUC-ME & 0.6938 & 0.7530 \\ 
-%     TSF-EUC-ME & 0.6938 & 0.7549 \\ 
-%     ERF-EUC-ME & 0.6942 & 0.7532 \\ 
-%     TS-EUC-HC & 0.6922 & 0.7540 \\ 
-%     ER-EUC-HC & 0.6920 & 0.7507 \\ 
-%     \textbf{TSF-EUC-HC} & \textbf{0.6909} & 0.7509 \\ 
-%     ERF-EUC-HC & 0.6910 & 0.7501 \\ 
-%     TS-DTW-ME & 0.6940 & 0.7528 \\ 
-%     \textbf{TS-DTW-HC} & 0.6911 & \textbf{0.7496} \\ 
-%     ER-DTW-ME & 0.6942 & 0.7531 \\ 
-%     ER-DTW-HC & 0.6912 & 0.7532 \\ \bottomrule
-% \end{tabular}
-
-% \end{table}
-
-\begin{table}
-    \centering
-    \vspace{-0.8in}
-\caption{\label{tab:P2_rmsse}Performance of cluster hierarchies and benchmark hierarchies in terms of average RMSSE across all evaluation windows on both datasets.
-Column-wise minimum values are displayed in bold.}
-\begin{tabular}{lrr}\toprule
-    Approach & tourism & mortality \\ \midrule
-    Base & 0.6945 & 0.7530 \\ 
-    Two-level & 0.6944 & 0.7528 \\ 
-    Natural & 0.6913 & 0.7501 \\ 
-    Grouped & 0.7068 & 0.8091\\
-    TS-EUC-ME & 0.6939 & 0.7528 \\ 
-    ER-EUC-ME & 0.6938 & 0.7530 \\ 
-    TSF-EUC-ME & 0.6938 & 0.7549 \\ 
-    ERF-EUC-ME & 0.6942 & 0.7532 \\ 
-    TS-EUC-HC & 0.6922 & 0.7540 \\ 
-    ER-EUC-HC & 0.6920 & 0.7507 \\ 
-    \textbf{TSF-EUC-HC} & \textbf{0.6909} & 0.7509 \\ 
-    ERF-EUC-HC & 0.6910 & 0.7501 \\ 
-    TS-DTW-ME & 0.6940 & 0.7528 \\ 
-    \textbf{TS-DTW-HC} & 0.6911 & \textbf{0.7496} \\ 
-    ER-DTW-ME & 0.6942 & 0.7531 \\ 
-    ER-DTW-HC & 0.6912 & 0.7532 \\ \bottomrule
-\end{tabular}
-
-\end{table}
-
-\textbf{Comment 12:} \textit{Page 15 rows 34--44.
-The example used to explain the permutation strategy employs a natural hierarchy structure.
-However, Figure 5 utilizes a graphical structure typical of the cluster presented in Figure 1 on the right.
-I suggest that the authors consider the structure in Figure 1 on the left, which is more commonly and easily identifiable as a natural hierarchy.}
-
-\medskip
-
-\noindent \textbf{Response:} {Thank you for your advice.
-Following this comment, we have revised Figure 5 of the manuscript and we are now using the structure in Figure 1 on the left for illustrative purposes.
-}\\
-
-\textbf{Comment 13:} \textit{Page 15 rows 36--41. The index $l$ is not specified.}
-
-\medskip
-
-\noindent \textbf{Response:} {Thank you for pointing this out. We have now defined index $l$ in the text, which is the total number of hierarchies included in the forecast combination. }
-
-\medskip
-
-\subsection*{Minor comments \& typos}
-
-\begin{table}[ht]
-    \centering
-    \resizebox{\textwidth}{!}{
-    \begin{tabular}{cc|c|l|l}
-    \toprule
-        \thead{Page} & \thead{Row} & \thead{Errata} &\thead{Corrige} & \thead{Note} \\
-        \midrule
-        6 & 17--24 & $\boldsymbol{a}_t$ & $a_t$ & Remove the bold for the scalar
-values \\ \midrule
-7 & 34/40 & raw & original & Coherent notation as proposed in page 3 row 41 \\\midrule
-7 & 50 & context time series & context of time series & \\ \midrule
-26 & 7 & A review.' & \makecell{A review’, International  \\ Journal  of Forecasting, \\40(2), 430--456.} & \\\bottomrule
-    \end{tabular}}
-\end{table}
-
-\medskip
-
-\noindent \textbf{Response:} We appreciate these comments and have made corrections accordingly.  
-%{\color{red} raw time series and original time series are not the same concept.} 
-{Please note that the ``raw'' and ``original'' time series refer to slightly different concepts, to advoid confusion, we have revised relevant sentences on page 7 to clarify our usage of ``raw''. }
-
-\clearpage
 \newpage
@@
 
-We appreciate your comments and we are glad that the referee found our paper interesting and well-written.
-Following the referee's guidance, we have made clarifications on the permutation method, and added further discussions on the performance of the natural hierarchy.
-Below, we present point-by-point responses to address your comments.
+\textit{Thank you for the clarifications you have provided, I think they are very helpful. The paper is useful and insightful, well done!}
 
-\subsection*{General comments}
+\textbf{Response:} Thank you for your review and valuable comments.
 
-%\textit{An excellent, well written, interesting paper.}
-
-\textbf{Comment 1:} \textit{I have one main point to make.
-I think that you could explain a little more clearly your work in section 4.
-Perhaps I am being a bit slow, but I really struggled with your description of what is going on when you discuss permuting an existing `natural' hierarchy.
-Surely you can only do this by disregarding or dropping some or of the `bottom' intermediate levels?
-Otherwise the hierarchy is fully specified and I cant see how you can randomly allocate bottom level series?
-If I am correct in this, please try to make this clear.
-If I am incorrect then perhaps you still need a much better description!
-I think this is quite unclear, however I can see where you are going in terms of ``grouping'' v ``structure''....
-you could just clarify how you get there.}
-
-\medskip
-
-\noindent \textbf{Response:} We appreciate these comments.
-We note that the structure of the hierarchy remains unchanged while all bottom level series are retained (they are simply permuted).
-In practice, \textit{all} middle level time series are dropped.
-When randomly shuffling the bottom level series, some middle level series of the natural hierarchy could be retained by chance, although this is highly unlikely.
-We understand where the confusion could arise, therefore we have revise the description of the permuted hierarchy in Section 4.
-In particular, we now work through the example in Figure 5 in detail, making it clear how the middle level series change as a result of the permutation.
-\\
-
-%that and we thank you for bringing this to our attention. Add comment in text making it clear that the forecasts of small population states can only borrow strength if they have neighbours.
-
-\textbf{Comment 2:} \textit{In terms of your broad conclusion it is interesting that the natural hierarchy performs more or less as well as the statistically generated ones.
-Obviously the natural hierarchy contains `prior' information\ldots which your statistical methods ignore.
-This may be a good reason why the natural hierarchy does well?}
-
-\medskip
-
-\noindent \textbf{Response:} Thank you for your comment.
-We fully agree with you that the natural hierarchy contains important prior information of the dataset, which may not have been taken into account in the clustering-based hierarchy construction.
-For example, tourist data from the same state are likely to be affected by common shocks and dynamics.
-This in turn, can potentially explain the competitive performance of the natural hierarchy compared to the other structures.
-In the revised manuscript, we have added this discussion in Sections 3.3.
-
-\clearpage
-\newpage
-
-\bibliography{references.bib}
 \end{document}

### 2024-09-08 submission/coverletter.tex
fix

--- 2024-09-08 Revision1/coverletter.tex
@@
 
-Thank you for giving us the opportunity to revise and resubmit this paper.
-We hope that the incorporation of the suggested changes will now make the revised paper suitable for \textit{International Journal of Forecasting}.
-We have addressed the comments from the Associate Editor and the two reviewers in separate files.
+Thank you for conditionally accepting our paper for publication in \textit{International Journal of Forecasting}.
+We have made a reproducibility package available in an online GitHub repository, which can be accessed at \url{https://github.com/AngelPone/project_hierarchy}.
 \\

### 2024-09-08 slides/slides.tex
update slides

@@
 }
-	\date{30 June - 3 July, 2024} % Date, can be changed to a custom date
+	\date{3 July, 2024} % Date, can be changed to a custom date
 
@@
 	\begin{itemize}
-		\item Forecast reconciliation can be interpreted from the forecast combination perspective (\citealp{hollymanUnderstandingForecastReconciliation2021,difonzoForecastCombinationbasedForecast2024}).
+		\item Forecast reconciliation can be interpreted from the forecast combination perspective (\citealp{hollymanUnderstandingForecastReconciliation2021,di2024forecast}).
 		\item Reconciled forecasts are weighted combination of ``direct'' and ``indirect'' base forecasts. 
@@
 	\begin{researchquestion}
-		In terms of forecast performance, can {\color{red} the use of middle level series lead to improvement} compared to a two-level hierarchy (consisting of only top and bottom time series)?
+		In terms of forecast performance, can {\color{red} augmenting middle level series lead to improvement}?
 If so, is it possible to {\color{red} construct hierarchies in a data-driven way} that leads to further improvements in forecast accuracy?
@@
 \begin{frame}{Time series clustering-based forecast reconciliation}
-	To the best of our knowledge, four studies have attempted to improve forecast accuracy in a reconciliation setting by constructing middle levels of the hierarchy using time series clustering.
+	Some previous studies have attempted to improve forecast accuracy in a reconciliation setting by constructing middle levels of the hierarchy using time series clustering.
 
@@
 	\begin{itemize}
-		\item {\color{red} Raw time series}.
-		\item {\color{red} In-sample one-step-ahead forecast error}. A key step in MinT reconciliation is to estimate $\boldsymbol{W}_h$ based on in-sample forecast error.
-		\item {\color{red} Time series features of raw time series}.
-		\item {\color{red} Time series features of in-sample one-step-ahead forecast error}. 
-		\begin{itemize}
-			\item Features are low dimensional representation of time series, and have been used in various tasks such as clustering and forecasting.
-			\item $56$ features calculated by the \texttt{tsfeatures} package in R are included.
-		\end{itemize}
+		\item {Raw time series}.
+		\item {In-sample one-step-ahead forecast error}. 
+		\item {Time series features of raw time series}.
+		\item {Time series features of in-sample one-step-ahead forecast error}.
 	\end{itemize}
@@
 	\begin{figure}
-		\includegraphics[width=0.8\textwidth]{../manuscript/figures/tourism.pdf}
+		\includegraphics[width=0.8\textwidth]{tourism.pdf}
 	\end{figure}
@@
 		\item Monthly Australian domestic tourism dataset, covering the period from January 1998 to December 2016 (\citealp{wickramasuriyaOptimalForecastReconciliation2019}).
-		\item Consists of $555$ time series with $304$ of those at the bottom level. The middle-level series are constructed based on state, region, city and travel purpose.
+		\item Consists of $525$ unique time series with $304$ of those at the bottom level. The middle-level series are constructed based on state, region, city and travel purpose.
 	\end{itemize}
@@
 	\begin{figure}
-		\includegraphics[width=0.8\textwidth]{../manuscript/figures/mortality.pdf}
+		\includegraphics[width=0.8\textwidth]{mortality.pdf}
 	\end{figure}
@@
 		\centering
-		\includegraphics[width=0.4\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P3_mcb_benchmarks_h12.pdf}
-		\includegraphics[width=0.4\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P3_mcb_benchmarks_h12.pdf}
+		\includegraphics[width=0.4\textwidth]{hierarchy_rmsse/tourism/P3_mcb_benchmarks_h12.pdf}
+		\includegraphics[width=0.4\textwidth]{hierarchy_rmsse/mortality/P3_mcb_benchmarks_h12.pdf}
 		\caption{Average ranks and 95\% confidence intervals for twelve cluster hierarchies and three benchmarks on tourism dataset (left) and mortality dataset (right) based on MCB test.}
@@
 		\centering
-		\includegraphics[width=0.8\textwidth]{../manuscript/figures/aggcluster_random.pdf}
+		\includegraphics[width=0.8\textwidth]{aggcluster_random.pdf}
 		\caption{Examples of a given hierarchy and its “twin”.}
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P2_natural_vs_pn_h12.pdf}
-	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P2_natural_vs_pn_h12.pdf}
+	\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/tourism/P2_natural_vs_pn_h12.pdf}
+	\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/mortality/P2_natural_vs_pn_h12.pdf}
 	\caption{Average ranks and 95\% confidence intervals for natural hierarchy and its 100 twins, tourism dataset (left) and mortality dataset(right).}
@@
 		\centering
-		\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P3_cluster_vs_pc_h12.pdf}
-		\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P3_cluster_vs_pc_h12.pdf}
+		\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/tourism/P3_cluster_vs_pc_h12.pdf}
+		\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/mortality/P3_cluster_vs_pc_h12.pdf}
 		\caption{Average ranks and 95\% confidence intervals for the best cluster hierarchy and its 100 twins, tourism dataset (left) and mortality dataset(right).}
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/tourism/P4_benchmarks_h12.pdf}
-	\includegraphics[width=0.45\textwidth]{../manuscript/figures/hierarchy_rmsse/mortality/P4_benchmarks_h12.pdf}
+	\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/tourism/P4_benchmarks_h12.pdf}
+	\includegraphics[width=0.45\textwidth]{hierarchy_rmsse/mortality/P4_benchmarks_h12.pdf}
 	\caption{Average ranks and 95\% confidence intervals for all approaches on tourism dataset(left) and mortality dataset(right) based on MCB test}
@@
 
-		\item[] \small\color{purple}Contact email: {\color{blue}   zhangbohan@buaa.edu.cn}
+		\item[] \small\color{purple}Homepage: {\color{blue}   \url{https://bohan-zhang.com}}
+            \item[] \small\color{purple}Paper on arXiv: {\color{blue} \url{https://arxiv.org/abs/2404.06064}}
+
+    \vspace{0.1cm}
+  {\large\color{black} Vote for me on Whova, thanks!}
 
@@
 \begin{frame}[noframenumbering]{References}
+\footnotesize
+\vspace{-0.02in}
 	\bibliographystyle{agsm}
-	\bibliography{../manuscript/references.bib}		
+	\bibliography{R1/references.bib}		
 \end{frame}
